### 2023-01-24 document_phases/content/02_model.tex
tex

\chapter{Model}
\label{chap:model}

This work focuses on the extended Hubbard model on a 2D square lattice with periodic boundary conditions.
Its general Hamiltonian in position space is given by

\begin{equation}
    \begin{aligned}
        H_\text{H} =&-t \sum_{\langle r,s \rangle,\sigma} \left( c_{r\sigma}^\dagger c_{s\sigma} + \text{h.c.} \right) 
                        + U \sum_r n_{r\uparrow} n_{r\downarrow} \\
                    &+ \frac{V}{2} \sum_{\langle r,s \rangle} \left( n_{r\uparrow} + n_{r\downarrow} \right) 
                        \left( n_{s\uparrow} + n_{s\downarrow} \right)\,,
    \end{aligned}  
\end{equation}

where $c_{r\sigma}^{(\dagger)}$ represents the standard fermionic annihilation (creation) operator 
and $n_{r\sigma}$ the number operator with spin $\sigma$ on the lattice site $r$.
The constants $t$, $U$, and $V$ govern the strength of the nearest neighbour hopping, 
the onsite interaction, and the nearest neighbour interaction, respectively.
Applying a Fourier transform yields the new momentum space Hamiltonian

\begin{equation}
    \begin{aligned}
        H_k =& \sum_{k \sigma} \epsilon_0 (k) n_{k\sigma} 
                + \frac{U}{N} \sum_{k,p,q} c_{k\uparrow}^\dagger c_{k+q\uparrow} c_{p\downarrow}^\dagger c_{p-q\downarrow} \\
            &+ \frac{V}{2N} \sum_{k,p,q} \sum_{\sigma, \sigma'} \sum_{\delta} \cos(q\delta) 
                    c_{k\sigma}^\dagger c_{k+q\sigma} c_{p\sigma'}^\dagger c_{p-q\sigma'}\,.
    \end{aligned} 
\end{equation}

Here, $k$, $p$, and $q$ are momenta, $\delta$ references the vectors connecting nearest neighbours within the lattice,
and $N$ is the total number of lattice sites.
The diagonal part is given by

\begin{equation}
    \epsilon_0 (k) := -2t \sum_\delta \cos(\delta k)\,.
\end{equation}

### 2023-10-03 RISE_Projektbeschreibung/RISE_Projektbeschreibung.tex
RISE

\documentclass[20pt]{article}

% set margins and ignore intends
\usepackage[margin=0.9in]{geometry}
\setlength{\parindent}{0pt}

% include graphics
\usepackage{graphicx}

% math stuff
\usepackage{amsmath}
\usepackage{physics}
\usepackage{bbm}

% colors and refs
\usepackage{color}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{url}

% definitions and commands
\xdefinecolor{tugreen}{RGB}{132, 184, 24} % define tu green
\def\blue#1{{\color{blue}{#1}}}
\newcommand{\mchapter}[1]{ \begin{center} \color{tugreen!95!black} \LARGE \bf \textbf{#1} \end{center}} % self-made chapters
\newcommand{\msection}[1]{ { \vspace{5mm} \hspace{-6mm} \large \textbf{#1}} \vspace{2mm} } % self-made sections
\newcommand{\mb}{\mathbf} % bold math symbols
\newcommand{\mcaption}[2]{ \\ Figure {#1}: {#2} } % self-made figure captions

% head
\input{head.tex}

\begin{document}

% Wer eine Schrift mit Serifen verwendet, kriegt vom Designer
% persönlich auf die Rübe. Darum \sf. 
\sf

% head:
\myhead

% title:
\vspace{2mm}
\mchapter{Collective excitations in correlated quantum materials}
\vspace{-3mm}

% text:
\msection{Scientific context}

Correlated quantum materials have been an everpresent subject of scientific research since the discovery of quantum mechanics.
The BCS-theory of superconductivity from 1957 was the first of its kind to be able to describe the phenomenon, discovered in 1911 by Onnes.
It explains that two electrons form so-called Cooper pairs, which - in contrary to the composing electrons - are bosonic quasiparticles.
If the temperature is below some critical temperature $T_c$ they can condese into a macroscopic occupation of the groundstate.
This mechanism essentially allows for the well-known perfect conductivity.

\msection{Dynamic mean-field theory for spins and applications}

\begin{minipage}{0.44\textwidth}
    The general idea of a mean-field approach is simple. We consider, e.g., a spin lattice consisting of a large number of interacting spins which essentially behave
    the same. Now, we focus on one of these spins and substitute its complex quantum environment by an averaged field which is called \emph{mean-field}. 
    This approximation reduces the intractable lattice problem to a single-site problem. Subsequently, the properties of the mean-field can be linked to those of 
    the remaining spin leading to a so-called \emph{self-consistency problem}. Solving this is the key issue of a mean-field approach.
\end{minipage}
\hspace{0.01\textwidth}
\begin{minipage}{0.54\textwidth}
    \begin{center}
        \includegraphics[width=\textwidth]{images/MFT_sketch.pdf}
        \mcaption{1}{Example for a mean-field approach on a spin lattice.}
    \end{center}
\end{minipage}

\begin{minipage}{0.44\textwidth}
    \begin{center}
        \includegraphics[width=0.8\textwidth]{images/Correlation_sketch.pdf}
        \mcaption{2}{Example for a correlation function of a spin-$1/2$. %At time zero the spin is aligned to its initial position yielding an expectation value of $1/4$. 
        As the time increases, the spin loses the memory of its initial orientation.}
    \end{center}
\end{minipage}
\hspace{0.01\textwidth}
\begin{minipage}{0.54\textwidth}
    In case of our dynamic mean-field theory for spins (spinDMFT), the mean-fields are time-dependent \cite{graes21}. It is developed to compute spin correlation functions such as 
    \begin{align*}
        g^{zz}(t,0) &:= \langle \mb{S}^{z}(t) \mb{S}^{z}(0) \rangle
    \end{align*}
    in the limit of large temperatures. These functions tell us, how much the spin at time $t$ is still correlated to its initial alignment. Correspondingly, they capture the 
    decoherence induced by the spins environment.     
\end{minipage}
\vspace{2mm}

\begin{minipage}{0.65\textwidth}
    A promising application of spinDMFT can be found in the context of nitrogen-vacancy (NV) centers in diamond \cite{jelez06}. They are subject of current research due 
    to their stable spin states up to room temperature which is ideal for many applications such as magnetic sensing \cite{sushk14}. Close to the diamond surface, however, 
    the NV-center coherence is strongly weakened because they are disturbed by other spins stemming from surface defects or adatoms. Understanding 
    the dynamics of these other spins requires considering a large spin ensemble which is where spinDMFT can strike. We are currently collaborating with an experimental 
    group from Boston who measures the correlation functions of the surface defect spins. While spinDMFT itself failed 
    to capture their measurements, we recently obtained good agreement with an extended approach called \emph{Cluster-spinDMFT}.
\end{minipage}
\hspace{0.01\textwidth}
\begin{minipage}{0.35\textwidth}
    \begin{center}
        \includegraphics[width=0.8\textwidth]{images/NV_ensemble.png}
        \mcaption{3}{NV-center at a diamond surface with perturbing spins on the surface (black) \cite{rossk14}.}
    \end{center}     
\end{minipage}
\vspace{1.3mm}

It is also possible to extend spinDMFT to external time dependencies. This enables us to introduce pulses to the mean-field simulation and to investigate phenomena such as 
\emph{dynamic decoupling} \cite{uhrig07}. The idea of this is to periodically rotate a considered spin in order to weaken the effects of its environment and, 
hence, to extend its coherence time.

Another potential project is the extension to spatial dependencies. Here, we plan to study how the effects of a pulse propagate through the sample. 
The underlying phenomenon is called spin diffusion \cite{zu21}.

As indicated above, a strong advantage of spinDMFT is its versatility. It can be easily extended to consider complex spin 
configurations, anisotropies, time dependencies and more. Since the theoretical and numerical background has already been established, applying spinDMFT to new 
scenarios becomes more and more important. Here, an internship is a great opportunity.

\msection{Possible tasks during an internship}

Generally, the internship involves mainly \emph{numerical} tasks and \emph{coding}. 
%The work flow for applying the mean-field-approach looks as 
%follows. First, a considered spin model has to be transformed to a mean-field model. Subsequently, the self-consistency conditions derived in the process can be solved with 
%existing code in \textbf{C++}. Sometimes, numerical difficulties arise that demand to change details of the method. In the end, the results can be evaluated to 
%observe exciting new phenomena. 
A specific project could be the investigation of dynamic decoupling in a system comprising a single \emph{spin subject to a Gaussian noise}. Such a project would start
with yourself reading through some literature provided by us so that you understand the fundamental ideas. Subsequently, you would start writing a first simple program in \textbf{C++}, 
that introduces noise, artificial or from a mean-field approach, to a spin. In doing so, you can use existing code fragments from us on some of the required numerical methods. Subsequently, 
you would introduce a pulse sequence such as \emph{UDD} \cite{uhrig07} to the spin in order to enhance its coherence.
One goal of the project could be to find an optimal pulse sequence in dependence of the underlying noise. We emphasize, that this is only \textbf{one} potential project 
and there are many other possibilities. Generally, a little experience 
in \textbf{C++}, \emph{Python} or coding is advantageous. Moreover, knowledge of quantum mechanics is desirable.

\msection{General information}

The chair currently consists of 9 people, that is, 6 PhD students, 1 postdoc as well as Prof. G\"otz S. Uhrig and Prof. Joachim Stolze. The group 
works on a broad range of physical topics such as topological magnonics, non-equilibrium physics, coherence control and more. We have a weekly seminar in which
progress is reported and articles are discussed (Journal Club). Feel free to visit our homepage 
at \url{https://cmt.physik.tu-dortmund.de/uhrig-group/}. 
The methodology and the investigation of collective excitations is the research area of the PhD student Joshua Alth\"user who will also be your supervisor.
You will get your own office space and access to our compute clusters. We do not offer a virtual internship.

% bibliography
\bibliography{lit} 
\bibliographystyle{ieeetr}

\end{document}

### 2023-10-04 RISE_Projektbeschreibung/RISE_Projektbeschreibung.tex
RISE

@@
 
+\newcommand{\expec}[1]{\langle #1 \rangle}
+\newcommand{\timeDeriv}{\frac{\mathrm{d}}{\mathrm{d}t}}
+
 \begin{document}
@@
 
-Correlated quantum materials have been an everpresent subject of scientific research since the discovery of quantum mechanics.
-The BCS-theory of superconductivity from 1957 was the first of its kind to be able to describe the phenomenon, discovered in 1911 by Onnes.
+Correlated quantum materials have been an ever-present subject of scientific research since the discovery of quantum mechanics.
+The BCS-theory of superconductivity\cite{theory_of_sc} from 1957 was the first of its kind to be able to describe the phenomenon.
 It explains that two electrons form so-called Cooper pairs, which - in contrary to the composing electrons - are bosonic quasiparticles.
-If the temperature is below some critical temperature $T_c$ they can condese into a macroscopic occupation of the groundstate.
-This mechanism essentially allows for the well-known perfect conductivity.
+This pair formation is driven by electron-phonon interactions, that yield an effective attractive electron-electron interaction.
 
-\msection{Dynamic mean-field theory for spins and applications}
+If the temperature is below some critical temperature $T_c$ they can condense into a macroscopic occupation of the ground state and allow for the famous perfect conductivity.
+The two prominent collective excitations in a superconductor are the so-called Higgs and phase modes \cite{higgs, bo22}.
+The former is energetically located at the band edge and sometimes referred to as the amplitude mode.
+The latter originates in the invariance of the complex phase. 
+Changing the phase does not affect the energy, thus the mode is located at 0.
 
-\begin{minipage}{0.44\textwidth}
-    The general idea of a mean-field approach is simple. We consider, e.g., a spin lattice consisting of a large number of interacting spins which essentially behave
-    the same. Now, we focus on one of these spins and substitute its complex quantum environment by an averaged field which is called \emph{mean-field}. 
-    This approximation reduces the intractable lattice problem to a single-site problem. Subsequently, the properties of the mean-field can be linked to those of 
-    the remaining spin leading to a so-called \emph{self-consistency problem}. Solving this is the key issue of a mean-field approach.
-\end{minipage}
-\hspace{0.01\textwidth}
-\begin{minipage}{0.54\textwidth}
-    \begin{center}
-        \includegraphics[width=\textwidth]{images/MFT_sketch.pdf}
-        \mcaption{1}{Example for a mean-field approach on a spin lattice.}
-    \end{center}
-\end{minipage}
+A well-known and often used model is the so-called Hubbard model. Its Hamiltonian reads
+\begin{equation}
+    \label{eqn:hubbard}
+    H = -t \sum_{\langle i, j \rangle, \sigma} c_{i\sigma}^\dagger c_{j\sigma}  + U \sum_i c_{i\uparrow}^\dagger c_{i\downarrow}^\dagger c_{i\downarrow} c_{i\uparrow}\,,
+\end{equation}
+where the $\langle i, j \rangle$ denotes the summation over next neighbours, $t$ is a hopping strength, 
+$U$ denotes the on-site interaction strength and $c_{i\sigma}^{(\dagger)}$ annihilates (creates) an electron with spin $\sigma$ on lattice site $i$.
+Most commonly, $U$ is positive and represents the repulsive Coulomb interaction of two electrons.
+In this case, the model exhibits antiferromagnetism (AFM).
 
-\begin{minipage}{0.44\textwidth}
-    \begin{center}
-        \includegraphics[width=0.8\textwidth]{images/Correlation_sketch.pdf}
-        \mcaption{2}{Example for a correlation function of a spin-$1/2$. %At time zero the spin is aligned to its initial position yielding an expectation value of $1/4$. 
-        As the time increases, the spin loses the memory of its initial orientation.}
-    \end{center}
-\end{minipage}
-\hspace{0.01\textwidth}
-\begin{minipage}{0.54\textwidth}
-    In case of our dynamic mean-field theory for spins (spinDMFT), the mean-fields are time-dependent \cite{graes21}. It is developed to compute spin correlation functions such as 
-    \begin{align*}
-        g^{zz}(t,0) &:= \langle \mb{S}^{z}(t) \mb{S}^{z}(0) \rangle
-    \end{align*}
-    in the limit of large temperatures. These functions tell us, how much the spin at time $t$ is still correlated to its initial alignment. Correspondingly, they capture the 
-    decoherence induced by the spins environment.     
-\end{minipage}
-\vspace{2mm}
+However, negative values for $U$ are also possible \cite{sentef}. They are oftentimes achieved by the aforementioned effective interactions mediated by phonons.
+If the system is precisely at half-filling and the underlying lattice of the system is bipartite, e.g. a square or simple cubic lattice, 
+the system can be transformed by a specific kind of particle-hole transformation \cite{micnas90}.
+This transformation effectively flips the sign of $U$, allowing researches to use the previously known antiferromagnetic results.
+However, instead of antiferromagnetism, the system now exhibits the coexistence of two distinct phases.
+Namely, s-wave superconductivity as described by the aforementioned BCS-theory and a so-called charge-density wave (CDW).
+The latter describes a system, where the electron density exhibits a wave like behaviour, similar to the spins in an antiferromagnetic phase.
 
-\begin{minipage}{0.65\textwidth}
-    A promising application of spinDMFT can be found in the context of nitrogen-vacancy (NV) centers in diamond \cite{jelez06}. They are subject of current research due 
-    to their stable spin states up to room temperature which is ideal for many applications such as magnetic sensing \cite{sushk14}. Close to the diamond surface, however, 
-    the NV-center coherence is strongly weakened because they are disturbed by other spins stemming from surface defects or adatoms. Understanding 
-    the dynamics of these other spins requires considering a large spin ensemble which is where spinDMFT can strike. We are currently collaborating with an experimental 
-    group from Boston who measures the correlation functions of the surface defect spins. While spinDMFT itself failed 
-    to capture their measurements, we recently obtained good agreement with an extended approach called \emph{Cluster-spinDMFT}.
-\end{minipage}
-\hspace{0.01\textwidth}
-\begin{minipage}{0.35\textwidth}
-    \begin{center}
-        \includegraphics[width=0.8\textwidth]{images/NV_ensemble.png}
-        \mcaption{3}{NV-center at a diamond surface with perturbing spins on the surface (black) \cite{rossk14}.}
-    \end{center}     
-\end{minipage}
-\vspace{1.3mm}
+\msection{Methodology: Mean field theory and iterated equations of motion}
 
-It is also possible to extend spinDMFT to external time dependencies. This enables us to introduce pulses to the mean-field simulation and to investigate phenomena such as 
-\emph{dynamic decoupling} \cite{uhrig07}. The idea of this is to periodically rotate a considered spin in order to weaken the effects of its environment and, 
-hence, to extend its coherence time.
+Handling a quartic Hamiltonian, such as \autoref{eqn:hubbard}, is practically very difficult up to impossible,
+as the Hilbert spaces grow exponentially with the system size.
+The mean field approximation aims to reduce those kinds of Hamiltonians to a bilinear form by neglecting fluctuations around the the equilibrium.
+Therefore, one introduces so-called normal ordered operators
+\begin{equation}
+    :A: = A - \expec{A}_0\,.
+\end{equation}
+These allow rewriting the quartic term in the Hubbard Hamiltonian to
+\begin{subequations}
+\begin{align}
+    c_{i\uparrow}^\dagger c_{i\downarrow}^\dagger c_{i\downarrow} c_{i\uparrow} &= :c_{i\uparrow}^\dagger c_{i\downarrow}^\dagger c_{i\downarrow} c_{i\uparrow}:\\
+        &+\expec{c_{i\uparrow}^\dagger c_{i\downarrow}^\dagger} :c_{i\downarrow} c_{i\uparrow}: 
+            + :c_{i\uparrow}^\dagger c_{i\downarrow}^\dagger: \expec{c_{i\downarrow} c_{i\uparrow}} \\
+        &-\expec{c_{i\uparrow}^\dagger c_{i\downarrow}} :c_{i\downarrow}^\dagger c_{i\uparrow}: 
+            - :c_{i\uparrow}^\dagger c_{i\downarrow}: \expec{c_{i\downarrow}^\dagger c_{i\uparrow}} \\
+        &+\expec{c_{i\uparrow}^\dagger c_{i\uparrow}} :c_{i\downarrow}^\dagger c_{i\downarrow}: 
+            + :c_{i\uparrow}^\dagger c_{i\uparrow}: \expec{c_{i\downarrow}^\dagger c_{i\downarrow}} + \text{const}\,,
+\end{align}
+\end{subequations}
+where the first term $:c_{i\uparrow}^\dagger c_{i\downarrow}^\dagger c_{i\downarrow} c_{i\uparrow}:$ describes only small fluctuations that are neglected.
+The remainder is only bilinear in terms of operators as the expectation values are merely numbers.
 
-Another potential project is the extension to spatial dependencies. Here, we plan to study how the effects of a pulse propagate through the sample. 
-The underlying phenomenon is called spin diffusion \cite{zu21}.
+The challenge here is obtaining these expectation values as they depend on the mean-field Hamiltonian, which in turn depends on the expectation values.
+The solution to this is a self-consistency calculation, for which one selects some starting values,
+solves the Hamiltonian for the new starting values and iterates until convergence is achieved.
 
-As indicated above, a strong advantage of spinDMFT is its versatility. It can be easily extended to consider complex spin 
-configurations, anisotropies, time dependencies and more. Since the theoretical and numerical background has already been established, applying spinDMFT to new 
-scenarios becomes more and more important. Here, an internship is a great opportunity.
+Afterwards, we use the iterated-equations-of-motion method (iEoM) to analyse the system for occurring excitations \cite{philip18, Kalthoff2017}.
+This method is based on the Heisenberg equations of motion 
+\begin{equation}
+    \timeDeriv A(t) = \frac{i}{\hbar} [H, A(t)]\,.
+\end{equation}
+To solve this equation, one needs an operator basis, which is complete in the sense, that each commutator $[H, A(t)]$ can be represented by this basis.
+Practically, this is often requires an infinite basis, which is impossible to implement numerically.
+The idea of the iEoM is, to iterate the commutation process and truncate at some point, assuming that the error becomes smaller with each iteration.
+
+Furthermore, an operator scalar product $(A|B)$ is introduced, which allows reducing the equations of motion from the operator form above to
+\begin{equation}
+    \timeDeriv \mathbf{c}(t) = \mathcal{M} \mathbf{c}(t)\,,
+\end{equation}
+where $\mathbf{c}(t)$ is a vector of time-dependent complex \emph{numbers} and a matrix
+\begin{equation}
+    \mathcal{M}_{ij} := (A_i | [H, A_j])\,,
+\end{equation}
+where $A_i, A_j$ are the operators from the aforementioned operator basis.
+
+All system dynamics are now contained within the complex-valued matrix $\mathcal{M}$, which can be analysed using a plethora of well-established numerical methods.
 
@@
 
-Generally, the internship involves mainly \emph{numerical} tasks and \emph{coding}. 
-%The work flow for applying the mean-field-approach looks as 
-%follows. First, a considered spin model has to be transformed to a mean-field model. Subsequently, the self-consistency conditions derived in the process can be solved with 
-%existing code in \textbf{C++}. Sometimes, numerical difficulties arise that demand to change details of the method. In the end, the results can be evaluated to 
-%observe exciting new phenomena. 
-A specific project could be the investigation of dynamic decoupling in a system comprising a single \emph{spin subject to a Gaussian noise}. Such a project would start
-with yourself reading through some literature provided by us so that you understand the fundamental ideas. Subsequently, you would start writing a first simple program in \textbf{C++}, 
-that introduces noise, artificial or from a mean-field approach, to a spin. In doing so, you can use existing code fragments from us on some of the required numerical methods. Subsequently, 
-you would introduce a pulse sequence such as \emph{UDD} \cite{uhrig07} to the spin in order to enhance its coherence.
-One goal of the project could be to find an optimal pulse sequence in dependence of the underlying noise. We emphasize, that this is only \textbf{one} potential project 
-and there are many other possibilities. Generally, a little experience 
-in \textbf{C++}, \emph{Python} or coding is advantageous. Moreover, knowledge of quantum mechanics is desirable.
+Generally, the internship involves mainly \emph{numerical} tasks and \emph{coding}, mainly utilising C++ and Python.
+Your project will involve the investigation of the excitations within a Hubbard model, depending on interactions or different lattices.
+You will begin by familiarising yourself with the topic using literature that we will provide.
+Subsequently, you would write a program that solves a self-consistency problem and analyses the system dynamics.
+We will provide you with some of our existing code fragments to help you get started.
+Generally, some experience in \textbf{C++}, \emph{Python} or coding is advantageous. Moreover, knowledge of quantum mechanics is required.
 
@@
 
-The chair currently consists of 9 people, that is, 6 PhD students, 1 postdoc as well as Prof. G\"otz S. Uhrig and Prof. Joachim Stolze. The group 
-works on a broad range of physical topics such as topological magnonics, non-equilibrium physics, coherence control and more. We have a weekly seminar in which
-progress is reported and articles are discussed (Journal Club). Feel free to visit our homepage 
-at \url{https://cmt.physik.tu-dortmund.de/uhrig-group/}. 
+The chair currently consists of 9 people, that is, 6 PhD students, 1 postdoc as well as Prof. G\"otz S. Uhrig and Prof. Joachim Stolze. 
+The group works on a broad range of physical topics such as topological magnonics, non-equilibrium physics, coherence control and more. 
+We have a weekly seminar in which progress is reported and articles are discussed (Journal Club). Feel free to visit our homepage at \url{https://cmt.physik.tu-dortmund.de/uhrig-group/}. 
+Our group already successfully hosted 2 RISE students in 2023.
 The methodology and the investigation of collective excitations is the research area of the PhD student Joshua Alth\"user who will also be your supervisor.

### 2023-10-05 cpp/HubbardMeanField/sources/Hubbard/DOSModels/DOSBasedModel.hpp
uni

@@ -53,7 +53,7 @@ namespace Hubbard {
 					dos.computeValues();
 					std::cout << "1 - DOS-Norm = " << std::scientific << 1. - DensityOfStates::computeNorm<DOS>() << std::endl;
 #ifdef _EXACT_DOS
-					Constants::setBasis(2U * DOS::size());
+					//Constants::setBasis(2U * DOS::size());
 #else
 					Constants::BASIS_SIZE += 1;
 #endif
@@ -185,7 +185,8 @@ namespace Hubbard {
 
 		inline global_floating_type getGammaFromIndex(int gamma_idx) const {
 #ifdef _EXACT_DOS
-			return DOS::abscissa_v(gamma_idx);
+			return (Constants::HALF_BASIS - gamma_idx - 0.5) * DOS::LOWER_BORDER / Constants::BASIS_SIZE;  
+			//return DOS::abscissa_v(gamma_idx);
 #else
 			return 2 * (Constants::HALF_BASIS - gamma_idx) * DOS::LOWER_BORDER / (Constants::BASIS_SIZE - 1);
 #endif
@@ -193,7 +194,8 @@ namespace Hubbard {
 
 		inline int shiftByQ(int k) const {
 #ifdef _EXACT_DOS
-			return k + (k < Constants::HALF_BASIS ? Constants::HALF_BASIS : -Constants::HALF_BASIS);
+			return (-k + 2 * Constants::HALF_BASIS - 1);
+			//return k + (k < Constants::HALF_BASIS ? Constants::HALF_BASIS : -Constants::HALF_BASIS);
 #else
 			return (-k + 2 * Constants::HALF_BASIS);
 #endif

### 2023-10-05 cpp/HubbardMeanField/sources/Hubbard/DensityOfStates/SimpleCubic.cpp

@@ -71,6 +71,10 @@ namespace Hubbard::DensityOfStates {
 		return 0.5 * static_cast<_internal_precision>(integrator.integrate(integrand, lower_bound, upper_bound));
 	}
 
+	global_floating_type SimpleCubic::computeValue(const global_floating_type& gamma) {
+		return boost::math::pow<3>(LONG_1_PI) * (I_1(gamma) - I_2(gamma));
+	}
+
 	template <class T>
 	inline auto append_vectors(std::vector<T>& a, const std::vector<T>& b) {
 		return a.insert(a.end(), b.begin(), b.end());
@@ -124,7 +128,7 @@ namespace Hubbard::DensityOfStates {
 				old_integral = new_integral;
 			}
 
-			std::cout << "Exit after " << tsh.level() << " levels with error = " << error << std::endl;
+			std::cout << "Simple cubic: Exit after " << tsh.level() << " levels with error = " << error << std::endl;
 			std::cout << "Total amount of values = " << buf_values.size() << std::endl;
 			if (i == 0) {
 				abscissa = std::move(buf_abscissa);

### 2023-10-05 cpp/HubbardMeanField/sources/Hubbard/DensityOfStates/Square.hpp

@@ -12,6 +12,7 @@ namespace Hubbard::DensityOfStates {
 		inline static size_t n_abscissa() noexcept {
 			return abscissa.size();
 		};
+		static global_floating_type computeValue(const global_floating_type& gamma);
 
 		virtual void computeValues() override;
 

### 2023-10-05 cpp/HubbardMeanField/sources/Hubbard/DensityOfStates/Square.cpp
uni

@@ -7,6 +7,10 @@ namespace Hubbard::DensityOfStates {
 	std::vector<abscissa_t> Square::upper_border_to_abscissa;
 	dos_precision Square::b_minus_a_halved;
 
+	global_floating_type Square::computeValue(const global_floating_type& gamma){
+		return (LONG_1_PI * LONG_1_PI) * boost::math::ellint_1(sqrt(1 - gamma * gamma));
+	};
+
 #ifdef _BOOST_PRECISION
 #pragma omp declare reduction(+:dos_precision:omp_out+=omp_in)
 #endif
@@ -49,7 +53,7 @@ namespace Hubbard::DensityOfStates {
 			old_integral = new_integral;
 		}
 
-		std::cout << "Exit after " << tsh.level() << " levels with error = " << abs(0.5 - new_integral) << std::endl;
+		std::cout << "Square: Exit after " << tsh.level() << " levels with error = " << abs(0.5 - new_integral) << std::endl;
 		std::cout << "Total amount of values = " << values.size() << std::endl;
 
 		computed = true;

### 2023-10-05 cpp/HubbardMeanField/sources/Hubbard/Helper/TermWithDOS.hpp

@@ -98,12 +98,14 @@ namespace Hubbard::Helper {
 			approximate_dos(Constants::BASIS_SIZE, 0.0)
 		{
 #ifdef _EXACT_DOS
-			for (size_t i = 0U; i < Constants::BASIS_SIZE; ++i)
+			for (int i = 0; i < Constants::BASIS_SIZE; ++i)
 			{
-				approximate_dos[i] = DOS::values_v(i) * DOS::weights_v(i);
+				approximate_dos[i] = DOS::computeValue(this->model->getGammaFromIndex(i));//DOS::values_v(i) * DOS::weights_v(i);
+				std::cout << this->model->getGammaFromIndex(i) << "  " << approximate_dos[i] << std::endl;
 			}
+			
 #else
-			constexpr int faktor = 20;
+			constexpr int faktor = 200;
 			Constants::K_DISCRETIZATION *= faktor;
 			Constants::PI_DIV_DISCRETIZATION /= faktor;
 
@@ -113,7 +115,7 @@ namespace Hubbard::Helper {
 				// Irgendeine Zahl zwischen 0 und BASIS_SIZE
 				approximate_dos.at(std::round(0.5 * (1 - ks.gamma() / DOS::LOWER_BORDER) * (Constants::BASIS_SIZE - 1))) += 1;
 			} while (ks.iterateFullBZ());
-			for (int i = 0U; i < Constants::HALF_BASIS; ++i)
+			for (int i = 0; i < Constants::HALF_BASIS; ++i)
 			{
 				approximate_dos[i] += approximate_dos[Constants::BASIS_SIZE - 1 - i];
 				approximate_dos[i] *= 0.5;

### 2023-10-05 RISE_Projektbeschreibung/RISE_Projektbeschreibung.tex
uni

@@
 
-If the temperature is below some critical temperature $T_c$ they can condense into a macroscopic occupation of the ground state and allow for the famous perfect conductivity.
+\vspace{10pt}
+\begin{minipage}{0.40\textwidth}
+    If the temperature is below some critical temperature $T_c$ the Cooper pairs can condense into a macroscopic occupation of the lowest energy level 
+    and allow for the famous perfect conductivity.
     The two prominent collective excitations in a superconductor are the so-called Higgs and phase modes \cite{higgs, bo22}.
     The former is energetically located at the band edge and sometimes referred to as the amplitude mode.
-The latter originates in the invariance of the complex phase. 
-Changing the phase does not affect the energy, thus the mode is located at 0.
+    The latter originates from the invariance of the complex phase. 
+    Changing the phase does not affect the energy, thus the mode is located at 0 energy in neutral superfluids.
+\end{minipage}
+\hspace{0.01\textwidth}
+\begin{minipage}{0.58\textwidth}
+    \begin{center}
+        \includegraphics[width=\textwidth]{images/resolvent_general.pdf}
+        \mcaption{1}{Example results for the spectral density in the superconducting phase.
+            The two lines show the phase mode at $z=0$ and the Higgs mode at the lower band edge.}
+    \end{center}
+\end{minipage}
+\vspace{10pt}
 
-A well-known and often used model is the so-called Hubbard model. Its Hamiltonian reads
+A well-known and often used model is the so-called extended Hubbard model. Its Hamiltonian reads
 \begin{equation}
     \label{eqn:hubbard}
-    H = -t \sum_{\langle i, j \rangle, \sigma} c_{i\sigma}^\dagger c_{j\sigma}  + U \sum_i c_{i\uparrow}^\dagger c_{i\downarrow}^\dagger c_{i\downarrow} c_{i\uparrow}\,,
+    H = -t \sum_{\langle i, j \rangle, \sigma} c_{i\sigma}^\dagger c_{j\sigma} 
+    + U \sum_i c_{i\uparrow}^\dagger c_{i\downarrow}^\dagger c_{i\downarrow} c_{i\uparrow}
+    + V \sum_{\langle i, j \rangle, \sigma, \sigma'} n_{i\sigma}n_{j\sigma'}\,,
 \end{equation}
-where the $\langle i, j \rangle$ denotes the summation over next neighbours, $t$ is a hopping strength, 
-$U$ denotes the on-site interaction strength and $c_{i\sigma}^{(\dagger)}$ annihilates (creates) an electron with spin $\sigma$ on lattice site $i$.
+where the $\langle i, j \rangle$ denotes the summation over next neighbours on a lattice, $t$ is a hopping strength, 
+$U$ denotes the on-site and $V$ the inter-site interaction strength and $c_{i\sigma}^{(\dagger)}$ annihilates (creates) an electron with spin $\sigma$ on lattice site $i$.
+The number operator $n_{i\sigma} = c_{i\sigma}^\dagger c_{i\sigma}$ counts the number of electrons with spin $\sigma$ on lattice site $i$.
 Most commonly, $U$ is positive and represents the repulsive Coulomb interaction of two electrons.
-In this case, the model exhibits antiferromagnetism (AFM).
+In this case, the model exhibits antiferromagnetism (AFM), if $|V|$ is not too large.
 
@@
 The latter describes a system, where the electron density exhibits a wave like behaviour, similar to the spins in an antiferromagnetic phase.
+This degeneracy is broken by any finite $V$.
+\newpage
 
@@
 
-Handling a quartic Hamiltonian, such as \autoref{eqn:hubbard}, is practically very difficult up to impossible,
+\begin{minipage}{0.40\textwidth}
+    Handling a quartic Hamiltonian, such as \autoref{eqn:hubbard}, is practically very difficult or even impossible,
     as the Hilbert spaces grow exponentially with the system size.
     The mean field approximation aims to reduce those kinds of Hamiltonians to a bilinear form by neglecting fluctuations around the the equilibrium.
-Therefore, one introduces so-called normal ordered operators
-\begin{equation}
-    :A: = A - \expec{A}_0\,.
-\end{equation}
-These allow rewriting the quartic term in the Hubbard Hamiltonian to
-\begin{subequations}
-\begin{align}
-    c_{i\uparrow}^\dagger c_{i\downarrow}^\dagger c_{i\downarrow} c_{i\uparrow} &= :c_{i\uparrow}^\dagger c_{i\downarrow}^\dagger c_{i\downarrow} c_{i\uparrow}:\\
-        &+\expec{c_{i\uparrow}^\dagger c_{i\downarrow}^\dagger} :c_{i\downarrow} c_{i\uparrow}: 
-            + :c_{i\uparrow}^\dagger c_{i\downarrow}^\dagger: \expec{c_{i\downarrow} c_{i\uparrow}} \\
-        &-\expec{c_{i\uparrow}^\dagger c_{i\downarrow}} :c_{i\downarrow}^\dagger c_{i\uparrow}: 
-            - :c_{i\uparrow}^\dagger c_{i\downarrow}: \expec{c_{i\downarrow}^\dagger c_{i\uparrow}} \\
-        &+\expec{c_{i\uparrow}^\dagger c_{i\uparrow}} :c_{i\downarrow}^\dagger c_{i\downarrow}: 
-            + :c_{i\uparrow}^\dagger c_{i\uparrow}: \expec{c_{i\downarrow}^\dagger c_{i\downarrow}} + \text{const}\,,
-\end{align}
-\end{subequations}
-where the first term $:c_{i\uparrow}^\dagger c_{i\downarrow}^\dagger c_{i\downarrow} c_{i\uparrow}:$ describes only small fluctuations that are neglected.
-The remainder is only bilinear in terms of operators as the expectation values are merely numbers.
+    The remainder of the Hamiltonian is a set of products of expectation values and bilinear operators.
 
@@
     solves the Hamiltonian for the new starting values and iterates until convergence is achieved.
+\end{minipage}
+\hspace{0.01\textwidth}
+\begin{minipage}{0.58\textwidth}
+    \begin{center}
+        \includegraphics[width=\textwidth]{images/phase_boundaries_T0.pdf}
+        \mcaption{1}{Example phase diagram obtained by mean field calculations.}
+    \end{center}
+\end{minipage}
+\vspace{10pt}
 
@@
 The idea of the iEoM is, to iterate the commutation process and truncate at some point, assuming that the error becomes smaller with each iteration.
-
-Furthermore, an operator scalar product $(A|B)$ is introduced, which allows reducing the equations of motion from the operator form above to
-\begin{equation}
-    \timeDeriv \mathbf{c}(t) = \mathcal{M} \mathbf{c}(t)\,,
-\end{equation}
-where $\mathbf{c}(t)$ is a vector of time-dependent complex \emph{numbers} and a matrix
-\begin{equation}
-    \mathcal{M}_{ij} := (A_i | [H, A_j])\,,
-\end{equation}
-where $A_i, A_j$ are the operators from the aforementioned operator basis.
-
-All system dynamics are now contained within the complex-valued matrix $\mathcal{M}$, which can be analysed using a plethora of well-established numerical methods.
+Introducing an operator scalar product $(A | B)$ allows us to reduce the operator-valued differential equations to simple matrices.
+All system dynamics are now contained within the complex-valued matrices, which can be analysed using a plethora of well-established numerical methods.
 

### 2023-11-23 paper/main.tex
xx

\documentclass[
    reprint, 
    aps,
    preprintnumbers,
    twocolumn,
    prb,
    superscriptaddress
]{revtex4-2}

%=======================
% Packages:
%=======================

\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage[multiple]{footmisc}
\usepackage{lipsum}
\usepackage{rotating}
\usepackage{perpage}
\usepackage{chronology}
\usepackage{lipsum}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage[T1]{fontenc}
\usepackage{etoolbox}
\usepackage{graphics}
\usepackage{abraces}
\makeatletter
\let\unit\relax % otherwise there are package conflicts with siunitx
\makeatother
\usepackage{siunitx}
\usepackage{hyperref}
%\usepackage{float}
\usepackage{multirow}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{url}
\usepackage{physics}
\usepackage{hyperref}
\usepackage{bbm}
\usepackage{color}
\usepackage{placeins}
\usepackage[normalem]{ulem}
\usepackage{mhchem}

%=======================
% New Commands:
%=======================

\newcommand{\vk}{\vec{k}}
\newcommand{\vQ}{\vec{Q}}
\newcommand{\up}{\uparrow}
\newcommand{\down}{\downarrow}
\newcommand{\kplusQ}{\vk+\vQ}
\newcommand{\kminusQ}{-\vk-\vQ}

\begin{document}

% Preliminary title
\title{Collective excitations in the 2- and 3-dimensional extended Hubbard model}

%=======================
% Authors:
%=======================

\author{Joshua Alth\"user}\email{joshua.althueser@tu-dortmund.de}
\affiliation{Condensed Matter Theory, TU Dortmund University,
Otto-Hahn Stra\ss{}e 4, 44221 Dortmund, Germany}

\author{G\"otz S.~Uhrig}
\email{goetz.uhrig@tu-dortmund.de}
\affiliation{Condensed Matter Theory, TU Dortmund University,
Otto-Hahn Stra\ss{}e 4, 44221 Dortmund, Germany}

\date{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%                                                  Abstract                                                 %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Abstract text Abstract text Abstract text Abstract text Abstract text Abstract text Abstract text 
\end{abstract}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%                                                Introduction                                               %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}\label{sec:introduction}

The Hubbard model has been employed in a plethora of previous studies. 
Early studies proved the existence of eigenstates to the Hubbard Hamiltonian that exhibit off-diagonal long-range order,
tantalizing the model's usage for the description of high-temperature superconductivity \cite{yang89}.
Shortly afterward, an exact $SO(4)$ symmetry was discovered,
which allows a degeneracy of superconductivity (SC) and a charge-density wave (CDW) governed by an attractive on-site interaction \cite{yang90}.
This coexistence can be argued by the existence of a particle-hole transformation on bipartite lattices, 
that maps the attractive Hubbard model exactly onto the repulsive one, exhibiting antiferromagnetism (AFM) \cite{Hirsch85}.
The previously mentioned SC and CDW phases map to different spin operators \cite{zitko15,lieb89}.
\newline
Many recent experimental and theoretical studies examined the driven systems in the hope of inducing superconductivity 
\cite{Nicoletti14,Krull14,Moor14,Casandruc15,patel16,sentef17,Buenemann17}.
Other studies, focusing on equilibrium systems, 
investigated the phases and various quantities therein of said model including various additional interactions with and without doping 
\cite{Micnas88,Micnas88b,Micnas89,Dzierzawa92,Kostyrko92,Eriksson95,Staudt00,Onari04,Toschi05,Brackett16,Paki19,romer20,Sushchyev22}.
In this paper, we will restrict ourselves to the half-filled Hubbard model, including an additional intersite interaction, on a square and a simple cubic lattice.
\textcolor{red}{Für den 3D Fall finde ich keine Phasendiagramme des extended Hubbard models, ggf nochmal suchen...}
The 2D case already exhibits a wide range of possible phases, including CDW, AFM as well as $s$- and $d_{x^2 - y^2}$-wave superconductivity
\cite{Micnas88b,Tsuchiura95,Su01,Su04,ha11,Huang13,Jiang22}.
\newline
In this article, we will first employ a mean-field approximation to the interaction terms 
and then use the methodology from the so-called iterated equations of motion approach,
which has already seen success in the handling of interaction quenches \cite{uhrig09,hamerla13,hamerla14,bleicker18}.
Here, one commutes operators from a suitable operator basis with the Hamiltonian and adds the newly occurring terms to it.
Naturally, a truncation is necessary for most practical applications, however, the approximation becomes better the more terms are included within the basis.
The functionality of this method has been compared to the density matrix formalism and has proved to be considerably more accurate \cite{Kalthoff17}.
Additionally, we will show an explicit way to obtain various Green's functions from the aforementioned methodology.
By extension, we also obtain the spectral functions of the investigated systems and discuss the excitations found therein.
The prominent examples in the SC phase are the well-known phase (Leggett) and amplitude (Higgs) modes \cite{Cea14,Krull16,Schwarz20,Fan22}.
\newline
The remainder of this paper is organized as follows:
In \autoref{sec:model} we will introduce the model and its Hamiltonian as well as the main equations and relations used throughout this article.
Next, we show our results in \autoref{sec:results}.
Lastly, in \autoref{sec:conclusion}, we will discuss our results.
In the appendix \textcolor{red}{(or in the supplemental material?)}, we will derive and explain our methods in detail.

\section{Model and governing equations}\label{sec:model}

The Hamiltonian of the extended Hubbard model is given by
\begin{equation}
    \begin{aligned}
        H = &-t \sum_{\langle i, j \rangle, \sigma} \left( c_{i\sigma}^\dagger c_{j\sigma} + \text{h.c.} \right) 
        + \mu \sum_{i,\sigma} n_{i\sigma} \\
        &+ U \sum_{i} n_{i\uparrow} n_{i\downarrow} 
        + \frac{V}{2} \sum_{\langle i, j\rangle, \sigma} n_{i\sigma} n_{j\sigma}\,,
    \end{aligned}
\end{equation}

where $c_{i\sigma}^{(\dagger)}$ annihilates (creates) an electron with spin $\sigma$ on lattice site $i$ and $\langle i, j\rangle$ denotes the summation over next neighbours.
The parameters are the hopping amplitude $t$, the onsite interaction $U$, the intersite interaction $V$ and the chemical potential $\mu$.
Throughout this article, we will give all energy-related quantities in terms of the hopping amplitude, which we subsequently set to unity $t=1$.
Applying a Fourier transformation into $k$-space yields the single-particle dispersion

\begin{equation}
    \epsilon_0 (\vk) = -2t \sum_{\alpha=1}^D \cos(k_\alpha)\,,\quad k_\alpha \in [-\pi, \pi)\,,
\end{equation}
with the system's dimension $D$ and the dimensionless momentum $\vk$.
The interaction terms are then mean-field decoupled. 
We follow the naming scheme of Ref. \cite{sentef17}

\begin{equation}
    \begin{aligned}
        n_{k\sigma} &:= c_{\vk\sigma}^\dagger c_{\vk\sigma}\,,      &f_k     &:= c_{-\vk\down} c_{\vk\up}\,, \\
        g_{k\sigma} &:= c_{\vk\sigma}^\dagger c_{\vk+\vQ\sigma}\,,  &\eta_k  &:= c_{-\vk-\vQ\down} c_{\vk\up}\,,
    \end{aligned}
\end{equation}

where $\vQ := (\pi, ...)$ defines the nesting vector for the CDW and AFM phases.
We use these abbreviations to write down the mean-field parameters

\begin{subequations}
    \begin{align}
        \Delta_\text{CDW} &= \left(\frac{U}{2N} - \frac{ZV}{N}\right) \sum_{\vk\sigma} \langle g_{\vk\sigma} \rangle\,, \\
        \Delta_\text{AFM} &= \frac{U}{2N} \sum_{\vk} \left( \langle g_{k\uparrow} \rangle - \langle g_{\vk\downarrow} \rangle \right)\,, \\
        \Delta_\text{SC} &= \frac{U}{N} \sum_{\vk} \langle f_{\vk} \rangle\,, \\
        \Delta_\eta &= \frac{U}{N} \sum_{\vk} \langle \eta_{\vk} \rangle\,, \\
        \Delta_n &= \frac{V}{N} \sum_{\vk,\sigma} \sum_{\alpha=1}^D \cos k_\alpha \langle n_{\vk\sigma} \rangle\,,
    \end{align}
\end{subequations}

where $Z$ denotes the coordination number of the lattice.
In total, we obtain the mean-field Hamiltonian in spinor representation as

\begin{equation}
    H_\text{MF} = \sum_{\vk} \Psi^\dagger (\vk) h(\vk) \Psi (\vk)\,,
\end{equation}

with the spinors
\begin{equation}
    \Psi^\dagger (\vk) := \left( c_{\vk\up}^\dagger\,, c_{\kplusQ\up}^\dagger\,, c_{-\vk\down}\,, c_{\kminusQ\down} \right)
\end{equation}

and

\begin{widetext}
\begin{equation}
    h(\vk) := \begin{pmatrix}
        \epsilon_0 (\vk) & \Delta_\text{CDW}^* - \Delta_\text{AFM}^* & \Delta_\text{SC} & \Delta_\eta \\
        \Delta_\text{CDW} - \Delta_\text{AFM} & \epsilon_0 (\vk + \vQ) & \Delta_\eta & \Delta_\text{SC} \\
        \Delta_\text{SC}^* & \Delta_\eta^* & - \epsilon_0 (-\vk) & - \Delta_\text{CDW} - \Delta_\text{AFM} \\
        \Delta_\eta^* & \Delta_\text{SC}^* & - \Delta_\text{CDW}^* - \Delta_\text{AFM}^* & - \epsilon_0 (-\vk - \vQ)\,.
        \end{pmatrix}
\end{equation}
\end{widetext}

Now, the entire Hamiltonian and thus all expectation values only depend on
\begin{equation}
    \hat{\gamma}(\vk) := \sum_{\alpha=1}^D \cos(k_\alpha)\,,
\end{equation}
i.e. for any operator $\hat{O}$ the following relation holds 
\begin{equation}
    \langle \hat{O}_{\vk} \rangle = \langle \hat{O}_{\vk'} \rangle =: \langle \hat{O}_{\gamma} \rangle\,,
\end{equation}
if $\hat{\gamma}(\vk) = \hat{\gamma}(\vk')$.
This allows us to replace the momentum sums with energy integrals using the bare density of states
\begin{equation}
    \rho(\gamma) := \frac{1}{N} \sum_{\vk} \delta \left(\gamma - \hat{\gamma} (\vk) \right)\,.
\end{equation}
As an example, consider 
\begin{equation}
    \Delta_\text{SC} = \frac{U}{2N} \int \mathrm{d}\gamma \rho(\gamma) \langle f_{\gamma} \rangle\,.
\end{equation}
We will be using the exact densities of states for the square and the simple cubic lattice found in Ref. \cite{Hanisch97}.
Solving the mean-field equations iteratively, one obtains the groundstate phase diagram at temperature $T=0$ as shown in \textcolor{red}{FIGURE}.
Note, that the phase-separated state as well as the $d_{x^2 - y^2}$-superconducting state, which has been confirmed in for the square lattice \cite{Micnas88b,Huang13},
cannot be described by our method. This is due to our restriction to terms that are proportional to $\hat{\gamma}(\vk)$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%                                                  Results                                                  %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Results}\label{sec:results}

...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%                                                Conclusion                                                 %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}\label{sec:conclusion}

...

%==============================================================================
% Acknowledgments 
%==============================================================================
\begin{acknowledgments} 
    ....
\end{acknowledgments}

\bibliography{sn-bibliography}
%\bibliography{../../A_bibinput/liter10.bib}

\end{document}

### 2023-11-23 paper/phase_diagram.py
text

@@ -1,2 +1,68 @@
 import numpy as np
-import 
+import matplotlib.pyplot as plt
+
+fig, axs = plt.subplots(nrows=2, sharex=True, figsize=(6.4, 9))
+
+############################################################################
+############                  Square lattice                    ############
+############################################################################
+micnas_d = np.loadtxt("../data/micnas_d_wave.csv").transpose()
+axs[0].plot(micnas_d[0], micnas_d[1], "k-")
+axs[0].plot(np.array([0, 2]), 0.25 * np.array([0, 2]), "k-")
+axs[0].plot(np.array([-2, 0]),        np.array([0, 0]), "k-")
+
+#Shade s-wave area
+common_x = np.linspace(-2, 0, 100)
+interpol = np.interp(common_x, micnas_d[0], micnas_d[1])
+axs[0].fill_between(common_x, np.zeros(100), interpol, color="blue", alpha=.5, label="$s$-wave")
+
+#Shade d-wave area
+axs[0].fill_between(micnas_d[0], micnas_d[1], -2 * np.ones(len(micnas_d[0])), color="red", alpha=.5, label="$d_{x^2 - y^2}$-wave")
+
+#Shade AFM area
+common_x = np.linspace(0, 2, 100)
+interpol = np.interp(common_x, micnas_d[0], micnas_d[1])
+axs[0].fill_between(common_x, .25 * common_x, interpol, color="green", alpha=.5, label="AFM")
+
+#Shade CDW area
+axs[0].fill_between(np.array([-2, 0, 2]), np.array([0, 0, 0.5]), np.array([2, 2, 2]), color="orange", alpha=.5, label="CDW")
+
+
+############################################################################
+############                  Cubic lattice                     ############
+############################################################################
+axs[1].plot(np.array([0, 2]),  np.array([0, 2]) / 6., "k-")
+axs[1].plot(np.array([-2, 0]), np.array([0, 0]),      "k-")
+axs[1].plot(np.array([0, 0]),  np.array([0, -2]),     "k-")
+
+#Shade s-wave area
+axs[1].fill_between([-2, 0], [0, 0], [-2, -2], color="blue", alpha=.5, label="$s$-wave")
+
+#Shade AFM area
+axs[1].fill_between([0, 2], [0, 1./3.], [-2, -2], color="green", alpha=.5, label="AFM")
+
+#Shade CDW area
[…]

### 2023-11-23 paper/main.tex
text

@@
 
+\newcommand{\ddt}{\frac{\mathrm{d}}{\mathrm{d}t}}
+
 \begin{document}
@@
 
-The Hubbard model has been employed in a plethora of previous studies. 
+The Hubbard model has been studied in a plethora of previous studies. 
 Early studies proved the existence of eigenstates to the Hubbard Hamiltonian that exhibit off-diagonal long-range order,
-tantalizing the model's usage for the description of high-temperature superconductivity \cite{yang89}.
+encouraging the model's usage for the description of high-temperature superconductivity \cite{yang89}.
 Shortly afterward, an exact $SO(4)$ symmetry was discovered,
@@
 Other studies, focusing on equilibrium systems, 
-investigated the phases and various quantities therein of said model including various additional interactions with and without doping 
+investigated the phases and various quantities therein of the said model including various additional interactions with and without doping 
 \cite{Micnas88,Micnas88b,Micnas89,Dzierzawa92,Kostyrko92,Eriksson95,Staudt00,Onari04,Toschi05,Brackett16,Paki19,romer20,Sushchyev22}.
+\newline
 In this paper, we will restrict ourselves to the half-filled Hubbard model, including an additional intersite interaction, on a square and a simple cubic lattice.
@@
 The remainder of this paper is organized as follows:
-In \autoref{sec:model} we will introduce the model and its Hamiltonian as well as the main equations and relations used throughout this article.
+In \autoref{sec:model} we will introduce the model and its Hamiltonian as well as the methods used in this article.
 Next, we show our results in \autoref{sec:results}.
@@
 
-\section{Model and governing equations}\label{sec:model}
+\section{Model}\label{sec:model}
 
@@
 \begin{equation}
+    \label{eqn:full_hamiltonian}
     \begin{aligned}
@@
 where $\vQ := (\pi, ...)$ defines the nesting vector for the CDW and AFM phases.
-We use these abbreviations to write down the mean-field parameters
+We use the following abbreviations to write down the mean-field parameters
 
@@
     \begin{align}
+        \label{eqn:delta_cdw}
         \Delta_\text{CDW} &= \left(\frac{U}{2N} - \frac{ZV}{N}\right) \sum_{\vk\sigma} \langle g_{\vk\sigma} \rangle\,, \\
+        \label{eqn:delta_afm}
         \Delta_\text{AFM} &= \frac{U}{2N} \sum_{\vk} \left( \langle g_{k\uparrow} \rangle - \langle g_{\vk\downarrow} \rangle \right)\,, \\
@@
 where $Z$ denotes the coordination number of the lattice.
+The last parameter, $\Delta_n$, renormalizes the hoping term to
+
+\begin{equation}
+    \epsilon( \vk ) := -(2 + \Delta_n) \sum_{\alpha=1}^D \cos(k_\alpha)\,.
+\end{equation}
+
 In total, we obtain the mean-field Hamiltonian in spinor representation as
@@
 \begin{equation}
+    \label{eqn:mf_hamiltonian}
     H_\text{MF} = \sum_{\vk} \Psi^\dagger (\vk) h(\vk) \Psi (\vk)\,,
@@
     h(\vk) := \begin{pmatrix}
-        \epsilon_0 (\vk) & \Delta_\text{CDW}^* - \Delta_\text{AFM}^* & \Delta_\text{SC} & \Delta_\eta \\
-        \Delta_\text{CDW} - \Delta_\text{AFM} & \epsilon_0 (\vk + \vQ) & \Delta_\eta & \Delta_\text{SC} \\
-        \Delta_\text{SC}^* & \Delta_\eta^* & - \epsilon_0 (-\vk) & - \Delta_\text{CDW} - \Delta_\text{AFM} \\
-        \Delta_\eta^* & \Delta_\text{SC}^* & - \Delta_\text{CDW}^* - \Delta_\text{AFM}^* & - \epsilon_0 (-\vk - \vQ)\,.
+        \epsilon (\vk) & \Delta_\text{CDW}^* - \Delta_\text{AFM}^* & \Delta_\text{SC} & \Delta_\eta \\
+        \Delta_\text{CDW} - \Delta_\text{AFM} & \epsilon (\vk + \vQ) & \Delta_\eta & \Delta_\text{SC} \\
+        \Delta_\text{SC}^* & \Delta_\eta^* & - \epsilon (-\vk) & - \Delta_\text{CDW} - \Delta_\text{AFM} \\
+        \Delta_\eta^* & \Delta_\text{SC}^* & - \Delta_\text{CDW}^* - \Delta_\text{AFM}^* & - \epsilon (-\vk - \vQ)\,.
         \end{pmatrix}
@@
 \end{widetext}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.48\textwidth]{plots/phase_diagram.pdf}
+    \caption{The phase diagram obtained for the extended Hubbard model on (a) a square lattice and (b) a simple cubic lattice using a mean-field approximation at temperature $T=0$.
+    The CDW-AFM boundary lies at $U = ZV$, where $Z$ is the coordination number. For $U<0$ and $V=0$, there is a coexistence of CDW and $s$-wave SC.
+    The boundary for the $d_{x^2 - y^2}$-wave SC for the square lattice has been taken from Ref. \cite{Micnas88b}, as it is not accessible using our formalism.}
+    \label{fig:phase_diagram}
+\end{figure}
 
@@
 We will be using the exact densities of states for the square and the simple cubic lattice found in Ref. \cite{Hanisch97}.
-Solving the mean-field equations iteratively, one obtains the groundstate phase diagram at temperature $T=0$ as shown in \textcolor{red}{FIGURE}.
-Note, that the phase-separated state as well as the $d_{x^2 - y^2}$-superconducting state, which has been confirmed in for the square lattice \cite{Micnas88b,Huang13},
-cannot be described by our method. This is due to our restriction to terms that are proportional to $\hat{\gamma}(\vk)$.
+Solving the mean-field equations iteratively, one obtains the groundstate phase diagram at temperature $T=0$ as shown in \autoref{fig:phase_diagram}.
+Note, that the $d_{x^2 - y^2}$-superconducting state, which has been confirmed for the square lattice \cite{Micnas88b,Huang13}, cannot be described by our method. 
+This is due to our restriction to terms that are proportional to $\hat{\gamma}(\vk)$.
+\newline
+The CDW-AFM boundary is located at $U = ZV$, where $Z$ is the coordination.
+This holds for both the square lattice ($Z=4$) and the simple cubic lattice ($Z=6$) and can be seen by comparing \eqref{eqn:delta_cdw} and \eqref{eqn:delta_afm}:
+Crossing the aforementioned line, changes which one of the two prefactors is larger.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%                                                  Methods                                                  %%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To investigate the collective modes, we employ the iterated equations of motion approach \cite{uhrig09,hamerla13,hamerla14,bleicker18}.
+We will present the general ideas briefly here and direct the interested reader to the appendix \textcolor{red}{!REF!} for a detailed explanation and derivation.
+\newline
+We start with some operator basis $\mathcal{B}$ that is complete with respect to commutation with a Hamiltonian $H$, 
+i.e. any commutator $[H, A]$ for any $A \in \mathcal{B}$ can be represented by linear combinations of operators in $\mathcal{B}$.
+We can then express any time-depend operator from this basis as
+
+\begin{equation}
+    a(t) = \sum_j c_j(t) A_j\,,
+\end{equation}
+
+where $c_j(t)$ captures the entire time dependence. 
+Plugging this into the Heisenberg equation of motion and applying an operator scalar product $(A_i|\cdot)$ to both sides of the equation yields
+
+\begin{equation}
+    \begin{aligned}
+        \ddt a(t) = \sum_j \ddt c_j(t) A_j &= i \sum_j c_j(t) [H, A_j] \\
+        \Rightarrow \sum_j \underbrace{(A_i | A_j)}_{:=\mathcal{N_{ij}}} \ddt c_j(t) &= i \sum_j \underbrace{(A_i | [H, A_j])}_{:=\mathcal{M_{ij}}} c_j(t) \\
+        \Rightarrow \mathcal{N} \ddt \vec{c}(t) &= i \mathcal{M} \vec{c}(t)\,.
+    \end{aligned}
+\end{equation}
+
+The matrices $\mathcal{N}$ and $\mathcal{M}$ contain all the dynamics and energetic properties of the system but have the significant advantage of being simple matrices rather than operators acting on an enormous Hilbert space.
+\newline
+However, most Hamiltonians do not allow any such operator basis to exist. 
+Therefore, one repeats this commutation process and includes the occurring terms within a bigger basis,
+hoping to get better results as the basis size increases.
+
+In this article, we will be using the operator pseudo scalar product
+
+\begin{equation}
+\label{eqn:scalar_product}
+    (A | B) := \langle [A^\dagger, B] \rangle\,,
+\end{equation}
+
+where the expectation values are taken with respect to the thermal equilibrium of the mean-field Hamiltonian \eqref{eqn:mf_hamiltonian}.
+Nevertheless, we will compute $\mathcal{M}$ using the full Hubbard Hamiltonian \eqref{eqn:full_hamiltonian} enabling us to capture collective behaviour rather than the one particle dynamics given by the mean-field approximation.
 

### 2023-11-24 paper/main.tex
tex und cluster

@@
 The remainder of this paper is organized as follows:
-In \autoref{sec:model} we will introduce the model and its Hamiltonian as well as the methods used in this article.
+In \autoref{sec:model} we will introduce the model and its Hamiltonian as well our mean-field theory.
+A brief overview over the iterated equations of motion approach is presented in \autoref{sec:ieom}.
 Next, we show our results in \autoref{sec:results}.
@@
 
-\section{Model}\label{sec:model}
+\section{Model and mean-field theory}\label{sec:model}
 
@@
 \begin{equation}
+    \label{eqn:operators}
     \begin{aligned}
@@
 \end{equation}
-i.e. for any operator $\hat{O}$ the following relation holds 
+i.e. for any operator $O$ the following relation holds 
 \begin{equation}
-    \langle \hat{O}_{\vk} \rangle = \langle \hat{O}_{\vk'} \rangle =: \langle \hat{O}_{\gamma} \rangle\,,
+    \label{eqn:equal_expecs}
+    \langle O_{\vk} \rangle = \langle O_{\vk'} \rangle =: \langle O_{\gamma} \rangle\,,
 \end{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%                                                  Methods                                                  %%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Iterated equations of motion and Green's functions}\label{sec:ieom}
 
@@
 \begin{equation}
+    \label{eqn:heisenberg}
     \begin{aligned}
@@
 Nevertheless, we will compute $\mathcal{M}$ using the full Hubbard Hamiltonian \eqref{eqn:full_hamiltonian} enabling us to capture collective behaviour rather than the one particle dynamics given by the mean-field approximation.
+\newline
+This choice enables us to write down matrix-valued Fourier-transformed Green's functions in terms of the aforementioned matrices
+
+\begin{equation}
+    \label{eqn:green_function}
+    \mathcal{G}(z = \omega + i0^+) = \mathcal{N} \frac{1}{-z \mathcal{N} - \mathcal{M}} \mathcal{N} := -\mathcal{N} \mathcal{R}(z) \mathcal{N}\,,
+\end{equation}
+
+where we defined the resolvent
+
+\begin{equation}
+    \label{eqn:resolvent}
+    \mathcal{R}(z) := \frac{1}{z \mathcal{N} + \mathcal{M}}\,.
+\end{equation}
+
+Here, the different matrix elements correspond to various Green's functions, depending on the operator basis.
+For example, assume the operator in the basis is $f_{\vk}$, then the top left element of $\mathcal{G}$ is the Green's function
+
+\begin{equation}
+    \mathcal{G}_{00}(z = \omega +i0^+) =  G(z) = -i \int_0^{\infty} \langle [f_{\vk}(t), f_{\vk}^\dagger(0)] \rangle e^{izt} \mathrm{d}t\,.
+\end{equation}
+
+For a detailed derivation of this statement, we refer the reader to the appendix \textcolor{red}{!REF!}.
+
+Our operator basis consists of operators of the type
+
+\begin{equation}
+    A_\gamma := \frac{1}{\sqrt{N}} \sum_{\vk} \delta (\gamma - \hat{\gamma}( \vk )) A_{\vk}\,,
+\end{equation}
+
+where $A_{\vk}$ represents each type of operator in \eqref{eqn:operators} and their Hermitian conjugates.
+Different indices are taken as additional basis operators, e.g. $n_{\vk \up}$ and $n_{\vk \down}$ are taken into the basis separately.
+We then order these operators in a way reminiscent of the $x$- and $p$-terms in the harmonic oscillator, i.e.
+
+\begin{equation}
+    X_i := A_i + A_i^\dagger\,,\quad P_i := A_i - A_i^\dagger\,.
+\end{equation}
+
+Our basis is then $\mathcal{B}_{XP} := {X_i, P_i}$.
+If some operators would be 0 ($P_i$ for any $n$-type term) or duplicates (certain $X_i$ for $g$-type terms), we omit them.
+\newline
+Due to this choice of basis, the matrices occurring in \eqref{eqn:heisenberg} have a special block structure
+
+\begin{equation}
+    \mathcal{M} = \begin{pmatrix}
+        \mathcal{K}_+ & \kappa \\ \kappa^\dagger & \mathcal{K}_-
+    \end{pmatrix}\,,\quad \mathcal{N} = \begin{pmatrix}
+        \Lambda_+ & \mathcal{L} \\ \mathcal{L}^\dagger & \Lambda_-
+    \end{pmatrix}\,,
+\end{equation}
+
+where $\Im [\mathcal{K}_\pm] = \Re [\kappa] = 0$ and $\Re [\Lambda_\pm] = \Im [\mathcal{L}] = 0$.
+Furthermore, if all occurring expectation values are real, both matrices have large empty blocks.
+This condition is fulfilled for all cases investigated in this article.
+Additionally, we can utilize this block structure to rewrite \eqref{eqn:resolvent} to
+
+\begin{equation}
+    \mathcal{R}(z) \vert_X = - \check{N}^{-1/2} \frac{1}{z^2 - \underbrace{\check{N}^{-1/2} \mathcal{K}_+ \check{N}^{-1/2}}_{:= \check{M}}} \check{N}^{-1/2}\,,
+\end{equation}
+
+where $\vert_X$ denotes the block corresponding to the $X$-terms in the basis and $\check{N} := \mathcal{L} \mathcal{K}_-^{-1} \mathcal{L}^\dagger$.
+An analogous form can be found for the $P$-block.
+
+Now, the task at hand is finding the inverse $1/(z^2 - \check{M})$ for all $z$.
+This can be achieved using a Lanczos tridiagonalization and subsequently a continued fraction expansion in the form of
+
+\begin{widetext}
+\begin{equation}
+    \left( z^2 - \begin{pmatrix}
+        z - a_0 & b_1 & 0 & 0 & \cdots \\
+        b_1 & z - a_1 & b_2 & 0 & \cdots \\
+        0 & b_2 & z - a_2 & b_3 & \cdots \\
+        \vdots & \vdots & \vdots & \vdots & \ddots
+    \end{pmatrix} \right)_{00}^{-1} = \dfrac{1}{z^2 - a_0 - \dfrac{b_1^2}{z^2 - a_1 - \dfrac{b_2^2}{ z^2 - a_2 - \hdots}}}\,\,
+\end{equation}
+\end{widetext}
+
+where $a_i$ and $b_i$ are the Lanczos coefficients \cite{PettiforRecursion,ViswanathRecursion}.
+In the single-band case, the coefficients approach the limit
+
+\begin{equation}
+    \label{eqn:inf_lanczos}
+    a_\infty = \frac{\omega_+ + \omega_-}{2}\text{ and } b_\infty = \frac{\omega_+ - \omega_-}{4}\,,
+\end{equation}
+
+where $\omega_\pm$ represent the upper and lower band edge, respectively.
+This behaviour allows us to terminate the continued fraction, if the convergence is good enough, using the so-called square root terminator
+
+\begin{equation}
+    T(\omega) = \frac{1}{2b_\infty^2} \left( \omega - a_\infty \mp \sqrt{(\omega - a_\infty)^2 - 4 b_\infty^2} \right)\,,
+\end{equation}
+
+where the negative sign is to be chosen for $\omega - a_\infty > 2b_\infty$ and $|\omega - a_\infty| < 2b_\infty$ and the positive one otherwise.
 
@@
 
-...
+\subsection{SC-CDW transition}
+
+\subsection{CDW-AFM transition}
 

### 2023-11-24 paper/main.tex

@@
 \newcommand{\ddt}{\frac{\mathrm{d}}{\mathrm{d}t}}
+\newcommand{\dgamma}{\mathrm{d}\gamma}
 
@@
 \begin{equation}
-    \Delta_\text{SC} = \frac{U}{2N} \int \mathrm{d}\gamma \rho(\gamma) \langle f_{\gamma} \rangle\,.
+    \Delta_\text{SC} = \frac{U}{2N} \int \dgamma \rho(\gamma) \langle f_{\gamma} \rangle\,.
 \end{equation}
@@
 Here, the different matrix elements correspond to various Green's functions, depending on the operator basis.
-For example, assume the operator in the basis is $f_{\vk}$, then the top left element of $\mathcal{G}$ is the Green's function
+For instance, assume the operator in the basis is $f_{\vk}$, then the top left element of $\mathcal{G}$ is the Green's function
 
@@
 
+In this section, we will be investigating four different diagonal Green's functions $G_{AA}(\omega + i0^+)$, namely with
+
+\begin{subequations}
+    \label{eqn:resolvent_bases}
+    \begin{align}
+        A_\text{Higgs} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} + f_{vk}^\dagger \right)\,,\\
+        A_\text{Phase} &= \frac{i}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} - f_{vk}^\dagger \right)\,,\\
+        A_\text{CDW} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} + g_{\vk \down} \right)\,,\\
+        A_\text{AFM} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} - g_{\vk \down} \right)\,,
+    \end{align}
+\end{subequations}
+
+where $N$ is the number of lattice sites in the system. 
+Note, that this choice of normalization cancels out with other system size-dependent terms so that our final results do not depend on it at all.
+The first operator catches the amplitude mode of the $s$-wave superconducting state, while the second one catches the phase mode \cite{Fan22}.
+The remaining two capture the collective behaviour of the CDW and AFM states, respectively.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=.98\textwidth]{plots/resolvent_overview.pdf}
+    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
+    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
+    The left edge of the plots is at $-0.05$ rather than $0$ in order to improve the visibility of the phase peak.
+    The shaded area marks the two-particle continuum.
+    The panels (a), (b), and (c) show the spectral functions in the SC, CDW, and AFM phases, respectively.}
+    \label{fig:resolvent_overview}
+\end{figure*}
+
+Let us first show and discuss the general form of the spectral functions
+\begin{equation}
+    \mathcal{A}(\omega) = -\frac{1}{\pi} \Im \left[ \mathcal{G}(\omega + i0^+) \right]
+\end{equation}
+
+in various phases and afterward, we will describe the behaviour of the occurring modes as the system approaches a phase transition.
+\newline
+Firstly, all of the aforementioned operators are (anti-)Hermitian. Therefore, their commutator $[A^\dagger, A]$ vanishes.
+Thus, abiding by the sum rule $\int_{-\infty}^\infty \mathcal{A}_{AB} (\omega) \mathrm{d}\omega = \langle [A^\dagger, A] \rangle = 0$ \cite{rickayzen80},
+all spectral functions must be symmetrical about $\omega=0$. Therefore, we will only show the $\omega \geq 0$ in our plots.
+\newline
+Multiple spectral functions in the SC, CDW, and AFM phases are shown in \autoref{fig:resolvent_overview}.
+
 \subsection{SC-CDW transition}

### 2023-11-27 paper/main.tex
plotting

@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=.98\textwidth]{plots/resolvent_overview.pdf}
-    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
-    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
-    The left edge of the plots is at $-0.05$ rather than $0$ in order to improve the visibility of the phase peak.
-    The shaded area marks the two-particle continuum.
-    The panels (a), (b), and (c) show the spectral functions in the SC, CDW, and AFM phases, respectively.}
-    \label{fig:resolvent_overview}
-\end{figure*}
+\subsection{SC-CDW transition}
 
@@
 
-in various phases and afterward, we will describe the behaviour of the occurring modes as the system approaches a phase transition.
+in the SC and CDW phase and afterward, we will describe the behaviour of the occurring modes as the system approaches a phase transition.
 \newline
-Firstly, all of the aforementioned operators are (anti-)Hermitian. Therefore, their commutator $[A^\dagger, A]$ vanishes.
-Thus, abiding by the sum rule $\int_{-\infty}^\infty \mathcal{A}_{AB} (\omega) \mathrm{d}\omega = \langle [A^\dagger, A] \rangle = 0$ \cite{rickayzen80},
-all spectral functions must be symmetrical about $\omega=0$. Therefore, we will only show the $\omega \geq 0$ in our plots.
+Firstly, all of the operators mentioned in \eqref{eqn:resolvent_bases} are (anti-)Hermitian. 
+Therefore, their commutator $[A^\dagger, A]$ vanishes and, 
+abiding by the sum rule $\int_{-\infty}^\infty \mathcal{A}_{A^\dagger A} (\omega) \mathrm{d}\omega = \langle [A^\dagger, A] \rangle = 0$ \cite{rickayzen80},
+all spectral functions must be symmetrical about $\omega=0$. 
+For this reason, we will only show the $\omega \geq 0$ in our plots.
 \newline
-Multiple spectral functions in the SC, CDW, and AFM phases are shown in \autoref{fig:resolvent_overview}.
+The corresponding spectral functions in the SC and CDW phases are shown in \autoref{fig:resolvent_overview_SC}.
+We chose $U=-2$ for all plots and $V=\pm0.1$.
 
-\subsection{SC-CDW transition}
+\begin{figure*}
+    \centering
+    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_SC_CDW.pdf}
+    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
+    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
+    The left edge of the plots is at $-0.05$ rather than $0$ in order to improve the visibility of the phase peak.
+    The shaded area marks the two-particle continuum.
+    The panels (a), (b), and (c) show the spectral functions in the SC and CDW phases, respectively.}
+    \label{fig:resolvent_overview_SC}
+\end{figure*}
 
-\subsection{CDW-AFM transition}
+\subsection{AFM-CDW transition}
+
+Similar to the previous section, we will first show the general form of the spectral functions with respect to the operators \eqref{eqn:resolvent_bases}.
+They are depicted in \autoref{fig:resolvent_overview_AFM}, choosing $V=1$ for the square lattice and $V=0.5$ for the simple cubic lattice.
+For the CDW phase (panel a) we chose $V=4.1$ and for the AFM phase (panel b) $V=3.9$.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_AFM_CDW.pdf}
+    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
+    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
+    %The left edge of the plots is at $-0.05$ rather than $0$ in order to improve the visibility of the phase peak.
+    The shaded area marks the two-particle continuum.
+    The panels (a) and (b) show the spectral functions in the CDW and AFM phases, respectively.}
+    \label{fig:resolvent_overview_AFM}
+\end{figure*}
 

### 2023-11-27 paper/resolvent_overview_AFM_CDW.py

@@ -1,0 +1,74 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+import os, sys
+if os.name == "nt":
+    sys.path.append(os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + r"\python")
+else:
+    sys.path.append(os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + "/python")
+
+import lib.continued_fraction as cf
+from lib.iterate_containers import naming_scheme_tuples
+import lib.plot_settings as ps
+from lib.create_zoom import *
+
+prop_cycle = plt.rcParams['axes.prop_cycle']
+colors = prop_cycle.by_key()['color']
+
+params = [ [0., 4.1, 1.], [0., 3.9, 1.] ]
+
+use_XP = True
+
+folders = ["../data/modes/square/dos_3k/", "../data/modes/cube/dos_3k/"]
+nrows = 2
+ncols = 2
+# ax = axs[row][col]
+fig, axs = plt.subplots(nrows=nrows, ncols=ncols, figsize=(12.8, 6), sharey=True, sharex="col", gridspec_kw=dict(hspace=0, wspace=0))
+
+plotters = np.empty((nrows, ncols), dtype=ps.CURVEFAMILY)
+for i in range(nrows):
+    for j in range(ncols):
+        axs[i][j].set_ylim(0, 0.75)
+        plotters[i][j] = ps.CURVEFAMILY(4, axis=axs[i][j])
+        plotters[i][j].set_individual_colors("nice")
+        plotters[i][j].set_individual_linestyles(["-", "--", "-", "-"])
+
+plot_lower_lim = 0#-0.05
+plot_upper_lim = 5.2
+
+name_suffices = ["phase_SC", "higgs_SC", "CDW", "AFM"]
+labels = ["Phase", "Higgs", "CDW", "AFM"]
+
+for j, folder in enumerate(folders):
+    usage_upper_lim = 2 * plot_upper_lim if j == 0 else 2.7 * plot_upper_lim
+    if j == 1: 
+        # the sc lattice uses a different V for the CDW-AFM border due to the changed coordination number
+        params[1][2] = 0.5
+        params[0][2] = 0.5
+        
+    for i, name in enumerate(naming_scheme_tuples(params)):
+        for name_suffix, label in zip(name_suffices, labels):
[…]

### 2023-11-27 paper/resolvent_overview_SC_CDW.py
plotting

@@ -14,15 +14,15 @@ import lib.plot_settings as ps
 prop_cycle = plt.rcParams['axes.prop_cycle']
 colors = prop_cycle.by_key()['color']
 
-params = [ [0., -2., -0.1], [0., -2.0, 0.], [0., 4.1, 1.] ]
+params = [ [0., -2., -0.1], [0., -2.0, 0.] ]
 
 use_XP = True
 
 folders = ["../data/modes/square/dos_3k/", "../data/modes/cube/dos_3k/"]
-nrows = 3
+nrows = 2
 ncols = 2
 # ax = axs[row][col]
-fig, axs = plt.subplots(nrows=nrows, ncols=ncols, figsize=(12.8, 7.2), sharey=True, sharex="col", gridspec_kw=dict(hspace=0, wspace=0))
+fig, axs = plt.subplots(nrows=nrows, ncols=ncols, figsize=(12.8, 6), sharey=True, sharex="col", gridspec_kw=dict(hspace=0, wspace=0))
 
 plotters = np.empty((nrows, ncols), dtype=ps.CURVEFAMILY)
 for i in range(nrows):
@@ -33,21 +33,18 @@ for i in range(nrows):
         plotters[i][j].set_individual_linestyles(["-", "--", "-", "-"])
 
 plot_lower_lim = -0.05
-plot_upper_lim = 4.98
+plot_upper_lim = 4.1
 
 name_suffices = ["phase_SC", "higgs_SC", "CDW", "AFM"]
 labels = ["Phase", "Higgs", "CDW", "AFM"]
 
 for j, folder in enumerate(folders):
     usage_upper_lim = 2 * plot_upper_lim if j == 0 else 3 * plot_upper_lim
-    if j == 1: 
-        # the sc lattice uses a different V for the CDW-AFM border due to the changed coordination number
-        params[2][2] = 0.5
         
     for i, name in enumerate(naming_scheme_tuples(params)):
         for name_suffix, label in zip(name_suffices, labels):
             data, data_real, w_lin, res = cf.resolvent_data(f"{folder}{name}", name_suffix, plot_lower_lim, usage_upper_lim, 
-                                                            number_of_values=20000, xp_basis=use_XP, imaginary_offset=1e-6, messages=False)
[…]

### 2023-11-29 paper/main.tex
please dont die

@@
     \begin{align}
-        A_\text{Higgs} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} + f_{vk}^\dagger \right)\,,\\
-        A_\text{Phase} &= \frac{i}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} - f_{vk}^\dagger \right)\,,\\
+        A_\text{Higgs} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} + f_{\vk}^\dagger \right)\,,\\
+        A_\text{Phase} &= \frac{i}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} - f_{\vk}^\dagger \right)\,,\\
         A_\text{CDW} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} + g_{\vk \down} \right)\,,\\
@@
 Similar to the previous section, we will first show the general form of the spectral functions with respect to the operators \eqref{eqn:resolvent_bases}.
-They are depicted in \autoref{fig:resolvent_overview_AFM}, choosing $V=1$ for the square lattice and $V=0.5$ for the simple cubic lattice.
-For the CDW phase (panel a) we chose $V=4.1$ and for the AFM phase (panel b) $V=3.9$.
+They are depicted in \autoref{fig:resolvent_overview_AFM}, choosing $V=1$ for the square lattice and $V=0.75$ for the simple cubic lattice.
+For the CDW phase (panel a) we chose $U=ZV + 0.1$ and for the AFM phase (panel b) $V=ZV - 0.1$.
 

### 2023-11-29 paper/resolvent_overview_AFM_CDW.py

@@ -30,8 +30,8 @@ for i in range(nrows):
     for j in range(ncols):
         axs[i][j].set_ylim(0, 0.75)
         plotters[i][j] = ps.CURVEFAMILY(4, axis=axs[i][j])
-        plotters[i][j].set_individual_colors("nice")
-        plotters[i][j].set_individual_linestyles(["-", "--", "-", "-"])
+        plotters[i][j].set_individual_colors("nice2")
+        #plotters[i][j].set_individual_linestyles(["-", "--", "-", "-"])
 
 plot_lower_lim = 0#-0.05
 plot_upper_lim = 5.2
@@ -43,23 +43,30 @@ for j, folder in enumerate(folders):
     usage_upper_lim = 2 * plot_upper_lim if j == 0 else 2.7 * plot_upper_lim
     if j == 1: 
         # the sc lattice uses a different V for the CDW-AFM border due to the changed coordination number
-        params[1][2] = 0.5
-        params[0][2] = 0.5
+        params[0][2] = 0.75
+        params[1][2] = 0.75
+        params[0][1] = 4.6
+        params[1][1] = 4.4
         
     for i, name in enumerate(naming_scheme_tuples(params)):
-        for name_suffix, label in zip(name_suffices, labels):
+        for k, (name_suffix, label) in enumerate(zip(name_suffices, labels)):
             data, data_real, w_lin, res = cf.resolvent_data(f"{folder}{name}", name_suffix, plot_lower_lim, usage_upper_lim, 
                                                             number_of_values=20000, xp_basis=use_XP, imaginary_offset=1e-6, messages=False)
-            plotters[i][j].plot(w_lin, data, label=label)
+            if k % 2 == 1:
+                plotters[i][j].plot(w_lin, data, label=label, dashes=(5, 4))
+            else:
+                plotters[i][j].plot(w_lin, data, label=label)
             
             cont = np.sqrt(res.roots[0])
-            create_zoom(axs[i][j], 0.5, 0.05, 0.2, 0.9, (cont - 0.025, cont), ylim=(0, 0.35))
             
+        axins = create_zoom(axs[i][j], 0.4, 0.2, 0.3, 0.75, (cont - 0.02, cont), ylim=(0, 0.35), y_func=lambda x: -res.continued_fraction(x + 1e-6j).imag)  
         axs[i][j].set_xlim(plot_lower_lim, usage_upper_lim)
[…]

### 2023-11-29 paper/main.tex
uni

@@
 \begin{abstract}
-Abstract text Abstract text Abstract text Abstract text Abstract text Abstract text Abstract text 
+    We investigate the superconducting (SC), charge-density wave (CDW), and antiferromagnetic (AFM) phases 
+    in the extended Hubbard model at zero temperature and half-filling.
+    We employ the iterated equations of motion approach \cite{Kalthoff17,bleicker18} to compute the two-particle Green's functions and
+    by extension, the corresponding spectral densities.
+    This renders a comprehensive analysis of the behaviour of collective excitations possible
+    as the model's parameters are changed across phase transitions.
+    We identify the well-known amplitude (Higgs) and phase (Leggett) modes within the 
+    superconducting phase and observe a similar excitation in the CDW phase
+    which shift towards zero energy as the system approaches the phase transition to the SC phase.
+    In the CDW phase, close to the phase transition to the AFM phase, we find a collective mode 
+    which does not change significantly and another modes which becomes soft
+    as the phase boundary is approached.
 \end{abstract}
@@
 The remaining two capture the collective behaviour of the CDW and AFM states, respectively.
+\newline
+Note additionally, that all of the aforementioned operators are (anti-)Hermitian. 
+Therefore, their commutator $[A^\dagger, A]$ vanishes and, 
+abiding by the sum rule $\int_{-\infty}^\infty \mathcal{A}_{A^\dagger A} (\omega) \mathrm{d}\omega = \langle [A^\dagger, A] \rangle = 0$ \cite{rickayzen80},
+all spectral functions
 
-\subsection{SC-CDW transition}
-
-Let us first show and discuss the general form of the spectral functions
 \begin{equation}
@@
 
-in the SC and CDW phase and afterward, we will describe the behaviour of the occurring modes as the system approaches a phase transition.
-\newline
-Firstly, all of the operators mentioned in \eqref{eqn:resolvent_bases} are (anti-)Hermitian. 
-Therefore, their commutator $[A^\dagger, A]$ vanishes and, 
-abiding by the sum rule $\int_{-\infty}^\infty \mathcal{A}_{A^\dagger A} (\omega) \mathrm{d}\omega = \langle [A^\dagger, A] \rangle = 0$ \cite{rickayzen80},
-all spectral functions must be symmetrical about $\omega=0$. 
+must be symmetrical about $\omega=0$.
 For this reason, we will only show the $\omega \geq 0$ in our plots.
-\newline
-The corresponding spectral functions in the SC and CDW phases are shown in \autoref{fig:resolvent_overview_SC}.
-We chose $U=-2$ for all plots and $V=\pm0.1$.
+
+\subsection{SC-CDW transition}
 
@@
     The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
-    The left edge of the plots is at $-0.05$ rather than $0$ in order to improve the visibility of the phase peak.
+    The left edge of each plot is at $-0.05$ rather than $0$ in order to improve the visibility of the phase peak.
     The shaded area marks the two-particle continuum.
@@
 
+Let us first show and discuss the general form of the spectral functions in the SC and CDW phase and afterward, 
+we will describe the behaviour of the occurring modes as the system approaches a phase transition.
+\newline
+The spectral functions corresponding to the individual operators in \eqref{eqn:resolvent_bases} are shown in \autoref{fig:resolvent_overview_SC}.
+We chose $U=-2$ for the square lattice and $U=-2.5$ for the simple cubic lattice and $V=\pm0.1$ for both lattices.
+\newline
+There are a variety of different features. The difference between the two lattices is mostly quantitative in nature.
+First and foremost, in the SC phase, there is a sharp peak located at $\omega=0$, only in the phase spectral function,
+and another peak, only in the amplitude spectral function, located at $\omega=2\Delta_\text{SC}$.
+We identify them with the well-known Leggett and Higgs modes in superconductors.
+In the CDW phase, both of these spectral functions become identical and form a sharp peak below the two-particle continuum.
+\newline
+The CDW spectral function shows a peak below the continuum only in the SC phase, while having another peak at $\omega=2\Delta$ in the CDW phase.
+The AFM spectral function is restricted to the continuum for both phases and both lattices.
+For the square lattice, however, there is a peak located at the upper edge of the two-particle continuum.
+
+To further classify the aforementioned peak that lie outside the two-particle continuum,
+we turn towards the real part of the Green's function.
+We plot it in close proximity to the peaks with a double logarithmic scale and fit the result linearly to obtain.
+
+It is related to the imaginary part by the Kramers-Kronig relations.
+
 \subsection{AFM-CDW transition}
-
-Similar to the previous section, we will first show the general form of the spectral functions with respect to the operators \eqref{eqn:resolvent_bases}.
-They are depicted in \autoref{fig:resolvent_overview_AFM}, choosing $V=1$ for the square lattice and $V=0.75$ for the simple cubic lattice.
-For the CDW phase (panel a) we chose $U=ZV + 0.1$ and for the AFM phase (panel b) $V=ZV - 0.1$.
 
@@
 \end{figure*}
+
+Similar to the previous section, we will first show the general form of the spectral functions with respect to the operators \eqref{eqn:resolvent_bases}.
+They are depicted in \autoref{fig:resolvent_overview_AFM}, choosing $V=1$ for the square lattice and $V=0.75$ for the simple cubic lattice.
+For the CDW phase (panel a) we chose $U=ZV + 0.1$ and for the AFM phase (panel b) $V=ZV - 0.1$.
 

### 2023-12-01 paper/main.tex
Paper stuff

@@
 \usepackage{mhchem}
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 
-where $\omega_\pm$ represent the upper and lower band edge, respectively.
+where $\omega_\pm$ represents the upper and lower band edge, respectively.
 This behaviour allows us to terminate the continued fraction, if the convergence is good enough, using the so-called square root terminator
@@
 \section{Results}\label{sec:results}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_SC_CDW.pdf}
+    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
+    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
+    The left edge of each plot is at $-0.05$ rather than $0$ in order to improve the visibility of the phase peak.
+    The shaded area marks the two-particle continuum.
+    The panels (a), (b), and (c) show the spectral functions in the SC and CDW phases, respectively.}
+    \label{fig:resolvent_overview_SC}
+\end{figure*}
 
@@
 For this reason, we will only show the $\omega \geq 0$ in our plots. 
+Additionally, we will add a small imaginary part of $10^{-5}$ to $\omega$ in order to visualize the occurring $\delta$ peaks.
 
 \subsection{SC-CDW transition}
-
-\begin{figure*}
-    \centering
-    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_SC_CDW.pdf}
-    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
-    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
-    The left edge of each plot is at $-0.05$ rather than $0$ in order to improve the visibility of the phase peak.
-    The shaded area marks the two-particle continuum.
-    The panels (a), (b), and (c) show the spectral functions in the SC and CDW phases, respectively.}
-    \label{fig:resolvent_overview_SC}
-\end{figure*}
 
@@
 \newline
-The CDW spectral function shows a peak below the continuum only in the SC phase, while having another peak at $\omega=2\Delta$ in the CDW phase.
+The CDW spectral function shows a peak below the continuum only in the SC phase while having another peak at $\omega=2\Delta$ in the CDW phase.
 The AFM spectral function is restricted to the continuum for both phases and both lattices.
@@
 
-To further classify the aforementioned peak that lie outside the two-particle continuum,
+\begin{figure}
+    \centering
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{plots/phase_peak.pdf}
+        \caption{Phase Green's function}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{plots/cdw_peak_in_sc.pdf}
+        \caption{CDW Green's function}
+    \end{subfigure}
+    \caption{Log-log plot of the real part of the phase (a) and CDW (b) Green's functions in the SC phase.
+    The results for both lattice types are shown but are qualitatively identical.
+    The power-law exponent is $a=-2$ and $a=-1$, respectively, indicating that the CDW peak is a $\delta$ distribution, while the phase peak is the derivative of one.}
+    \label{fig:peaks_in_sc}
+\end{figure}
+
+To further classify the aforementioned peak that lies outside the two-particle continuum,
 we turn towards the real part of the Green's function.
-We plot it in close proximity to the peaks with a double logarithmic scale and fit the result linearly to obtain.
+We plot it in close proximity to the peaks with a double logarithmic scale and fit the result linearly to obtain its power-law behaviour.
+In practice, we use
 
-It is related to the imaginary part by the Kramers-Kronig relations.
+\begin{align}
+    \ln(\Re[\mathcal{G}](\omega - \omega_0 )) &= a \ln(\omega - \omega_0) + b \nonumber \\ 
+    \Leftrightarrow \Re[\mathcal{G}] (\omega) &= (\omega - \omega_0)^a e^b\,,
+\end{align}
+
+where $\omega_0$ is the peak's position and $a, b$ are fit parameters.
+The real part is related to the imaginary part via the Kramers-Kronig relations.
+Specifically, if the imaginary part is a $\delta$ distribution, the real part will be proportional to $1/\omega$, i.e. $a=-1$ and the peak has the weight $\exp(b)$.
+Furthermore, an exponent of $a=-2$ corresponds to the derivative of the $\delta$ distribution, i.e. $\delta'(\omega - \omega_0)$.
+
+The plots for the phase peak and the CDW peak in the SC phase can be seen in \autoref{fig:peaks_in_sc}.
+The SC peak in the CDW phase behaves similarly to the latter and is therefore not shown explicitly.
+We get a good agreement with the power-law behaviour near the peaks with the exponents $a=-2$ (phase) and $a=-1$ (CDW), respectively.
+Therefore, we conclude that the CDW peak corresponds to a $\delta$ distribution, while the phase peak is its derivative.
+Note, that the latter is located at $\omega=0$ of a perfectly asymmetrical bosonic spectral function and therefore must have 0 weight.
+This is given here, because $\int \delta'(\omega) \mathrm{d}\omega = 0$.
+The peak itself can be interpreted as two $\delta$ distributions at $0^\pm$.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.48\textwidth]{plots/higgs_peak.pdf}
+    \caption{Log-log plot of the Higgs spectral function near $\omega = \omega_0 = 2\Delta_\text{SC}$ in the SC phase.
+    We additionally plot the difference between the Higgs and the phase spectral functions and fit it, as we interpret the latter as a background within the two-particle continuum.
+    The upper (lower) panel shows the results for the square (simple cubic) lattice.
+    The spectral function behaves as $1 / \sqrt{\omega - \omega_0}$.}
+    \label{fig:higgs_peak}
+\end{figure}
+
+Next, we will investigate the Higgs peak. 
+Additionally, we see in \autoref{fig:resolvent_overview_SC} that the Higgs and phase spectral functions become indistinguishable towards the upper half of the two-particle continuum.
+Therefore, we interpret the latter as a background to the Higgs peak itself and compute the difference between both spectral functions.
+We plot the result double logarithmically and fit it again linearly, as seen in \autoref{fig:higgs_peak}.
+This time around, the exponent is $a\approx-0.5$, indicating that the peak behaves as $1 / \sqrt{\omega - \omega_0}$.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=.98\textwidth]{plots/sc_peak_in_cdw_position.pdf}
+    \caption{todo}
+    \label{fig:sc_in_cdw_behaviour}
+\end{figure*}
+
+With the prevalent peaks discussed, we turn towards their behaviour as the system approaches the phase transition at $V=0$.
 

### 2023-12-01 paper/phase_peak.py

@@ -1,0 +1,51 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+import os, sys
+if os.name == "nt":
+    sys.path.append(os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + r"\python")
+else:
+    sys.path.append(os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + "/python")
+import lib.continued_fraction as cf
+import lib.plot_settings as ps
+
+from scipy.optimize import curve_fit
+def func_ln(x, a, b):
+    return a * x + b
+
+T = 0.
+Us = [-2., -2.5]
+V = -0.1
+
+folders = ["../data/modes/square/dos_3k/", "../data/modes/cube/dos_3k/"]
+labels = ["Square", "Simple cubic"]
+name_suffix = "phase_SC"
+fig, axs = plt.subplots(nrows=2, figsize=(6.4, 4.8), sharex=True, gridspec_kw=dict(hspace=0, wspace=0))
+
+plotters = np.empty(2, dtype=ps.CURVEFAMILY)
+plot_lower_lim = 0.006
+plot_upper_lim = plot_lower_lim + 0.1
+
+for i in range(2):
+    plotters[i] = ps.CURVEFAMILY(4, axis=axs[i])
+    plotters[i].set_individual_colors("nice2")
+    plotters[i].set_individual_dashes()
+
+    name = f"T={T}/U={Us[i]}/V={V}"
+    data_imag, data, w_lin, res = cf.resolvent_data(f"{folders[i]}{name}", name_suffix, plot_lower_lim, plot_upper_lim, xp_basis=True, imaginary_offset=0, number_of_values=1000, messages=False)
+
+    w_log = np.log(w_lin.real)
+    plotters[i].plot(w_log, np.log(data), label=f"{labels[i]} data")
+    popt, pcov = curve_fit(func_ln, w_log, np.log(data))
+    plotters[i].plot(w_log, func_ln(w_log, *popt), label=f"{labels[i]} fit")
+    axs[i].legend()
+    axs[i].text(0.05, 0.4, f"$a={popt[0]:.4f}\pm{np.sqrt(pcov[0][0]):.4f}$", transform = axs[i].transAxes)
+    axs[i].text(0.05, 0.3, f"$b={popt[1]:.4f}\pm{np.sqrt(pcov[1][1]):.4f}$", transform = axs[i].transAxes)
+    
[…]

### 2023-12-01 paper/sc_peak_in_cdw_position.py

@@ -1,0 +1,110 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+import os, sys
+if os.name == "nt":
+    sys.path.append(os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + r"\python")
+else:
+    sys.path.append(os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + "/python")
+
+from lib.iterate_containers import *
+from lib.extract_key import *
+import lib.resolvent_peak as rp
+import lib.plot_settings as ps
+
+from scipy.optimize import curve_fit
+
+Ts = np.array([0.])
+Us = np.array([-2., -2.5])
+Vs = np.array(["50.0", "25.0", "15.0", "10.0", "8.0", "6.0", "4.0", "3.5", "3.0", "2.5", "2.0", "1.5", "1.4", "1.3",
+               "1.2", "1.1", "1.0", "0.9", "0.8", "0.7", "0.6", "0.5", 
+               "0.45", "0.4", "0.35", "0.3", "0.25", "0.2", "0.15",
+               "0.1", "0.07", "0.05", "0.04", "0.03", "0.02", "0.01", 
+               "0.007", "0.005", "0.004", "0.003", "0.002", "0.0015", "0.001", 
+               "0.0007", "0.0005", "0.0004", "0.0003", "0.0002", "0.00015", "0.0001", 
+               "0.00007", "0.00005", "0.00003"])
+v_data = np.log(np.array([float(v) for v in Vs]))
+
+folders = ["../data/modes/square/dos_3k/", "../data/modes/cube/dos_3k/"]
+element_names = ["a", "a+b", "a+ib"]
+
+name_suffix = "phase_SC"
+
+weights = np.zeros(len(Vs))
+peak_positions = np.zeros(len(Vs))
+fig, axs = plt.subplots(nrows=2, ncols=2, figsize=(12.8, 8.2), sharex=True, sharey="row", gridspec_kw=dict(hspace=0, wspace=0))
+
+plotters = np.empty((2,2), dtype=ps.CURVEFAMILY)
+
+for i in range(len(Us)):
+    counter = 0
+    plotters[0][i] = ps.CURVEFAMILY(3, axis=axs[0][i])
+    plotters[0][i].set_individual_colors("nice")
+    plotters[0][i].set_individual_linestyles(["-", "", ""])
[…]

### 2023-12-01 paper/cdw_peak_in_sc.py
Paper stuff

@@ -1,0 +1,50 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+import os, sys
+if os.name == "nt":
+    sys.path.append(os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + r"\python")
+else:
+    sys.path.append(os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + "/python")
+import lib.continued_fraction as cf
+import lib.plot_settings as ps
+import lib.resolvent_peak as rp
+
+T = 0.
+Us = [-2., -2.5]
+V = -0.1
+
+folders = ["../data/modes/square/dos_3k/", "../data/modes/cube/dos_3k/"]
+labels = ["Square", "Simple cubic"]
+name_suffix = "CDW"
+fig, axs = plt.subplots(nrows=2, figsize=(6.4, 4.8), sharex=True, gridspec_kw=dict(hspace=0, wspace=0))
+
+plotters = np.empty(2, dtype=ps.CURVEFAMILY)
+plot_lower_lim = 0.006
+plot_upper_lim = plot_lower_lim + 0.1
+
+for i in range(2):
+    plotters[i] = ps.CURVEFAMILY(4, axis=axs[i])
+    plotters[i].set_individual_colors("nice2")
+    plotters[i].set_individual_dashes()
+
+    name = f"T={T}/U={Us[i]}/V={V}"
+    peak = rp.Peak(f"{folders[i]}{name}", name_suffix, initial_search_bounds=(0.3, 0.8))
+    #print(peak.peak_position)
+    peak.improved_peak_position(x0_offset=1e-1, gradient_epsilon=1e-12)
+    popt, pcov, w_space, y_data = peak.fit_real_part(range=0.05, begin_offset=1e-10, reversed=False)
+    
+    axs[i].text(0.05, 0.4, f"$a={popt[0]:.4f}\pm{np.sqrt(pcov[0][0]):.4f}$", transform = axs[i].transAxes)
+    axs[i].text(0.05, 0.3, f"$b={popt[1]:.4f}\pm{np.sqrt(pcov[1][1]):.4f}$", transform = axs[i].transAxes)
+    plotters[i].plot(w_space, y_data, label=f"{labels[i]} data")
+    plotters[i].plot(w_space, rp.linear_function(w_space, *popt), "k--", label=f"{labels[i]} fit")
+    axs[i].set_ylim(0, 22.5)#
[…]

### 2023-12-01 paper/phase_peak_ln.py

@@ -1,55 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-
-import os, sys
-if os.name == "nt":
-    sys.path.append(os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + r"\python")
-else:
-    sys.path.append(os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + "/python")
-import lib.continued_fraction as cf
-import lib.plot_settings as ps
-
-from scipy.optimize import curve_fit
-def func_ln(x, a, b):
-    return a * x + b
-
-T = 0.
-Us = [-2., -2.5]
-V = -0.1
-use_xp = True
-
-folders = ["data/modes/square/dos_3k/", "data/modes/cube/dos_3k/"]
-labels = ["Square", "Simple cubic"]
-name_suffix = "phase_SC"
-fig, axs = plt.subplots(nrows=2, figsize=(6.4, 4.8), sharex=True)
-
-plotters = np.empty(2, dtype=ps.CURVEFAMILY)
-plot_lower_lim = 0.005
-plot_upper_lim = plot_lower_lim + 0.2
-
-for i in range(2):
-    plotters[i] = ps.CURVEFAMILY(4, axis=axs[0])
-    plotters[i].set_individual_colors("nice2")
-    plotters[i].set_individual_linestyles(["-", "--"])
-
-    name = f"T={T}/U={Us[i]}/V={V}"
-    data_imag, data, w_lin, res = cf.resolvent_data(f"{folders[i]}{name}", name_suffix, plot_lower_lim, plot_upper_lim, xp_basis=use_xp, imaginary_offset=0)
-
-    w_log = np.log(w_lin.real)
-    plotters[i].plot(w_log, np.log(data), label=f"{labels[i]} data")
-    popt, pcov = curve_fit(func_ln, w_log, np.log(data))
-    plotters[i].plot(w_log, func_ln(w_log, *popt), label=f"{labels[i]} fit")
-    axs[i].legend()
-    axs[i].text(0.05, 0.35, f"$a={popt[0]:.4f}\pm{np.sqrt(pcov[0][0]):.4f}$")
-    axs[i].text(0.05, 0.3, f"$b={popt[1]:.4f}\pm{np.sqrt(pcov[1][1]):.4f}$")
-    
-axs[0].set_xlabel(r"$\ln(\omega)$")
[…]

### 2023-12-01 paper/resolvent_overview_AFM_CDW.py

@@ -16,7 +16,6 @@ from lib.create_zoom import *
 # visually scale the data for visibility
 SCALE = 5
 params = [ [0., 4.1, 1.], [0., 3.9, 1.] ]
-use_XP = True
 
 folders = ["../data/modes/square/dos_3k/", "../data/modes/cube/dos_3k/"]
 nrows = 2
@@ -51,7 +50,7 @@ for j, folder in enumerate(folders):
         resolvents = np.empty(len(name_suffices), dtype=cf.ContinuedFraction)
         for k, (name_suffix, label) in enumerate(zip(name_suffices, labels)):
             data, data_real, w_lin, resolvents[k] = cf.resolvent_data(f"{folder}{name}", name_suffix, plot_lower_lim, usage_upper_lim, 
-                                                            number_of_values=5000, xp_basis=use_XP, imaginary_offset=1e-5, messages=False)
+                                                            number_of_values=5000, xp_basis=True, imaginary_offset=1e-5, messages=False)
             plotters[i][j].plot(w_lin, SCALE*data, label=label)
             
         cont = np.sqrt(resolvents[0].roots[0])
@@ -66,9 +65,9 @@ for j, folder in enumerate(folders):
 legend = axs[0][1].legend(loc='upper center', bbox_to_anchor=(0., 1.25), ncol=2, shadow=True)
 
 for i in range(ncols):
-    axs[nrows - 1][i].set_xlabel(r"$z / t$")
+    axs[nrows - 1][i].set_xlabel(r"$\omega / t$")
 for i in range(nrows):
-    axs[i][0].set_ylabel(r"$\mathcal{A}(\omega)$ / a.u.")
+    axs[i][0].set_ylabel(r"$\mathcal{A}(\omega + i0^+)$ / a.u.")
 axs[0][0].title.set_text("Square - $V=1$")
 axs[0][1].title.set_text("Simple cubic - $V=0.75$")
 

### 2023-12-04 paper/higgs_peak.py
Home

@@ -45,7 +45,7 @@ for i in range(2):
     axs[i].text(0.05, 0.3, f"$b={popt[1]:.4f}\pm{np.sqrt(pcov[1][1]):.4f}$", transform = axs[i].transAxes)
     plotters[i].plot(w_log, func(w_log, *popt), label="Fit")
 
-axs[0].legend("upper right")
+axs[0].legend(loc="upper right")
 
 axs[1].set_xlabel(r"$\ln((\omega - \omega_0) / t)$")
 axs[1].text(-0.08, 1, r"$\ln(-\Im \mathcal{G}_\mathrm{Higgs}(\omega - \omega_0 + i0^+))$", va='center', ha='center', rotation='vertical', transform = axs[1].transAxes)

### 2023-12-04 paper/main.tex
Home

@@
 \newcommand{\dgamma}{\mathrm{d}\gamma}
+
+\newcommand{\mM}{\mathcal{M}}
+\newcommand{\mN}{\mathcal{N}}
 
@@
         \ddt a(t) = \sum_j \ddt c_j(t) A_j &= i \sum_j c_j(t) [H, A_j] \\
-        \Rightarrow \sum_j \underbrace{(A_i | A_j)}_{:=\mathcal{N_{ij}}} \ddt c_j(t) &= i \sum_j \underbrace{(A_i | [H, A_j])}_{:=\mathcal{M_{ij}}} c_j(t) \\
-        \Rightarrow \mathcal{N} \ddt \vec{c}(t) &= i \mathcal{M} \vec{c}(t)\,.
+        \Rightarrow \sum_j \underbrace{(A_i | A_j)}_{:=\mN_{ij}} \ddt c_j(t) &= i \sum_j \underbrace{(A_i | [H, A_j])}_{:=\mM_{ij}} c_j(t) \\
+        \Rightarrow \mN \ddt \vec{c}(t) &= i \mM \vec{c}(t)\,.
     \end{aligned}
@@
 
-The matrices $\mathcal{N}$ and $\mathcal{M}$ contain all the dynamics and energetic properties of the system but have the significant advantage of being simple matrices rather than operators acting on an enormous Hilbert space.
+The matrices $\mN$ and $\mM$ contain all the dynamics and energetic properties of the system but have the significant advantage of being simple matrices rather than operators acting on an enormous Hilbert space.
 \newline
@@
 where the expectation values are taken with respect to the thermal equilibrium of the mean-field Hamiltonian \eqref{eqn:mf_hamiltonian}.
-Nevertheless, we will compute $\mathcal{M}$ using the full Hubbard Hamiltonian \eqref{eqn:full_hamiltonian} enabling us to capture collective behaviour rather than the one particle dynamics given by the mean-field approximation.
+Nevertheless, we will compute $\mM$ using the full Hubbard Hamiltonian \eqref{eqn:full_hamiltonian} enabling us to capture collective behaviour rather than the one particle dynamics given by the mean-field approximation.
 \newline
@@
     \label{eqn:green_function}
-    \mathcal{G}(z = \omega + i0^+) = \mathcal{N} \frac{1}{-z \mathcal{N} - \mathcal{M}} \mathcal{N} := -\mathcal{N} \mathcal{R}(z) \mathcal{N}\,,
+    \mathcal{G}(z = \omega + i0^+) = \mN \frac{1}{-z \mN - \mM} \mN := -\mN \mathcal{R}(z) \mN\,,
 \end{equation}
@@
     \label{eqn:resolvent}
-    \mathcal{R}(z) := \frac{1}{z \mathcal{N} + \mathcal{M}}\,.
+    \mathcal{R}(z) := \frac{1}{z \mN + \mM}\,.
 \end{equation}
@@
 \begin{equation}
-    \mathcal{M} = \begin{pmatrix}
+    \label{eqn:xp_basis}
+    \mM = \begin{pmatrix}
         \mathcal{K}_+ & \kappa \\ \kappa^\dagger & \mathcal{K}_-
-    \end{pmatrix}\,,\quad \mathcal{N} = \begin{pmatrix}
+    \end{pmatrix}\,,\quad \mN = \begin{pmatrix}
         \Lambda_+ & \mathcal{L} \\ \mathcal{L}^\dagger & \Lambda_-
@@
 
+\textcolor{red}{Die Festellung, dass die Peaks deltas bzw Ableitungen von deltas sind, könnte ich mir auch in einem Anhang vorstellen.}
 To further classify the aforementioned peak that lies outside the two-particle continuum,
@@
 where $\omega_0$ is the peak's position and $a, b$ are fit parameters.
-The real part is related to the imaginary part via the Kramers-Kronig relations.
+The real part is related to the imaginary part via the Kramers-Kronig relations. \textcolor{red}{Zitiert man die oder nimmt man an, dass jeder weiß, worum es da geht?}
 Specifically, if the imaginary part is a $\delta$ distribution, the real part will be proportional to $1/\omega$, i.e. $a=-1$ and the peak has the weight $\exp(b)$.
@@
     \includegraphics[width=.98\textwidth]{plots/sc_peak_in_cdw_position.pdf}
-    \caption{todo}
+    \caption{The upper panels show double logarithmic plots of the positions $\omega_0$ of the SC peak in the CDW phases while the lower panels show their respective weights $w_0 = e^{b}$.
+    The left column shows the results for the square lattice at $U=-2$ and the right column for the simple cubic lattice at $U=-2.5$.
+    The fits are linear, i.e. $y(V) = c \ln(V/t) + d$ and the parameters are printed on the individual panals.}
     \label{fig:sc_in_cdw_behaviour}
@@
 With the prevalent peaks discussed, we turn towards their behaviour as the system approaches the phase transition at $V=0$.
+\textcolor{red}{TODO; weiter beschreiben}
 
@@
 
+\appendix
+\section{Obtaining Green's functions from the iEoM-matrices}
+
+In this appendix section, we will derive the relation between the matrices $\mM, \mN$ from \eqref{eqn:heisenberg} and the Green's functions of the system.
+For that, consider their definition
+
+\begin{align}
+    G_{AB^\dagger}^\text{ret} (t) &= - i \langle [ A(t), B^\dagger(0) ] \rangle \theta(t) \nonumber \\ 
+    \Rightarrow G^\text{ret} (z = \omega + i0^+) &= - i \int_0^\infty \exp(izt) \langle [ A(t), B^\dagger(0) ] \rangle \mathrm{d}t \nonumber
+\end{align}
+
+Since $A$ and $B$ are included in the operator basis, we can rewrite them as dot-products of the vector
+\begin{equation}
+    \vec{A} := \left( A_1, A_2, \dots, A_N \right)\,, \quad
+    \vec{A}^\dagger := \begin{pmatrix}
+        A_1^\dagger \\ A_2^\dagger \\ \vdots \\ A_N^\dagger
+    \end{pmatrix}\,,
+\end{equation}
+
+and some other vector with complex-valued vector $\vec{a}$ which has its coefficients set in such a way,
+that $\vec{a} \cdot \vec{A}$ is equal to the desired operator. 
+For instance, $\vec{a} \equiv \vec{e}_1$ in order to represent $A_1$.
+Furthermore, assuming, that $\mN$ is invertible, we can easily solve the differential equation \eqref{eqn:heisenberg} to obtain
+
+\begin{equation}
+    \vec{c}(t) = \exp \left( i \mN^{-1} \mM t \right) \vec{c}(0)\,.
+\end{equation}
+
+This allows us to finally obtain
+
+\begin{align}
+    G^\text{ret} (z) &= i \int_0^\infty \exp(izt) \langle [ (\vec{A} \vec{b}(0))^\dagger, \vec{A} \vec{a}(t) ] \rangle\ \mathrm{d}t \nonumber \\
+        &= i \int_0^\infty \exp(izt) \vec{b}^\dagger(0) \underbrace{\langle [ \vec{A}^\dagger, \vec{A} ] \rangle}_{\equiv \mN} \vec{a}(t) \mathrm{d}t \nonumber \\
+        &= i  \int_0^\infty \vec{b}^\dagger(0) \mN \exp \left( i \left(\mN^{-1} \mM + z \right) t \right) \vec{a}(0) \mathrm{d}t  \nonumber \\
+        &= - \vec{b}^\dagger(0) \left[ \mN \frac{1}{\mN^{-1} \mM + z} \right] \vec{a}(0) \nonumber \\
+        &= - \vec{b}^\dagger(0) \left[ \mN \frac{1}{ \underbrace{\mM + z \mN}}_{\equiv \mathcal{R}(z)} \mN \right] \vec{a}(0)\,,
+\end{align}
+
+where $\vec{a}(0)$ and $\vec{b}(0)$ are chosen such, that their product with $\vec{A}$ yields $A(0)$ and $B(0)$, respectively.
+The task at hand is finding the resolvent as $\mathcal{R}$.
+Normally, one would desire to compute
+
+\begin{align}
+    \mathcal{R}(z) = \mN^{-1/2} \frac{1}{z +\mN^{-1/2} \mM \mN^{-1/2}} \mN^{-1/2}\,,
+\end{align}
+
+and then utilize a Lanczos algorithm to obtain a tridiagonal form of $\mN^{-1/2} \mM \mN^{-1/2}$.
+However, $\mN$ is not positive in our case due to the nature of the commutator, which means that $\mN$ cannot have a real square root.
+One could also fathom computing
+
+\begin{align}
+    \mathcal{R}(z) = \frac{1}{z} \mM^{-1/2} \frac{1}{\mM^{-1/2}\mathcal{N}\mM^{-1/2} + \frac{1}{z} } \mM^{-1/2}\,,
+\end{align}
+
+which does in fact work, if $\mM$ is positive, however resolving feature that lie near $z=0$ are difficult to resolve.
+Nevertheless, let us show that $\mathcal{M}$ is positive semidefinite if the system is in thermal equilibrium.
+For any $\vec{x} \in \mathbb{C}^N$, consider
+
+\begin{align}
+    \vec{x}^\dagger \mM \vec{x} &= \sum_{ij} x_i^* x_j \mM_{ij} \nonumber \\
+        &= \langle \left[ \sum_i x_i^* A_i^\dagger, \left[ H, \sum_j x_j A_j \right] \right]  \rangle \nonumber \\
+        &= \langle [B^\dagger, [H, B]] \rangle\,,\quad B := \sum_j x_j A_j\,.
+\end{align}
+
+Expanding the thermal expectation value $\langle O \rangle = \frac{1}{Z} \Trace [\exp(-\beta H_\text{MF}) O]$, where $\beta$ is the inverse temperature and $Z$ the partition function, and the commutators, we obtain
+
+\begin{widetext}
+    \begin{align}
+        \langle [B^\dagger, [H, B]] \rangle &= \frac{1}{Z} \Trace [\exp(-\beta H) [B^\dagger, [H, B]]] \nonumber \\
+            &= \frac{1}{Z} \sum_j e^{-\beta \epsilon_j} \bra{\psi_j} [B^\dagger, [H, B]] \ket{\psi_j} \nonumber \\
+            &= \frac{1}{Z} \sum_j e^{-\beta \epsilon_j} \left[ \bra{\psi_j} B^\dagger (H - \epsilon_j) B \ket{\psi_j} + \bra{\psi_j} B (H - \epsilon_j) B^\dagger \ket{\psi_j} \right] \nonumber \\
+            &= \frac{1}{Z} \sum_{ij} e^{-\beta \epsilon_j} \left[ \bra{\psi_j} B^\dagger \ket{\psi_i} (\epsilon_i - \epsilon_j) \bra{\psi_i} B \ket{\psi_j} + \bra{\psi_j} B \ket{\psi_i} (\epsilon_i - \epsilon_j) \bra{\psi_i} B^\dagger \ket{\psi_j} \right] \nonumber \\
+            &= \frac{1}{Z} \sum_{ij} e^{-\beta \epsilon_j} (\epsilon_i - \epsilon_j) \underbrace{ \left[ \bra{\psi_j} B^\dagger \ket{\psi_i} \bra{\psi_i} B \ket{\psi_j} + \bra{\psi_j} B \ket{\psi_i} \bra{\psi_i} B^\dagger \ket{\psi_j} \right]}_{:=C_{ij} = C_{ji} \geq 0} \nonumber \\
+            &= \frac{1}{2Z} \left[ \sum_{ij} C_{ij} e^{-\beta \epsilon_j} (\epsilon_i - \epsilon_j) - \sum_{ij} C_{ij} e^{-\beta \epsilon_i} (\epsilon_i - \epsilon_j) \right] \nonumber \\
+            &= \frac{1}{2Z} \sum_{ij} C_{ij} \left( e^{-\beta \epsilon_j} - e^{-\beta \epsilon_i} \right) \left( \epsilon_i - \epsilon_j \right) \geq 0\,.
+    \end{align}
+\end{widetext}
+
+Thus, we are able to compute a real square root of $\mathcal{M}$.
+
+We embrace the matrix structure in \eqref{eqn:xp_basis} and assume that all matrix entries are real.
+Then, with $m|_X$ denoting the block of a matrix $m$ spanned by the $X$-operators in the basis, we can calculate
+
+\begin{align}
+    r(z) &:= \mathcal{R}(z)|_X = \left. \frac{1}{\mM + z \mN} \right\vert_X \nonumber \\
+        &= \left[ \frac{1}{\mM} - \frac{1}{\mM} z \mN \frac{1}{\mM} + \frac{1}{\mM} z \mN \frac{1}{\mM} z \mN \frac{1}{\mM} - \cdots \right]_X \nonumber \\
+        &= \left. \frac{1}{\mM} \sum_{j=0}^\infty \left( -z \mN \frac{1}{\mM} \right)^j \right\vert_X \,.
+\end{align}
+
+We may omit every second element of the sum, as we want to obtain the upper left block of the matrix, and $\mN$ always swaps the upper left and lower right block.
+Thus, we obtain
+
+\begin{align}
+    r(z) &= \left. \frac{1}{\mM} \sum_{j=0}^\infty z^{2j} \left( \mN \frac{1}{\mM} \right)^{2j} \right\vert_X \nonumber \\
+        &= \left. \frac{1}{\mM - z^2 \mN \mM^{-1} \mN} \right\vert_X \nonumber \\
+        &= \frac{1}{\mathcal{K}_+ - z^2 \mathcal{L} \mathcal{K}_-^{-1} \mathcal{L}^\dagger}\,.
+\end{align}
+
+Next, we define $\mathcal{L} \mathcal{K}_-^{-1} \mathcal{L}^\dagger := \check{N}$ for brevity.
+Since $\mathcal{M}$ is positive semidefinite and block diagonal, its blocks $\mathcal{K}_\pm$ must be positive semidefinite as well.
+Therefore, $\check{N}$ is also positive semidefinite and we can define its square root.
+The inverse in the following can be replaced by the pseudo-inverse in case $\check{N}$ has a singular part.
+We obtain
+
+\begin{equation}
+    r(z) = \check{N}^{-1/2} \frac{1}{\check{N}^{-1/2} \mathcal{K}_+ \check{N}^{-1/2} - z^2} \check{N}^{-1/2}\,.
+\end{equation}
+
+The matrix $\check{M} := \check{N}^{-1/2} \mathcal{K}_+ \check{N}^{-1/2}$ is positive semidefinite and Hermitian by the previous arguments.
+Hence, we can tridiagonalize it using a standard Lanczos algorithm in order to obtain a continued fraction expansion.
+
 \bibliography{sn-bibliography}

### 2023-12-06 cpp/HubbardMeanField/sources/Hubbard/Helper/XPModes.cpp
wip

@@ -189,15 +189,15 @@ namespace Hubbard::Helper {
 			{
 #pragma omp section
 				{
-					resolvents[3 * i].compute(solver_matrix, LANCZOS_ITERATION_NUMBER);
+					resolvents[3 * i].computeWithReorthogonalization(solver_matrix, LANCZOS_ITERATION_NUMBER);
 				}
 #pragma omp section
 				{
-					resolvents[3 * i + 1].compute(solver_matrix, LANCZOS_ITERATION_NUMBER);
+					resolvents[3 * i + 1].computeWithReorthogonalization(solver_matrix, LANCZOS_ITERATION_NUMBER);
 				}
 #pragma omp section
 				{
-					resolvents[3 * i + 2].compute(solver_matrix, LANCZOS_ITERATION_NUMBER);
+					resolvents[3 * i + 2].computeWithReorthogonalization(solver_matrix, LANCZOS_ITERATION_NUMBER);
 				}
 			}
 		}

### 2023-12-06 cpp/HubbardMeanField/sources/Utility/GramSchmidt.hpp

@@ -1,0 +1,57 @@
+#pragma once
+#include <Eigen/Dense>
+#include <limits>
+#include <vector>
+#include "UnderlyingFloatingPoint.hpp"
+
+namespace Utility
+{
+    using std::abs;
+
+    template <typename DataType>
+    class GramSchmidt{
+		typedef Eigen::Vector<DataType, Eigen::Dynamic> vector_t;
+
+        inline static vector_t projection(const vector_t& from, const vector_t& to) {
+            // This function is only called with normalized vectors
+            return from.dot(to) * to;
+        };
+    public:
+        static vector_t& orthogonalizeSingleVector(vector_t& vector, const std::vector<vector_t>& basis){
+            for (size_t j = 0U; j < basis.size(); ++j)
+            {
+                vector -= projection(vector, basis[j]);
+            }
+            return vector;
+        };
+
+        static std::vector<vector_t> compute(const std::vector<vector_t>& vectors){
+            auto buffer = vectors;
+            buffer.front().normalize();
+            for (size_t i = 1U; i < vectors.size(); ++i)
+            {
+                buffer[i] = vectors[i];
+                for (size_t j = 0U; j < i; ++j)
+                {
+                    buffer[i] -= projection(buffer[i], buffer[j]);
+                }
+                buffer[i].normalize();
+            }
+
+            return buffer;
+        };
+
+        static std::vector<vector_t>& compute_and_overwrite(std::vector<vector_t>& vectors){
+            vectors.front().normalize();
+            for (size_t i = 1U; i < vectors.size(); ++i)
+            {
+                for (size_t j = 0U; j < i; ++j)
+                {
+                    vectors[i] -= projection(vectors[i], vectors[j]);
+                }
+                vectors[i].normalize();
+            }
+            return vectors;
+        };
+    };
+} 

### 2023-12-06 cpp/HubbardMeanField/sources/Utility/Resolvent.hpp

@@ -3,6 +3,7 @@
 #define assertm(exp, msg) assert(((void)msg, exp))
 
 #include "OutputConvenience.hpp"
+#include "GramSchmidt.hpp"
 #include <type_traits>
 #include <Eigen/Dense>
 #include <cmath>
@@ -394,6 +395,103 @@ namespace Utility {
 			}
 			data.push_back(std::move(res));
 		};
+		
+		// Computes the resolvent for a Hermitian problem (i.e. the symplectic matrix is the identity)
+		// Additionally, this function orthogonalizes the Krylov basis each step
+		void computeWithReorthogonalization(const matrix_t& toSolve, int maxIter, double errorMargin = 1e-10)
+		{
+			const size_t matrixSize = toSolve.rows();
+
+			if (toSolve.rows() != toSolve.cols()) {
+				std::cerr << "Matrix is not square!" << std::endl;
+				throw;
+			}
+
+			vector_t currentSolution(matrixSize); // corresponds to |q_(i+1)>
+			// First filling
+			std::vector<vector_t> basisVectors;
+			vector_t second = this->startingState; // corresponds to |q_1>
+			resolvent_data res;
+			res.b_i.push_back(second.squaredNorm());
+
+			second /= sqrt(res.b_i.back());
+			basisVectors.push_back(second);
+
+			std::vector<RealType> deltas, gammas;
+			gammas.push_back(1);
+
+			RealVector eigenDelta(1);
+			RealVector eigenGamma(1);
+
+			Eigen::SelfAdjointEigenSolver<matrix_t> diagonalize;
+			RealVector diagonal; //stores the diagonal elements in a vector
+			RealType oldEigenValue{};
+			RealType newEigenValue{};
+			size_t position{};
+			size_t iterNum{};
+			bool goOn = true;
+			vector_t buffer;
+
+			while (goOn) {
+				// algorithm
+				buffer = toSolve * basisVectors.back();
+				if constexpr (isComplex) {
+					// This has to be real, as <x|H|x> is always real if H=H^+
+					deltas.push_back(basisVectors.back().dot(buffer).real());
+				}
+				else {
+					deltas.push_back(basisVectors.back().dot(buffer));
+				}
+				if (iterNum > 0U) {
+					currentSolution = (buffer - (deltas.back() * basisVectors.back())) - (gammas.back() * basisVectors[iterNum]);
+				} else {
[…]

### 2023-12-06 paper/phase_diagram.py
wip

@@ -6,35 +6,28 @@ fig, axs = plt.subplots(nrows=2, sharex=True, figsize=(6.4, 9))
 ############################################################################
 ############                  Square lattice                    ############
 ############################################################################
-micnas_d = np.loadtxt("../data/micnas_d_wave.csv").transpose()
-axs[0].plot(micnas_d[0], micnas_d[1], "k-")
-axs[0].plot(np.array([0, 2]), 0.25 * np.array([0, 2]), "k-")
-axs[0].plot(np.array([-2, 0]),        np.array([0, 0]), "k-")
-
 #Shade s-wave area
-common_x = np.linspace(-2, 0, 100)
-interpol = np.interp(common_x, micnas_d[0], micnas_d[1])
-axs[0].fill_between(common_x, np.zeros(100), interpol, color="blue", alpha=.5, label="$s$-wave")
-
-#Shade d-wave area
-axs[0].fill_between(micnas_d[0], micnas_d[1], -2 * np.ones(len(micnas_d[0])), color="red", alpha=.5, label="$d_{x^2 - y^2}$-wave")
+axs[0].fill_between([-2, 0], [0, 0], [-2, -2], color="blue", alpha=.5, label="$s$-wave")
 
 #Shade AFM area
-common_x = np.linspace(0, 2, 100)
-interpol = np.interp(common_x, micnas_d[0], micnas_d[1])
-axs[0].fill_between(common_x, .25 * common_x, interpol, color="green", alpha=.5, label="AFM")
+axs[0].fill_between([0, 2], [0, .5], [-2, -2], color="green", alpha=.5, label="AFM")
 
 #Shade CDW area
-axs[0].fill_between(np.array([-2, 0, 2]), np.array([0, 0, 0.5]), np.array([2, 2, 2]), color="orange", alpha=.5, label="CDW")
+axs[0].fill_between(np.array([-2, 0, 2]), np.array([0, 0, .5]), np.array([2, 2, 2]), color="orange", alpha=.5, label="CDW")
 
+#Shade d-wave area
+#axs[0].fill_between(micnas_d[0], micnas_d[1], -2 * np.ones(len(micnas_d[0])), color="red", alpha=.5, label="$d_{x^2 - y^2}$-wave")
+
+#Plot boundaries
+micnas_d = np.loadtxt("../data/micnas_d_wave.csv").transpose()
+axs[0].plot(micnas_d[0], micnas_d[1], "k--", label="$d_{x^2 - y^2}$-boundary")
[…]

### 2023-12-06 paper/main.tex
wip

@@
 \usepackage{mhchem}
-\usepackage{caption}
-\usepackage{subcaption}
 
@@
 % Preliminary title
-\title{Collective excitations in the 2- and 3-dimensional extended Hubbard model}
+\title{Collective excitations in competing phases in two and three dimensions}
 
@@
 encouraging the model's usage for the description of high-temperature superconductivity \cite{yang89}.
-Shortly afterward, an exact $SO(4)$ symmetry was discovered,
+Shortly afterward, an exact SO(4) symmetry was discovered,
 which allows a degeneracy of superconductivity (SC) and a charge-density wave (CDW) governed by an attractive on-site interaction \cite{yang90}.
@@
 The previously mentioned SC and CDW phases map to different spin operators \cite{zitko15,lieb89}.
-\newline
+
 Many recent experimental and theoretical studies examined the driven systems in the hope of inducing superconductivity 
@@
 \cite{Micnas88,Micnas88b,Micnas89,Dzierzawa92,Kostyrko92,Eriksson95,Staudt00,Onari04,Toschi05,Brackett16,Paki19,romer20,Sushchyev22}.
-\newline
+
 In this paper, we will restrict ourselves to the half-filled Hubbard model, including an additional intersite interaction, on a square and a simple cubic lattice.
@@
 \cite{Micnas88b,Tsuchiura95,Su01,Su04,ha11,Huang13,Jiang22}.
-\newline
+
 In this article, we will first employ a mean-field approximation to the interaction terms 
@@
 The prominent examples in the SC phase are the well-known phase (Leggett) and amplitude (Higgs) modes \cite{Cea14,Krull16,Schwarz20,Fan22}.
-\newline
+
 The remainder of this paper is organized as follows:
@@
 \section{Model and mean-field theory}\label{sec:model}
+
+\subsection{Model}
+
+\textcolor{red}{Schreiben wie cool das Hubbard Model ist}
 
@@
 \end{equation}
-
-where $c_{i\sigma}^{(\dagger)}$ annihilates (creates) an electron with spin $\sigma$ on lattice site $i$ and $\langle i, j\rangle$ denotes the summation over next neighbours.
+where $c_{i\sigma}^{(\dagger)}$ annihilates (creates) an electron with spin $\sigma$ on lattice site $i$ 
+and $\langle i, j\rangle$ denotes the summation over next neighbours.
 The parameters are the hopping amplitude $t$, the onsite interaction $U$, the intersite interaction $V$ and the chemical potential $\mu$.
-Throughout this article, we will give all energy-related quantities in terms of the hopping amplitude, which we subsequently set to unity $t=1$.
 Applying a Fourier transformation into $k$-space yields the single-particle dispersion 
-
 \begin{equation}
@@
 with the system's dimension $D$ and the dimensionless momentum $\vk$.
-The interaction terms are then mean-field decoupled. 
-We follow the naming scheme of Ref. \cite{sentef17}
 
+\subsection{Static mean-field theory}
+
+Next, we decouple the the interaction terms.
+We define 
 \begin{equation}
@@
     \begin{aligned}
-        n_{k\sigma} &:= c_{\vk\sigma}^\dagger c_{\vk\sigma}\,,      &f_k     &:= c_{-\vk\down} c_{\vk\up}\,, \\
-        g_{k\sigma} &:= c_{\vk\sigma}^\dagger c_{\vk+\vQ\sigma}\,,  &\eta_k  &:= c_{-\vk-\vQ\down} c_{\vk\up}\,,
+        n_{k\sigma} &\coloneqq  c_{\vk\sigma}^\dagger c_{\vk\sigma}\,,      &f_k     &\coloneqq  c_{-\vk\down} c_{\vk\up}\,, \\
+        g_{k\sigma} &\coloneqq  c_{\vk\sigma}^\dagger c_{\vk+\vQ\sigma}\,,  &\eta_k  &\coloneqq  c_{-\vk-\vQ\down} c_{\vk\up}\,,
     \end{aligned}
 \end{equation}
-
-where $\vQ := (\pi, ...)$ defines the nesting vector for the CDW and AFM phases.
+where $\vQ \coloneqq  (\pi, ...)$ defines the nesting vector for the CDW and AFM phases, see Ref. \cite{sentef17}.
 We use the following abbreviations to write down the mean-field parameters
-
 \begin{subequations}
@@
         \label{eqn:delta_cdw}
-        \Delta_\text{CDW} &= \left(\frac{U}{2N} - \frac{ZV}{N}\right) \sum_{\vk\sigma} \langle g_{\vk\sigma} \rangle\,, \\
+        \Delta_\text{CDW} &= \left(\frac{U}{2N} - \frac{zV}{N}\right) \sum_{\vk\sigma} \langle g_{\vk\sigma} \rangle\,, \\
         \label{eqn:delta_afm}
@@
 \end{subequations}
-
-where $Z$ denotes the coordination number of the lattice.
-The last parameter, $\Delta_n$, renormalizes the hoping term to
-
+where $z$ denotes the coordination number of the lattice.
+The last parameter, $\Delta_n$, renormalizes the hopping term to
 \begin{equation}
-    \epsilon( \vk ) := -(2 + \Delta_n) \sum_{\alpha=1}^D \cos(k_\alpha)\,.
+    \epsilon( \vk ) \coloneqq  -(2 + \Delta_n) \sum_{\alpha=1}^D \cos(k_\alpha)\,.
 \end{equation}
-
 In total, we obtain the mean-field Hamiltonian in spinor representation as
-
 \begin{equation}
@@
 \end{equation}
-
 with the spinors
 \begin{equation}
-    \Psi^\dagger (\vk) := \left( c_{\vk\up}^\dagger\,, c_{\kplusQ\up}^\dagger\,, c_{-\vk\down}\,, c_{\kminusQ\down} \right)
+    \Psi^\dagger (\vk) \coloneqq  \left( c_{\vk\up}^\dagger\,, c_{\kplusQ\up}^\dagger\,, c_{-\vk\down}\,, c_{\kminusQ\down} \right)
 \end{equation}
-
 and 
-
-\begin{widetext}
 \begin{equation}
-    h(\vk) := \begin{pmatrix}
-        \epsilon (\vk) & \Delta_\text{CDW}^* - \Delta_\text{AFM}^* & \Delta_\text{SC} & \Delta_\eta \\
-        \Delta_\text{CDW} - \Delta_\text{AFM} & \epsilon (\vk + \vQ) & \Delta_\eta & \Delta_\text{SC} \\
-        \Delta_\text{SC}^* & \Delta_\eta^* & - \epsilon (-\vk) & - \Delta_\text{CDW} - \Delta_\text{AFM} \\
-        \Delta_\eta^* & \Delta_\text{SC}^* & - \Delta_\text{CDW}^* - \Delta_\text{AFM}^* & - \epsilon (-\vk - \vQ)\,.
-        \end{pmatrix}
+    h(\vk) \coloneqq  \begin{pmatrix}
+        \epsilon (\vk) & \Delta_-^* & \Delta_\text{SC} & \Delta_\eta \\
+        \Delta_- & \epsilon (\vk + \vQ) & \Delta_\eta & \Delta_\text{SC} \\
+        \Delta_\text{SC}^* & \Delta_\eta^* & - \epsilon (-\vk) & - \Delta_+ \\
+        \Delta_\eta^* & \Delta_\text{SC}^* & - \Delta_+^* & - \epsilon (-\vk - \vQ)
+        \end{pmatrix}\,,
 \end{equation}
-\end{widetext}
+where we defined $\Delta_\pm \coloneqq  \Delta_\text{CDW} \pm \Delta_\text{AFM}$.
 
@@
     \includegraphics[width=.48\textwidth]{plots/phase_diagram.pdf}
-    \caption{The phase diagram obtained for the extended Hubbard model on (a) a square lattice and (b) a simple cubic lattice using a mean-field approximation at temperature $T=0$.
-    The CDW-AFM boundary lies at $U = ZV$, where $Z$ is the coordination number. For $U<0$ and $V=0$, there is a coexistence of CDW and $s$-wave SC.
-    The boundary for the $d_{x^2 - y^2}$-wave SC for the square lattice has been taken from Ref. \cite{Micnas88b}, as it is not accessible using our formalism.}
+    \caption{The phase diagram obtained for the extended Hubbard model on 
+    (a) a square lattice and (b) a simple cubic lattice using a mean-field approximation at temperature $T=0$.
+    The CDW-AFM boundary lies at $U = zV$, where $z$ is the coordination number. 
+    For $U<0$ and $V=0$, there is a coexistence of CDW and $s$-wave SC.
+    The boundary for the $d_{x^2 - y^2}$-wave SC (dashed line) for the square lattice has been taken from Ref. \cite{Micnas88b}, 
+    as it is not accessible using our formalism.}
     \label{fig:phase_diagram}
@@
 
-Now, the entire Hamiltonian and thus all expectation values only depend on
+We observe that the entire Hamiltonian and thus all expectation values only depend on
 \begin{equation}
-    \hat{\gamma}(\vk) := \sum_{\alpha=1}^D \cos(k_\alpha)\,,
+    \hat{\gamma}(\vk) \coloneqq \frac{1}{D} \sum_{\alpha=1}^D \cos(k_\alpha)\,,
 \end{equation}
-i.e. for any operator $O$ the following relation holds 
+i.e., for any operator $\hat{O}$ the following relation holds 
 \begin{equation}
     \label{eqn:equal_expecs}
-    \langle O_{\vk} \rangle = \langle O_{\vk'} \rangle =: \langle O_{\gamma} \rangle\,,
+    \langle \hat{O}_{\vk} \rangle = \langle \hat{O}_{\vk'} \rangle \eqqcolon \langle \hat{O}_{\gamma} \rangle\,,
 \end{equation}
 if $\hat{\gamma}(\vk) = \hat{\gamma}(\vk')$.
-This allows us to replace the momentum sums with energy integrals using the bare density of states
+While two-dimensional systems around the size of $100\times100$ lattice sites can still be solved by using momentum sums,
+computing solutions for large three-dimensional systems becomes impossible due to the $N=L^3$ scaling.
+This issue can be resolved by using the aforementioned fact and replacing the momentum sums with energy integrals using the bare density of states (DOS)
 \begin{equation}
-    \rho(\gamma) := \frac{1}{N} \sum_{\vk} \delta \left(\gamma - \hat{\gamma} (\vk) \right)\,.
+    \rho(\gamma) \coloneqq  \frac{1}{N} \sum_{\vk} \delta \left(\gamma - \hat{\gamma} (\vk) \right)\,.
 \end{equation}
-As an example, consider 
+As an example, we consider 
 \begin{equation}
-    \Delta_\text{SC} = \frac{U}{2N} \int \dgamma \rho(\gamma) \langle f_{\gamma} \rangle\,.
+    \Delta_\text{SC} = \frac{U}{2N} \int_{-1}^{1} \dgamma \rho(\gamma) \langle f_{\gamma} \rangle\,.
 \end{equation}
 We will be using the exact densities of states for the square and the simple cubic lattice found in Ref. \cite{Hanisch97}.
-Solving the mean-field equations iteratively, one obtains the groundstate phase diagram at temperature $T=0$ as shown in \autoref{fig:phase_diagram}.
+This allows us to access both two- and three-dimensional models on equal footing.
+We can compute any phase as long as it does not introduce another kind of momentum dependence.
+
+We solve the mean-field equations self-consistently.
+The $\gamma$-integrals are approximated numerically using a $\tanh$-$\sinh$ quadrature \cite{takahasi73}, 
+terminating once $|1 - \int \dgamma \rho(\gamma)| < 10^{-13}$ and reusing the computed points and weights.
+This method excells at dealing with the singularities in the DOS, 
+requiring merely a few hundred function evaluations to achieve the desired accuracy.
+
+This procedure yields the groundstate phase diagram at temperature $T=0$ shown in \autoref{fig:phase_diagram}.
+The CDW-AFM boundary is located at $U = zV$, where $z$ is the coordination.
+This holds for both the square lattice ($z=4$) and the simple cubic lattice ($z=6$) and can be seen by comparing \eqref{eqn:delta_cdw} and \eqref{eqn:delta_afm}:
+Crossing the aforementioned line, changes which one of the two prefactors is larger.
+
 Note, that the $d_{x^2 - y^2}$-superconducting state, which has been confirmed for the square lattice \cite{Micnas88b,Huang13}, cannot be described by our method. 
 This is due to our restriction to terms that are proportional to $\hat{\gamma}(\vk)$.
-\newline
-The CDW-AFM boundary is located at $U = ZV$, where $Z$ is the coordination.
-This holds for both the square lattice ($Z=4$) and the simple cubic lattice ($Z=6$) and can be seen by comparing \eqref{eqn:delta_cdw} and \eqref{eqn:delta_afm}:
-Crossing the aforementioned line, changes which one of the two prefactors is larger.
 
@@
 We will present the general ideas briefly here and direct the interested reader to the appendix \textcolor{red}{!REF!} for a detailed explanation and derivation.
-\newline
+
 We start with some operator basis $\mathcal{B}$ that is complete with respect to commutation with a Hamiltonian $H$, 
-i.e. any commutator $[H, A]$ for any $A \in \mathcal{B}$ can be represented by linear combinations of operators in $\mathcal{B}$.
+i.e., any commutator $[H, A]$ for any $A \in \mathcal{B}$ can be represented by linear combinations of operators in $\mathcal{B}$.
 We can then express any time-depend operator from this basis as
-
 \begin{equation}
@@
 \end{equation}
-
 where $c_j(t)$ captures the entire time dependence. 
 Plugging this into the Heisenberg equation of motion and applying an operator scalar product $(A_i|\cdot)$ to both sides of the equation yields
-
 \begin{equation}
@@
         \ddt a(t) = \sum_j \ddt c_j(t) A_j &= i \sum_j c_j(t) [H, A_j] \\
-        \Rightarrow \sum_j \underbrace{(A_i | A_j)}_{:=\mN_{ij}} \ddt c_j(t) &= i \sum_j \underbrace{(A_i | [H, A_j])}_{:=\mM_{ij}} c_j(t) \\
+        \Rightarrow \sum_j \underbrace{(A_i | A_j)}_{\coloneqq \mN_{ij}} \ddt c_j(t) &= i \sum_j \underbrace{(A_i | [H, A_j])}_{\coloneqq \mM_{ij}} c_j(t) \\
         \Rightarrow \mN \ddt \vec{c}(t) &= i \mM \vec{c}(t)\,.
@@
 \end{equation}
+The matrices $\mN$ and $\mM$ contain all the dynamics and energetic properties of the system but have the significant advantage of being simple matrices rather than operators acting on an enormous Hilbert space.
 
-The matrices $\mN$ and $\mM$ contain all the dynamics and energetic properties of the system but have the significant advantage of being simple matrices rather than operators acting on an enormous Hilbert space.
-\newline
 However, most Hamiltonians do not allow any such operator basis to exist. 
@@
 In this article, we will be using the operator pseudo scalar product
-
 \begin{equation}
 \label{eqn:scalar_product}
-    (A | B) := \langle [A^\dagger, B] \rangle\,,
+    (A | B) \coloneqq  \langle [A^\dagger, B] \rangle\,,
 \end{equation}
-
 where the expectation values are taken with respect to the thermal equilibrium of the mean-field Hamiltonian \eqref{eqn:mf_hamiltonian}.
 Nevertheless, we will compute $\mM$ using the full Hubbard Hamiltonian \eqref{eqn:full_hamiltonian} enabling us to capture collective behaviour rather than the one particle dynamics given by the mean-field approximation.
-\newline
+
 This choice enables us to write down matrix-valued Fourier-transformed Green's functions in terms of the aforementioned matrices
-
 \begin{equation}
     \label{eqn:green_function}
-    \mathcal{G}(z = \omega + i0^+) = \mN \frac{1}{-z \mN - \mM} \mN := -\mN \mathcal{R}(z) \mN\,,
+    \mathcal{G}(z = \omega + i0^+) = \mN \frac{1}{-z \mN - \mM} \mN \coloneqq  -\mN \mathcal{R}(z) \mN\,,
 \end{equation}
-
 where we defined the resolvent
-
 \begin{equation}
     \label{eqn:resolvent}
-    \mathcal{R}(z) := \frac{1}{z \mN + \mM}\,.
+    \mathcal{R}(z) \coloneqq  \frac{1}{z \mN + \mM}\,.
 \end{equation}
-
 Here, the different matrix elements correspond to various Green's functions, depending on the operator basis.
 For instance, assume the operator in the basis is $f_{\vk}$, then the top left element of $\mathcal{G}$ is the Green's function 
-
 \begin{equation}
@@
 \end{equation}
-
 For a detailed derivation of this statement, we refer the reader to the appendix \textcolor{red}{!REF!}.
@@
 Our operator basis consists of operators of the type
-
 \begin{equation}
-    A_\gamma := \frac{1}{\sqrt{N}} \sum_{\vk} \delta (\gamma - \hat{\gamma}( \vk )) A_{\vk}\,,
+    A_\gamma \coloneqq  \frac{1}{\sqrt{N}} \sum_{\vk} \delta (\gamma - \hat{\gamma}( \vk )) A_{\vk}\,,
 \end{equation}
-
 where $A_{\vk}$ represents each type of operator in \eqref{eqn:operators} and their Hermitian conjugates.
@@
 We then order these operators in a way reminiscent of the $x$- and $p$-terms in the harmonic oscillator, i.e.
+\begin{equation}
+    X_i \coloneqq  A_i + A_i^\dagger\,,\quad P_i \coloneqq  A_i - A_i^\dagger\,.
+\end{equation}
+Our basis is then $\mathcal{B}_{XP} \coloneqq  {X_i, P_i}$.
+If some operators would be 0 ($P_i$ for any $n$-type term) or duplicates (certain $X_i$ for $g$-type terms), we omit them.
 
-\begin{equation}
-    X_i := A_i + A_i^\dagger\,,\quad P_i := A_i - A_i^\dagger\,.
-\end{equation}
-
-Our basis is then $\mathcal{B}_{XP} := {X_i, P_i}$.
-If some operators would be 0 ($P_i$ for any $n$-type term) or duplicates (certain $X_i$ for $g$-type terms), we omit them.
-\newline
 Due to this choice of basis, the matrices occurring in \eqref{eqn:heisenberg} have a special block structure
-
 \begin{equation}
@@
 \end{equation}
-
 where $\Im [\mathcal{K}_\pm] = \Re [\kappa] = 0$ and $\Re [\Lambda_\pm] = \Im [\mathcal{L}] = 0$.
@@
 Additionally, we can utilize this block structure to rewrite \eqref{eqn:resolvent} to
-
 \begin{equation}
-    \mathcal{R}(z) \vert_X = - \check{N}^{-1/2} \frac{1}{z^2 - \underbrace{\check{N}^{-1/2} \mathcal{K}_+ \check{N}^{-1/2}}_{:= \check{M}}} \check{N}^{-1/2}\,,
+    \mathcal{R}(z) \vert_X = - \check{N}^{-1/2} \frac{1}{z^2 - \underbrace{\check{N}^{-1/2} \mathcal{K}_+ \check{N}^{-1/2}}_{\coloneqq  \check{M}}} \check{N}^{-1/2}\,,
 \end{equation}
-
-where $\vert_X$ denotes the block corresponding to the $X$-terms in the basis and $\check{N} := \mathcal{L} \mathcal{K}_-^{-1} \mathcal{L}^\dagger$.
+where $\vert_X$ denotes the block corresponding to the $X$-terms in the basis and $\check{N} \coloneqq  \mathcal{L} \mathcal{K}_-^{-1} \mathcal{L}^\dagger$.
 An analogous form can be found for the $P$-block.
@@
 In the single-band case, the coefficients approach the limit
-
 \begin{equation}
@@
 \end{equation}
-
 where $\omega_\pm$ represents the upper and lower band edge, respectively.
 This behaviour allows us to terminate the continued fraction, if the convergence is good enough, using the so-called square root terminator
-
 \begin{equation}
@@
 \end{equation}
-
 where the negative sign is to be chosen for $\omega - a_\infty > 2b_\infty$ and $|\omega - a_\infty| < 2b_\infty$ and the positive one otherwise.
@@
 In this section, we will be investigating four different diagonal Green's functions $G_{AA}(\omega + i0^+)$, namely with
-
 \begin{subequations}
@@
 \end{subequations}
-
 where $N$ is the number of lattice sites in the system. 
@@
 The remaining two capture the collective behaviour of the CDW and AFM states, respectively.
-\newline
+
 Note additionally, that all of the aforementioned operators are (anti-)Hermitian. 
@@
 all spectral functions
-
 \begin{equation}
@@
 \end{equation}
-
 must be symmetrical about $\omega=0$.
@@
 we will describe the behaviour of the occurring modes as the system approaches a phase transition.
-\newline
+
 The spectral functions corresponding to the individual operators in \eqref{eqn:resolvent_bases} are shown in \autoref{fig:resolvent_overview_SC}.
 We chose $U=-2$ for the square lattice and $U=-2.5$ for the simple cubic lattice and $V=\pm0.1$ for both lattices.
-\newline
+
 There are a variety of different features. The difference between the two lattices is mostly quantitative in nature.
@@
 In the CDW phase, both of these spectral functions become identical and form a sharp peak below the two-particle continuum.
-\newline
+
 The CDW spectral function shows a peak below the continuum only in the SC phase while having another peak at $\omega=2\Delta$ in the CDW phase.
@@
 
+\centering
 \begin{figure}
     \centering
-    \begin{subfigure}{0.48\textwidth}
-        \includegraphics[width=\textwidth]{plots/phase_peak.pdf}
+    \includegraphics[width=0.48\textwidth]{plots/phase_peak.pdf}
     \caption{Phase Green's function}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.48\textwidth}
-        \includegraphics[width=\textwidth]{plots/cdw_peak_in_sc.pdf}
-        \caption{CDW Green's function}
-    \end{subfigure}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.48\textwidth]{plots/cdw_peak_in_sc.pdf}
     \caption{Log-log plot of the real part of the phase (a) and CDW (b) Green's functions in the SC phase.
@@
 In practice, we use
-
 \begin{align}
@@
 \end{align}
-
 where $\omega_0$ is the peak's position and $a, b$ are fit parameters.
 The real part is related to the imaginary part via the Kramers-Kronig relations. \textcolor{red}{Zitiert man die oder nimmt man an, dass jeder weiß, worum es da geht?}
-Specifically, if the imaginary part is a $\delta$ distribution, the real part will be proportional to $1/\omega$, i.e. $a=-1$ and the peak has the weight $\exp(b)$.
-Furthermore, an exponent of $a=-2$ corresponds to the derivative of the $\delta$ distribution, i.e. $\delta'(\omega - \omega_0)$.
+Specifically, if the imaginary part is a $\delta$ distribution, the real part will be proportional to $1/\omega$, i.e., $a=-1$ and the peak has the weight $\exp(b)$.
+Furthermore, an exponent of $a=-2$ corresponds to the derivative of the $\delta$ distribution, i.e., $\delta'(\omega - \omega_0)$.
 
@@
     The left column shows the results for the square lattice at $U=-2$ and the right column for the simple cubic lattice at $U=-2.5$.
-    The fits are linear, i.e. $y(V) = c \ln(V/t) + d$ and the parameters are printed on the individual panals.}
+    The fits are linear, i.e., $y(V) = c \ln(V/t) + d$ and the parameters are printed on the individual panals.}
     \label{fig:sc_in_cdw_behaviour}
@@
 They are depicted in \autoref{fig:resolvent_overview_AFM}, choosing $V=1$ for the square lattice and $V=0.75$ for the simple cubic lattice.
-For the CDW phase (panel a) we chose $U=ZV + 0.1$ and for the AFM phase (panel b) $V=ZV - 0.1$.
+For the CDW phase (panel a) we chose $U=zV + 0.1$ and for the AFM phase (panel b) $V=zV - 0.1$.
 
@@
 For that, consider their definition
-
 \begin{align}
@@
 \end{align}
-
 Since $A$ and $B$ are included in the operator basis, we can rewrite them as dot-products of the vector
 \begin{equation}
-    \vec{A} := \left( A_1, A_2, \dots, A_N \right)\,, \quad
-    \vec{A}^\dagger := \begin{pmatrix}
+    \vec{A} \coloneqq  \left( A_1, A_2, \dots, A_N \right)\,, \quad
+    \vec{A}^\dagger \coloneqq  \begin{pmatrix}
         A_1^\dagger \\ A_2^\dagger \\ \vdots \\ A_N^\dagger
@@
 \end{equation}
-
 and some other vector with complex-valued vector $\vec{a}$ which has its coefficients set in such a way,
@@
 Furthermore, assuming, that $\mN$ is invertible, we can easily solve the differential equation \eqref{eqn:heisenberg} to obtain
-
 \begin{equation}
@@
 \end{equation}
-
 This allows us to finally obtain
-
 \begin{align}
@@
 \end{align}
-
 where $\vec{a}(0)$ and $\vec{b}(0)$ are chosen such, that their product with $\vec{A}$ yields $A(0)$ and $B(0)$, respectively.
@@
 Normally, one would desire to compute
-
 \begin{align}
@@
 \end{align}
-
 and then utilize a Lanczos algorithm to obtain a tridiagonal form of $\mN^{-1/2} \mM \mN^{-1/2}$.
@@
 One could also fathom computing
-
 \begin{align}
@@
 \end{align}
-
 which does in fact work, if $\mM$ is positive, however resolving feature that lie near $z=0$ are difficult to resolve.
@@
 For any $\vec{x} \in \mathbb{C}^N$, consider
-
 \begin{align}
@@
         &= \langle \left[ \sum_i x_i^* A_i^\dagger, \left[ H, \sum_j x_j A_j \right] \right]  \rangle \nonumber \\
-        &= \langle [B^\dagger, [H, B]] \rangle\,,\quad B := \sum_j x_j A_j\,.
+        &= \langle [B^\dagger, [H, B]] \rangle\,,\quad B \coloneqq  \sum_j x_j A_j\,.
 \end{align}
-
 Expanding the thermal expectation value $\langle O \rangle = \frac{1}{Z} \Trace [\exp(-\beta H_\text{MF}) O]$, where $\beta$ is the inverse temperature and $Z$ the partition function, and the commutators, we obtain
@@
             &= \frac{1}{Z} \sum_{ij} e^{-\beta \epsilon_j} \left[ \bra{\psi_j} B^\dagger \ket{\psi_i} (\epsilon_i - \epsilon_j) \bra{\psi_i} B \ket{\psi_j} + \bra{\psi_j} B \ket{\psi_i} (\epsilon_i - \epsilon_j) \bra{\psi_i} B^\dagger \ket{\psi_j} \right] \nonumber \\
-            &= \frac{1}{Z} \sum_{ij} e^{-\beta \epsilon_j} (\epsilon_i - \epsilon_j) \underbrace{ \left[ \bra{\psi_j} B^\dagger \ket{\psi_i} \bra{\psi_i} B \ket{\psi_j} + \bra{\psi_j} B \ket{\psi_i} \bra{\psi_i} B^\dagger \ket{\psi_j} \right]}_{:=C_{ij} = C_{ji} \geq 0} \nonumber \\
+            &= \frac{1}{Z} \sum_{ij} e^{-\beta \epsilon_j} (\epsilon_i - \epsilon_j) \underbrace{ \left[ \bra{\psi_j} B^\dagger \ket{\psi_i} \bra{\psi_i} B \ket{\psi_j} + \bra{\psi_j} B \ket{\psi_i} \bra{\psi_i} B^\dagger \ket{\psi_j} \right]}_{\coloneqq C_{ij} = C_{ji} \geq 0} \nonumber \\
             &= \frac{1}{2Z} \left[ \sum_{ij} C_{ij} e^{-\beta \epsilon_j} (\epsilon_i - \epsilon_j) - \sum_{ij} C_{ij} e^{-\beta \epsilon_i} (\epsilon_i - \epsilon_j) \right] \nonumber \\
@@
 Then, with $m|_X$ denoting the block of a matrix $m$ spanned by the $X$-operators in the basis, we can calculate
-
 \begin{align}
-    r(z) &:= \mathcal{R}(z)|_X = \left. \frac{1}{\mM + z \mN} \right\vert_X \nonumber \\
+    r(z) &\coloneqq  \mathcal{R}(z)|_X = \left. \frac{1}{\mM + z \mN} \right\vert_X \nonumber \\
         &= \left[ \frac{1}{\mM} - \frac{1}{\mM} z \mN \frac{1}{\mM} + \frac{1}{\mM} z \mN \frac{1}{\mM} z \mN \frac{1}{\mM} - \cdots \right]_X \nonumber \\
@@
 \end{align}
-
 We may omit every second element of the sum, as we want to obtain the upper left block of the matrix, and $\mN$ always swaps the upper left and lower right block.
 Thus, we obtain
-
 \begin{align}
@@
 \end{align}
-
-Next, we define $\mathcal{L} \mathcal{K}_-^{-1} \mathcal{L}^\dagger := \check{N}$ for brevity.
+Next, we define $\mathcal{L} \mathcal{K}_-^{-1} \mathcal{L}^\dagger \coloneqq  \check{N}$ for brevity.
 Since $\mathcal{M}$ is positive semidefinite and block diagonal, its blocks $\mathcal{K}_\pm$ must be positive semidefinite as well.
@@
 We obtain
-
 \begin{equation}
@@
 \end{equation}
-
-The matrix $\check{M} := \check{N}^{-1/2} \mathcal{K}_+ \check{N}^{-1/2}$ is positive semidefinite and Hermitian by the previous arguments.
+The matrix $\check{M} \coloneqq  \check{N}^{-1/2} \mathcal{K}_+ \check{N}^{-1/2}$ is positive semidefinite and Hermitian by the previous arguments.
 Hence, we can tridiagonalize it using a standard Lanczos algorithm in order to obtain a continued fraction expansion.

### 2023-12-06 paper/main.tex
uni

@@
 In this article, we will first employ a mean-field approximation to the interaction terms 
-and then use the methodology from the so-called iterated equations of motion approach,
+and then use the methodology from the so-called iterated equations of motion approach (iEoM),
 which has already seen success in the handling of interaction quenches \cite{uhrig09,hamerla13,hamerla14,bleicker18}.
@@
 
-To investigate the collective modes, we employ the iterated equations of motion approach \cite{uhrig09,hamerla13,hamerla14,bleicker18}.
-We will present the general ideas briefly here and direct the interested reader to the appendix \textcolor{red}{!REF!} for a detailed explanation and derivation.
+So far we have discussed the static mean-field equations that essentially describe the static groundstate.
+These results will be used to compute the quantities, namely expectation values, necessary for the iterated equations of motion approach \cite{uhrig09,hamerla13,hamerla14,bleicker18}.
+With it, we can describe two-particle quantities like the various collective excitations of the system.
+We will present the general ideas briefly here and refer the interested reader to the appendix \textcolor{red}{!REF!} for a detailed explanation and derivation.
 
-We start with some operator basis $\mathcal{B}$ that is complete with respect to commutation with a Hamiltonian $H$, 
+We start with some operator set $\mathcal{B}$ that is complete with respect to commutation with a Hamiltonian $H$, 
 i.e., any commutator $[H, A]$ for any $A \in \mathcal{B}$ can be represented by linear combinations of operators in $\mathcal{B}$.
-We can then express any time-depend operator from this basis as
+We can then express any time-depend operator from this set as
 \begin{equation}
@@
 where $c_j(t)$ captures the entire time dependence. 
-Plugging this into the Heisenberg equation of motion and applying an operator scalar product $(A_i|\cdot)$ to both sides of the equation yields
+Inserting this into the Heisenberg equation of motion and applying an operator scalar product $(A_i|\cdot)$ to both sides of the equation yields
 \begin{equation}
@@
 \end{equation}
-The matrices $\mN$ and $\mM$ contain all the dynamics and energetic properties of the system but have the significant advantage of being simple matrices rather than operators acting on an enormous Hilbert space.
+The matrices $\mN$ and $\mM$ contain all the dynamics and energetic properties of the system.
+The advantage is that one can now handle simple matrices rather than operators acting on an enormous Hilbert space.
+The size of these matrices depends entirely on the set of operators.
 
-However, most Hamiltonians do not allow any such operator basis to exist. 
-Therefore, one repeats this commutation process and includes the occurring terms within a bigger basis,
-hoping to get better results as the basis size increases.
+However, most Hamiltonians do not allow any such operator set to exist as the commutation usually introduces terms of higher order.
+For instance, a commuting a bilinear term with a quartic Hamiltonian yields, quartic terms. Repeating the commutation yields hexartic ones and so on.
+Therefore, one repeats this commutation process and includes the occurring terms within a bigger set,
+hoping to get better results as the set size increases.
 
@@
 where the expectation values are taken with respect to the thermal equilibrium of the mean-field Hamiltonian \eqref{eqn:mf_hamiltonian}.
-Nevertheless, we will compute $\mM$ using the full Hubbard Hamiltonian \eqref{eqn:full_hamiltonian} enabling us to capture collective behaviour rather than the one particle dynamics given by the mean-field approximation.
+Note, that this is not a proper scalar product, as a norm defined using it can also be negative.
+For example, assume that for some operator $A$
+\begin{equation}
+    ||A|| = (A | A) = \langle [A^\dagger, A] \rangle > 0\,,
+\end{equation}
+then
+\begin{equation}
+    ||A^\dagger|| = (A^\dagger | A^\dagger) = \langle [A, A^\dagger] \rangle = - ||A|| < 0\,.
+\end{equation}
+We will compute $\mM$ by commutating with the full Hubbard Hamiltonian \eqref{eqn:full_hamiltonian} enabling us to capture collective behaviour rather than the one particle dynamics given by the mean-field approximation.
 
-This choice enables us to write down matrix-valued Fourier-transformed Green's functions in terms of the aforementioned matrices
+To study the collective excitation, we investigate various retarded Green's functions 
 \begin{equation}
+    G_{AB}^\text{ret} (t) = - i \langle [A(t), B] \rangle \Theta(t)\,,
+\end{equation}
+where $\Theta(t)$ is the Heaviside function, and their Fourier transformed
+\begin{equation}
+    \label{eqn:standard_gf}
+    G_{AB}(\omega + i0^+) = -i \int_0^{\infty} e^{izt} \langle [A(t), B] \rangle \mathrm{d}t\,.
+\end{equation}
+Our previous choice of pseudo scalar product enables us to write down a matrix-valued Green's functions in terms of the aforementioned matrices
+\begin{align}
     \label{eqn:green_function}
-    \mathcal{G}(z = \omega + i0^+) = \mN \frac{1}{-z \mN - \mM} \mN \coloneqq  -\mN \mathcal{R}(z) \mN\,,
-\end{equation}
-where we defined the resolvent
+    \mathcal{G}(z &= \omega + i0^+) = \mN \frac{1}{-z \mN - \mM} \mN \\
+        &\coloneqq  -\mN \mathcal{R}(z) \mN\,,
+\end{align}
+where we used the resolvent
 \begin{equation}
@@
 \end{equation}
-Here, the different matrix elements correspond to various Green's functions, depending on the operator basis.
-For instance, assume the operator in the basis is $f_{\vk}$, then the top left element of $\mathcal{G}$ is the Green's function 
+The entries of this matrix $\mathcal{G}(z)$ are the Fourier transformed Green's functions mentioned in \eqref{eqn:standard_gf} with respect to the operators from the initially chosen set.
+For instance, assume the operator in the set is $f_{\vk}$, then the top left element of $\mathcal{G}$ is the Green's function 
 \begin{equation}
@@
 
-Our operator basis consists of operators of the type
+Our operator set consists of operators of the type
 \begin{equation}
@@
 where $A_{\vk}$ represents each type of operator in \eqref{eqn:operators} and their Hermitian conjugates.
-Different indices are taken as additional basis operators, e.g. $n_{\vk \up}$ and $n_{\vk \down}$ are taken into the basis separately.
+Different indices are taken as additional set operators, e.g. $n_{\vk \up}$ and $n_{\vk \down}$ are taken into the set separately.
 We then order these operators in a way reminiscent of the $x$- and $p$-terms in the harmonic oscillator, i.e.
@@
 \end{equation}
-Our basis is then $\mathcal{B}_{XP} \coloneqq  {X_i, P_i}$.
+Our set is then $\mathcal{B}_{XP} \coloneqq  {X_i, P_i}$.
 If some operators would be 0 ($P_i$ for any $n$-type term) or duplicates (certain $X_i$ for $g$-type terms), we omit them.
 
-Due to this choice of basis, the matrices occurring in \eqref{eqn:heisenberg} have a special block structure
+Due to this choice of set, the matrices occurring in \eqref{eqn:heisenberg} have a special block structure
 \begin{equation}
-    \label{eqn:xp_basis}
+    \label{eqn:xp_set}
     \mM = \begin{pmatrix}
@@
 \end{equation}
-where $\vert_X$ denotes the block corresponding to the $X$-terms in the basis and $\check{N} \coloneqq  \mathcal{L} \mathcal{K}_-^{-1} \mathcal{L}^\dagger$.
+where $\vert_X$ denotes the block corresponding to the $X$-terms in the set and $\check{N} \coloneqq  \mathcal{L} \mathcal{K}_-^{-1} \mathcal{L}^\dagger$.
 An analogous form can be found for the $P$-block.
@@
     \left( z^2 - \begin{pmatrix}
-        z - a_0 & b_1 & 0 & 0 & \cdots \\
-        b_1 & z - a_1 & b_2 & 0 & \cdots \\
-        0 & b_2 & z - a_2 & b_3 & \cdots \\
+        a_0 & b_1 & 0 & 0 & \cdots \\
+        b_1 & a_1 & b_2 & 0 & \cdots \\
+        0 & b_2 & a_2 & b_3 & \cdots \\
         \vdots & \vdots & \vdots & \vdots & \ddots
@@
 The spectral functions corresponding to the individual operators in \eqref{eqn:resolvent_bases} are shown in \autoref{fig:resolvent_overview_SC}.
-We chose $U=-2$ for the square lattice and $U=-2.5$ for the simple cubic lattice and $V=\pm0.1$ for both lattices.
+We chose $U=-2.5$ and $V=\pm0.1$ for both lattices.
 
@@
 
-\centering
 \begin{figure}
@@
     \caption{The upper panels show double logarithmic plots of the positions $\omega_0$ of the SC peak in the CDW phases while the lower panels show their respective weights $w_0 = e^{b}$.
-    The left column shows the results for the square lattice at $U=-2$ and the right column for the simple cubic lattice at $U=-2.5$.
+    The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5$.
     The fits are linear, i.e., $y(V) = c \ln(V/t) + d$ and the parameters are printed on the individual panals.}
@@
 \end{align}
-Since $A$ and $B$ are included in the operator basis, we can rewrite them as dot-products of the vector
+Since $A$ and $B$ are included in the operator set, we can rewrite them as dot-products of the vector
 \begin{equation}
@@
 
-We embrace the matrix structure in \eqref{eqn:xp_basis} and assume that all matrix entries are real.
-Then, with $m|_X$ denoting the block of a matrix $m$ spanned by the $X$-operators in the basis, we can calculate
+We embrace the matrix structure in \eqref{eqn:xp_set} and assume that all matrix entries are real.
+Then, with $m|_X$ denoting the block of a matrix $m$ spanned by the $X$-operators in the set, we can calculate
 \begin{align}

### 2023-12-06 paper/higgs_peak.py

@@ -14,7 +14,7 @@ def func_ln(x, a, b):
     return a * x + b
 
 T = 0.
-Us = [-2., -2.5]
+U = -2.5
 V = -0.1
 
 folders = ["../data/modes/square/dos_3k/", "../data/modes/cube/dos_3k/"]
@@ -28,7 +28,7 @@ for i in range(2):
     plotters[i].set_individual_colors(["blue", "black", "orange"])
     plotters[i].set_individual_dashes([(1, 0), (1, 1), (5, 5)])
 
-    name = f"T={T}/U={Us[i]}/V={V}"
+    name = f"T={T}/U={U}/V={V}"
     phase_imag, phase_real, w_log, res = cf.resolvent_data_log_z(f"{folders[i]}{name}", "phase_SC", range=0.05, begin_offset=1e-3, number_of_values=10000, imaginary_offset=0, xp_basis=True, messages=False)
     higgs_imag, higgs_real, w_log, res = cf.resolvent_data_log_z(f"{folders[i]}{name}", "higgs_SC", range=0.05, begin_offset=1e-3, number_of_values=10000, imaginary_offset=0, xp_basis=True, messages=False)
 

### 2023-12-06 paper/phase_peak.py

@@ -14,7 +14,7 @@ def func_ln(x, a, b):
     return a * x + b
 
 T = 0.
-Us = [-2., -2.5]
+U = -2.5
 V = -0.1
 
 folders = ["../data/modes/square/dos_3k/", "../data/modes/cube/dos_3k/"]
@@ -31,7 +31,7 @@ for i in range(2):
     plotters[i].set_individual_colors("nice2")
     plotters[i].set_individual_dashes()
 
-    name = f"T={T}/U={Us[i]}/V={V}"
+    name = f"T={T}/U={U}/V={V}"
     data_imag, data, w_lin, res = cf.resolvent_data(f"{folders[i]}{name}", name_suffix, plot_lower_lim, plot_upper_lim, xp_basis=True, imaginary_offset=0, number_of_values=1000, messages=False)
 
     w_log = np.log(w_lin.real)

### 2023-12-06 paper/resolvent_overview_SC_CDW.py

@@ -13,7 +13,7 @@ import lib.plot_settings as ps
 
 # visually scale the data for visibility
 SCALE = 5
-params = [ [0., -2., -0.1], [0., -2.0, 0.1] ]
+params = [ [0., -2.5, -0.1], [0., -2.5, 0.1] ]
 
 folders = ["../data/modes/square/dos_3k/", "../data/modes/cube/dos_3k/"]
 nrows = 2
@@ -37,9 +37,7 @@ labels = ["Phase", "Higgs", "CDW", "AFM"]
 
 for j, folder in enumerate(folders):
     usage_upper_lim = 2 * plot_upper_lim if j == 0 else 3 * plot_upper_lim
-    if j == 1:
-        params[0][1] = -2.5
-        params[1][1] = -2.5
+
     for i, name in enumerate(naming_scheme_tuples(params)):
         for k, (name_suffix, label) in enumerate(zip(name_suffices, labels)):
             data, data_real, w_lin, res = cf.resolvent_data(f"{folder}{name}", name_suffix, plot_lower_lim, usage_upper_lim, 
@@ -51,11 +49,11 @@ for j, folder in enumerate(folders):
 
 legend = axs[0][1].legend(loc='upper center', bbox_to_anchor=(0., 1.25), ncol=2, shadow=True)
 for i in range(ncols):
-    axs[nrows - 1][i].set_xlabel(r"$\omega / t$")
+    axs[nrows - 1][i].set_xlabel(r"$\omega [t]$")
 for i in range(nrows):
-    axs[i][0].set_ylabel(r"$\mathcal{A}(\omega + i0^+)$ / a.u.")
-axs[0][0].title.set_text("Square - $U=-2$")
-axs[0][1].title.set_text("Simple cubic - $U=-2.5$")
+    axs[i][0].set_ylabel(r"$\mathcal{A}(\omega + i0^+) [t^{-1}]$")
+axs[0][0].title.set_text("Square")
+axs[0][1].title.set_text("Simple cubic")
 
 axs[0][1].text(10.6, 0.87, r"(a) SC")
 axs[1][1].text(10.6, 0.87, r"(b) CDW")

### 2023-12-06 paper/cdw_peak_in_sc.py
uni

@@ -11,7 +11,7 @@ import lib.plot_settings as ps
 import lib.resolvent_peak as rp
 
 T = 0.
-Us = [-2., -2.5]
+U = -2.5
 V = -0.1
 
 folders = ["../data/modes/square/dos_3k/", "../data/modes/cube/dos_3k/"]
@@ -28,7 +28,7 @@ for i in range(2):
     plotters[i].set_individual_colors("nice2")
     plotters[i].set_individual_dashes()
 
-    name = f"T={T}/U={Us[i]}/V={V}"
+    name = f"T={T}/U={U}/V={V}"
     peak = rp.Peak(f"{folders[i]}{name}", name_suffix, initial_search_bounds=(0.3, 0.8))
     #print(peak.peak_position)
     peak.improved_peak_position(x0_offset=1e-1, gradient_epsilon=1e-12)
@@ -41,7 +41,7 @@ for i in range(2):
     axs[i].set_ylim(0, 22.5)#
     axs[i].legend()
     
-axs[1].set_xlabel(r"$\ln(\omega - \omega_0)$")
+axs[1].set_xlabel(r"$\ln((\omega - \omega_0) / t)$")
 axs[1].text(-0.08, 1, r"$\ln(\Re[\mathcal{G}_\mathrm{CDW}](\omega - \omega_0))$", va='center', ha='center', rotation='vertical', transform = axs[1].transAxes)
 fig.tight_layout()
 

### 2023-12-07 paper/main.tex
xy

@@
     in the extended Hubbard model at zero temperature and half-filling.
-    We employ the iterated equations of motion approach \cite{Kalthoff17,bleicker18} to compute the two-particle Green's functions and
-    by extension, the corresponding spectral densities.
-    This renders a comprehensive analysis of the behaviour of collective excitations possible
-    as the model's parameters are changed across phase transitions.
-    We identify the well-known amplitude (Higgs) and phase (Leggett) modes within the 
-    superconducting phase and observe a similar excitation in the CDW phase
-    which shift towards zero energy as the system approaches the phase transition to the SC phase.
-    In the CDW phase, close to the phase transition to the AFM phase, we find a collective mode 
-    which does not change significantly and another modes which becomes soft
-    as the phase boundary is approached.
+    We employ the iterated equations of motion approach \cite{Kalthoff17,bleicker18} to compute the two-particle Green's functions and by extension, the corresponding spectral densities.
+    This renders comprehensive analysis of the behaviour of collective excitations possible as the model's parameters are changed across phase transitions.
+    We identify the well-known amplitude (Higgs) and phase (Leggett) modes within the superconducting phase and observe a similar excitation in the CDW phase which shifts towards zero energy as the system approaches the phase transition to the SC phase.
+    In the CDW phase, close to the phase transition to the AFM phase, we find a collective mode that does not change significantly and another mode that becomes soft as the phase boundary is approached.
 \end{abstract}
@@
 The remainder of this paper is organized as follows:
-In \autoref{sec:model} we will introduce the model and its Hamiltonian as well our mean-field theory.
-A brief overview over the iterated equations of motion approach is presented in \autoref{sec:ieom}.
+In \autoref{sec:model} we will introduce the model and its Hamiltonian as well as our mean-field theory.
+A brief overview of the iterated equations of motion approach is presented in \autoref{sec:ieom}.
 Next, we show our results in \autoref{sec:results}.
@@
 and $\langle i, j\rangle$ denotes the summation over next neighbours.
-The parameters are the hopping amplitude $t$, the onsite interaction $U$, the intersite interaction $V$ and the chemical potential $\mu$.
-Applying a Fourier transformation into $k$-space yields the single-particle dispersion 
+The parameters are the hopping amplitude $t$, the onsite interaction $U$, the intersite interaction $V$, and the chemical potential $\mu$.
+Applying a Fourier-transformation into $k$-space yields the single-particle dispersion 
 \begin{equation}
@@
 
-Next, we decouple the the interaction terms.
+Next, we decouple the interaction terms.
 We define 
@@
 terminating once $|1 - \int \dgamma \rho(\gamma)| < 10^{-13}$ and reusing the computed points and weights.
-This method excells at dealing with the singularities in the DOS, 
+This method excels at dealing with the singularities in the DOS, 
 requiring merely a few hundred function evaluations to achieve the desired accuracy.
 
-This procedure yields the groundstate phase diagram at temperature $T=0$ shown in \autoref{fig:phase_diagram}.
+This procedure yields the ground state phase diagram at temperature $T=0$ shown in \autoref{fig:phase_diagram}.
 The CDW-AFM boundary is located at $U = zV$, where $z$ is the coordination.
@@
 
-So far we have discussed the static mean-field equations that essentially describe the static groundstate.
+So far we have discussed the static mean-field equations that essentially describe the static ground state.
 These results will be used to compute the quantities, namely expectation values, necessary for the iterated equations of motion approach \cite{uhrig09,hamerla13,hamerla14,bleicker18}.
@@
 However, most Hamiltonians do not allow any such operator set to exist as the commutation usually introduces terms of higher order.
-For instance, a commuting a bilinear term with a quartic Hamiltonian yields, quartic terms. Repeating the commutation yields hexartic ones and so on.
+For instance, commuting a bilinear term with a quartic Hamiltonian yields, quartic terms. Repeating the commutation yields hexartic ones and so on.
 Therefore, one repeats this commutation process and includes the occurring terms within a bigger set,
@@
 \end{equation}
-where $\Theta(t)$ is the Heaviside function, and their Fourier transformed
+where $\Theta(t)$ is the Heaviside function, and their Fourier-transformed
 \begin{equation}
@@
 where $A_{\vk}$ represents each type of operator in \eqref{eqn:operators} and their Hermitian conjugates.
-Different indices are taken as additional set operators, e.g. $n_{\vk \up}$ and $n_{\vk \down}$ are taken into the set separately.
+Different indices are taken as additional set operators, e.g. $n_{\vk \up}$, and $n_{\vk \down}$ are taken into the set separately.
 We then order these operators in a way reminiscent of the $x$- and $p$-terms in the harmonic oscillator, i.e.
@@
 \end{equation}
-Our set is then $\mathcal{B}_{XP} \coloneqq  {X_i, P_i}$.
+Our set is then $\mathcal{B}_{XP} \coloneqq  \{ X_i, P_i \}$.
 If some operators would be 0 ($P_i$ for any $n$-type term) or duplicates (certain $X_i$ for $g$-type terms), we omit them.
@@
 
-There are a variety of different features. The difference between the two lattices is mostly quantitative in nature.
+There are a variety of different features. The difference between the two lattices is mostly quantitative.
 First and foremost, in the SC phase, there is a sharp peak located at $\omega=0$, only in the phase spectral function,
@@
     The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5$.
-    The fits are linear, i.e., $y(V) = c \ln(V/t) + d$ and the parameters are printed on the individual panals.}
+    The fits are linear, i.e., $y(V) = c \ln(V/t) + d$, and the parameters are printed on the individual panels.}
     \label{fig:sc_in_cdw_behaviour}

### 2023-12-07 paper/main.tex

@@
     \label{eqn:equal_expecs}
-    \langle \hat{O}_{\vk} \rangle = \langle \hat{O}_{\vk'} \rangle \eqqcolon \langle \hat{O}_{\gamma} \rangle\,,
+    \langle \hat{O}_{\vk} \rangle = \langle \hat{O}_{\vk'} \rangle \eqqcolon \langle \hat{O}( \gamma ) \rangle\,,
 \end{equation}
@@
 \begin{equation}
-    \Delta_\text{SC} = \frac{U}{2N} \int_{-1}^{1} \dgamma \rho(\gamma) \langle f_{\gamma} \rangle\,.
+    \Delta_\text{SC} = \frac{U}{2N} \int_{-1}^{1} \dgamma \rho(\gamma) \langle f( \gamma ) \rangle\,.
 \end{equation}
@@
 i.e., any commutator $[H, A]$ for any $A \in \mathcal{B}$ can be represented by linear combinations of operators in $\mathcal{B}$.
-We can then express any time-depend operator from this set as
+We can then express any time-dependent operator from this set as
 \begin{equation}
@@
 
-To study the collective excitation, we investigate various retarded Green's functions 
+We create our operator set on the basis of \eqref{eqn:equal_expecs}.
+It consists of operators of the type
+\begin{equation}
+    A_\gamma \coloneqq \frac{1}{\sqrt{N}} \sum_{\vk} \delta (\gamma - \hat{\gamma}( \vk )) A_{\vk}\,,
+\end{equation}
+where $A_{\vk}$ represents each type of operator in \eqref{eqn:operators} and their Hermitian conjugates.
+Operators with different indices are put into the set individually, e.g., $n_{\gamma \up}$, and $n_{\gamma \down}$ are distinct operators in our set.
+
+Naturally, we have to discretize $\gamma$, 
+however, this allows us to obtain good results with drastically smaller matrices compared to a momentum-based operator set and obtain results for a three-dimensional system in the first place.
+Practically, we choose $N_\gamma = 3000$ equally spaced discretization points.
+A detailed explanation of the numerics is provided in the appendix \textcolor{red}{!REF!}.
+
+Next, we order these operators in a way reminiscent of the $x$- and $p$-terms in the harmonic oscillator, i.e.,
+\begin{equation}
+    X_i \coloneqq  A_i + A_i^\dagger\,,\quad P_i \coloneqq  A_i - A_i^\dagger\,.
+\end{equation}
+Then, our set is given by $\mathcal{B}_{XP} \coloneqq \{ X_i, P_i \}$.
+If some operators would be 0 ($P_i$ for any $n$-type term) or duplicates (certain $X_i$ for $g$-type terms), we omit them.
+
+Due to this choice of set, the matrices occurring in \eqref{eqn:heisenberg} have a special block structure
+\begin{equation}
+    \label{eqn:xp_set}
+    \mM = \begin{pmatrix}
+        \mathcal{K}_+ & \kappa \\ \kappa^\dagger & \mathcal{K}_-
+    \end{pmatrix}\,,\quad \mN = \begin{pmatrix}
+        \Lambda_+ & \mathcal{L} \\ \mathcal{L}^\dagger & \Lambda_-
+    \end{pmatrix}\,,
+\end{equation}
+where the upper block refers to all $X_i$ and the lower block to all $P_i$.
+Furthermore, due to symmetry, the relations $\Im [\mathcal{K}_\pm] = \Re [\kappa] = 0$ and $\Re [\Lambda_\pm] = \Im [\mathcal{L}] = 0$ hold.
+Thus, if all occurring expectation values are real, both matrices have large empty blocks.
+This condition is fulfilled for all cases investigated in this article.
+Additionally, the matrix $\mM$ is positive semidefinite if the system is in thermal equilibrium.
+We proof this statement in the appendix \textcolor{red}{!REF!}.
+
+To study the collective excitations, we investigate various retarded Green's functions 
 \begin{equation}
@@
 \end{equation}
-where $\Theta(t)$ is the Heaviside function, and their Fourier-transformed
+and their Fourier-transformed
 \begin{equation}
     \label{eqn:standard_gf}
-    G_{AB}(\omega + i0^+) = -i \int_0^{\infty} e^{izt} \langle [A(t), B] \rangle \mathrm{d}t\,.
+    G_{AB}(\omega + i0^+) = -i \int_0^{\infty} e^{izt} \langle [A(t), B] \rangle \mathrm{d}t\,,
 \end{equation}
+where $\Theta(t)$ is the Heaviside function.
 Our previous choice of pseudo scalar product enables us to write down a matrix-valued Green's functions in terms of the aforementioned matrices
@@
 \end{equation}
-The entries of this matrix $\mathcal{G}(z)$ are the Fourier transformed Green's functions mentioned in \eqref{eqn:standard_gf} with respect to the operators from the initially chosen set.
+The entries of this matrix $\mathcal{G}(z)$ are the Fourier-transformed Green's functions mentioned in \eqref{eqn:standard_gf} with respect to the operators from the initially chosen set.
 For instance, assume the operator in the set is $f_{\vk}$, then the top left element of $\mathcal{G}$ is the Green's function 
+\begin{align}
+    \mathcal{G}_{00}(z = \omega +i0^+) &=  G_{f_{\vk}(t) f_{\vk}^\dagger} (z) \nonumber \\
+        &= -i \int_0^{\infty} \langle [f_{\vk}(t), f_{\vk}^\dagger(0)] \rangle e^{izt} \mathrm{d}t\,.
+\end{align}
+
+In the following, we will derive this relation.
+For that, consider the Fourier-transformed Green's function \eqref{eqn:standard_gf} with respect to two operators $A$ and $B^\dagger$ that are included in our operator set
+\begin{align}
+    G_{AB^\dagger} (z) &= - i \int_0^\infty \exp(izt) \langle [ A(t), B^\dagger(0) ] \rangle \mathrm{d}t
+\end{align}
+Since $A$ and $B$ are included in the operator set, we can rewrite them as dot products of the vector
 \begin{equation}
-    \mathcal{G}_{00}(z = \omega +i0^+) =  G(z) = -i \int_0^{\infty} \langle [f_{\vk}(t), f_{\vk}^\dagger(0)] \rangle e^{izt} \mathrm{d}t\,.
-\end{equation}
-For a detailed derivation of this statement, we refer the reader to the appendix \textcolor{red}{!REF!}.
-
-Our operator set consists of operators of the type
-\begin{equation}
-    A_\gamma \coloneqq  \frac{1}{\sqrt{N}} \sum_{\vk} \delta (\gamma - \hat{\gamma}( \vk )) A_{\vk}\,,
-\end{equation}
-where $A_{\vk}$ represents each type of operator in \eqref{eqn:operators} and their Hermitian conjugates.
-Different indices are taken as additional set operators, e.g. $n_{\vk \up}$, and $n_{\vk \down}$ are taken into the set separately.
-We then order these operators in a way reminiscent of the $x$- and $p$-terms in the harmonic oscillator, i.e.
-\begin{equation}
-    X_i \coloneqq  A_i + A_i^\dagger\,,\quad P_i \coloneqq  A_i - A_i^\dagger\,.
-\end{equation}
-Our set is then $\mathcal{B}_{XP} \coloneqq  \{ X_i, P_i \}$.
-If some operators would be 0 ($P_i$ for any $n$-type term) or duplicates (certain $X_i$ for $g$-type terms), we omit them.
-
-Due to this choice of set, the matrices occurring in \eqref{eqn:heisenberg} have a special block structure
-\begin{equation}
-    \label{eqn:xp_set}
-    \mM = \begin{pmatrix}
-        \mathcal{K}_+ & \kappa \\ \kappa^\dagger & \mathcal{K}_-
-    \end{pmatrix}\,,\quad \mN = \begin{pmatrix}
-        \Lambda_+ & \mathcal{L} \\ \mathcal{L}^\dagger & \Lambda_-
+    \vec{A} \coloneqq  \left( A_1, A_2, \dots, A_N \right)\,, \quad
+    \vec{A}^\dagger \coloneqq  \begin{pmatrix}
+        A_1^\dagger \\ A_2^\dagger \\ \vdots \\ A_N^\dagger
     \end{pmatrix}\,,
 \end{equation}
-where $\Im [\mathcal{K}_\pm] = \Re [\kappa] = 0$ and $\Re [\Lambda_\pm] = \Im [\mathcal{L}] = 0$.
-Furthermore, if all occurring expectation values are real, both matrices have large empty blocks.
-This condition is fulfilled for all cases investigated in this article.
-Additionally, we can utilize this block structure to rewrite \eqref{eqn:resolvent} to
+and some other complex-valued vector $\vec{a}$ which has its coefficients set in such a way,
+that $\vec{a} \cdot \vec{A}$ is equal to the desired operator. 
+For instance, $\vec{a} \equiv \vec{e}_1$ in order to represent $A_1$.
+
+Furthermore, assuming, that $\mN$ is invertible, we can easily solve the differential equation \eqref{eqn:heisenberg} to obtain
 \begin{equation}
-    \mathcal{R}(z) \vert_X = - \check{N}^{-1/2} \frac{1}{z^2 - \underbrace{\check{N}^{-1/2} \mathcal{K}_+ \check{N}^{-1/2}}_{\coloneqq  \check{M}}} \check{N}^{-1/2}\,,
+    \vec{c}(t) = \exp \left( i \mN^{-1} \mM t \right) \vec{c}(0)\,.
 \end{equation}
-where $\vert_X$ denotes the block corresponding to the $X$-terms in the set and $\check{N} \coloneqq  \mathcal{L} \mathcal{K}_-^{-1} \mathcal{L}^\dagger$.
-An analogous form can be found for the $P$-block.
+This allows us to finally obtain
+\begin{align}
+    G_{AB^\dagger} (z) &= i \int_0^\infty \exp(izt) \langle [ (\vec{A \cdot} \vec{b}(0))^\dagger, \vec{A} \cdot \vec{a}(t) ] \rangle\ \mathrm{d}t \nonumber \\
+        &= i \int_0^\infty \exp(izt) \vec{b}^\dagger(0) \underbrace{\langle [ \vec{A}^\dagger, \vec{A} ] \rangle}_{\equiv \mN} \vec{a}(t) \mathrm{d}t \nonumber \\
+        &= i  \int_0^\infty \vec{b}^\dagger(0) \mN \exp \left( i \left(\mN^{-1} \mM + z \right) t \right) \vec{a}(0) \mathrm{d}t  \nonumber \\
+        &= - \vec{b}^\dagger(0) \left[ \mN \frac{1}{\mN^{-1} \mM + z} \right] \vec{a}(0) \nonumber \\
+        &= - \vec{b}^\dagger(0) \left[ \mN \frac{1}{ \underbrace{\mM + z \mN}}_{\equiv \mathcal{R}(z)} \mN \right] \vec{a}(0)\,,
+\end{align}
+where $\vec{a}(0)$ and $\vec{b}(0)$ are chosen such, that their product with $\vec{A}$ yields $A(0)$ and $B(0)$, respectively.
+The task at hand is finding the resolvent as $\mathcal{R}$.
+
+To do that, we embrace this matrix structure in \eqref{eqn:xp_set} and assume that all matrix entries are real.
+Then, with $\mathcal{R}|_X$ denoting the block of a matrix $\mathcal{R}$ corresponding to the $X$-operators, we can calculate
+\begin{align}
+    r(z) &\coloneqq  \mathcal{R}(z)|_X = \left. \frac{1}{\mM + z \mN} \right\vert_X \nonumber \\
+        &= \left[ \frac{1}{\mM} - \frac{1}{\mM} z \mN \frac{1}{\mM} + \frac{1}{\mM} z \mN \frac{1}{\mM} z \mN \frac{1}{\mM} - \cdots \right]_X \nonumber \\
+        &= \left. \frac{1}{\mM} \sum_{j=0}^\infty \left( -z \mN \frac{1}{\mM} \right)^j \right\vert_X \,.
+\end{align}
+We may omit every second element of the sum, as we want to obtain the upper left block of the matrix, and $\mN$ always swaps the upper left and lower right block.
+Thus, we obtain
+\begin{align}
+    r(z) &= \left. \frac{1}{\mM} \sum_{j=0}^\infty z^{2j} \left( \mN \frac{1}{\mM} \right)^{2j} \right\vert_X \nonumber \\
+        &= \left. \frac{1}{\mM - z^2 \mN \mM^{-1} \mN} \right\vert_X \nonumber \\
+        &= \frac{1}{\mathcal{K}_+ - z^2 \mathcal{L} \mathcal{K}_-^{-1} \mathcal{L}^\dagger}\,.
+\end{align}
+Next, we define $\check{N} \coloneqq \mathcal{L} \mathcal{K}_-^{-1} \mathcal{L}^\dagger$ for brevity.
+Since $\mathcal{M}$ is positive semidefinite and block diagonal, its blocks $\mathcal{K}_\pm$ must be positive semidefinite as well.
+Therefore, $\check{N}$ is also positive semidefinite and we can define its square root.
+We obtain
+\begin{equation}
+    r(z) = \check{N}^{-1/2} \frac{1}{\check{N}^{-1/2} \mathcal{K}_+ \check{N}^{-1/2} - z^2} \check{N}^{-1/2}\,.
+\end{equation}
+The matrix $\check{M} \coloneqq  \check{N}^{-1/2} \mathcal{K}_+ \check{N}^{-1/2}$ is positive semidefinite and Hermitian by the previous arguments.
+If $\check{N}$ has a singular part, the inverse can be replaced by the pseudo-inverse.
+The same calculation can be repeated by exchanging $X$ with $P$, yielding the relation for the remaining block.
 
@@
         0 & b_2 & a_2 & b_3 & \cdots \\
-        \vdots & \vdots & \vdots & \vdots & \ddots
+        0 & 0 & b_3 & a_3 & \ddots \\
+        \vdots & \vdots & \vdots & \ddots & \ddots
     \end{pmatrix} \right)_{00}^{-1} = \dfrac{1}{z^2 - a_0 - \dfrac{b_1^2}{z^2 - a_1 - \dfrac{b_2^2}{ z^2 - a_2 - \hdots}}}\,\,
@@
 \end{equation}
-where $\omega_\pm$ represents the upper and lower band edge, respectively.
-This behaviour allows us to terminate the continued fraction, if the convergence is good enough, using the so-called square root terminator
+where $\omega_\pm$ represents the upper and lower band edge, respectively \cite{PettiforRecursion}.
+This behaviour allows us to terminate the continued fraction, once the coefficients have converged close enough to these values, using the so-called square root terminator
 \begin{equation}
@@
 where the negative sign is to be chosen for $\omega - a_\infty > 2b_\infty$ and $|\omega - a_\infty| < 2b_\infty$ and the positive one otherwise.
+It is to be noted, that the coefficients start to drop off from this limit as more and more Lanczos iterations are performed \cite{ViswanathRecursion}.
+Therefore, we terminate the continued fraction with the aforementioned terminator at the coefficient pair that has the least deviation from $a_\infty$ and $b_\infty$.
 
@@
 
-In this section, we will be investigating four different diagonal Green's functions $G_{AA}(\omega + i0^+)$, namely with
+In this section, we will be investigating four different diagonal Green's functions $G_{AA^\dagger}(\omega + i0^+)$, namely with
 \begin{subequations}
@@
     \begin{align}
-        A_\text{Higgs} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} + f_{\vk}^\dagger \right)\,,\\
-        A_\text{Phase} &= \frac{i}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} - f_{\vk}^\dagger \right)\,,\\
-        A_\text{CDW} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} + g_{\vk \down} \right)\,,\\
-        A_\text{AFM} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} - g_{\vk \down} \right)\,,
+        A_\text{Higgs} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} + f_{\vk}^\dagger \right) \nonumber \\ 
+            &= \int_{-1}^{1} \rho(\gamma) \left( f(\gamma) + f^\dagger (\gamma) \right) \mathrm{d}\gamma \,,\\
+        A_\text{Phase} &= \frac{i}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} - f_{\vk}^\dagger \right) \nonumber \\ 
+            &= i \int_{-1}^{1} \rho(\gamma) \left( f(\gamma) - f^\dagger (\gamma) \right) \mathrm{d}\gamma \,,\\
+        A_\text{CDW} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} + g_{\vk \down} \right) \nonumber \\ 
+            &= \int_{-1}^{1} \rho(\gamma) \left( g_{\up}(\gamma) + g_{\down}(\gamma) \right) \mathrm{d}\gamma \,,\\
+        A_\text{AFM} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} - g_{\vk \down} \right) \nonumber \\ 
+            &= \int_{-1}^{1} \rho(\gamma) \left( g_{\up}(\gamma) - g_{\down}(\gamma) \right) \mathrm{d}\gamma \,,
     \end{align}
@@
 where $N$ is the number of lattice sites in the system. 
+Each one of these operators generates a different kind of collective mode.
+The first operator captures the amplitude mode of the $s$-wave superconducting state, while the second one catches the phase mode \cite{Fan22}.
+The remaining two capture the collective behaviour of the CDW and AFM states, respectively.
 Note, that this choice of normalization cancels out with other system size-dependent terms so that our final results do not depend on it at all.
-The first operator catches the amplitude mode of the $s$-wave superconducting state, while the second one catches the phase mode \cite{Fan22}.
-The remaining two capture the collective behaviour of the CDW and AFM states, respectively.
 
@@
 
-In this appendix section, we will derive the relation between the matrices $\mM, \mN$ from \eqref{eqn:heisenberg} and the Green's functions of the system.
-For that, consider their definition
-\begin{align}
-    G_{AB^\dagger}^\text{ret} (t) &= - i \langle [ A(t), B^\dagger(0) ] \rangle \theta(t) \nonumber \\ 
-    \Rightarrow G^\text{ret} (z = \omega + i0^+) &= - i \int_0^\infty \exp(izt) \langle [ A(t), B^\dagger(0) ] \rangle \mathrm{d}t \nonumber
-\end{align}
-Since $A$ and $B$ are included in the operator set, we can rewrite them as dot-products of the vector
-\begin{equation}
-    \vec{A} \coloneqq  \left( A_1, A_2, \dots, A_N \right)\,, \quad
-    \vec{A}^\dagger \coloneqq  \begin{pmatrix}
-        A_1^\dagger \\ A_2^\dagger \\ \vdots \\ A_N^\dagger
-    \end{pmatrix}\,,
-\end{equation}
-and some other vector with complex-valued vector $\vec{a}$ which has its coefficients set in such a way,
-that $\vec{a} \cdot \vec{A}$ is equal to the desired operator. 
-For instance, $\vec{a} \equiv \vec{e}_1$ in order to represent $A_1$.
-Furthermore, assuming, that $\mN$ is invertible, we can easily solve the differential equation \eqref{eqn:heisenberg} to obtain
-\begin{equation}
-    \vec{c}(t) = \exp \left( i \mN^{-1} \mM t \right) \vec{c}(0)\,.
-\end{equation}
-This allows us to finally obtain
-\begin{align}
-    G^\text{ret} (z) &= i \int_0^\infty \exp(izt) \langle [ (\vec{A} \vec{b}(0))^\dagger, \vec{A} \vec{a}(t) ] \rangle\ \mathrm{d}t \nonumber \\
-        &= i \int_0^\infty \exp(izt) \vec{b}^\dagger(0) \underbrace{\langle [ \vec{A}^\dagger, \vec{A} ] \rangle}_{\equiv \mN} \vec{a}(t) \mathrm{d}t \nonumber \\
-        &= i  \int_0^\infty \vec{b}^\dagger(0) \mN \exp \left( i \left(\mN^{-1} \mM + z \right) t \right) \vec{a}(0) \mathrm{d}t  \nonumber \\
-        &= - \vec{b}^\dagger(0) \left[ \mN \frac{1}{\mN^{-1} \mM + z} \right] \vec{a}(0) \nonumber \\
-        &= - \vec{b}^\dagger(0) \left[ \mN \frac{1}{ \underbrace{\mM + z \mN}}_{\equiv \mathcal{R}(z)} \mN \right] \vec{a}(0)\,,
-\end{align}
-where $\vec{a}(0)$ and $\vec{b}(0)$ are chosen such, that their product with $\vec{A}$ yields $A(0)$ and $B(0)$, respectively.
-The task at hand is finding the resolvent as $\mathcal{R}$.
-Normally, one would desire to compute
-\begin{align}
-    \mathcal{R}(z) = \mN^{-1/2} \frac{1}{z +\mN^{-1/2} \mM \mN^{-1/2}} \mN^{-1/2}\,,
-\end{align}
-and then utilize a Lanczos algorithm to obtain a tridiagonal form of $\mN^{-1/2} \mM \mN^{-1/2}$.
-However, $\mN$ is not positive in our case due to the nature of the commutator, which means that $\mN$ cannot have a real square root.
-One could also fathom computing
-\begin{align}
-    \mathcal{R}(z) = \frac{1}{z} \mM^{-1/2} \frac{1}{\mM^{-1/2}\mathcal{N}\mM^{-1/2} + \frac{1}{z} } \mM^{-1/2}\,,
-\end{align}
-which does in fact work, if $\mM$ is positive, however resolving feature that lie near $z=0$ are difficult to resolve.
 Nevertheless, let us show that $\mathcal{M}$ is positive semidefinite if the system is in thermal equilibrium.
@@
 
-We embrace the matrix structure in \eqref{eqn:xp_set} and assume that all matrix entries are real.
-Then, with $m|_X$ denoting the block of a matrix $m$ spanned by the $X$-operators in the set, we can calculate
-\begin{align}
-    r(z) &\coloneqq  \mathcal{R}(z)|_X = \left. \frac{1}{\mM + z \mN} \right\vert_X \nonumber \\
-        &= \left[ \frac{1}{\mM} - \frac{1}{\mM} z \mN \frac{1}{\mM} + \frac{1}{\mM} z \mN \frac{1}{\mM} z \mN \frac{1}{\mM} - \cdots \right]_X \nonumber \\
-        &= \left. \frac{1}{\mM} \sum_{j=0}^\infty \left( -z \mN \frac{1}{\mM} \right)^j \right\vert_X \,.
-\end{align}
-We may omit every second element of the sum, as we want to obtain the upper left block of the matrix, and $\mN$ always swaps the upper left and lower right block.
-Thus, we obtain
-\begin{align}
-    r(z) &= \left. \frac{1}{\mM} \sum_{j=0}^\infty z^{2j} \left( \mN \frac{1}{\mM} \right)^{2j} \right\vert_X \nonumber \\
-        &= \left. \frac{1}{\mM - z^2 \mN \mM^{-1} \mN} \right\vert_X \nonumber \\
-        &= \frac{1}{\mathcal{K}_+ - z^2 \mathcal{L} \mathcal{K}_-^{-1} \mathcal{L}^\dagger}\,.
-\end{align}
-Next, we define $\mathcal{L} \mathcal{K}_-^{-1} \mathcal{L}^\dagger \coloneqq  \check{N}$ for brevity.
-Since $\mathcal{M}$ is positive semidefinite and block diagonal, its blocks $\mathcal{K}_\pm$ must be positive semidefinite as well.
-Therefore, $\check{N}$ is also positive semidefinite and we can define its square root.
-The inverse in the following can be replaced by the pseudo-inverse in case $\check{N}$ has a singular part.
-We obtain
-\begin{equation}
-    r(z) = \check{N}^{-1/2} \frac{1}{\check{N}^{-1/2} \mathcal{K}_+ \check{N}^{-1/2} - z^2} \check{N}^{-1/2}\,.
-\end{equation}
-The matrix $\check{M} \coloneqq  \check{N}^{-1/2} \mathcal{K}_+ \check{N}^{-1/2}$ is positive semidefinite and Hermitian by the previous arguments.
-Hence, we can tridiagonalize it using a standard Lanczos algorithm in order to obtain a continued fraction expansion.
-
 \bibliography{sn-bibliography}

### 2023-12-11 cpp/HubbardMeanField/sources/Hubbard/Helper/GeneralBasis.cpp
asd

@@ -165,22 +165,24 @@ namespace Hubbard::Helper {
 		* 2 - CDW
 		* 3 - AFM
 		*/
-		const global_floating_type norm_factor = 1. / sqrt((global_floating_type)Constants::BASIS_SIZE);
+		const double norm_constant = this->usingDOS
+			? sqrt((2.0 * this->dos_dimension) / Constants::BASIS_SIZE)
+			: sqrt(1. / ((double)Constants::BASIS_SIZE));
 		std::vector<VectorCL> psis(NUMBER_OF_GREENSFUNCTIONS, VectorCL::Zero(TOTAL_BASIS));
 		for (int i = 0; i < Constants::BASIS_SIZE; i++)
 		{
-			psis[0](i* number_of_basis_terms) = norm_factor;
-			psis[0](i* number_of_basis_terms + 1) = norm_factor;
+			psis[0](i* number_of_basis_terms) = norm_constant;
+			psis[0](i* number_of_basis_terms + 1) = norm_constant;
 
-			psis[1](i* number_of_basis_terms) = norm_factor;
-			psis[1](i* number_of_basis_terms + 1) = -norm_factor;
+			psis[1](i* number_of_basis_terms) = norm_constant;
+			psis[1](i* number_of_basis_terms + 1) = -norm_constant;
 
 			if (number_of_basis_terms >= 6) {
-				psis[2](i* number_of_basis_terms + 4) = norm_factor;
-				psis[2](i* number_of_basis_terms + 5) = norm_factor;
+				psis[2](i* number_of_basis_terms + 4) = norm_constant;
+				psis[2](i* number_of_basis_terms + 5) = norm_constant;
 
-				psis[3](i* number_of_basis_terms + 4) = norm_factor;
-				psis[3](i* number_of_basis_terms + 5) = -norm_factor;
+				psis[3](i* number_of_basis_terms + 4) = norm_constant;
+				psis[3](i* number_of_basis_terms + 5) = -norm_constant;
 			}
 		}
 

### 2023-12-11 cpp/HubbardMeanField/sources/Hubbard/Helper/ModeHelper.cpp
asd

@@ -68,6 +68,19 @@ namespace Hubbard::Helper {
 		: number_of_basis_terms{ input.getInt("number_of_basis_terms") }, start_basis_at{ input.getInt("start_basis_at") },
 		usingDOS(input.getBool("use_DOS"))
 	{
+		if (this->usingDOS) {
+			const auto lattice = input.getString("lattice_type");
+			if (lattice == "square") {
+				this->dos_dimension = 2;
+			}
+			else if (lattice == "cube") {
+				this->dos_dimension = 3;
+			}
+			else {
+				std::cerr << "Did not recognize lattice type in ModeHelper!" << std::endl;
+				throw;
+			}
+		}
 		if (this->start_basis_at < 0) {
 			// We investigate the special x-p-basis
 			this->TOTAL_BASIS = Constants::BASIS_SIZE * 8;

### 2023-12-11 paper/main.tex
ssd
asd

@@
 \newcommand{\vk}{\vec{k}}
+\newcommand{\vl}{\vec{l}}
 \newcommand{\vQ}{\vec{Q}}
@@
 \begin{equation}
-    \Delta_\text{SC} = \frac{U}{2N} \int_{-1}^{1} \dgamma \rho(\gamma) \langle f( \gamma ) \rangle\,.
+    \Delta_\text{SC} = \frac{U}{N} \int_{-1}^{1} \dgamma \rho(\gamma) \langle f( \gamma ) \rangle\,.
 \end{equation}
@@
 The matrices $\mN$ and $\mM$ contain all the dynamics and energetic properties of the system.
+The former is referred to as a dynamical matrix while the latter is called a norm matrix.
 The advantage is that one can now handle simple matrices rather than operators acting on an enormous Hilbert space.
@@
 \begin{equation}
+    \label{eqn:ieom_basis_operator}
     A_\gamma \coloneqq \frac{1}{\sqrt{N}} \sum_{\vk} \delta (\gamma - \hat{\gamma}( \vk )) A_{\vk}\,,
@@
 \begin{align}
-    r(z) &\coloneqq  \mathcal{R}(z)|_X = \left. \frac{1}{\mM + z \mN} \right\vert_X \nonumber \\
+    r_X (z) &\coloneqq \mathcal{R}(z)|_X = \left. \frac{1}{\mM + z \mN} \right\vert_X \nonumber \\
         &= \left[ \frac{1}{\mM} - \frac{1}{\mM} z \mN \frac{1}{\mM} + \frac{1}{\mM} z \mN \frac{1}{\mM} z \mN \frac{1}{\mM} - \cdots \right]_X \nonumber \\
@@
 \begin{align}
-    r(z) &= \left. \frac{1}{\mM} \sum_{j=0}^\infty z^{2j} \left( \mN \frac{1}{\mM} \right)^{2j} \right\vert_X \nonumber \\
+    r_X (z) &= \left. \frac{1}{\mM} \sum_{j=0}^\infty z^{2j} \left( \mN \frac{1}{\mM} \right)^{2j} \right\vert_X \nonumber \\
         &= \left. \frac{1}{\mM - z^2 \mN \mM^{-1} \mN} \right\vert_X \nonumber \\
@@
 \begin{equation}
-    r(z) = \check{N}^{-1/2} \frac{1}{\check{N}^{-1/2} \mathcal{K}_+ \check{N}^{-1/2} - z^2} \check{N}^{-1/2}\,.
+    r_X (z) = -\check{N}^{-1/2} \frac{1}{z^2 - \check{N}^{-1/2} \mathcal{K}_+ \check{N}^{-1/2}} \check{N}^{-1/2}\,.
 \end{equation}
@@
 The same calculation can be repeated by exchanging $X$ with $P$, yielding the relation for the remaining block.
+Then, the definitions of the matrices above change in the following way
+\begin{equation}
+    \check{N}_P \coloneqq \mathcal{L}^\dagger \mathcal{K}_+^{-1} \mathcal{L}\,,\quad \check{M}_P \coloneqq \check{N}_P^{-1/2} \mathcal{K}_- \check{N}_P^{-1/2}\,.
+\end{equation}
+In conclusion, the Green's function is given by
+\begin{subequations}
+    \begin{align}
+        G_{AB^\dagger} \vert_P (z) &= - \left[ \vec{b}^\dagger (0) \right]_P \mathcal{L}^\dagger r_X (z) \mathcal{L} \left[ \vec{a}(0) \right]_P\,, \\
+        G_{AB^\dagger} \vert_X (z) &= - \left[ \vec{b}^\dagger (0) \right]_X \mathcal{L} r_P (z) \mathcal{L}^\dagger \left[ \vec{a}(0) \right]_X\,.
+    \end{align}
+\end{subequations}
 
@@
         0 & b_2 & a_2 & b_3 & \cdots \\
-        0 & 0 & b_3 & a_3 & \ddots \\
-        \vdots & \vdots & \vdots & \ddots & \ddots
+        0 & 0 & b_3 & a_3 & \cdots \\
+        \vdots & \vdots & \vdots & \vdots & \ddots
     \end{pmatrix} \right)_{00}^{-1} = \dfrac{1}{z^2 - a_0 - \dfrac{b_1^2}{z^2 - a_1 - \dfrac{b_2^2}{ z^2 - a_2 - \hdots}}}\,\,
@@
 where $a_i$ and $b_i$ are the Lanczos coefficients \cite{PettiforRecursion,ViswanathRecursion}.
+Obtaining a diagonal block of $\mathcal{G}$ is easily achieved by setting $\vec{b}(0) = \vec{a}(0)$.
+Obtaining an off-diagonal block requires linear combinations in the form of \textcolor{red}{Ich bin damit nicht glücklich, da $\mathcal{G}$ ja eigentlich nicht hermitisch ist (wegen dem $z = \omega + i0^+$).
+Das ist für die Ergebnisse völlig egal, da ich eh nur diagonale Blöcke betrachte, aber nunja...}
+\begin{subequations}
+    \begin{align}
+        4 \Re [ \vec{a}^\dagger \mathcal{G} \vec{b} ] &= (\vec{a} + \vec{b})^\dagger \mathcal{G} (\vec{a} + \vec{b}) - (\vec{a} - \vec{b})^\dagger \mathcal{G} (\vec{a} - \vec{b}) \nonumber \\
+            &= 2 \vec{a}^\dagger \mathcal{G} \vec{b} + 2 \vec{b}^\dagger \mathcal{G} \vec{a}\,, \\
+        4i \Im [ \vec{a}^\dagger \mathcal{G} \vec{b} ] &= (\vec{a} + i \vec{b})^\dagger \mathcal{G} (\vec{a} + i \vec{b}) - (\vec{a} - i \vec{b})^\dagger \mathcal{G} (\vec{a} - i \vec{b}) \nonumber \\
+            &= 2i \vec{a}^\dagger \mathcal{G} \vec{b} - 2i \vec{b}^\dagger \mathcal{G} \vec{a}\,.
+    \end{align}
+\end{subequations}
 In the single-band case, the coefficients approach the limit
@@
     \begin{align}
-        A_\text{Higgs} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} + f_{\vk}^\dagger \right) \nonumber \\ 
-            &= \int_{-1}^{1} \rho(\gamma) \left( f(\gamma) + f^\dagger (\gamma) \right) \mathrm{d}\gamma \,,\\
-        A_\text{Phase} &= \frac{i}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} - f_{\vk}^\dagger \right) \nonumber \\ 
-            &= i \int_{-1}^{1} \rho(\gamma) \left( f(\gamma) - f^\dagger (\gamma) \right) \mathrm{d}\gamma \,,\\
-        A_\text{CDW} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} + g_{\vk \down} \right) \nonumber \\ 
-            &= \int_{-1}^{1} \rho(\gamma) \left( g_{\up}(\gamma) + g_{\down}(\gamma) \right) \mathrm{d}\gamma \,,\\
-        A_\text{AFM} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} - g_{\vk \down} \right) \nonumber \\ 
-            &= \int_{-1}^{1} \rho(\gamma) \left( g_{\up}(\gamma) - g_{\down}(\gamma) \right) \mathrm{d}\gamma \,,
+        A_\text{Higgs} &= \frac{1}{N} \sum_{\vk} \left( f_{\vk} + f_{\vk}^\dagger \right) \,,\\
+        A_\text{Phase} &= \frac{i}{N} \sum_{\vk} \left( f_{\vk} - f_{\vk}^\dagger \right) \,,\\
+        A_\text{CDW} &= \frac{1}{N} \sum_{\vk} \left( g_{\vk \up} + g_{\vk \down} \right) \,,\\
+        A_\text{AFM} &= \frac{1}{N} \sum_{\vk} \left( g_{\vk \up} - g_{\vk \down} \right) \,,
     \end{align}
@@
 \appendix
-\section{Obtaining Green's functions from the iEoM-matrices}
+\section{Semipositivity of the dynamical matrix}
 
-Nevertheless, let us show that $\mathcal{M}$ is positive semidefinite if the system is in thermal equilibrium.
+We show that $\mathcal{M}$ is positive semidefinite if the system is in thermal equilibrium.
 For any $\vec{x} \in \mathbb{C}^N$, consider
@@
             &= \frac{1}{2Z} \left[ \sum_{ij} C_{ij} e^{-\beta \epsilon_j} (\epsilon_i - \epsilon_j) - \sum_{ij} C_{ij} e^{-\beta \epsilon_i} (\epsilon_i - \epsilon_j) \right] \nonumber \\
-            &= \frac{1}{2Z} \sum_{ij} C_{ij} \left( e^{-\beta \epsilon_j} - e^{-\beta \epsilon_i} \right) \left( \epsilon_i - \epsilon_j \right) \geq 0\,.
+            &= \frac{1}{2Z} \sum_{ij} C_{ij} \left( e^{-\beta \epsilon_j} - e^{-\beta \epsilon_i} \right) \left( \epsilon_i - \epsilon_j \right) \geq 0 \,.
     \end{align}
@@
 
-Thus, we are able to compute a real square root of $\mathcal{M}$.
+\section{Numerical treatment of the iEoM matrices}
+
+We would like to use operators like \eqref{eqn:ieom_basis_operator} to span our operator set.
+However, numerically, it is impossible to matrices with infinite dimensions, requiring us to discretize.
+Additionally, we cannot numerically write down $\delta$ distributions as matrix elements. Therefore, we need some special treatments, which we will describe in this section.
+We discretize the $\gamma$-space equally with each abscissa $\gamma_i$ being spaced by $\Delta \gamma$.
+Then, we define an approximate $\delta$ function
+\begin{equation}
+    h(\gamma) \coloneqq \begin{cases}
+        \frac{1}{\Delta \gamma} & |\gamma| < \frac{\Delta \gamma}{2} \\ 0 & \text{otherwise}
+    \end{cases}\,.
+\end{equation}
+Computing an integral yields
+\begin{equation}
+    \int f(\tilde{\gamma}) h(\tilde{\gamma} - \gamma_j) \mathrm{d} \tilde{\gamma} \approx \sum_i f(\gamma_i) h(\gamma_i - \gamma_j) \Delta \gamma = f(\gamma_j)\,,
+\end{equation}
+and thereby mimicking the continuous $\delta$ distribution for a discrete description.
+Note, that if one takes the limit $\Delta \gamma \to 0$ there $\delta$ distribution is exactly reproduced.
+
+Numerically, we can compute the matrix elements like this
+\begin{align}
+    (A_i | A_j) &= \frac{(\Delta \gamma)^2}{N} \sum_{\vk \vl} h(\gamma_i - \hat{\gamma}(\vk)) h(\gamma_j - \hat{\gamma}(\vl)) (A_{\vk} | A_{\vl}) 
+\end{align}
 

### 2023-12-12 paper/main.tex
uni

@@
     \begin{align}
-        A_\text{Higgs} &= \frac{1}{N} \sum_{\vk} \left( f_{\vk} + f_{\vk}^\dagger \right) \,,\\
-        A_\text{Phase} &= \frac{i}{N} \sum_{\vk} \left( f_{\vk} - f_{\vk}^\dagger \right) \,,\\
-        A_\text{CDW} &= \frac{1}{N} \sum_{\vk} \left( g_{\vk \up} + g_{\vk \down} \right) \,,\\
-        A_\text{AFM} &= \frac{1}{N} \sum_{\vk} \left( g_{\vk \up} - g_{\vk \down} \right) \,,
+        A_\text{Higgs} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} + f_{\vk}^\dagger \right) \,,\\
+        A_\text{Phase} &= \frac{i}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} - f_{\vk}^\dagger \right) \,,\\
+        A_\text{CDW}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} + g_{\vk \down} \right) \,,\\
+        A_\text{AFM}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} - g_{\vk \down} \right) \,,
     \end{align}
@@
 
-Note additionally, that all of the aforementioned operators are (anti-)Hermitian. 
-Therefore, their commutator $[A^\dagger, A]$ vanishes and, 
-abiding by the sum rule $\int_{-\infty}^\infty \mathcal{A}_{A^\dagger A} (\omega) \mathrm{d}\omega = \langle [A^\dagger, A] \rangle = 0$ \cite{rickayzen80},
-all spectral functions
-\begin{equation}
-    \mathcal{A}(\omega) = -\frac{1}{\pi} \Im \left[ \mathcal{G}(\omega + i0^+) \right]
-\end{equation}
-must be symmetrical about $\omega=0$.
+Note additionally, that all of the aforementioned operators are Hermitian. 
+This that all spectral functions need to be completely antisymmetrical, see \autoref{sec:antisymmetry_spectral}.
 For this reason, we will only show the $\omega \geq 0$ in our plots. 
@@
 \begin{align}
-    (A_i | A_j) &= \frac{(\Delta \gamma)^2}{N} \sum_{\vk \vl} h(\gamma_i - \hat{\gamma}(\vk)) h(\gamma_j - \hat{\gamma}(\vl)) (A_{\vk} | A_{\vl}) 
+    (A_i | A_j) &= \frac{(\Delta \gamma)^2}{N} \sum_{\vk \vl} h(\gamma_i - \hat{\gamma}(\vk)) h(\gamma_j - \hat{\gamma}(\vl)) (A_{\vk} | A_{\vl})\,.
 \end{align}
+Here, all expression are finite numbers and do not require further treatment.
+Mutatis mutandis, one obtains a similar expression for $(A_i | [H, A_j])$.
+Additionally note, that the expressions $(A_{\vk} | A_{\vl})$ and $(A_{\vk} | [H, A_{\vl}])$ can be reduced to sums of terms that are proportional to $\gamma_i$ or $\gamma_j$, respectively.
+Therefore, it is not necessary to implement any sort of momentum space computations.
+
+\section{Antisymmetry of the spectral functions}
+\label{sec:antisymmetry_spectral}
+
+Consider any Hermitian operator $A$. 
+We compute the Fourier-transformed Green's function for positive and negative $\omega$
+\begin{align}
+    G_{AA}(\omega) &= -i \int_0^\infty e^{i \omega t} \langle [A(t), A] \rangle \mathrm{d}t\,, \nonumber \\
+    G_{AA}(- \omega) &= -i \int_0^\infty e^{-i \omega t} \langle [A(t), A] \rangle \mathrm{d}t\,.
+\end{align}
+We also compute the complex conjugate of the former
+\begin{align}
+    G_{AA}^* (\omega) &= i \int_0^\infty e^{-i \omega t} \langle [A(t), A] \rangle^* \mathrm{d}t \nonumber \\
+        &= i \int_0^\infty e^{-i \omega t} \langle [A^\dagger, A^\dagger(t)] \rangle \\
+        &= -i \int_0^\infty e^{-i \omega t} \langle [A(t), A] \rangle \\
+        &= G_{AA}(- \omega)
+\end{align}
+Taking the imaginary part reveals
+\begin{align}
+    \Im [ G_{AA}^* (\omega) ] = - \Im [G_{AA} (\omega) ] = \Im [G_{AA} (-\omega)]\,.
+\end{align}
+This proves that the imaginary part of such a Fourier-transformed Green's function is antisymmetrical and therefore the same applies to the spectral functions.
+Note that this fully abides by the sum rule $\int_{-\infty}^\infty \mathcal{A}_{A^\dagger A} (\omega) \mathrm{d}\omega = \langle [A^\dagger, A] \rangle = 0$ \cite{rickayzen80}.
 

### 2023-12-13 paper/main.tex
sdahfousgfousa

@@
     \begin{align}
-        A_\text{Higgs} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} + f_{\vk}^\dagger \right) \,,\\
-        A_\text{Phase} &= \frac{i}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} - f_{\vk}^\dagger \right) \,,\\
-        A_\text{CDW}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} + g_{\vk \down} \right) \,,\\
-        A_\text{AFM}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} - g_{\vk \down} \right) \,,
+        A_\text{Higgs} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} + f_{\vk}^\dagger \right)  
+            = \int \dgamma \left( f_{\gamma} + f_{\gamma}^\dagger \right) \,,\\
+        A_\text{Phase} &= \frac{i}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} - f_{\vk}^\dagger \right) = \int \dgamma \left( f_{\gamma} - f_{\gamma}^\dagger \right) \,,\\
+        A_\text{CDW}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} + g_{\vk \down} \right) = \int \dgamma \left( g_{\gamma \up} + g_{\gamma \down} \right) \,,\\
+        A_\text{AFM}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} - g_{\vk \down} \right) = \int \dgamma \left( g_{\gamma \up} - g_{\gamma \down} \right) \,,
     \end{align}
@@
 The remaining two capture the collective behaviour of the CDW and AFM states, respectively.
-Note, that this choice of normalization cancels out with other system size-dependent terms so that our final results do not depend on it at all.
 
-Note additionally, that all of the aforementioned operators are Hermitian. 
-This that all spectral functions need to be completely antisymmetrical, see \autoref{sec:antisymmetry_spectral}.
+Note, that all of the aforementioned operators are Hermitian. 
+This means that all spectral functions need to be completely antisymmetrical, see \autoref{sec:antisymmetry_spectral}.
 For this reason, we will only show the $\omega \geq 0$ in our plots. 
-Additionally, we will add a small imaginary part of $10^{-5}$ to $\omega$ in order to visualize the occurring $\delta$ peaks.
+Additionally, we will add a small imaginary part of $10^{-5}t$ to $\omega$ in order to visualize the occurring $\delta$ peaks.
 
-\subsection{SC-CDW transition}
+\subsection{Classification of the spectral functions}
 
-Let us first show and discuss the general form of the spectral functions in the SC and CDW phase and afterward, 
-we will describe the behaviour of the occurring modes as the system approaches a phase transition.
-
-The spectral functions corresponding to the individual operators in \eqref{eqn:resolvent_bases} are shown in \autoref{fig:resolvent_overview_SC}.
-We chose $U=-2.5$ and $V=\pm0.1$ for both lattices.
+To begin, let us describe the the spectral function with respect to the operators above in the various phases.
+A plot of those in the SC and CDW phase, close to the phase transition, is shown in \autoref{fig:resolvent_overview_SC}.
+We chose $U=-2.5t$ and $V=\pm0.1t$ for both lattices.
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.48\textwidth]{plots/phase_peak.pdf}
-    \caption{Phase Green's function}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.48\textwidth]{plots/cdw_peak_in_sc.pdf}
-    \caption{Log-log plot of the real part of the phase (a) and CDW (b) Green's functions in the SC phase.
-        The results for both lattice types are shown but are qualitatively identical.
-        The power-law exponent is $a=-2$ and $a=-1$, respectively, indicating that the CDW peak is a $\delta$ distribution, while the phase peak is the derivative of one.}
-        \label{fig:peaks_in_sc}
-\end{figure}
-
-\textcolor{red}{Die Festellung, dass die Peaks deltas bzw Ableitungen von deltas sind, könnte ich mir auch in einem Anhang vorstellen.}
-To further classify the aforementioned peak that lies outside the two-particle continuum,
+To further classify the aforementioned peaks that lie outside the two-particle continuum,
 we turn towards the real part of the Green's function.
-We plot it in close proximity to the peaks with a double logarithmic scale and fit the result linearly to obtain its power-law behaviour.
-In practice, we use
-\begin{align}
-    \ln(\Re[\mathcal{G}](\omega - \omega_0 )) &= a \ln(\omega - \omega_0) + b \nonumber \\ 
-    \Leftrightarrow \Re[\mathcal{G}] (\omega) &= (\omega - \omega_0)^a e^b\,,
-\end{align}
-where $\omega_0$ is the peak's position and $a, b$ are fit parameters.
-The real part is related to the imaginary part via the Kramers-Kronig relations. \textcolor{red}{Zitiert man die oder nimmt man an, dass jeder weiß, worum es da geht?}
-Specifically, if the imaginary part is a $\delta$ distribution, the real part will be proportional to $1/\omega$, i.e., $a=-1$ and the peak has the weight $\exp(b)$.
+We plot it in close proximity to the peaks with a double logarithmic scale and fit the result linearly $y = ax + b$ to obtain its power-law behaviour.
+The real part is related to the imaginary part via the Kramers-Kronig relations.
+Specifically, if the imaginary part is a $\delta$ distribution, the real part will be proportional to $1/\omega$, i.e., $a=-1$ and the peak has the weight $w_0 = \exp(b)$.
 Furthermore, an exponent of $a=-2$ corresponds to the derivative of the $\delta$ distribution, i.e., $\delta'(\omega - \omega_0)$.
 
-The plots for the phase peak and the CDW peak in the SC phase can be seen in \autoref{fig:peaks_in_sc}.
+The plots for the phase peak and the CDW peak in the SC phase can be found in \autoref{sec:fit_greens_functions}.
 The SC peak in the CDW phase behaves similarly to the latter and is therefore not shown explicitly.
@@
 
-\begin{figure}
+\begin{figure*}
     \centering
-    \includegraphics[width=.48\textwidth]{plots/higgs_peak.pdf}
-    \caption{Log-log plot of the Higgs spectral function near $\omega = \omega_0 = 2\Delta_\text{SC}$ in the SC phase.
-    We additionally plot the difference between the Higgs and the phase spectral functions and fit it, as we interpret the latter as a background within the two-particle continuum.
-    The upper (lower) panel shows the results for the square (simple cubic) lattice.
-    The spectral function behaves as $1 / \sqrt{\omega - \omega_0}$.}
-    \label{fig:higgs_peak}
-\end{figure}
+    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_AFM_CDW.pdf}
+    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
+    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
+    The shaded area marks the two-particle continuum.
+    The panels (a) and (b) show the spectral functions in the CDW and AFM phases, respectively.}
+    \label{fig:resolvent_overview_AFM}
+\end{figure*}
 
-Next, we will investigate the Higgs peak. 
-Additionally, we see in \autoref{fig:resolvent_overview_SC} that the Higgs and phase spectral functions become indistinguishable towards the upper half of the two-particle continuum.
+Next, we will investigate the Higgs peak, this time around, turning towards the spectral function itself. 
+We see in \autoref{fig:resolvent_overview_SC} that the Higgs and phase spectral functions become indistinguishable towards the upper half of the two-particle continuum.
 Therefore, we interpret the latter as a background to the Higgs peak itself and compute the difference between both spectral functions.
-We plot the result double logarithmically and fit it again linearly, as seen in \autoref{fig:higgs_peak}.
-This time around, the exponent is $a\approx-0.5$, indicating that the peak behaves as $1 / \sqrt{\omega - \omega_0}$.
+Using the same methodology as before we obtain that the exponent is $a\approx-0.5$, indicating that the peak behaves as $1 / \sqrt{\omega - \omega_0}$.
+
+Lastly, we investigate the same spectral functions close to the AFM-CDW phase transition, depicted in \autoref{fig:resolvent_overview_AFM}.
+We choose $V=1t$ for both lattices and $U=zV \pm 0.1t$, where $z$ is the coordination number.
+Again, the both SC-related spectral functions are identical in both the CDW and AFM phase.
+Within the continuum their weight is shifted towards the upper edge and on the square lattice only, there is a peak above the continuum.
+In the AFM phase, both the CDW and AFM spectral functions have a peak close, but yet below, the two-particle continuum.
+The AFM peak is at a lower energy than the CDW one.
+In the CDW phase, this behaviour is reversed, i.e., the CDW peak lies lower.
+Using the same analysis as before, we conclude that each of these peaks is a $\delta$-peak.
+
+\subsection{SC-CDW transition}
 
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_AFM_CDW.pdf}
-    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
-    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
-    %The left edge of the plots is at $-0.05$ rather than $0$ in order to improve the visibility of the phase peak.
-    The shaded area marks the two-particle continuum.
-    The panels (a) and (b) show the spectral functions in the CDW and AFM phases, respectively.}
-    \label{fig:resolvent_overview_AFM}
-\end{figure*}
-
-Similar to the previous section, we will first show the general form of the spectral functions with respect to the operators \eqref{eqn:resolvent_bases}.
-They are depicted in \autoref{fig:resolvent_overview_AFM}, choosing $V=1$ for the square lattice and $V=0.75$ for the simple cubic lattice.
-For the CDW phase (panel a) we chose $U=zV + 0.1$ and for the AFM phase (panel b) $V=zV - 0.1$.
+TODO
 
@@
 \end{align}
-Expanding the thermal expectation value $\langle O \rangle = \frac{1}{Z} \Trace [\exp(-\beta H_\text{MF}) O]$, where $\beta$ is the inverse temperature and $Z$ the partition function, and the commutators, we obtain
+For $\mM$ to be positive semidefinite the expression above must not be negative.
+Therefore, we need to show, that any diagonal element of $\mM$ is nonnegative.
+To do this, we expand the commutators and the thermal expectation value $\langle O \rangle = \frac{1}{Z} \Trace [\exp(-\beta H_\text{MF}) O]$, 
+where $\beta$ is the inverse temperature and $Z$ the partition function.
+This procedure yields
 
@@
 \end{widetext}
+
+This concludes our proof. Note, that the only assumption made, is that the expectation is to be taken with respect to the thermal equilibrium.
 
@@
 
+\section{Fits to the Green's functions}
+\label{sec:fit_greens_functions}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.48\textwidth]{plots/phase_peak.pdf}
+    \caption{Phase Green's function}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.48\textwidth]{plots/cdw_peak_in_sc.pdf}
+    \caption{Log-log plot of the real part of the phase (a) and CDW (b) Green's functions in the SC phase.
+        The results for both lattice types are shown but are qualitatively identical.
+        The power-law exponent is $a=-2$ and $a=-1$, respectively, indicating that the CDW peak is a $\delta$ distribution, while the phase peak is the derivative of one.}
+        \label{fig:peaks_in_sc}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.48\textwidth]{plots/higgs_peak.pdf}
+    \caption{Log-log plot of the Higgs spectral function near $\omega = \omega_0 = 2\Delta_\text{SC}$ in the SC phase.
+    We additionally plot the difference between the Higgs and the phase spectral functions and fit it, as we interpret the latter as a background within the two-particle continuum.
+    The upper (lower) panel shows the results for the square (simple cubic) lattice.
+    The spectral function behaves as $1 / \sqrt{\omega - \omega_0}$.}
+    \label{fig:higgs_peak}
+\end{figure}
+
 \bibliography{sn-bibliography}

### 2023-12-14 paper/main.tex
as

@@
     We employ the iterated equations of motion approach \cite{Kalthoff17,bleicker18} to compute the two-particle Green's functions and by extension, the corresponding spectral densities.
-    This renders comprehensive analysis of the behaviour of collective excitations possible as the model's parameters are changed across phase transitions.
+    This renders comprehensive analysis of the behavior of collective excitations possible as the model's parameters are changed across phase transitions.
     We identify the well-known amplitude (Higgs) and phase (Leggett) modes within the superconducting phase and observe a similar excitation in the CDW phase which shifts towards zero energy as the system approaches the phase transition to the SC phase.
@@
 Many recent experimental and theoretical studies examined the driven systems in the hope of inducing superconductivity 
-\cite{Nicoletti14,Krull14,Moor14,Casandruc15,patel16,sentef17,Buenemann17}.
+\cite{Volkov73,Yuzbashyan05,Yuzbashyan06,Nicoletti14,Krull14,Moor14,Casandruc15,patel16,sentef17,Buenemann17}.
 Other studies, focusing on equilibrium systems, 
@@
 By extension, we also obtain the spectral functions of the investigated systems and discuss the excitations found therein.
-The prominent examples in the SC phase are the well-known phase (Leggett) and amplitude (Higgs) modes \cite{Cea14,Krull16,Schwarz20,Fan22}.
+The prominent examples in the SC phase are the well-known phase (Leggett) and amplitude (Higgs) modes \cite{Cea14,Tsuji15,Krull16,Schwarz20,Fan22}.
+The former is located at zero energy as our model describes neutral superfluids.
+The latter is found at the lower edge of the two-particle continuum.
 
@@
 where $c_{i\sigma}^{(\dagger)}$ annihilates (creates) an electron with spin $\sigma$ on lattice site $i$ 
-and $\langle i, j\rangle$ denotes the summation over next neighbours.
+and $\langle i, j\rangle$ denotes the summation over the next neighbors.
 The parameters are the hopping amplitude $t$, the onsite interaction $U$, the intersite interaction $V$, and the chemical potential $\mu$.
-Applying a Fourier-transformation into $k$-space yields the single-particle dispersion 
+Applying a Fourier transform into $k$ space yields the single-particle dispersion 
 \begin{equation}
@@
 \end{equation}
-We will compute $\mM$ by commutating with the full Hubbard Hamiltonian \eqref{eqn:full_hamiltonian} enabling us to capture collective behaviour rather than the one particle dynamics given by the mean-field approximation.
+We will compute $\mM$ by commutating with the full Hubbard Hamiltonian \eqref{eqn:full_hamiltonian} enabling us to capture collective behavior rather than the one particle dynamics given by the mean-field approximation.
 
@@
 Obtaining a diagonal block of $\mathcal{G}$ is easily achieved by setting $\vec{b}(0) = \vec{a}(0)$.
-Obtaining an off-diagonal block requires linear combinations in the form of \textcolor{red}{Ich bin damit nicht glücklich, da $\mathcal{G}$ ja eigentlich nicht hermitisch ist (wegen dem $z = \omega + i0^+$).
-Das ist für die Ergebnisse völlig egal, da ich eh nur diagonale Blöcke betrachte, aber nunja...}
-\begin{subequations}
+Obtaining an off-diagonal block requires linear combinations in the form of 
 \begin{align}
-        4 \Re [ \vec{a}^\dagger \mathcal{G} \vec{b} ] &= (\vec{a} + \vec{b})^\dagger \mathcal{G} (\vec{a} + \vec{b}) - (\vec{a} - \vec{b})^\dagger \mathcal{G} (\vec{a} - \vec{b}) \nonumber \\
-            &= 2 \vec{a}^\dagger \mathcal{G} \vec{b} + 2 \vec{b}^\dagger \mathcal{G} \vec{a}\,, \\
-        4i \Im [ \vec{a}^\dagger \mathcal{G} \vec{b} ] &= (\vec{a} + i \vec{b})^\dagger \mathcal{G} (\vec{a} + i \vec{b}) - (\vec{a} - i \vec{b})^\dagger \mathcal{G} (\vec{a} - i \vec{b}) \nonumber \\
-            &= 2i \vec{a}^\dagger \mathcal{G} \vec{b} - 2i \vec{b}^\dagger \mathcal{G} \vec{a}\,.
+    \vec{a}^\dagger \mathcal{G} \vec{b} &= \frac{1}{4} \Big\{ 
+        \underbrace{\left[ (\vec{a} + \vec{b})^\dagger \mathcal{G} (\vec{a} + \vec{b}) - (\vec{a} - \vec{b})^\dagger \mathcal{G} (\vec{a} - \vec{b}) \right]}_{ = 2 \vec{a}^\dagger \mathcal{G} \vec{b} + 2 \vec{b}^\dagger \mathcal{G} \vec{a}} \\
+    &-i \underbrace{\left[ (\vec{a} + i \vec{b})^\dagger \mathcal{G} (\vec{a} + i \vec{b}) - (\vec{a} - i \vec{b})^\dagger \mathcal{G} (\vec{a} - i \vec{b}) \right]}_{= 2i \vec{a}^\dagger \mathcal{G} \vec{b} - 2i \vec{b}^\dagger \mathcal{G} \vec{a}} \Big\}\,, \nonumber
 \end{align}
-\end{subequations}
+i.e., one computes the four diagonal blocks and then simply adds them as described above.
+
 In the single-band case, the coefficients approach the limit
@@
 where $\omega_\pm$ represents the upper and lower band edge, respectively \cite{PettiforRecursion}.
-This behaviour allows us to terminate the continued fraction, once the coefficients have converged close enough to these values, using the so-called square root terminator
+This behavior allows us to terminate the continued fraction, once the coefficients have converged close enough to these values, using the so-called square root terminator
 \begin{equation}
@@
 The first operator captures the amplitude mode of the $s$-wave superconducting state, while the second one catches the phase mode \cite{Fan22}.
-The remaining two capture the collective behaviour of the CDW and AFM states, respectively.
+The remaining two capture the collective behavior of the CDW and AFM states, respectively.
 
@@
 
-To begin, let us describe the the spectral function with respect to the operators above in the various phases.
+\begin{figure*}
+    \centering
+    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_AFM_CDW.pdf}
+    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
+    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
+    The shaded area marks the two-particle continuum.
+    The panels (a) and (b) show the spectral functions in the CDW and AFM phases, respectively.}
+    \label{fig:resolvent_overview_AFM}
+\end{figure*}
+
+To begin, let us describe the spectral function with respect to the operators above in the various phases.
 A plot of those in the SC and CDW phase, close to the phase transition, is shown in \autoref{fig:resolvent_overview_SC}.
@@
 we turn towards the real part of the Green's function.
-We plot it in close proximity to the peaks with a double logarithmic scale and fit the result linearly $y = ax + b$ to obtain its power-law behaviour.
+We plot it in close proximity to the peaks with a double logarithmic scale and fit the result linearly $y = ax + b$ to obtain its power-law behavior.
 The real part is related to the imaginary part via the Kramers-Kronig relations.
@@
 The SC peak in the CDW phase behaves similarly to the latter and is therefore not shown explicitly.
-We get a good agreement with the power-law behaviour near the peaks with the exponents $a=-2$ (phase) and $a=-1$ (CDW), respectively.
+We get a good agreement with the power-law behavior near the peaks with the exponents $a=-2$ (phase) and $a=-1$ (CDW), respectively.
 Therefore, we conclude that the CDW peak corresponds to a $\delta$ distribution, while the phase peak is its derivative.
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_AFM_CDW.pdf}
-    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
-    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
-    The shaded area marks the two-particle continuum.
-    The panels (a) and (b) show the spectral functions in the CDW and AFM phases, respectively.}
-    \label{fig:resolvent_overview_AFM}
-\end{figure*}
-
-Next, we will investigate the Higgs peak, this time around, turning towards the spectral function itself. 
+Next, we will investigate the Higgs peak, this time around, turning toward the spectral function itself. 
 We see in \autoref{fig:resolvent_overview_SC} that the Higgs and phase spectral functions become indistinguishable towards the upper half of the two-particle continuum.
@@
 We choose $V=1t$ for both lattices and $U=zV \pm 0.1t$, where $z$ is the coordination number.
-Again, the both SC-related spectral functions are identical in both the CDW and AFM phase.
+Again, both SC-related spectral functions are identical in both the CDW and AFM phases.
 Within the continuum their weight is shifted towards the upper edge and on the square lattice only, there is a peak above the continuum.
@@
 The AFM peak is at a lower energy than the CDW one.
-In the CDW phase, this behaviour is reversed, i.e., the CDW peak lies lower.
-Using the same analysis as before, we conclude that each of these peaks is a $\delta$-peak.
+In the CDW phase, this behavior is reversed, i.e., the CDW peak lies lower.
+Using the same analysis as before, we conclude that each of these peaks is a $\delta$ peak.
 
@@
     The fits are linear, i.e., $y(V) = c \ln(V/t) + d$, and the parameters are printed on the individual panels.}
-    \label{fig:sc_in_cdw_behaviour}
+    \label{fig:sc_in_cdw_behavior}
 \end{figure*}
 
-With the prevalent peaks discussed, we turn towards their behaviour as the system approaches the phase transition at $V=0$.
+With the prevalent peaks discussed, we turn towards their behavior as the system approaches the phase transition at $V=0$.
 \textcolor{red}{TODO; weiter beschreiben}
@@
 \end{align}
-Here, all expression are finite numbers and do not require further treatment.
+Here, all expressions are finite numbers and do not require further treatment.
 Mutatis mutandis, one obtains a similar expression for $(A_i | [H, A_j])$.
-Additionally note, that the expressions $(A_{\vk} | A_{\vl})$ and $(A_{\vk} | [H, A_{\vl}])$ can be reduced to sums of terms that are proportional to $\gamma_i$ or $\gamma_j$, respectively.
+Additionally, note, that the expressions $(A_{\vk} | A_{\vl})$ and $(A_{\vk} | [H, A_{\vl}])$ can be reduced to sums of terms that are proportional to $\gamma_i$ or $\gamma_j$, respectively.
 Therefore, it is not necessary to implement any sort of momentum space computations.

### 2023-12-14 paper/main.tex
stuff

@@
 By extension, we also obtain the spectral functions of the investigated systems and discuss the excitations found therein.
-The prominent examples in the SC phase are the well-known phase (Leggett) and amplitude (Higgs) modes \cite{Cea14,Tsuji15,Krull16,Schwarz20,Fan22}.
+The prominent examples in the SC phase are the well-known phase (Leggett) and amplitude (Higgs) modes \cite{Varma02,Cea14,Measson14,Tsuji15,Krull16,Schwarz20,Fan22}.
 The former is located at zero energy as our model describes neutral superfluids.
@@
 Lastly, in \autoref{sec:conclusion}, we will discuss our results.
-In the appendix \textcolor{red}{(or in the supplemental material?)}, we will derive and explain our methods in detail.
+%In the appendix \textcolor{red}{(or in the supplemental material?)}, we will derive and explain our methods in detail.
 
@@
 With it, we can describe two-particle quantities like the various collective excitations of the system.
-We will present the general ideas briefly here and refer the interested reader to the appendix \textcolor{red}{!REF!} for a detailed explanation and derivation.
 
@@
 Practically, we choose $N_\gamma = 3000$ equally spaced discretization points.
-A detailed explanation of the numerics is provided in the appendix \textcolor{red}{!REF!}.
+A detailed explanation of the numerics is provided in the appendix \autoref{sec:numerical_ieom}.
 
@@
 Additionally, the matrix $\mM$ is positive semidefinite if the system is in thermal equilibrium.
-We proof this statement in the appendix \textcolor{red}{!REF!}.
+We proof this statement in the appendix \autoref{sec:positive_M}.
 
@@
 \begin{align}
+    \label{eqn:green_derivation}
     G_{AB^\dagger} (z) &= i \int_0^\infty \exp(izt) \langle [ (\vec{A \cdot} \vec{b}(0))^\dagger, \vec{A} \cdot \vec{a}(t) ] \rangle\ \mathrm{d}t \nonumber \\
@@
 \section{Semipositivity of the dynamical matrix}
+\label{sec:positive_M}
 
@@
 \section{Numerical treatment of the iEoM matrices}
+\label{sec:numerical_ieom}
 
@@
 \end{equation}
-and thereby mimicking the continuous $\delta$ distribution for a discrete description.
-Note, that if one takes the limit $\Delta \gamma \to 0$ there $\delta$ distribution is exactly reproduced.
+showing that $h(\gamma)$ mimicks the continuous $\delta$ distribution for a discrete description.
+Note, that if one takes the limit $\Delta \gamma \to 0$ the $\delta$ distribution is exactly reproduced.
 
 Numerically, we can compute the matrix elements like this
-\begin{align}
-    (A_i | A_j) &= \frac{(\Delta \gamma)^2}{N} \sum_{\vk \vl} h(\gamma_i - \hat{\gamma}(\vk)) h(\gamma_j - \hat{\gamma}(\vl)) (A_{\vk} | A_{\vl})\,.
-\end{align}
+\begin{equation}
+    \label{eqn:numerical_example}
+    (A_i | A_j) = \frac{1}{N} \sum_{\vk \vl} h(\gamma_i - \hat{\gamma}(\vk)) h(\gamma_j - \hat{\gamma}(\vl)) (A_{\vk} | A_{\vl})\,.
+\end{equation}
 Here, all expressions are finite numbers and do not require further treatment.
@@
 Therefore, it is not necessary to implement any sort of momentum space computations.
+For example, consider $A_{\vk} = f_{\vk}^\dagger$, then
+\begin{equation}
+    ( f_{\vk}^\dagger | f_{\vl}^\dagger ) = \delta_{\vk, \vl} \langle 1 - n_{\vk \uparrow} - n_{\vk \downarrow} \rangle \eqqcolon \delta_{\vk, \vl} \alpha(\vk)
+\end{equation}
+holds. Inserting this into \eqref{eqn:numerical_example} yields
+\begin{align}
+    (A_i | A_j) &= \frac{1}{N} \sum_{\vk} h(\gamma_i - \hat{\gamma}(\vk)) h(\gamma_j - \hat{\gamma}(\vk)) \alpha(\vk)\,.
+\end{align}
+As stated in the main text, see \eqref{eqn:equal_expecs}, $\alpha(\vk)$ depends only on $\hat{\gamma}(\vk)$, hence we can switch from the momentum sum to a $\gamma$ integration
+\begin{align}
+    (A_i | A_j) &= \int \rho(\gamma) h(\gamma_i - \gamma) h(\gamma_j - \gamma) \alpha(\gamma) \dgamma \nonumber \\
+        &\approx \rho(\gamma_i) h(\gamma_j - \gamma_i) \alpha(\gamma_i) \nonumber \\
+        &= \frac{\delta_{ij}}{\Delta \gamma} \rho(\gamma_i) \alpha(\gamma_i)\,.
+\end{align}
+Later on, when we compute the spectral functions, we perform another two $\gamma$ integrations, for example, let us compute the first Lanczos coefficient for $A_\text{Higgs}$.
+Then, the elements of the vectors mentioned in \eqref{eqn:green_derivation} are given by
+\begin{equation}
+    a_i = b_i = \begin{cases}
+        \Delta \gamma & i \text{ corresponds to an } f\text{-type basis operator} \\
+        0 & \text{otherwise}
+    \end{cases}\,.
+\end{equation}
 

### 2023-12-14 paper/resolvent_overview_AFM_CDW.py

@@ -13,8 +13,6 @@ from lib.iterate_containers import naming_scheme_tuples
 import lib.plot_settings as ps
 from lib.create_zoom import *
 
-# visually scale the data for visibility
-SCALE = 5
 params = [ [0., 4.1, 1.], [0., 3.9, 1.] ]
 
 folders = ["../data/modes/square/dos_3k/", "../data/modes/cube/dos_3k/"]
@@ -49,13 +47,13 @@ for j, folder in enumerate(folders):
         for k, (name_suffix, label) in enumerate(zip(name_suffices, labels)):
             data, data_real, w_lin, resolvents[k] = cf.resolvent_data(f"{folder}{name}", name_suffix, plot_lower_lim, usage_upper_lim, 
                                                             number_of_values=10000, xp_basis=True, imaginary_offset=1e-5, messages=False)
-            plotters[i][j].plot(w_lin, SCALE*data, label=label)
+            plotters[i][j].plot(w_lin, data, label=label)
             
         cont = np.sqrt(resolvents[0].roots[0])
         zoomed_region = (cont - 0.02, cont) if j == 0 else (cont - 0.07, cont - 0.03) 
 
         axins = create_zoom(axs[i][j], 0.4, 0.2, 0.3, 0.75, zoomed_region, ylim=(0, 0.55), 
-                            y_funcs=[lambda x, res=res: SCALE*res.spectral_density(x + 1e-5j) for res in resolvents])
+                            y_funcs=[lambda x, res=res: res.spectral_density(x + 1e-5j) for res in resolvents])
   
         axs[i][j].set_xlim(plot_lower_lim, usage_upper_lim)
         resolvents[0].mark_continuum(axs[i][j], None)

### 2023-12-15 paper/main.tex
improved peak fitting

@@
 
-Many recent experimental and theoretical studies examined the driven systems in the hope of inducing superconductivity 
-\cite{Volkov73,Yuzbashyan05,Yuzbashyan06,Nicoletti14,Krull14,Moor14,Casandruc15,patel16,sentef17,Buenemann17}.
-Other studies, focusing on equilibrium systems, 
-investigated the phases and various quantities therein of the said model including various additional interactions with and without doping 
+Numerous studies have been performed on equilibrium systems. 
+These investigated the phases and various quantities therein of the said model including various additional interactions with and without doping 
 \cite{Micnas88,Micnas88b,Micnas89,Dzierzawa92,Kostyrko92,Eriksson95,Staudt00,Onari04,Toschi05,Brackett16,Paki19,romer20,Sushchyev22}.
+For a long time, works on the dynamics of the superconducting gap parameter focused on its behavior after an instantaneous quench, 
+yielding damped or persistent oscillations depending on the magnitude of the quench \cite{Volkov73,Yuzbashyan05,Yuzbashyan06,Barankov06,Cui19}.
+More recent experimental and theoretical studies examined the driven systems in the hope of inducing superconductivity \cite{Nicoletti14,Krull14,Moor14,Casandruc15,patel16,sentef17,Buenemann17}.
 
@@
 Additionally, the matrix $\mM$ is positive semidefinite if the system is in thermal equilibrium.
-We proof this statement in the appendix \autoref{sec:positive_M}.
+We prove this statement in the appendix \autoref{sec:positive_M}.
 
@@
 \end{align}
-Later on, when we compute the spectral functions, we perform another two $\gamma$ integrations, for example, let us compute the first Lanczos coefficient for $A_\text{Higgs}$.
-Then, the elements of the vectors mentioned in \eqref{eqn:green_derivation} are given by
+Since $\Delta \gamma$ is a positive constant factor, it does not impact any of our matrix operations, i.e., we can pull it out to the front of the expressions $\mM \to \tilde{m} (\Delta \gamma)^2$ and $\mN \to \tilde{n} (\Delta \gamma)^2$.
+Then, we can rewrite \eqref{eqn:green_derivation} as
+\begin{equation}
+    G_{AB^\dagger} = - (\Delta \gamma)^2 \vec{b}^\dagger (0) \left[ \tilde{n} \frac{1}{\tilde{m} + z \tilde{n}} \tilde{n} \right] \vec{a}(0)\,.
+\end{equation}
+To give a practical example, let us compute $A_\text{Higgs}$ from \eqref{eqn:resolvent_bases}.
+We order our operator set such that all $f_\gamma^{(\dagger)}$ are upfront. 
+This requires the vector elements $\vec{a}$ and $\vec{b}$ to be
 \begin{equation}
     a_i = b_i = \begin{cases}
-        \Delta \gamma & i \text{ corresponds to an } f\text{-type basis operator} \\
+        1 & i < 2 N_\gamma \\
         0 & \text{otherwise}
-    \end{cases}\,.
+    \end{cases}\,,
 \end{equation}
+where $N_\gamma$ is the number of discretization points.
+Using this, we can expand the relation for the Green's function
+\begin{align}
+    G_{AB^\dagger} (z) &= -(\Delta \gamma)^2 \sum_{i=0}^{2 N_\gamma} \sum_{j=0}^{2 N_\gamma} \left[ \tilde{n} \frac{1}{\tilde{m} + z \tilde{n}} \tilde{n} \right]_{ij} \nonumber \\
+        &\approx - \int \dgamma \int \dgamma' \left[ \tilde{n} \frac{1}{\tilde{m} + z \tilde{n}} \tilde{n} \right](\gamma, \gamma')\,.
+\end{align}
+The first line is an approximation of the integral in the second line, as each matrix element corresponds to a specific value for $\gamma$.
+Note, that the sum going up to $2N_\gamma$ rather than $N_\gamma$ merely arises from the fact, that we need to integrate over both $f_\gamma$ and $f_\gamma^\dagger$ to obtain $A_\text{Higgs}$.
 

### 2023-12-15 paper/cdw_peak_in_sc.py
improved peak fitting

@@ -31,7 +31,7 @@ for i in range(2):
     name = f"T={T}/U={U}/V={V}"
     peak = rp.Peak(f"{folders[i]}{name}", name_suffix, initial_search_bounds=(0.3, 0.8))
     #print(peak.peak_position)
-    peak.improved_peak_position(x0_offset=1e-1, gradient_epsilon=1e-12)
+    peak.improved_peak_position(xtol=1e-13)
     popt, pcov, w_space, y_data = peak.fit_real_part(range=0.05, begin_offset=1e-10, reversed=False)
     
     axs[i].text(0.05, 0.4, f"$a={popt[0]:.4f}\pm{np.sqrt(pcov[0][0]):.4f}$", transform = axs[i].transAxes)

### 2023-12-18 paper/peak_fits.py
home

@@ -1,0 +1,60 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+import os, sys
+if os.name == "nt":
+    sys.path.append(os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + r"\python")
+else:
+    sys.path.append(os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + "/python")
+import lib.continued_fraction as cf
+import lib.plot_settings as ps
+import lib.resolvent_peak as rp
+
+folders = ["../data/modes/square/dos_3k/", "../data/modes/cube/dos_3k/"]
+
+fig, axs = plt.subplots(nrows=4, ncols=2, figsize=(12.8, 9.6), sharey="row", sharex=True, gridspec_kw=dict(hspace=0, wspace=0))
+def plot_general_peak(plot_axs, T, U, V, name_suffix, initial_search_bounds, text="", reversed=False):
+    plotters = np.empty(2, dtype=ps.CURVEFAMILY)
+    
+    for i in range(2):
+        plotters[i] = ps.CURVEFAMILY(2, axis=plot_axs[i])
+        plotters[i].set_individual_colors("nice2")
+        plotters[i].set_individual_dashes()
+
+        name = f"T={T}/U={U[i] if hasattr(U, '__len__') else U}/V={V}"
+        peak = rp.Peak(f"{folders[i]}{name}", name_suffix, initial_search_bounds=initial_search_bounds)
+
+        peak.improved_peak_position(xtol=1e-13)
+        popt, pcov, w_space, y_data = peak.fit_real_part(range=0.05, begin_offset=1e-10, reversed=reversed)
+
+        plot_axs[i].text(0.05, 0.4, f"$a={popt[0]:.4f}\pm{np.sqrt(pcov[0][0]):.4f}$", transform = plot_axs[i].transAxes)
+        plot_axs[i].text(0.05, 0.3, f"$b={popt[1]:.4f}\pm{np.sqrt(pcov[1][1]):.4f}$", transform = plot_axs[i].transAxes)
+        plotters[i].plot(w_space, y_data, label="Data")
+        plotters[i].plot(w_space, rp.linear_function(w_space, *popt), label="Fit")
+
[…]

### 2023-12-18 paper/main.tex
home

@@
     The shaded area marks the two-particle continuum.
-    The panels (a), (b), and (c) show the spectral functions in the SC and CDW phases, respectively.}
+    The panels (a) and (b) show the spectral functions in the SC and CDW phases, respectively.
+    The parameters are set to $U=-2.5t$, $V=\pm0.1t$, and $N_\gamma = 3000$.}
     \label{fig:resolvent_overview_SC}
@@
     The shaded area marks the two-particle continuum.
-    The panels (a) and (b) show the spectral functions in the CDW and AFM phases, respectively.}
+    The panels (a) and (b) show the spectral functions in the CDW and AFM phases, respectively.
+    The parameters are set to $U=zV \pm 0.1t$, $V=1t$, and $N_\gamma = 3000$.}
     \label{fig:resolvent_overview_AFM}
@@
 
-To begin, let us describe the spectral function with respect to the operators above in the various phases.
-A plot of those in the SC and CDW phase, close to the phase transition, is shown in \autoref{fig:resolvent_overview_SC}.
+To begin, let us describe the spectral functions $\mathcal{A}(\omega) = - (1/\pi) \Im [\mathcal{G} (\omega + i0^+)]$ with respect to the operators above in the various phases.
+A plot of them in the SC and CDW phase, close to the phase transition, is shown in \autoref{fig:resolvent_overview_SC}.
 We chose $U=-2.5t$ and $V=\pm0.1t$ for both lattices.
@@
     \caption{The upper panels show double logarithmic plots of the positions $\omega_0$ of the SC peak in the CDW phases while the lower panels show their respective weights $w_0 = e^{b}$.
-    The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5$.
+    The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
     The fits are linear, i.e., $y(V) = c \ln(V/t) + d$, and the parameters are printed on the individual panels.}
@@
 This concludes our proof. Note, that the only assumption made, is that the expectation is to be taken with respect to the thermal equilibrium.
+
+\section{Fits to the Green's functions}
+\label{sec:fit_greens_functions}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.48\textwidth]{plots/phase_peak.pdf}
+    \caption{Log-log plot of the real part of the $A_\text{Phase}$ Green's function in the SC phase at $U=-2.5t$ and $V=-0.1t$ as well as a linear fit to it.
+    The upper (lower) panel shows the results for the square (simple cubic) lattice.
+    The function behaves as $1/\omega^2$ indicating that the peak in the spectral function is the derivative of a $\delta$ distribution.}
+    \label{fig:phase_peak}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.48\textwidth]{plots/higgs_peak.pdf}
+    \caption{Log-log plot of the $A_\text{Higgs}$ spectral function near $\omega = \omega_0 = 2\Delta_\text{SC}$ in the SC phase at $U=-2.5t$ and $V=-0.1t$..
+    We additionally plot the difference between the Higgs and the phase spectral functions and fit it, as we interpret the latter as a background within the two-particle continuum.
+    The upper (lower) panel shows the results for the square (simple cubic) lattice.
+    The spectral function behaves as $1 / \sqrt{\omega - \omega_0}$.}
+    \label{fig:higgs_peak}
+\end{figure}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.98\textwidth]{plots/peak_fits.pdf}
+    \caption{Log-log plot of the real part of various Green's functions, the labels indicate its type and the text in the panels indicate the phase.
+        The results for both lattice types are shown but are qualitatively identical.
+        The power-law exponent is $a=-1$ in cases, indicating that these peaks are $\delta$ distributions.}
+        \label{fig:peak_fits}
+\end{figure*}
+
+In this appendix section, we show fits to the real and imaginary parts of various Green's functions in the different phases.
+All fits are linear of the type $y = ax + b$ in double logarithmic plots, i.e., $a$ describes the power-law behavior of the functions.
+Firstly, the real part of the $A_\text{Phase}$ Green's function is shown in \autoref{fig:phase_peak}.
+It behaves as $1/\omega^2$ indicating that the peak we find in the spectral function at $\omega=0$ corresponds to the derivative of a $\delta$ distribution.
+
+Continuing, we investigate the divergence at $\omega = 2\Delta$ found in the $A_\text{Higgs}$ spectral function within the SC phase.
+It behaves as $1/\sqrt{\omega}$ as shown in \autoref{fig:higgs_peak}.
+
+Lastly, we show all the remaining peaks in \autoref{fig:peak_fits}.
+The real part of each one of them behaves as $1/\omega$ in close vicinity to the peak position.
+This indicates that the peaks are $\delta$ distributions.
+The $A_\text{AFM}$ and $A_\text{CDW}$ peaks close the the phase transition are identical when swapped, i.e., $\mathcal{A}_\text{AFM} (\omega)$ in the CDW phase is the same as $\mathcal{A}_\text{CDW} (\omega)$ in the AFM phase.
 
@@
 
-\section{Fits to the Green's functions}
-\label{sec:fit_greens_functions}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.48\textwidth]{plots/phase_peak.pdf}
-    \caption{Phase Green's function}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.48\textwidth]{plots/cdw_peak_in_sc.pdf}
-    \caption{Log-log plot of the real part of the phase (a) and CDW (b) Green's functions in the SC phase.
-        The results for both lattice types are shown but are qualitatively identical.
-        The power-law exponent is $a=-2$ and $a=-1$, respectively, indicating that the CDW peak is a $\delta$ distribution, while the phase peak is the derivative of one.}
-        \label{fig:peaks_in_sc}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=.48\textwidth]{plots/higgs_peak.pdf}
-    \caption{Log-log plot of the Higgs spectral function near $\omega = \omega_0 = 2\Delta_\text{SC}$ in the SC phase.
-    We additionally plot the difference between the Higgs and the phase spectral functions and fit it, as we interpret the latter as a background within the two-particle continuum.
-    The upper (lower) panel shows the results for the square (simple cubic) lattice.
-    The spectral function behaves as $1 / \sqrt{\omega - \omega_0}$.}
-    \label{fig:higgs_peak}
-\end{figure}
-
 \bibliography{sn-bibliography}

### 2023-12-18 paper/cdw_peak_in_sc.py

@@ -1,50 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-
-import os, sys
-if os.name == "nt":
-    sys.path.append(os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + r"\python")
-else:
-    sys.path.append(os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + "/python")
-import lib.continued_fraction as cf
-import lib.plot_settings as ps
-import lib.resolvent_peak as rp
-
-T = 0.
-U = -2.5
-V = -0.1
-
-folders = ["../data/modes/square/dos_3k/", "../data/modes/cube/dos_3k/"]
-labels = ["Square", "Simple cubic"]
-name_suffix = "CDW"
-fig, axs = plt.subplots(nrows=2, figsize=(6.4, 4.8), sharex=True, gridspec_kw=dict(hspace=0, wspace=0))
-
-plotters = np.empty(2, dtype=ps.CURVEFAMILY)
-plot_lower_lim = 0.006
-plot_upper_lim = plot_lower_lim + 0.1
-
-for i in range(2):
-    plotters[i] = ps.CURVEFAMILY(4, axis=axs[i])
-    plotters[i].set_individual_colors("nice2")
-    plotters[i].set_individual_dashes()
-
-    name = f"T={T}/U={U}/V={V}"
-    peak = rp.Peak(f"{folders[i]}{name}", name_suffix, initial_search_bounds=(0.3, 0.8))
-    #print(peak.peak_position)
-    peak.improved_peak_position(xtol=1e-13)
-    popt, pcov, w_space, y_data = peak.fit_real_part(range=0.05, begin_offset=1e-10, reversed=False)
-    
-    axs[i].text(0.05, 0.4, f"$a={popt[0]:.4f}\pm{np.sqrt(pcov[0][0]):.4f}$", transform = axs[i].transAxes)
-    axs[i].text(0.05, 0.3, f"$b={popt[1]:.4f}\pm{np.sqrt(pcov[1][1]):.4f}$", transform = axs[i].transAxes)
-    plotters[i].plot(w_space, y_data, label=f"{labels[i]} data")
-    plotters[i].plot(w_space, rp.linear_function(w_space, *popt), "k--", label=f"{labels[i]} fit")
-    axs[i].set_ylim(0, 22.5)#
-    axs[i].legend()
-    
[…]

### 2023-12-18 paper/phase_peak.py

@@ -23,8 +23,6 @@ name_suffix = "phase_SC"
 fig, axs = plt.subplots(nrows=2, figsize=(6.4, 4.8), sharex=True, gridspec_kw=dict(hspace=0, wspace=0))
 
 plotters = np.empty(2, dtype=ps.CURVEFAMILY)
-plot_lower_lim = 0.006
-plot_upper_lim = plot_lower_lim + 0.1
 
 for i in range(2):
     plotters[i] = ps.CURVEFAMILY(4, axis=axs[i])
@@ -32,16 +30,16 @@ for i in range(2):
     plotters[i].set_individual_dashes()
 
     name = f"T={T}/U={U}/V={V}"
-    data_imag, data, w_lin, res = cf.resolvent_data(f"{folders[i]}{name}", name_suffix, plot_lower_lim, plot_upper_lim, xp_basis=True, imaginary_offset=0, number_of_values=1000, messages=False)
-
-    w_log = np.log(w_lin.real)
-    plotters[i].plot(w_log, np.log(data), label=f"{labels[i]} data")
-    popt, pcov = curve_fit(func_ln, w_log, np.log(data))
-    plotters[i].plot(w_log, func_ln(w_log, *popt), label=f"{labels[i]} fit")
-    axs[i].legend()
+    data_imag, data, w_log, res = cf.resolvent_data_log_z(f"{folders[i]}{name}", name_suffix, lower_edge=0, begin_offset=3e-3, range=0.2, xp_basis=True, imaginary_offset=0, number_of_values=1000, messages=False)
+    
+    data = np.log(data)
+    plotters[i].plot(w_log, data, label=f"Data")
+    popt, pcov = curve_fit(func_ln, w_log, data)
+    plotters[i].plot(w_log, func_ln(w_log, *popt), label=f"Fit")
     axs[i].text(0.05, 0.4, f"$a={popt[0]:.4f}\pm{np.sqrt(pcov[0][0]):.4f}$", transform = axs[i].transAxes)
     axs[i].text(0.05, 0.3, f"$b={popt[1]:.4f}\pm{np.sqrt(pcov[1][1]):.4f}$", transform = axs[i].transAxes)
-    
+
+axs[0].legend()
 axs[1].set_xlabel(r"$\ln(\omega)$")
 axs[1].text(-0.08, 1, r"$\ln(\Re[\mathcal{G}_\mathrm{Phase}](\omega))$", va='center', ha='center', rotation='vertical', transform = axs[1].transAxes)
 fig.tight_layout()

### 2023-12-19 paper/main.tex
uni

@@
 Note, that all of the aforementioned operators are Hermitian. 
-This means that all spectral functions need to be completely antisymmetrical, see \autoref{sec:antisymmetry_spectral}.
+This means that all spectral functions need to be completely antisymmetrical, see appendix \autoref{sec:antisymmetry_spectral}.
 For this reason, we will only show the $\omega \geq 0$ in our plots. 
@@
 
-The plots for the phase peak and the CDW peak in the SC phase can be found in \autoref{sec:fit_greens_functions}.
+The plots for the phase peak and the CDW peak in the SC phase can be found in appendix \autoref{sec:fit_greens_functions}.
 The SC peak in the CDW phase behaves similarly to the latter and is therefore not shown explicitly.
@@
     \caption{The upper panels show double logarithmic plots of the positions $\omega_0$ of the SC peak in the CDW phases while the lower panels show their respective weights $w_0 = e^{b}$.
+    In the upper panel, the pink markers additionally show the peak position devided by the gap $\omega_0 / \Delta_\text{CDW}$.
     The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
@@
 
-With the prevalent peaks discussed, we turn towards their behavior as the system approaches the phase transition at $V=0$.
-\textcolor{red}{TODO; weiter beschreiben}
+With the prevalent peaks discussed, we turn towards their behavior as the system approaches the phase transition at $V=0$ for $U=-2.5t$.
+First and foremost, we investigate the peak in $\mathcal{A}_\text{Phase}(\omega)$ and $\mathcal{A}_\text{Higgs}(\omega)$ in the CDW phase.
+The evolution of its position $\omega_0$ and its weight $w_0$ as $V$ is varied can be viewed double logarithmically in \autoref{fig:sc_in_cdw_behavior}.
+For $V \ll 1$, the position grows with the square root of $V$. This behavior then transitions to a purely linear growth for large $V$.
+Deviding $\omega_0$ by the gap $\Delta_\text{CDW}$ results in a plateau for large $V$ while leaving the square root behavior at the beginning mostly unchanged.
 

### 2023-12-19 paper/peak_fits.py
uni

@@ -51,8 +51,8 @@ axs[3][0].set_ylabel(r"$\ln(\Re[\mathcal{G}_\mathrm{AFM}](\omega))$")
 legend = axs[0][1].legend(loc='upper center', bbox_to_anchor=(0., 1.25), ncol=2, shadow=True)
 axs[0][0].title.set_text("Square")
 axs[0][1].title.set_text("Simple cubic")
-axs[len(axs)-1][0].set_xlabel(r"$\ln(\omega - \omega_0)$")
-axs[len(axs)-1][1].set_xlabel(r"$\ln(\omega - \omega_0)$")
+axs[len(axs)-1][0].set_xlabel(r"$\ln((\omega - \omega_0) / t)$")
+axs[len(axs)-1][1].set_xlabel(r"$\ln((\omega - \omega_0) / t)$")
 fig.tight_layout()
 
 import os

### 2023-12-19 paper/phase_peak.py

@@ -40,7 +40,7 @@ for i in range(2):
     axs[i].text(0.05, 0.3, f"$b={popt[1]:.4f}\pm{np.sqrt(pcov[1][1]):.4f}$", transform = axs[i].transAxes)
 
 axs[0].legend()
-axs[1].set_xlabel(r"$\ln(\omega)$")
+axs[1].set_xlabel(r"$\ln(\omega / t)$")
 axs[1].text(-0.08, 1, r"$\ln(\Re[\mathcal{G}_\mathrm{Phase}](\omega))$", va='center', ha='center', rotation='vertical', transform = axs[1].transAxes)
 fig.tight_layout()
 

### 2023-12-19 paper/higgs_peak.py
uni

@@ -48,7 +48,7 @@ for i in range(2):
 axs[0].legend(loc="upper right")
 
 axs[1].set_xlabel(r"$\ln((\omega - \omega_0) / t)$")
-axs[1].text(-0.08, 1, r"$\ln(-\Im \mathcal{G}_\mathrm{Higgs}(\omega - \omega_0 + i0^+))$", va='center', ha='center', rotation='vertical', transform = axs[1].transAxes)
+axs[1].text(-0.08, 1, r"$\ln(-\Im \mathcal{G}_\mathrm{Higgs}(\omega))$", va='center', ha='center', rotation='vertical', transform = axs[1].transAxes)
 fig.tight_layout()
 
 import os

### 2023-12-19 paper/sc_peak_in_cdw_position.py

@@ -41,19 +41,18 @@ name_suffix = "phase_SC"
 
 weights = np.zeros(len(Vs))
 peak_positions = np.zeros(len(Vs))
+peak_positions_div_delta = np.zeros(len(Vs))
 fig, axs = plt.subplots(nrows=2, ncols=2, figsize=(12.8, 8.2), sharex=True, sharey="row", gridspec_kw=dict(hspace=0, wspace=0))
 
 plotters = np.empty((2,2), dtype=ps.CURVEFAMILY)
 
-#cr = ps.color_ranges["nice"]
-
 
 for i in range(2):
     counter = 0
-    plotters[0][i] = ps.CURVEFAMILY(5, axis=axs[0][i])
+    plotters[0][i] = ps.CURVEFAMILY(6, axis=axs[0][i])
     plotters[0][i].set_individual_colors("nice")
-    plotters[0][i].set_individual_linestyles(["-", "-", "", "", ""])
-    plotters[0][i].set_individual_markerstyles(["", "", "x", "x", "v"])
+    plotters[0][i].set_individual_linestyles(["-", "-", "", "", "", ""])
+    plotters[0][i].set_individual_markerstyles(["", "", "x", "x", "v", "1"])
     
     plotters[1][i] = ps.CURVEFAMILY(3, axis=axs[1][i])
     plotters[1][i].set_individual_colors("nice")
@@ -62,6 +61,7 @@ for i in range(2):
     
     for T, U, V in iterate_containers(Ts, Us, Vs):
         name = f"T={T}/U={U}/V={V}"
+        
         cont_edges = cf.continuum_edges(f"{folders[i]}{name}", name_suffix, True)
         
         lower = 0 if float(V) < 1 else float(V)
@@ -76,7 +76,8 @@ for i in range(2):
 
         peak_pos_value = peak_result["x"]
         peak_positions[counter] = np.copy(peak_pos_value)
-
+        peak_positions_div_delta[counter] = np.copy(peak_pos_value) / extract_key(f"{folders[i]}{name}/resolvent_{name_suffix}.dat.gz", "Total Gap")
+        
         popt, pcov, w_log, y_data = peak.fit_real_part(0.001, 1e-7)
         weights[counter] = popt[1]
[…]

### 2023-12-20 paper/main.tex
uni

@@
 \newcommand{\mN}{\mathcal{N}}
+
+\newcommand{\greens}[1]{\mathcal{G}_\text{#1} (\omega)}
+\newcommand{\spectral}[1]{\mathcal{A}_\text{#1}  (\omega)}
 
@@
     The shaded area marks the two-particle continuum.
-    The panels (a) and (b) show the spectral functions in the SC and CDW phases, respectively.
-    The parameters are set to $U=-2.5t$, $V=\pm0.1t$, and $N_\gamma = 3000$.}
+    For each plot, the parameters are set to $U=-2.5t$ and $N_\gamma = 3000$, while $V$ is varied to according to the text in the individual panels.
+    The panels show the spectral functions in the (a) pure SC phase, (b) SC/CDW-coexistence, and (c) and (d) pure CDW phase, respectively.}
     \label{fig:resolvent_overview_SC}
@@
 The remaining two capture the collective behavior of the CDW and AFM states, respectively.
+In the following, we will refer to the Green's functions generated by these operators as $\mathcal{G}_{i}(\omega) = G_{A_i A_i^\dagger}(\omega)$.
 
@@
     The shaded area marks the two-particle continuum.
-    The panels (a) and (b) show the spectral functions in the CDW and AFM phases, respectively.
-    The parameters are set to $U=zV \pm 0.1t$, $V=1t$, and $N_\gamma = 3000$.}
+    For each plot, the parameters are set to $V=1t$ and $N_\gamma = 3000$, while $U$ is varied to according to the text in the individual panels.
+    The panels (a) and (c) show the spectral functions in the AFM phase, and the panels (b) and (d) in the CDW phase.}
     \label{fig:resolvent_overview_AFM}
@@
 
-To begin, let us describe the spectral functions $\mathcal{A}(\omega) = - (1/\pi) \Im [\mathcal{G} (\omega + i0^+)]$ with respect to the operators above in the various phases.
-A plot of them in the SC and CDW phase, close to the phase transition, is shown in \autoref{fig:resolvent_overview_SC}.
-We chose $U=-2.5t$ and $V=\pm0.1t$ for both lattices.
+To begin, let us describe the spectral functions $\mathcal{A}_i (\omega) = - (1/\pi) \Im [\mathcal{G}_i (\omega + i0^+)]$ with respect to the operators above in the various phases.
+\autoref{fig:resolvent_overview_SC} shows them at $U = -2.5t$ in the SC ($V=-0.1t$) and CDW ($V=0.1t$ and $V=0.5t$) phase, as well as in the SC-CDW coexistence at $V=0$.
 
 There are a variety of different features. The difference between the two lattices is mostly quantitative.
-First and foremost, in the SC phase, there is a sharp peak located at $\omega=0$, only in the phase spectral function,
-and another peak, only in the amplitude spectral function, located at $\omega=2\Delta_\text{SC}$.
+First and foremost, in the SC phase, see panel (a), there is a sharp peak located at $\omega=0$ in $\mathcal{A}_\text{Phase}$,
+and another peak, only in $\spectral{Higgs}$, located at $\omega=2\Delta_\text{SC}$.
 We identify them with the well-known Leggett and Higgs modes in superconductors.
+The former can be found at zero energy because our model describes a neutral superfluid wherein there is no coupling of the phase of the order parameter to the electromagnetic potential.
+Therefore, this phase may be chosen arbitrarily and changing it requires no energy which ultimately allows a Goldstone mode to exist in the first place. \textcolor{red}{Zitieren!}
 In the CDW phase, both of these spectral functions become identical and form a sharp peak below the two-particle continuum.
+Following the Landau theory for continuous phase transitions, this is to be expected as the free energy is expanded in terms of the order parameter as
+\begin{equation}
+    f(\Delta_\text{SC}) \approx r |\Delta_\text{SC}|^2 + \frac{u}{2} |\Delta_\text{SC}|^4\,,
+\end{equation}
+with $r > 0$ and $u > 0$ if the system is outside of the superconducting phase. \textcolor{Zitieren!}
+In this case, the only minimum is at $\Delta_\text{SC} = 0$. 
+That means that both possible modes have to overcome the same energy to be excited in the first place. \textcolor{red}{Passt die Beschreibung so?}
 
-The CDW spectral function shows a peak below the continuum only in the SC phase while having another peak at $\omega=2\Delta$ in the CDW phase.
-The AFM spectral function is restricted to the continuum for both phases and both lattices.
+At $V=0$, both the SC and the CDW phase coexist.
+Here, $\spectral{Higgs}$ and $\spectral{CDW}$ are identical. Both have a peak at $\omega = 0$ and another one at $\omega = 2\Delta$.
+
+$\spectral{CDW}$ shows a peak below the continuum only in the SC phase corresponding to the finite energy necessary to excite this kind of electronic density modulation.
+For moderate sized values of $V>0$, i.e., in the CDW phase, see panel (c) at $V=0.1t$, the aforementioned spectral function has a peak at $\omega=2\Delta$.
+This peak becomes hard and moves outside the two-particle continuum as $V$ is increased, see panel (d) at $V=0.5t$.
+
+$\spectral{AFM}$ is restricted to the continuum for both phases and both lattices.
 For the square lattice, however, there is a peak located at the upper edge of the two-particle continuum.
@@
     \includegraphics[width=0.48\textwidth]{plots/phase_peak.pdf}
-    \caption{Log-log plot of the real part of the $A_\text{Phase}$ Green's function in the SC phase at $U=-2.5t$ and $V=-0.1t$ as well as a linear fit to it.
+    \caption{Log-log plot of the real part of $\spectral{Phase}$ in the SC phase at $U=-2.5t$ and $V=-0.1t$ as well as a linear fit to it.
     The upper (lower) panel shows the results for the square (simple cubic) lattice.
@@
     \includegraphics[width=.48\textwidth]{plots/higgs_peak.pdf}
-    \caption{Log-log plot of the $A_\text{Higgs}$ spectral function near $\omega = \omega_0 = 2\Delta_\text{SC}$ in the SC phase at $U=-2.5t$ and $V=-0.1t$..
-    We additionally plot the difference between the Higgs and the phase spectral functions and fit it, as we interpret the latter as a background within the two-particle continuum.
+    \caption{Log-log plot of $\spectral{}{Higgs}$ near $\omega = \omega_0 = 2\Delta_\text{SC}$ in the SC phase at $U=-2.5t$ and $V=-0.1t$..
+    We additionally plot the difference between $\spectral{}{Higgs}$ and $\spectral{Phase}$ and fit it, as we interpret the latter as a background within the two-particle continuum.
     The upper (lower) panel shows the results for the square (simple cubic) lattice.
@@
 All fits are linear of the type $y = ax + b$ in double logarithmic plots, i.e., $a$ describes the power-law behavior of the functions.
-Firstly, the real part of the $A_\text{Phase}$ Green's function is shown in \autoref{fig:phase_peak}.
+Firstly, the real part of $\greens{}{Phase}$ is shown in \autoref{fig:phase_peak}.
 It behaves as $1/\omega^2$ indicating that the peak we find in the spectral function at $\omega=0$ corresponds to the derivative of a $\delta$ distribution.
 
-Continuing, we investigate the divergence at $\omega = 2\Delta$ found in the $A_\text{Higgs}$ spectral function within the SC phase.
+Continuing, we investigate the divergence at $\omega = 2\Delta$ found in $\spectral{Higgs}$ within the SC phase.
 It behaves as $1/\sqrt{\omega}$ as shown in \autoref{fig:higgs_peak}.
@@
 This indicates that the peaks are $\delta$ distributions.
-The $A_\text{AFM}$ and $A_\text{CDW}$ peaks close the the phase transition are identical when swapped, i.e., $\mathcal{A}_\text{AFM} (\omega)$ in the CDW phase is the same as $\mathcal{A}_\text{CDW} (\omega)$ in the AFM phase.
+The peaks of $\spectral{AFM}$ and $\spectral{CDW}$ close the the phase transition are identical when swapped, i.e., $\mathcal{A}_\text{AFM} (\omega)$ in the CDW phase is the same as $\mathcal{A}_\text{CDW} (\omega)$ in the AFM phase.
 
@@
 \end{equation}
-To give a practical example, let us compute $A_\text{Higgs}$ from \eqref{eqn:resolvent_bases}.
+To give a practical example, let us compute $\greens{Higgs}$ from \eqref{eqn:resolvent_bases}.
 We order our operator set such that all $f_\gamma^{(\dagger)}$ are upfront. 
@@
 The first line is an approximation of the integral in the second line, as each matrix element corresponds to a specific value for $\gamma$.
-Note, that the sum going up to $2N_\gamma$ rather than $N_\gamma$ merely arises from the fact, that we need to integrate over both $f_\gamma$ and $f_\gamma^\dagger$ to obtain $A_\text{Higgs}$.
+Note, that the sum going up to $2N_\gamma$ rather than $N_\gamma$ merely arises from the fact, that we need to integrate over both $f_\gamma$ and $f_\gamma^\dagger$ to obtain $\greens{Higgs}$.
 

### 2023-12-20 paper/resolvent_overview_AFM_CDW.py

@@ -13,21 +13,21 @@ from lib.iterate_containers import naming_scheme_tuples
 import lib.plot_settings as ps
 from lib.create_zoom import *
 
-params = [ [0., 4.1, 1.], [0., 3.9, 1.] ]
+params = [ [0., 4.1, 1.], [0., 3.9, 1.], [0., 4.5, 1.], [0., 3.5, 1.] ]
 
 folders = ["../data/modes/square/dos_3k/", "../data/modes/cube/dos_3k/"]
-nrows = 2
+nrows = 4
 ncols = 2
 # ax = axs[row][col]
-fig, axs = plt.subplots(nrows=nrows, ncols=ncols, figsize=(12.8, 6), sharey=True, sharex="col", gridspec_kw=dict(hspace=0, wspace=0))
+fig, axs = plt.subplots(nrows=nrows, ncols=ncols, figsize=(12.8, 10), sharey=True, sharex="col", gridspec_kw=dict(hspace=0, wspace=0))
 
 plotters = np.empty((nrows, ncols), dtype=ps.CURVEFAMILY)
 for i in range(nrows):
     for j in range(ncols):
         axs[i][j].set_ylim(0, .99)
         plotters[i][j] = ps.CURVEFAMILY(4, axis=axs[i][j])
-        plotters[i][j].set_individual_colors("nice2")
-        plotters[i][j].set_individual_dashes([(1,0), (6,6), (1,0), (6,6)])
+        plotters[i][j].set_individual_colors("nice")
+        plotters[i][j].set_individual_dashes([ [1,0], [3,6,3,0], [1.5, 2], [2,4,1.5,4,2,0] ])
 
 plot_lower_lim = 0#-0.05
 plot_upper_lim = 5.37
@@ -41,23 +41,26 @@ for j, folder in enumerate(folders):
         # the sc lattice uses a different V for the CDW-AFM border due to the changed coordination number
         params[0][1] = 6.1
         params[1][1] = 5.9
+        params[2][1] = 7.0
+        params[3][1] = 5.0
         
     for i, name in enumerate(naming_scheme_tuples(params)):
         resolvents = np.empty(len(name_suffices), dtype=cf.ContinuedFraction)
         for k, (name_suffix, label) in enumerate(zip(name_suffices, labels)):
[…]

### 2023-12-21 paper/resolvent_overview_AFM_CDW.py
text

@@ -13,7 +13,7 @@ from lib.iterate_containers import naming_scheme_tuples
 import lib.plot_settings as ps
 from lib.create_zoom import *
 
-params = [ [0., 4.1, 1.], [0., 3.9, 1.], [0., 4.5, 1.], [0., 3.5, 1.] ]
+params = [ [0., 4.1, 1.], [0., 3.9, 1.], [0., 4.6, 1.], [0., 3.4, 1.] ]
 
 folders = ["../data/modes/square/dos_3k/", "../data/modes/cube/dos_3k/"]
 nrows = 4
@@ -41,8 +41,8 @@ for j, folder in enumerate(folders):
         # the sc lattice uses a different V for the CDW-AFM border due to the changed coordination number
         params[0][1] = 6.1
         params[1][1] = 5.9
-        params[2][1] = 7.0
-        params[3][1] = 5.0
+        params[2][1] = 7.
+        params[3][1] = 5.
         
     for i, name in enumerate(naming_scheme_tuples(params)):
         resolvents = np.empty(len(name_suffices), dtype=cf.ContinuedFraction)
@@ -72,10 +72,10 @@ for i in range(nrows):
 axs[0][0].title.set_text("Square")
 axs[0][1].title.set_text("Simple cubic")
 
-axs[0][1].text(11.5, 0.66, "(a) AFM\n$zV + 0.1t$")
-axs[1][1].text(11.5, 0.66, "(b) CDW\n$zV - 0.1t$")
-axs[2][1].text(11.5, 0.66, "(a) AFM\n$z(V + 0.125t)$")
-axs[3][1].text(11.5, 0.66, "(b) CDW\n$z(V - 0.125t)$")
+axs[0][1].text(11.3, 0.66, "(a) AFM\n$zV + 0.1t$")
+axs[1][1].text(11.3, 0.66, "(b) CDW\n$zV - 0.1t$")
+axs[2][1].text(11.3, 0.66, "(a) AFM\n$z(V + 0.2t)$")
+axs[3][1].text(11.3, 0.66, "(b) CDW\n$z(V - 0.2t)$")
 
 fig.tight_layout()
 plt.savefig("plots/resolvent_overview_AFM_CDW.pdf")

### 2023-12-21 paper/main.tex
text

@@
 \begin{align}
-    G_{AB^\dagger} (z) &= - i \int_0^\infty \exp(izt) \langle [ A(t), B^\dagger(0) ] \rangle \mathrm{d}t
+    G_{AB^\dagger} (z) &= - i \int_0^\infty \exp(i z t) \langle [ A(t), B^\dagger(0) ] \rangle \mathrm{d}t
 \end{align}
@@
     The shaded area marks the two-particle continuum.
-    For each plot, the parameters are set to $U=-2.5t$ and $N_\gamma = 3000$, while $V$ is varied to according to the text in the individual panels.
+    For each plot, the parameters are set to $U=-2.5t$ and $N_\gamma = 3000$, while $V$ is varied according to the text in the individual panels.
     The panels show the spectral functions in the (a) pure SC phase, (b) SC/CDW-coexistence, and (c) and (d) pure CDW phase, respectively.}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%                                           Classification                                                  %%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Classification of the spectral functions}
@@
     The shaded area marks the two-particle continuum.
-    For each plot, the parameters are set to $V=1t$ and $N_\gamma = 3000$, while $U$ is varied to according to the text in the individual panels.
+    For each plot, the parameters are set to $V=1t$ and $N_\gamma = 3000$, while $U$ is varied according to the text in the individual panels.
     The panels (a) and (c) show the spectral functions in the AFM phase, and the panels (b) and (d) in the CDW phase.}
@@
 There are a variety of different features. The difference between the two lattices is mostly quantitative.
-First and foremost, in the SC phase, see panel (a), there is a sharp peak located at $\omega=0$ in $\mathcal{A}_\text{Phase}$,
-and another peak, only in $\spectral{Higgs}$, located at $\omega=2\Delta_\text{SC}$.
+First and foremost, in the SC phase, see panel (a), there is a sharp peak located at $\omega=0$ in $\mathcal{A}_\text{Phase}$ and a singularity in $\spectral{Higgs}$ located at $\omega=2\Delta_\text{SC}$.
 We identify them with the well-known Leggett and Higgs modes in superconductors.
 The former can be found at zero energy because our model describes a neutral superfluid wherein there is no coupling of the phase of the order parameter to the electromagnetic potential.
-Therefore, this phase may be chosen arbitrarily and changing it requires no energy which ultimately allows a Goldstone mode to exist in the first place. \textcolor{red}{Zitieren!}
+Therefore, this phase may be chosen arbitrarily, and changing it requires no energy which ultimately allows a Goldstone mode to exist in the first place. \textcolor{red}{Zitieren!}
+
+To classify the occurring peaks that lie outside the two-particle continuum, we turn towards the real part of the Green's function.
+We plot it in close proximity to the peaks with a double logarithmic scale and fit the result linearly $y = ax + b$ to obtain its power-law behavior.
+The real part is related to the imaginary part via the Kramers-Kronig relations.
+Specifically, if the imaginary part is a $\delta$ distribution, the real part will be proportional to $1/\omega$, i.e., $a=-1$, and the peak has the weight $w_0 = \exp(b)$.
+Furthermore, an exponent of $a=-2$ corresponds to the derivative of the $\delta$ distribution, i.e., $\delta'(\omega)$.
+The fits themselves can be found in appendix \autoref{sec:fit_greens_functions}.
+
+This analysis provides that the real part of $\greens{Phase}$ behaves as $1/\omega^2$ indicating that the peak in $\spectral{Phase}$ is the derivative of a $\delta$ distribution.
+Note, that it is located at $\omega=0$ of a perfectly asymmetrical bosonic spectral function and therefore must have 0 weight.
+This is given here, because $\int \delta'(\omega) \mathrm{d}\omega = 0$.
+
+\textcolor{red}{Ich spekuliere mal...}
+The singularity in $\spectral{Higgs}$ behaves as $1/\sqrt{\omega - 2 \Delta_\text{SC}}$.
+Previous studies on the dynamics of the order parameter found damped oscillations after a quench.
+These have the frequency $\Omega = 2 \Delta_\text{SC}$ and fell of as $1/\sqrt{t}$.
+An inverse Fourier transform of $\spectral{Higgs}$ yields precisely the same behavior, thereby reinforcing the validity of our results.
+
 In the CDW phase, both of these spectral functions become identical and form a sharp peak below the two-particle continuum.
@@
 \end{equation}
-with $r > 0$ and $u > 0$ if the system is outside of the superconducting phase. \textcolor{Zitieren!}
+with $r > 0$ and $u > 0$ if the system is outside of the superconducting phase. \textcolor{red}{Zitieren!}
 In this case, the only minimum is at $\Delta_\text{SC} = 0$. 
-That means that both possible modes have to overcome the same energy to be excited in the first place. \textcolor{red}{Passt die Beschreibung so?}
+That means that both possible modes have to overcome the same energy to be excited at all. \textcolor{red}{Passt die Beschreibung so?}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 At $V=0$, both the SC and the CDW phase coexist. 
-Here, $\spectral{Higgs}$ and $\spectral{CDW}$ are identical. Both have a peak at $\omega = 0$ and another one at $\omega = 2\Delta$.
+Since the degeneracy of both phases is exact \textcolor{red}{Zitat}, there should not be any difference between $\spectral{Higgs}$ and $\spectral{CDW}$ as both spectral functions capture the amplitude fluctuations of their respective order parameters.
+This is precisely what can be seen in panel (b) of \autoref{fig:resolvent_overview_SC}.
+Both spectral functions have a peak at $\omega = 0$ and a singularity at the lower edge of the two-particle continuum $\omega = 2\Delta_\text{tot}$, with $\Delta_\text{tot} \coloneqq \sqrt{|\Delta_\text{CDW}|^2 + |\Delta_\text{SC}|^2}$.
+
+\textcolor{red}{Ich spekuliere mal...}
+In this phase, the mean-field single-particle energies are given by
+\begin{equation}
+    E_{\pm} = \pm \sqrt{\epsilon^2 + |\Delta_\text{CDW}|^2 + |\Delta_\text{SC}|^2}\,.
+\end{equation}
+This means that the proper order parameter is $\Delta_\text{tot}$.
+Here, $\Delta_\text{CDW}$ and $\Delta_\text{SC}$ can change arbitrarily without affecting the system's energy as long as $\Delta_\text{tot}$ remains constant.
+Thus, we associate the peak at $\omega=0$ with this shifting of order parameters.
+The singularity at the lower edge of the two-particle continuum can be interpreted in a similar manner as the Higgs mode in a pure superconductor.
+It captures the change of $\Delta_\text{tot}$ by changing either one of the composing order parameters.
+
+$\spectral{Phase}$ behaves just as it does in the pure SC phase. It has only a peak at $\omega = 0$ that can be associated with the change of the phase of $\Delta_\text{SC}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 $\spectral{CDW}$ shows a peak below the continuum only in the SC phase corresponding to the finite energy necessary to excite this kind of electronic density modulation.
-For moderate sized values of $V>0$, i.e., in the CDW phase, see panel (c) at $V=0.1t$, the aforementioned spectral function has a peak at $\omega=2\Delta$.
+For moderate-sized values of $V>0$, i.e., in the CDW phase, see panel (c) at $V=0.1t$, the aforementioned spectral function has a peak at $\omega=2\Delta_\text{CDW}$.
 This peak becomes hard and moves outside the two-particle continuum as $V$ is increased, see panel (d) at $V=0.5t$.
@@
 For the square lattice, however, there is a peak located at the upper edge of the two-particle continuum.
-
-To further classify the aforementioned peaks that lie outside the two-particle continuum,
-we turn towards the real part of the Green's function.
-We plot it in close proximity to the peaks with a double logarithmic scale and fit the result linearly $y = ax + b$ to obtain its power-law behavior.
-The real part is related to the imaginary part via the Kramers-Kronig relations.
-Specifically, if the imaginary part is a $\delta$ distribution, the real part will be proportional to $1/\omega$, i.e., $a=-1$ and the peak has the weight $w_0 = \exp(b)$.
-Furthermore, an exponent of $a=-2$ corresponds to the derivative of the $\delta$ distribution, i.e., $\delta'(\omega - \omega_0)$.
 
@@
     \caption{The upper panels show double logarithmic plots of the positions $\omega_0$ of the SC peak in the CDW phases while the lower panels show their respective weights $w_0 = e^{b}$.
-    In the upper panel, the pink markers additionally show the peak position devided by the gap $\omega_0 / \Delta_\text{CDW}$.
+    In the upper panel, the pink markers additionally show the peak position divided by the gap $\omega_0 / \Delta_\text{CDW}$.
     The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
@@
 For $V \ll 1$, the position grows with the square root of $V$. This behavior then transitions to a purely linear growth for large $V$.
-Deviding $\omega_0$ by the gap $\Delta_\text{CDW}$ results in a plateau for large $V$ while leaving the square root behavior at the beginning mostly unchanged.
+Dividing $\omega_0$ by the gap $\Delta_\text{CDW}$ results in a plateau for large $V$ while leaving the square root behavior at the beginning mostly unchanged.
 

### 2024-01-08 paper/main.tex

@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_SC_CDW.pdf}
-    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
-    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
-    The left edge of each plot is at $-0.05$ rather than $0$ in order to improve the visibility of the phase peak.
-    The shaded area marks the two-particle continuum.
-    For each plot, the parameters are set to $U=-2.5t$ and $N_\gamma = 3000$, while $V$ is varied according to the text in the individual panels.
-    The panels show the spectral functions in the (a) pure SC phase, (b) SC/CDW-coexistence, and (c) and (d) pure CDW phase, respectively.}
-    \label{fig:resolvent_overview_SC}
-\end{figure*}
-
 In this section, we will be investigating four different diagonal Green's functions $G_{AA^\dagger}(\omega + i0^+)$, namely with
@@
     \centering
-    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_AFM_CDW.pdf}
+    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_SC_CDW.pdf}
     \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
     The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
+    The left edge of each plot is at $-0.05$ rather than $0$ in order to improve the visibility of the phase peak.
     The shaded area marks the two-particle continuum.
-    For each plot, the parameters are set to $V=1t$ and $N_\gamma = 3000$, while $U$ is varied according to the text in the individual panels.
-    The panels (a) and (c) show the spectral functions in the AFM phase, and the panels (b) and (d) in the CDW phase.}
-    \label{fig:resolvent_overview_AFM}
+    For each plot, the parameters are set to $U=-2.5t$ and $N_\gamma = 3000$, while $V$ is varied according to the text in the individual panels.
+    The panels show the spectral functions in the (a) pure SC phase, (b) SC/CDW-coexistence, and (c) and (d) pure CDW phase, respectively.}
+    \label{fig:resolvent_overview_SC}
 \end{figure*}
@@
 
-In the CDW phase, both of these spectral functions become identical and form a sharp peak below the two-particle continuum.
+In the CDW phase, see panels (c) and (d), both of $\spectral{Higgs}$ and $\spectral{Phase}$ become identical and form a $\delta$ peak below the two-particle continuum.
 Following the Landau theory for continuous phase transitions, this is to be expected as the free energy is expanded in terms of the order parameter as
@@
 At $V=0$, both the SC and the CDW phase coexist. 
-Since the degeneracy of both phases is exact \textcolor{red}{Zitat}, there should not be any difference between $\spectral{Higgs}$ and $\spectral{CDW}$ as both spectral functions capture the amplitude fluctuations of their respective order parameters.
+Since the degeneracy of both phases is exact due to the SO(4) symmetry \cite{yang90}, there should not be any difference between $\spectral{Higgs}$ and $\spectral{CDW}$ as both spectral functions capture the amplitude fluctuations of their respective order parameters.
 This is precisely what can be seen in panel (b) of \autoref{fig:resolvent_overview_SC}.
@@
 
-$\spectral{CDW}$ shows a peak below the continuum only in the SC phase corresponding to the finite energy necessary to excite this kind of electronic density modulation.
-For moderate-sized values of $V>0$, i.e., in the CDW phase, see panel (c) at $V=0.1t$, the aforementioned spectral function has a peak at $\omega=2\Delta_\text{CDW}$.
-This peak becomes hard and moves outside the two-particle continuum as $V$ is increased, see panel (d) at $V=0.5t$.
+In the SC phase, $\spectral{CDW}$ features a $\delta$ peak below the continuum corresponding to the finite energy necessary to excite this kind of electronic density modulation.
+For moderate-sized values of $V>0$, i.e., in the CDW phase, see panel (c) at $V=0.1t$, the aforementioned spectral function has a singularity at $\omega=2\Delta_\text{CDW}$.
+This mode becomes hard and moves outside the two-particle continuum as $V$ is increased, see panel (d) at $V=0.5t$.
+\textcolor{red}{Ich muss mal suchen, ob sowas schonmal beobachtet wurde.}
 
 $\spectral{AFM}$ is restricted to the continuum for both phases and both lattices.
-For the square lattice, however, there is a peak located at the upper edge of the two-particle continuum.
+For the square lattice, however, there is a singularity located at the upper edge of the two-particle continuum.
 
@@
 Using the same methodology as before we obtain that the exponent is $a\approx-0.5$, indicating that the peak behaves as $1 / \sqrt{\omega - \omega_0}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_AFM_CDW.pdf}
+    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
+    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
+    The shaded area marks the two-particle continuum.
+    For each plot, the parameters are set to $V=1t$ and $N_\gamma = 3000$, while $U$ is varied according to the text in the individual panels.
+    The panels (a) and (c) show the spectral functions in the AFM phase, and the panels (b) and (d) in the CDW phase.}
+    \label{fig:resolvent_overview_AFM}
+\end{figure*}
 

### 2024-01-08 paper/main.tex
Clean unused data

@@
 There are a variety of different features. The difference between the two lattices is mostly quantitative.
-First and foremost, in the SC phase, see panel (a), there is a sharp peak located at $\omega=0$ in $\mathcal{A}_\text{Phase}$ and a singularity in $\spectral{Higgs}$ located at $\omega=2\Delta_\text{SC}$.
+First and foremost, in the SC phase, see panel (a), there is a sharp peak located at $\omega=0$ in $\spectral{Phase}$ and a singularity in $\spectral{Higgs}$ located at $\omega=2\Delta_\text{SC}$.
 We identify them with the well-known Leggett and Higgs modes in superconductors.
@@
 
-This analysis provides that the real part of $\greens{Phase}$ behaves as $1/\omega^2$ indicating that the peak in $\spectral{Phase}$ is the derivative of a $\delta$ distribution.
+This analysis provides that the real part of $\greens{Phase}$ near $\omega=0$ behaves as $1/\omega^2$ indicating that the peak in $\spectral{Phase}$ is the derivative of a $\delta$ distribution.
 Note, that it is located at $\omega=0$ of a perfectly asymmetrical bosonic spectral function and therefore must have 0 weight.
@@
 Previous studies on the dynamics of the order parameter found damped oscillations after a quench.
-These have the frequency $\Omega = 2 \Delta_\text{SC}$ and fell of as $1/\sqrt{t}$.
+These have the frequency $\Omega = 2 \Delta_\text{SC}$ and fall off as $1/\sqrt{t}$ \cite{Yuzbashyan06}.
 An inverse Fourier transform of $\spectral{Higgs}$ yields precisely the same behavior, thereby reinforcing the validity of our results.
@@
 At $V=0$, both the SC and the CDW phase coexist. 
-Since the degeneracy of both phases is exact due to the SO(4) symmetry \cite{yang90}, there should not be any difference between $\spectral{Higgs}$ and $\spectral{CDW}$ as both spectral functions capture the amplitude fluctuations of their respective order parameters.
+Since the degeneracy of both phases is exact due to the SO(4) symmetry \cite{yang90}, 
+there should not be any difference between $\spectral{Higgs}$ and $\spectral{CDW}$ as both spectral functions capture the amplitude fluctuations of their respective order parameters.
 This is precisely what can be seen in panel (b) of \autoref{fig:resolvent_overview_SC}.
@@
 
-The plots for the phase peak and the CDW peak in the SC phase can be found in appendix \autoref{sec:fit_greens_functions}.
-The SC peak in the CDW phase behaves similarly to the latter and is therefore not shown explicitly.
-We get a good agreement with the power-law behavior near the peaks with the exponents $a=-2$ (phase) and $a=-1$ (CDW), respectively.
-Therefore, we conclude that the CDW peak corresponds to a $\delta$ distribution, while the phase peak is its derivative.
-Note, that the latter is located at $\omega=0$ of a perfectly asymmetrical bosonic spectral function and therefore must have 0 weight.
-This is given here, because $\int \delta'(\omega) \mathrm{d}\omega = 0$.
-The peak itself can be interpreted as two $\delta$ distributions at $0^\pm$.
-
-Next, we will investigate the Higgs peak, this time around, turning toward the spectral function itself. 
-We see in \autoref{fig:resolvent_overview_SC} that the Higgs and phase spectral functions become indistinguishable towards the upper half of the two-particle continuum.
-Therefore, we interpret the latter as a background to the Higgs peak itself and compute the difference between both spectral functions.
-Using the same methodology as before we obtain that the exponent is $a\approx-0.5$, indicating that the peak behaves as $1 / \sqrt{\omega - \omega_0}$.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Lastly, we investigate the same spectral functions close to the AFM-CDW phase transition, depicted in \autoref{fig:resolvent_overview_AFM}.
-We choose $V=1t$ for both lattices and $U=zV \pm 0.1t$, where $z$ is the coordination number.
+We choose $V=1t$ for both lattices and $U=zV \pm 0.1t$, where $z$ is the coordination number, see panels (a) and (b).
 Again, both SC-related spectral functions are identical in both the CDW and AFM phases.
 Within the continuum their weight is shifted towards the upper edge and on the square lattice only, there is a peak above the continuum.
-In the AFM phase, both the CDW and AFM spectral functions have a peak close, but yet below, the two-particle continuum.
-The AFM peak is at a lower energy than the CDW one.
-In the CDW phase, this behavior is reversed, i.e., the CDW peak lies lower.
+In the AFM phase, both $\spectral{AFM}$ and $\spectral{CDW}$ have a peak close, but yet below, the two-particle continuum.
+The peak of the former is at a lower energy than the peak of the latter.
+In the CDW phase, this behavior is reversed, i.e., the peak in $\spectral{CDW}$ lies lower.
 Using the same analysis as before, we conclude that each of these peaks is a $\delta$ peak.
+Moving further away from the phase transition, here $U=z(V+0.2t)$ in panels (c) and (d), the upper peak becomes soft as it shifts into the quasiparticle continuum.
 
@@
 With the prevalent peaks discussed, we turn towards their behavior as the system approaches the phase transition at $V=0$ for $U=-2.5t$.
-First and foremost, we investigate the peak in $\mathcal{A}_\text{Phase}(\omega)$ and $\mathcal{A}_\text{Higgs}(\omega)$ in the CDW phase.
+First and foremost, we investigate the peak in $\spectral{Phase}$ and $\spectral{Higgs}$ in the CDW phase.
 The evolution of its position $\omega_0$ and its weight $w_0$ as $V$ is varied can be viewed double logarithmically in \autoref{fig:sc_in_cdw_behavior}.
-For $V \ll 1$, the position grows with the square root of $V$. This behavior then transitions to a purely linear growth for large $V$.
+For $V \ll t$, the position grows with the square root of $V$. This behavior then transitions to a purely linear growth for large $V$.
 Dividing $\omega_0$ by the gap $\Delta_\text{CDW}$ results in a plateau for large $V$ while leaving the square root behavior at the beginning mostly unchanged.
+
+The peak weights $w_0$ fall off as $1/\sqrt{V}$ for $V \ll t$. 
+Afterward, it reaches a shallow minimum and rises slightly to reach a constant value.
 
@@
 
-\begin{figure}
+\begin{figure*}
     \centering
-    \includegraphics[width=0.48\textwidth]{plots/phase_peak.pdf}
-    \caption{Log-log plot of the real part of $\spectral{Phase}$ in the SC phase at $U=-2.5t$ and $V=-0.1t$ as well as a linear fit to it.
-    The upper (lower) panel shows the results for the square (simple cubic) lattice.
-    The function behaves as $1/\omega^2$ indicating that the peak in the spectral function is the derivative of a $\delta$ distribution.}
-    \label{fig:phase_peak}
-\end{figure}
+    \includegraphics[width=0.98\textwidth]{plots/zero_peaks.pdf}
+    \caption{The upper panel shows a log-log plot of the real part of $\spectral{Phase}$ in the SC phase at $U=-2.5t$ and $V=-0.1t$ as well as a linear fit to it.
+    The lower panel shows the same plot for $\spectral{Higgs}$ in the coexistence phase at $V=0$. The columns show the results for the square and the simple cubic lattice, respectively.
+    The functions behave as $1/\omega^2$ indicating that the peaks in the spectral functions are the derivative of a $\delta$ distribution.}
+    \label{fig:zero_peaks}
+\end{figure*}
 
@@
     \includegraphics[width=.48\textwidth]{plots/higgs_peak.pdf}
-    \caption{Log-log plot of $\spectral{}{Higgs}$ near $\omega = \omega_0 = 2\Delta_\text{SC}$ in the SC phase at $U=-2.5t$ and $V=-0.1t$..
-    We additionally plot the difference between $\spectral{}{Higgs}$ and $\spectral{Phase}$ and fit it, as we interpret the latter as a background within the two-particle continuum.
+    \caption{Log-log plot of $\spectral{Higgs}$ near $\omega = \omega_0 = 2\Delta_\text{SC}$ in the SC phase at $U=-2.5t$ and $V=-0.1t$.
+    We additionally plot the difference between $\spectral{Higgs}$ and $\spectral{Phase}$ and fit it, as we interpret the latter as a background within the two-particle continuum.
     The upper (lower) panel shows the results for the square (simple cubic) lattice.
@@
         The results for both lattice types are shown but are qualitatively identical.
-        The power-law exponent is $a=-1$ in cases, indicating that these peaks are $\delta$ distributions.}
+        The power-law exponent is $a=-1$ in all cases, indicating that these peaks are $\delta$ distributions.}
         \label{fig:peak_fits}
@@
 All fits are linear of the type $y = ax + b$ in double logarithmic plots, i.e., $a$ describes the power-law behavior of the functions.
-Firstly, the real part of $\greens{}{Phase}$ is shown in \autoref{fig:phase_peak}.
+Firstly, the real part of $\greens{Phase}$ in the SC phase is shown in panel (a) of \autoref{fig:zero_peaks}.
 It behaves as $1/\omega^2$ indicating that the peak we find in the spectral function at $\omega=0$ corresponds to the derivative of a $\delta$ distribution.
+The same results are obtained for the peak in $\spectral{Higgs}$ and $\spectral{CDW}$ in the coexistence phase.
 
@@
 This indicates that the peaks are $\delta$ distributions.
-The peaks of $\spectral{AFM}$ and $\spectral{CDW}$ close the the phase transition are identical when swapped, i.e., $\mathcal{A}_\text{AFM} (\omega)$ in the CDW phase is the same as $\mathcal{A}_\text{CDW} (\omega)$ in the AFM phase.
+The peaks of $\spectral{AFM}$ and $\spectral{CDW}$ close the the phase transition are identical when swapped, i.e., $\spectral{AFM}$ in the CDW phase is the same as $\spectral{CDW}$ in the AFM phase.
 
@@
 \begin{equation}
-    ( f_{\vk}^\dagger | f_{\vl}^\dagger ) = \delta_{\vk, \vl} \langle 1 - n_{\vk \uparrow} - n_{\vk \downarrow} \rangle \eqqcolon \delta_{\vk, \vl} \alpha(\vk)
+    ( f_{\vk}^\dagger | f_{\vl}^\dagger ) = \delta_{\vk, \vl}\, \langle 1 - n_{\vk \uparrow} - n_{\vk \downarrow} \rangle \eqqcolon \delta_{\vk, \vl}\, \alpha(\vk)
 \end{equation}
 holds. Inserting this into \eqref{eqn:numerical_example} yields
-\begin{align}
-    (A_i | A_j) &= \frac{1}{N} \sum_{\vk} h(\gamma_i - \hat{\gamma}(\vk)) h(\gamma_j - \hat{\gamma}(\vk)) \alpha(\vk)\,.
-\end{align}
+\begin{equation}
+    (A_i | A_j) = \frac{1}{N} \sum_{\vk} h(\gamma_i - \hat{\gamma}(\vk)) h(\gamma_j - \hat{\gamma}(\vk)) \alpha(\vk)\,.
+\end{equation}
 As stated in the main text, see \eqref{eqn:equal_expecs}, $\alpha(\vk)$ depends only on $\hat{\gamma}(\vk)$, hence we can switch from the momentum sum to a $\gamma$ integration
@@
 \begin{equation}
-    G_{AB^\dagger} = - (\Delta \gamma)^2 \vec{b}^\dagger (0) \left[ \tilde{n} \frac{1}{\tilde{m} + z \tilde{n}} \tilde{n} \right] \vec{a}(0)\,.
+    G_{AB^\dagger}(z) = - (\Delta \gamma)^2 \vec{b}^\dagger (0) \left[ \tilde{n} \frac{1}{\tilde{m} + z \tilde{n}} \tilde{n} \right] \vec{a}(0)\,.
 \end{equation}
 To give a practical example, let us compute $\greens{Higgs}$ from \eqref{eqn:resolvent_bases}.
-We order our operator set such that all $f_\gamma^{(\dagger)}$ are upfront. 
+We order our operator set such that all $f_\gamma + f_\gamma^{\dagger}$ are upfront. 
 This requires the vector elements $\vec{a}$ and $\vec{b}$ to be
@@
     a_i = b_i = \begin{cases}
-        1 & i < 2 N_\gamma \\
+        1 & i < N_\gamma \\
         0 & \text{otherwise}
@@
 \begin{align}
-    G_{AB^\dagger} (z) &= -(\Delta \gamma)^2 \sum_{i=0}^{2 N_\gamma} \sum_{j=0}^{2 N_\gamma} \left[ \tilde{n} \frac{1}{\tilde{m} + z \tilde{n}} \tilde{n} \right]_{ij} \nonumber \\
+    \greens{Higgs} (z) &= -(\Delta \gamma)^2 \sum_{i=0}^{N_\gamma} \sum_{j=0}^{N_\gamma} \left[ \tilde{n} \frac{1}{\tilde{m} + z \tilde{n}} \tilde{n} \right]_{ij} \nonumber \\
         &\approx - \int \dgamma \int \dgamma' \left[ \tilde{n} \frac{1}{\tilde{m} + z \tilde{n}} \tilde{n} \right](\gamma, \gamma')\,.
@@
 The first line is an approximation of the integral in the second line, as each matrix element corresponds to a specific value for $\gamma$.
-Note, that the sum going up to $2N_\gamma$ rather than $N_\gamma$ merely arises from the fact, that we need to integrate over both $f_\gamma$ and $f_\gamma^\dagger$ to obtain $\greens{Higgs}$.
 

### 2024-01-08 paper/phase_peak.py
Clean unused data

@@ -1,49 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-
-import os, sys
-if os.name == "nt":
-    sys.path.append(os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + r"\python")
-else:
-    sys.path.append(os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + "/python")
-import lib.continued_fraction as cf
-import lib.plot_settings as ps
-
-from scipy.optimize import curve_fit
-def func_ln(x, a, b):
-    return a * x + b
-
-T = 0.
-U = -2.5
-V = -0.1
-
-folders = ["../data/modes/square/dos_3k/", "../data/modes/cube/dos_3k/"]
-labels = ["Square", "Simple cubic"]
-name_suffix = "phase_SC"
-fig, axs = plt.subplots(nrows=2, figsize=(6.4, 4.8), sharex=True, gridspec_kw=dict(hspace=0, wspace=0))
-
-plotters = np.empty(2, dtype=ps.CURVEFAMILY)
-
-for i in range(2):
-    plotters[i] = ps.CURVEFAMILY(4, axis=axs[i])
-    plotters[i].set_individual_colors("nice2")
-    plotters[i].set_individual_dashes()
-
-    name = f"T={T}/U={U}/V={V}"
-    data_imag, data, w_log, res = cf.resolvent_data_log_z(f"{folders[i]}{name}", name_suffix, lower_edge=0, begin_offset=3e-3, range=0.2, xp_basis=True, imaginary_offset=0, number_of_values=1000, messages=False)
-    
-    data = np.log(data)
-    plotters[i].plot(w_log, data, label=f"Data")
-    popt, pcov = curve_fit(func_ln, w_log, data)
-    plotters[i].plot(w_log, func_ln(w_log, *popt), label=f"Fit")
-    axs[i].text(0.05, 0.4, f"$a={popt[0]:.4f}\pm{np.sqrt(pcov[0][0]):.4f}$", transform = axs[i].transAxes)
-    axs[i].text(0.05, 0.3, f"$b={popt[1]:.4f}\pm{np.sqrt(pcov[1][1]):.4f}$", transform = axs[i].transAxes)
-
-axs[0].legend()
-axs[1].set_xlabel(r"$\ln(\omega / t)$")
[…]

### 2024-01-11 paper/main.tex
home

@@
 Using the same analysis as before, we conclude that each of these peaks is a $\delta$ peak.
-Moving further away from the phase transition, here $U=z(V+0.2t)$ in panels (c) and (d), the upper peak becomes soft as it shifts into the quasiparticle continuum.
+Moving further away from the phase transition, here $U=z(V+0.2t)$ in panels (c) and (d), the upper peak becomes soft as it shifts into the two-particle continuum.
 

### 2024-01-12 paper/main.tex
Läuft

@@
 
+\textcolor{red}{Intro auf die Phasen und Anregungen beziehen, danach Theorie auspacken}
 The Hubbard model has been studied in a plethora of previous studies. 
@@
 
+\begin{figure*}
+    \centering
+    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_SC_CDW.pdf}
+    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
+    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
+    The left edge of each plot is at $-0.05$ rather than $0$ in order to improve the visibility of the phase peak.
+    The shaded area marks the two-particle continuum.
+    For each plot, the parameters are set to $U=-2.5t$ and $N_\gamma = 3000$, while $V$ is varied according to the text in the individual panels.
+    The panels show the spectral functions in the (a) SC phase and the (b and c) CDW phase, respectively.}
+    \label{fig:resolvent_overview_SC}
+\end{figure*}
+
 \section{Results}\label{sec:results}
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_SC_CDW.pdf}
-    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
-    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
-    The left edge of each plot is at $-0.05$ rather than $0$ in order to improve the visibility of the phase peak.
-    The shaded area marks the two-particle continuum.
-    For each plot, the parameters are set to $U=-2.5t$ and $N_\gamma = 3000$, while $V$ is varied according to the text in the individual panels.
-    The panels show the spectral functions in the (a) pure SC phase, (b) SC/CDW-coexistence, and (c) and (d) pure CDW phase, respectively.}
-    \label{fig:resolvent_overview_SC}
-\end{figure*}
-
 To begin, let us describe the spectral functions $\mathcal{A}_i (\omega) = - (1/\pi) \Im [\mathcal{G}_i (\omega + i0^+)]$ with respect to the operators above in the various phases.
@@
 
-To classify the occurring peaks that lie outside the two-particle continuum, we turn towards the real part of the Green's function.
+To classify the occurring peaks that lie outside the two-particle continuum, we turn toward the real part of the Green's function.
 We plot it in close proximity to the peaks with a double logarithmic scale and fit the result linearly $y = ax + b$ to obtain its power-law behavior.
@@
 
-\textcolor{red}{Ich spekuliere mal...}
 The singularity in $\spectral{Higgs}$ behaves as $1/\sqrt{\omega - 2 \Delta_\text{SC}}$.
@@
 
-In the CDW phase, see panels (c) and (d), both of $\spectral{Higgs}$ and $\spectral{Phase}$ become identical and form a $\delta$ peak below the two-particle continuum.
+In the CDW phase, see panels (b) and (c), both of $\spectral{Higgs}$ and $\spectral{Phase}$ become identical and form a $\delta$ peak below the two-particle continuum.
 Following the Landau theory for continuous phase transitions, this is to be expected as the free energy is expanded in terms of the order parameter as
@@
 
+In the SC phase, $\spectral{CDW}$ features a $\delta$ peak below the continuum corresponding to the finite energy necessary to excite this kind of electronic density modulation.
+For moderate-sized values of $V>0$, i.e., in the CDW phase, see panel (b) at $V=0.1t$, the aforementioned spectral function has a singularity at $\omega=2\Delta_\text{CDW}$.
+This mode becomes hard and moves outside the two-particle continuum as $V$ is increased, see panel (c) at $V=0.5t$.
+
+$\spectral{AFM}$ is restricted to the continuum for both phases and both lattices.
+For the square lattice, however, there is a singularity located at the upper edge of the two-particle continuum.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+\begin{figure*}
+    \centering
+    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_V0.pdf}
+    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
+    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
+    The left edge of each plot is at $-0.05$ rather than $0$ in order to improve the visibility of the peaks at $\omega=0$.
+    The shaded area marks the two-particle continuum.
+    For each plot, the parameters are set to $U=-2.5t$, $V=0$, and $N_\gamma = 3000$.
+    Since the ratio of $\Delta_\text{SC}$ to $\Delta_\text{CDW}$ may be chosen arbitrarily, we show in (a) the spectral functions for $\Delta_\text{CDW} = 0$ and in (b) for $\Delta_\text{SC} = 0$.}
+    \label{fig:resolvent_overview_V0}
+\end{figure*}
+
 At $V=0$, both the SC and the CDW phase coexist. 
-Since the degeneracy of both phases is exact due to the SO(4) symmetry \cite{yang90}, 
-there should not be any difference between $\spectral{Higgs}$ and $\spectral{CDW}$ as both spectral functions capture the amplitude fluctuations of their respective order parameters.
-This is precisely what can be seen in panel (b) of \autoref{fig:resolvent_overview_SC}.
-Both spectral functions have a peak at $\omega = 0$ and a singularity at the lower edge of the two-particle continuum $\omega = 2\Delta_\text{tot}$, with $\Delta_\text{tot} \coloneqq \sqrt{|\Delta_\text{CDW}|^2 + |\Delta_\text{SC}|^2}$.
-
-\textcolor{red}{Ich spekuliere mal...}
 In this phase, the mean-field single-particle energies are given by
@@
 \end{equation}
-This means that the proper order parameter is $\Delta_\text{tot}$.
+This means that the proper order parameter is $\Delta_\text{tot} \coloneqq \sqrt{|\Delta_\text{CDW}|^2 + |\Delta_\text{SC}|^2}$.
 Here, $\Delta_\text{CDW}$ and $\Delta_\text{SC}$ can change arbitrarily without affecting the system's energy as long as $\Delta_\text{tot}$ remains constant.
-Thus, we associate the peak at $\omega=0$ with this shifting of order parameters.
-The singularity at the lower edge of the two-particle continuum can be interpreted in a similar manner as the Higgs mode in a pure superconductor.
+Note that the degeneracy of both phases is exact due to the SO(4) symmetry \cite{yang90}.
+
+In \autoref{fig:resolvent_overview_V0}, we show the spectral functions for $U=-2.5t$ and $V=0$.
+The different panels correspond to different choices for $\Delta_\text{CDW}$ and $\Delta_\text{SC}$.
+First, in panel (a), we set $\Delta_\text{CDW} = 0$.
+This results in a purely superconducting phase with the same features as in \autoref{fig:resolvent_overview_SC} panel (a).
+The peak in $\spectral{CDW}$ moves to a very small, yet finite, $\omega$.
+
+Secondly, panel (b) shows the spectral functions for $\Delta_\text{SC} = 0$, i.e., in a purely charge-ordered phase.
+Similar to before, there is not much change compared to \autoref{fig:resolvent_overview_SC} panel (b).
+The spectral functions $\spectral{Higgs}$ and $\spectral{Phase}$ are still identical, however, both exhibit a sharp peak at $\omega=0$.
+This peak is described by $\delta'(\omega)$.
+\textcolor{red}{Warum hat Higgs nun einen Peak bei 0, aber CDW hatte einen bei endlichem $\omega$?
+Das müsste ja bedeuten, dass ein Cooper-Paar energtisch kostenfrei ist, aber ein CDW-Exziton kostet uns etwas Energie.}
+
+Lastly, we chose $\Delta_\text{CDW} = \Delta_\text{SC}$ for panel (c).
+Now, $\spectral{Higgs}$ and $\spectral{CDW}$ are identical.
+Note, that this only occurs for this specific ratio of $\Delta_\text{CDW}$ and $\Delta_\text{SC}$, otherwise the occurring peaks differ in magnitude.
+Both spectral functions have a peak at $\omega = 0$, described by $\delta'(\omega)$, and a singularity at the lower edge of the two-particle continuum $\omega = 2\Delta_\text{tot}$.
+\textcolor{red}{TODO: Exponent}
+
+We associate the peak at $\omega=0$ with this shifting of order parameters, i.e., diminishing one and increasing the other while keeping $\Delta_\text{tot}$ constant.
+The singularity at the lower edge of the two-particle continuum can be interpreted similarly to the Higgs mode in a pure superconductor.
 It captures the change of $\Delta_\text{tot}$ by changing either one of the composing order parameters.
@@
 $\spectral{Phase}$ behaves just as it does in the pure SC phase. It has only a peak at $\omega = 0$ that can be associated with the change of the phase of $\Delta_\text{SC}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In the SC phase, $\spectral{CDW}$ features a $\delta$ peak below the continuum corresponding to the finite energy necessary to excite this kind of electronic density modulation.
-For moderate-sized values of $V>0$, i.e., in the CDW phase, see panel (c) at $V=0.1t$, the aforementioned spectral function has a singularity at $\omega=2\Delta_\text{CDW}$.
-This mode becomes hard and moves outside the two-particle continuum as $V$ is increased, see panel (d) at $V=0.5t$.
-\textcolor{red}{Ich muss mal suchen, ob sowas schonmal beobachtet wurde.}
-
-$\spectral{AFM}$ is restricted to the continuum for both phases and both lattices.
-For the square lattice, however, there is a singularity located at the upper edge of the two-particle continuum.
 
@@
 Afterward, it reaches a shallow minimum and rises slightly to reach a constant value.
+
+Specifically, we learn that for $V \ll t$, the peak position follows $\omega_0 = \alpha \sqrt{V}$ and its weight follows $w_0 = \beta / \sqrt{V}$, where $\alpha$ and $\beta$ are some constants.
+This allows us to write $w_0 = \beta / (\alpha \omega_0)$. Furthermore, we know that the spectral functions need to be perfectly antisymmetrical about $\omega = 0$, i.e. we can observe
+\begin{align}
+    \mathcal{A}_\text{Phase} (\omega \ll t) &= w_0 (\delta (\omega - \omega_0) - \delta (\omega + \omega_0)) \nonumber \\
+        &= - \frac{2\beta}{\alpha} \frac{\delta (\omega + \omega_0) - \delta (\omega - \omega_0)}{2\omega_0} \,.
+\end{align} 
+Taking the limit of $V \to 0$ corresponds to the limit $\omega_0 \to 0$, i.e., leading to an expression reminiscent of symmetric derivative
+\begin{equation}
+    \lim_{h \to 0} \frac{f(x + h) - f(x - h)}{2h} = f'(x)\,,
+\end{equation}
+where the equality holds for any differentiable $f$.
+Applying this to our case yields
+\begin{align}
+    \lim_{\omega_0 \to 0} \mathcal{A}_\text{Phase} (\omega \ll t) = - \frac{2 \beta}{\alpha} \delta'(\omega)\,.
+\end{align}
+This analysis reinforces our previous identification of the phase peak as $\delta' (\omega)$.
 

### 2024-01-12 paper/resolvent_overview_V0.py

@@ -12,9 +12,12 @@ from lib.iterate_containers import naming_scheme_tuples
 import lib.plot_settings as ps
 from lib.create_zoom import *
 
-params = [ [0., -2.5, -0.1], [0., -2.5, 0.1], [0., -2.5, 0.5] ]
+T = 0.0
+U = -2.5
+V = 0.0
 
-folders = ["../data/modes/square/dos_3k/", "../data/modes/cube/dos_3k/"]
+folders = ["../data/modes/square/dos_3k", "../data/modes/cube/dos_3k"]
+folder_extensions = ["_SC/", "_CDW/", "/"]
 nrows = 3
 ncols = 2
 # ax = axs[row][col]
@@ -36,25 +39,20 @@ labels = ["Phase", "Higgs", "CDW", "AFM"]
 
 for j, folder in enumerate(folders):
     usage_upper_lim = 2 * plot_upper_lim if j == 0 else 3 * plot_upper_lim
-
-    for i, name in enumerate(naming_scheme_tuples(params)):
+    name = f"T={T}/U={U}/V={V}"
+    for i, folder_extension in enumerate(folder_extensions):
         resolvents = np.empty(len(name_suffices), dtype=cf.ContinuedFraction)
         for k, (name_suffix, label) in enumerate(zip(name_suffices, labels)):
-            data, data_real, w_lin, resolvents[k] = cf.resolvent_data(f"{folder}{name}", name_suffix, plot_lower_lim, usage_upper_lim, 
+            data, data_real, w_lin, resolvents[k] = cf.resolvent_data(f"{folder}{folder_extension}{name}", name_suffix, plot_lower_lim, usage_upper_lim, 
                                                             number_of_values=7000, xp_basis=True, imaginary_offset=1e-5, messages=False)
             plotters[i][j].plot_with_peak(w_lin, data, label=label)
             
         axs[i][j].set_xlim(plot_lower_lim, usage_upper_lim)
-        if i == 2:
-            cont = np.sqrt(resolvents[0].roots[0])
-            zommed_xlim = (cont - 0.08, cont + 0.03) 
[…]

### 2024-01-15 paper/main.tex
uni

@@
     \centering
-    \includegraphics[width=.98\textwidth]{plots/sc_peak_in_cdw_position.pdf}
+    \includegraphics[width=.98\textwidth]{plots/sc_peak_in_cdw.pdf}
     \caption{The upper panels show double logarithmic plots of the positions $\omega_0$ of the SC peak in the CDW phases while the lower panels show their respective weights $w_0 = e^{b}$.
@@
 
-Specifically, we learn that for $V \ll t$, the peak position follows $\omega_0 = \alpha \sqrt{V}$ and its weight follows $w_0 = \beta / \sqrt{V}$, where $\alpha$ and $\beta$ are some constants.
-This allows us to write $w_0 = \beta / (\alpha \omega_0)$. Furthermore, we know that the spectral functions need to be perfectly antisymmetrical about $\omega = 0$, i.e. we can observe
+Specifically, we learn that for $V \ll t$, the peak position follows $\omega_0 = \alpha \sqrt{V}$ and its weight follows $w_0 = \beta / \sqrt{V}$, 
+where $\alpha$ and $\beta$ are some constants.
+This allows us to write $w_0 = \beta / (\alpha \omega_0)$. 
+Furthermore, we know that the spectral functions need to be perfectly antisymmetrical about $\omega = 0$, i.e., we can observe
 \begin{align}

### 2024-01-15 paper/resolvent_overview_V0.py

@@ -29,7 +29,7 @@ for i in range(nrows):
         axs[i][j].set_ylim(0, .99)
         plotters[i][j] = ps.CURVEFAMILY(4, axis=axs[i][j])
         plotters[i][j].set_individual_colors("nice")
-        plotters[i][j].set_individual_dashes([ [1,0], [3,6,3,0], [1.5, 2], [2,4,1.5,4,2,0] ])
+        plotters[i][j].set_individual_dashes([ [1,0], [3,6,3,0], [1.5, 2], [3,5,1.5,5,3,0] ])
 
 plot_lower_lim = -0.05
 plot_upper_lim = 4.25

### 2024-01-15 paper/sc_peak_in_cdw.py

@@ -18,20 +18,20 @@ from scipy.optimize import curve_fit
 Ts = np.array([0.])
 Us = np.array([-2.5])
 Vs = np.array(["0.00001", "0.000013", "0.000015", "0.000017", "0.00002", "0.000025", 
-               "0.00003", "0.00004", "0.00005", "0.00006", "0.00007", "0.00008", "0.00009", 
-               
-               "0.0001", "0.00013", "0.00015", "0.00017", "0.0002", "0.00025", "0.0003", 
-               "0.0004", "0.0005", "0.0006", "0.0007", "0.0008", "0.0009", 
-               
-               "0.001", "0.0013", "0.0015", "0.0017", "0.002", "0.0025", 
-               "0.003", "0.004", "0.005", "0.006", "0.007", "0.008", "0.009", 
-               
-               "0.01", "0.013", "0.015", "0.017", "0.02", "0.025", 
-               "0.03", "0.04", "0.05", "0.06", "0.07", "0.08", "0.09", 
-               
-               "0.1", "0.13", "0.15", "0.2", "0.25", "0.3", "0.35", "0.4", "0.45", "0.5", "0.6", "0.7", "0.8", "0.9", 
-               "1.0", "1.1", "1.2", "1.3", "1.4", "1.5", "1.6", "1.7", "1.8", "1.9", "2.0", 
-               "2.5", "3.0", "3.5", "4.0", "6.0", "8.0", "10.0", "15.0", "25.0", "50.0"])
+                "0.00003", "0.00004", "0.00005", "0.00006", "0.00007", "0.00008", "0.00009", 
+                
+                "0.0001", "0.00013", "0.00015", "0.00017", "0.0002", "0.00025", "0.0003", 
+                "0.0004", "0.0005", "0.0006", "0.0007", "0.0008", "0.0009", 
+                
+                "0.001", "0.0013", "0.0015", "0.0017", "0.002", "0.0025", 
+                "0.003", "0.004", "0.005", "0.006", "0.007", "0.008", "0.009", 
+                
+                "0.01", "0.013", "0.015", "0.017", "0.02", "0.025", 
+                "0.03", "0.04", "0.05", "0.06", "0.07", "0.08", "0.09", 
+                
+                "0.1", "0.13", "0.15", "0.2", "0.25", "0.3", "0.35", "0.4", "0.45", "0.5", "0.6", "0.7", "0.8", "0.9", 
[…]

### 2024-01-15 paper/resolvent_overview_SC_CDW.py
uni

@@ -26,7 +26,7 @@ for i in range(nrows):
         axs[i][j].set_ylim(0, .99)
         plotters[i][j] = ps.CURVEFAMILY(4, axis=axs[i][j])
         plotters[i][j].set_individual_colors("nice")
-        plotters[i][j].set_individual_dashes([ [1,0], [3,6,3,0], [1.5, 2], [2,4,1.5,4,2,0] ])
+        plotters[i][j].set_individual_dashes([ [1,0], [3,6,3,0], [1.5, 2], [3,5,1.5,5,3,0] ])
 
 plot_lower_lim = -0.05
 plot_upper_lim = 4.25

### 2024-01-16 paper/main.tex
home

@@
     \includegraphics[width=.98\textwidth]{plots/sc_peak_in_cdw.pdf}
-    \caption{The upper panels show double logarithmic plots of the positions $\omega_0$ of the SC peak in the CDW phases while the lower panels show their respective weights $w_0 = e^{b}$.
-    In the upper panel, the pink markers additionally show the peak position divided by the gap $\omega_0 / \Delta_\text{CDW}$.
+    \caption{The upper panels (a) show double logarithmic plots of the positions $\omega_0$ of the peak in $\spectral{SC}$ in the CDW phase while the lower panels (b) show their respective weights $w_0 = e^{b}$.
+    In the upper panels, the pink markers additionally show the peak position divided by the gap $\omega_0 / \Delta_\text{CDW}$.
     The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
@@
 
+\begin{figure*}
+    \centering
+    \includegraphics[width=.98\textwidth]{plots/cdw_peak_in_sc.pdf}
+    \caption{The upper panels (a) show double logarithmic plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ in the SC phase while the lower panels (b) show their respective weights $w_0 = e^{b}$.
+    In the upper panels, the green markers additionally show the peak position divided by the gap $\omega_0 / \Delta_\text{SC}$.
+    The dashed lines represent the value found for $U=-2.5t$ and $V=0$ while fixing $\Delta_\text{CDW}=0$.
+    The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
+    The fits are linear, i.e., $y(V) = c \ln|V/t| + d$, and the parameters are printed on the individual panels.}
+    \label{fig:cdw_in_sc_behavior}
+\end{figure*}
+
 \subsection{AFM-CDW transition}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=.98\textwidth]{plots/afm_cdw_peaks_overview.pdf}
+    \caption{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ (orange lines) and $\spectral{AFM}$ (blue lines) close to the corresponding phase transition $U = zV$.
+    The middle panels (b) depict the peak positions relative to the lower edge of the two-particle continuum $\omega_-$, while the bottom panels (c) show their respective weights.
+    The shadings indicate the phase the system is in. Blue represents AFM while orange represents CDW.
+    The left column shows the results for the square and the right column for the simple cubic lattice at $V=-1t$.
+    Note the difference in the scales for the two lattices.}
+    \label{fig:afm_cdw_peaks_overview}
+\end{figure*}
 

### 2024-01-16 paper/sc_peak_in_cdw.py

@@ -101,6 +101,11 @@ for i in range(2):
 axs[0][0].title.set_text("Square")
 axs[0][1].title.set_text("Simple cubic")
 
+axs[0][0].text(0.8, 0.92, "(a.1)", transform = axs[0][0].transAxes)
+axs[0][1].text(0.8, 0.92, "(a.2)", transform = axs[0][1].transAxes)
+axs[1][0].text(0.8, 0.92, "(b.1)", transform = axs[1][0].transAxes)
+axs[1][1].text(0.8, 0.92, "(b.2)", transform = axs[1][1].transAxes)
+
 axs[1][0].set_xlabel(r"$\ln(V / t)$")
 axs[1][1].set_xlabel(r"$\ln(V / t)$")
 axs[1][0].set_ylabel(r"$b = \ln(w_0)$")

### 2024-01-16 paper/afm_cdw_peaks_details.py
home

@@ -15,9 +15,9 @@ import lib.plot_settings as ps
 
 
 Ts = np.array([0.])
-Us_base = np.array([0.0001, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4])
+Us = np.array([0.0001, 0.00015, 0.0002, 0.0003, 0.0004, 0.0005, 0.0007, 0.001, 0.0015, 0.002, 0.003, 0.004, 0.005, 0.007, 
+                0.01, 0.015, 0.02, 0.03, 0.04, 0.05, 0.07, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4])
 Us_cube = np.array([0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 1.0])
-Us = np.concatenate((-Us_base[::-1], Us_base))
 Vs = np.array([1.0])
 
 
@@ -25,7 +25,7 @@ folders = ["../data/modes/square/dos_3k/", "../data/modes/cube/dos_3k/"]
 element_names = ["a", "a+b", "a+ib"]
 
 name_suffices = ["AFM", "CDW"]
-nrows=3
+nrows=2
 fig, axs = plt.subplots(nrows=nrows, ncols=2, figsize=(12.8, 8.2), sharex="col", gridspec_kw=dict(hspace=0))
 plotters = np.empty((nrows,2), dtype=ps.CURVEFAMILY)
 
@@ -38,7 +38,8 @@ for i in range(2):
     if i == 0:
         u_data = 4.0 + Us
     else:
-        u_data = 6.0 + np.concatenate((-Us_cube[::-1], Us, Us_cube))
+        Us = np.append(Us, Us_cube)
+        u_data = 6.0 + Us
     
     weights = np.zeros(len(u_data))
     peak_positions = np.zeros(len(u_data))
@@ -56,34 +57,21 @@ for i in range(2):
             peak_positions_to_cont[counter] = cont_edges[0] - peak_positions[counter]
             counter += 1
         
-        plotters[0][i].plot(u_data, peak_positions, label=f"Data - $\\mathcal{{A}}_\\mathrm{{{name_suffix}}} (\\omega)$")
-        plotters[1][i].plot(u_data, peak_positions_to_cont)
-        plotters[2][i].plot(u_data, np.exp(weights))
[…]

### 2024-01-16 paper/resolvent_overview_SC_CDW.py

@@ -42,7 +42,7 @@ for j, folder in enumerate(folders):
         for k, (name_suffix, label) in enumerate(zip(name_suffices, labels)):
             data, data_real, w_lin, resolvents[k] = cf.resolvent_data(f"{folder}{name}", name_suffix, plot_lower_lim, usage_upper_lim, 
                                                             number_of_values=7000, xp_basis=True, imaginary_offset=1e-5, messages=False)
-            plotters[i][j].plot_with_peak(w_lin, data, label=label)
+            plotters[i][j].plot_with_peak(w_lin, data, label=r"$\mathcal{A}_\mathrm{" + label + r"} (\omega)$")
             
         axs[i][j].set_xlim(plot_lower_lim, usage_upper_lim)
         if i == 2:

### 2024-01-16 paper/resolvent_overview_V0.py

@@ -45,7 +45,7 @@ for j, folder in enumerate(folders):
         for k, (name_suffix, label) in enumerate(zip(name_suffices, labels)):
             data, data_real, w_lin, resolvents[k] = cf.resolvent_data(f"{folder}{folder_extension}{name}", name_suffix, plot_lower_lim, usage_upper_lim, 
                                                             number_of_values=7000, xp_basis=True, imaginary_offset=1e-5, messages=False)
-            plotters[i][j].plot_with_peak(w_lin, data, label=label)
+            plotters[i][j].plot_with_peak(w_lin, data, label=r"$\mathcal{A}_\mathrm{" + label + r"} (\omega)$")
             
         axs[i][j].set_xlim(plot_lower_lim, usage_upper_lim)
         zommed_xlim = (-0.01, 0.099)

### 2024-01-16 paper/resolvent_overview_AFM_CDW.py
home

@@ -49,7 +49,7 @@ for j, folder in enumerate(folders):
         for k, (name_suffix, label) in enumerate(zip(name_suffices, labels)):
             data, data_real, w_lin, resolvents[k] = cf.resolvent_data(f"{folder}{name}", name_suffix, plot_lower_lim, usage_upper_lim, 
                                                             number_of_values=10000, xp_basis=True, imaginary_offset=1e-5, messages=False)
-            plotters[i][j].plot_with_peak(w_lin, data, label=label)
+            plotters[i][j].plot_with_peak(w_lin, data, label=r"$\mathcal{A}_\mathrm{" + label + r"} (\omega)$")
             
         cont = np.sqrt(resolvents[0].roots[0])
         zommed_xlim = (cont - 0.035, cont + 0.025) if j == 0 else (cont - 0.12, cont + 0.05) 
@@ -58,7 +58,6 @@ for j, folder in enumerate(folders):
         axins = create_zoom(axs[i][j], zoom_xpos, 0.29, 0.275, 0.66, zommed_xlim, ylim=(0, 0.55), 
                             y_funcs=[lambda x, res=res: res.spectral_density(x + 1e-5j) for res in resolvents],
                             skip_lines=[1, 3, 5, 7], yticks=[0, 0.2, 0.4], mark_inset=False)
-  
         axs[i][j].set_xlim(plot_lower_lim, usage_upper_lim)
         resolvents[0].mark_continuum(axs[i][j], None)
         resolvents[0].mark_continuum(axins, None)

### 2024-01-17 paper/main.tex
uni

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%                                                  SC-CDW                                                   %%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{SC-CDW transition}
@@
     \includegraphics[width=.98\textwidth]{plots/cdw_peak_in_sc.pdf}
-    \caption{The upper panels (a) show double logarithmic plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ in the SC phase while the lower panels (b) show their respective weights $w_0 = e^{b}$.
-    In the upper panels, the green markers additionally show the peak position divided by the gap $\omega_0 / \Delta_\text{SC}$.
-    The dashed lines represent the value found for $U=-2.5t$ and $V=0$ while fixing $\Delta_\text{CDW}=0$.
+    \caption{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ in the SC phase, 
+    as well as the position relative to the lower edge of the continuum $\omega_-$.% and in units of $\Delta_\text{SC}$. 
+    The lower panels (b) show their respective weights $w_0 = e^{b}$.
+    The dashed lines represent the value of $\omega_0$ and $w_0$ computed for $U=-2.5t$ and $V=0$ while fixing $\Delta_\text{CDW}=0$.
     The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
-    The fits are linear, i.e., $y(V) = c \ln|V/t| + d$, and the parameters are printed on the individual panels.}
+    The $V$-axis is scaled logarithmically.
+    %The fits are linear, i.e., $y(V) = c \ln|V/t| + d$, and the parameters are printed on the individual panels. \textcolor{red}{ind möglicherweise auch gar nicht sinnvoll.}
+    The left-most values are $V=-0.28t$ for the square lattice and $V=-0.34t$ for the simple cubic lattice.
+    Choosing even smaller values results in $\mathcal{M}$ no longer being positive, i.e., the system is not in thermal equilibrium.}
     \label{fig:cdw_in_sc_behavior}
 \end{figure*}
+
+As a next step, we want to analyze the peak in $\spectral{CDW}$ that occurs if the system is in the SC phase ($V<0$).
+A plot of its position $\omega_0$ and weight $w_0$ can be seen in \autoref{fig:sc_in_cdw_behavior}.
+Both of them smoothly approach a finite value for $|V| \ll 1t$, marked by the dashed line.
+These values are obtained by computing the peaks position and weight for $V=0$ and setting $\Delta_\text{CDW}=0$, see \autoref{fig:resolvent_overview_V0} (a).
+
+Moving towards smaller $V$, the peaks move toward greater $\omega$, i.e., closer toward the two-particle continuum.
+Additionally, the weights drop off, first with increasing speed and then slowing down.
+They seem to converge toward some value, but we are unable to compute the Green's functions for additional, 
+even smaller $V$ because the matrix $\mM$ is not nonnegative anymore after $V\approx -0.28t$ (square lattice) or $V\approx -0.34t$ (simple cubic lattice).
+Note, that our proof for the nonnegativity is based on the system being in thermal equilibrium.
+Therefore, we conclude that beyond these $V$, the superconducting phase is not the true groundstate of the system.
+Specifically, the s-wave superconducting phase on the square lattice seems to be even smaller than first estimated using the $d_{x^2 -y^2}$ data from \cite{Micnas88b}.
+In recent research, there has been evidence for a phase seperated state for negative values of $V$,
+which would explain our results here \cite{Linner23}. 
+The magnitude of $V$ for which our calculation stops working is in the same order as in the referenced paper.
+Note however, that we did our computations at $T=0$ while the reference worked on finite temperature systems.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%                                                  AFM-CDW                                                  %%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-TODO
+Lastly, we investigate how the modes behave a the system transitions between the CDW and AFM phases.
+Similar to the previous subsection, we plot the occurring peaks in $\spectral{CDW}$ and $\spectral{AFM}$ within the respective phase in \autoref{fig:afm_cdw_peaks_overview}.
+On the right side of each panel, i.e., for $U > zV$, the system is in the AFM phase (blue shading).
+On the left side, it is in the CDW phase (orange shading).
+In general, the peak in $\spectral{AFM}$ behaves exactly as the peak in $\spectral{CDW}$ if the phases are swapped.
+
+The panels (a) show the peaks' positions unmodified. They essentially move linearly as $U$ is varied.
+It is noteworthy, that the in the AFM phase, the peak in $\spectral{AFM}$ lies lower than the one in $\spectral{CDW}$.
+Naturally, this is reversed, if the system is in the CDW phase.
+This is to be expected, as creating an AFM excitation should be energetically more favorable if the system is already in said phase.
+
+Additionally, we plot in (b) the peaks' positions relative to the lower edge of the two-particle continuum.
+We see that the lower lying peak, i.e., the peak corresponding to the phase the system is in, 
+strays further away from the continuum as the system moves away from the phase boundary.
+The other peak, however, moves evercloser to the aforementioned continuum until they reach it.
+At this point, the weight of said peak also vanishes, see panels (c).
+This occurs around $U=4V \pm 0.4t$ for the square lattice and around $U=6V \pm 1t$ for the simple cubic lattice.
+
+On the square lattice, the weights of the peak in $\spectral{AFM}$ in the AFM phase (the same applies for CDW) grows as the system moves away from the phase transition.
+On the simple cubic lattice, however, the weights fall off very slightly.
 

### 2024-01-17 paper/cdw_peak_in_sc.py

@@ -25,78 +25,82 @@ Vs = np.array(["-0.00001", "-0.000013", "-0.000015", "-0.000017", "-0.00002", "-
                 "-0.003", "-0.004", "-0.005", "-0.006", "-0.007", "-0.008", "-0.009", 
                 "-0.01", "-0.013", "-0.015", "-0.017", "-0.02", "-0.025", 
                 "-0.03", "-0.04", "-0.05", "-0.06", "-0.07", "-0.08", "-0.09", 
-                "-0.1", "-0.13", "-0.15", "-0.2", "-0.25"
+                "-0.1", "-0.13", "-0.15", "-0.2", "-0.25", "-0.28"
                 ])
-v_data = np.log(np.array([np.abs(float(v)) for v in Vs]))
 
 folders = ["../data/modes/square/dos_3k/", "../data/modes/cube/dos_3k/"]
 element_names = ["a", "a+b", "a+ib"]
 
 name_suffix = "higgs_CDW"
-
-weights = np.zeros(len(Vs))
-peak_positions = np.zeros(len(Vs))
-peak_positions_div_delta = np.zeros(len(Vs))
-fig, axs = plt.subplots(nrows=2, ncols=2, figsize=(12.8, 8.2), sharex=True, sharey="row", gridspec_kw=dict(hspace=0, wspace=0))
+fig, axs = plt.subplots(nrows=2, ncols=2, figsize=(12.8, 8.2), sharex="col", sharey="row", gridspec_kw=dict(hspace=0, wspace=0))
 
 plotters = np.empty((2,2), dtype=ps.CURVEFAMILY)
 
 
 for i in range(2):
     counter = 0
-    plotters[0][i] = ps.CURVEFAMILY(6, axis=axs[0][i])
+    plotters[0][i] = ps.CURVEFAMILY(3, axis=axs[0][i])
     plotters[0][i].set_individual_colors("nice")
-    plotters[0][i].set_individual_linestyles(["-", "", "", ""])
-    plotters[0][i].set_individual_markerstyles(["", "x", "v", "1"])
+    plotters[0][i].set_individual_linestyles(["", "", "-"])
+    plotters[0][i].set_individual_markerstyles(["x", "v", ""])
     
-    plotters[1][i] = ps.CURVEFAMILY(3, axis=axs[1][i])
+    plotters[1][i] = ps.CURVEFAMILY(2, axis=axs[1][i])
[…]

### 2024-01-18 paper/afm_cdw_peaks_details.py
textz

@@ -17,7 +17,7 @@ import lib.plot_settings as ps
 Ts = np.array([0.])
 Us = np.array([0.0001, 0.00015, 0.0002, 0.0003, 0.0004, 0.0005, 0.0007, 0.001, 0.0015, 0.002, 0.003, 0.004, 0.005, 0.007, 
                 0.01, 0.015, 0.02, 0.03, 0.04, 0.05, 0.07, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4])
-Us_cube = np.array([0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 1.0])
+Us_cube = np.array([0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 1.0, 1.1])
 Vs = np.array([1.0])
 
 
@@ -57,8 +57,8 @@ for i in range(2):
             peak_positions_to_cont[counter] = cont_edges[0] - peak_positions[counter]
             counter += 1
         
-        plotters[0][i].plot(np.log(Us), np.log(peak_positions_to_cont), label=f"Data - $\\mathcal{{A}}_\\mathrm{{{name_suffix}}} (\\omega)$")
-        plotters[1][i].plot(np.log(Us), weights)
+        plotters[0][i].plot(np.log(Us), (peak_positions_to_cont), label=f"Data - $\\mathcal{{A}}_\\mathrm{{{name_suffix}}} (\\omega)$")
+        plotters[1][i].plot(np.log(Us), np.exp(weights))
 
 axs[0][0].title.set_text("Square")
 axs[0][1].title.set_text("Simple cubic")
@@ -72,7 +72,7 @@ axs[nrows-1][0].set_xlabel(r"$\ln((U - 4V) / t)$")
 axs[nrows-1][1].set_xlabel(r"$\ln((U - 6V) / t)$")
 axs[0][0].set_ylabel(r"$\ln((\omega_- - \omega_0) / t)$")
 axs[1][0].set_ylabel(r"$w_0$")
-legend = axs[0][1].legend(loc='upper center')
+legend = axs[0][1].legend()
 fig.tight_layout()
 
 import os

### 2024-01-18 paper/main.tex
textz

@@
 
-\textcolor{red}{Intro auf die Phasen und Anregungen beziehen, danach Theorie auspacken}
-The Hubbard model has been studied in a plethora of previous studies. 
+Collective excitations hold profound scientific interest as they unveil the intricate dynamics of correlated electron systems, offering key insights into the emergent properties of materials.
+On the theoretical side, the Hubbard model has been employed in a plethora of previous studies. 
 Early studies proved the existence of eigenstates to the Hubbard Hamiltonian that exhibit off-diagonal long-range order,
@@
 In this paper, we will restrict ourselves to the half-filled Hubbard model, including an additional intersite interaction, on a square and a simple cubic lattice.
-\textcolor{red}{Für den 3D Fall finde ich keine Phasendiagramme des extended Hubbard models, ggf nochmal suchen...}
+\textcolor{red}{Für den 3D Fall finde ich keine Phasendiagramme des extended Hubbard models.
+Es gibt eines zum normalen Hubbard model \cite{Staudt00} und nen Haufen zum Bose-Hubbard-Model, aber das ist halt etwas anderes.}
 The 2D case already exhibits a wide range of possible phases, including CDW, AFM as well as $s$- and $d_{x^2 - y^2}$-wave superconductivity
@@
 The remainder of this paper is organized as follows:
-In \autoref{sec:model} we will introduce the model and its Hamiltonian as well as our mean-field theory.
-A brief overview of the iterated equations of motion approach is presented in \autoref{sec:ieom}.
+In \autoref{sec:model} we will introduce the model and its Hamiltonian as well as our mean-field theory for the ground state.
+We give a brief overview of the iterated equations of motion approach and derive a rigorous link to Green's functions in \autoref{sec:ieom}.
 Next, we show our results in \autoref{sec:results}.
 Lastly, in \autoref{sec:conclusion}, we will discuss our results.
-%In the appendix \textcolor{red}{(or in the supplemental material?)}, we will derive and explain our methods in detail.
 
@@
 
-\textcolor{red}{Schreiben wie cool das Hubbard Model ist}
-
-The Hamiltonian of the extended Hubbard model is given by
+In our study, we employ the extended Hubbard model because it encompasses various phases and thereby provides direct access to a rich spectrum of excitation spectra therein.
+Its Hamiltonian is given by
 \begin{equation}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%                                                  Figures                                                  %%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_SC_CDW.pdf}
+    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
+    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
+    The left edge of each plot is at $-0.05$ rather than $0$ in order to improve the visibility of the phase peak.
+    The shaded area marks the two-particle continuum.
+    For each plot, the parameters are set to $U=-2.5t$ and $N_\gamma = 3000$, while $V$ is varied according to the text in the individual panels.
+    The panels show the spectral functions in the (a) SC phase and the (b and c) CDW phase, respectively.}
+    \label{fig:resolvent_overview_SC}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_V0.pdf}
+    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
+    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
+    The left edge of each plot is at $-0.05$ rather than $0$ in order to improve the visibility of the peaks at $\omega=0$.
+    The shaded area marks the two-particle continuum.
+    For each plot, the parameters are set to $U=-2.5t$, $V=0$, and $N_\gamma = 3000$.
+    Since the ratio of $\Delta_\text{SC}$ to $\Delta_\text{CDW}$ may be chosen arbitrarily, we show in (a) the spectral functions for $\Delta_\text{CDW} = 0$ and in (b) for $\Delta_\text{SC} = 0$.}
+    \label{fig:resolvent_overview_V0}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_AFM_CDW.pdf}
+    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
+    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
+    The shaded area marks the two-particle continuum.
+    For each plot, the parameters are set to $V=1t$ and $N_\gamma = 3000$, while $U$ is varied according to the text in the individual panels.
+    The panels (a) and (c) show the spectral functions in the AFM phase, and the panels (b) and (d) in the CDW phase.}
+    \label{fig:resolvent_overview_AFM}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=.98\textwidth]{plots/sc_peak_in_cdw.pdf}
+    \caption{The upper panels (a) show double logarithmic plots of the positions $\omega_0$ of the peak in $\spectral{SC}$ in the CDW phase while the lower panels (b) show their respective weights $w_0 = e^{b}$.
+    In the upper panels, the pink markers additionally show the peak position divided by the gap $\omega_0 / \Delta_\text{CDW}$.
+    The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
+    The fits are linear, i.e., $y(V) = c \ln(V/t) + d$, and the parameters are printed on the individual panels.}
+    \label{fig:sc_in_cdw_behavior}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=.98\textwidth]{plots/cdw_peak_in_sc.pdf}
+    \caption{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ in the SC phase, 
+    as well as the position relative to the lower edge of the continuum $\omega_-$.% and in units of $\Delta_\text{SC}$. 
+    The lower panels (b) show their respective weights $w_0 = e^{b}$.
+    The dashed lines represent the value of $\omega_0$ and $w_0$ computed for $U=-2.5t$ and $V=0$ while fixing $\Delta_\text{CDW}=0$.
+    The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
+    The $V$-axis is scaled logarithmically.
+    The left-most values are $V=-0.28t$ for the square lattice and $V=-0.34t$ for the simple cubic lattice.
+    Choosing even smaller values results in $\mathcal{M}$ no longer being positive, i.e., the system is not in thermal equilibrium.
+    \textcolor{red}{Der Fit im unteren Panel ist ein artanh(ln|V|), damit landet man bei sowas wie $(1-V^2)/(1+V^2)$.
+    Darüber muss ich noch etwas nachdenken.}}
+    \label{fig:cdw_in_sc_behavior}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=.98\textwidth]{plots/afm_cdw_peaks_overview.pdf}
+    \caption{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ (orange lines) and $\spectral{AFM}$ (blue lines) close to the corresponding phase transition $U = zV$.
+    The middle panels (b) depict the peak positions relative to the lower edge of the two-particle continuum $\omega_-$, while the bottom panels (c) show their respective weights.
+    The shadings indicate the phase the system is in. Blue represents AFM while orange represents CDW.
+    The left column shows the results for the square and the right column for the simple cubic lattice at $V=-1t$.
+    Note the difference in the scales for the two lattices.}
+    \label{fig:afm_cdw_peaks_overview}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%                                                  Figures                                                  %%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Now, the task at hand is finding the inverse $1/(z^2 - \check{M})$ for all $z$.
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_SC_CDW.pdf}
-    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
-    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
-    The left edge of each plot is at $-0.05$ rather than $0$ in order to improve the visibility of the phase peak.
-    The shaded area marks the two-particle continuum.
-    For each plot, the parameters are set to $U=-2.5t$ and $N_\gamma = 3000$, while $V$ is varied according to the text in the individual panels.
-    The panels show the spectral functions in the (a) SC phase and the (b and c) CDW phase, respectively.}
-    \label{fig:resolvent_overview_SC}
-\end{figure*}
-
 \section{Results}\label{sec:results}
@@
 The former can be found at zero energy because our model describes a neutral superfluid wherein there is no coupling of the phase of the order parameter to the electromagnetic potential.
-Therefore, this phase may be chosen arbitrarily, and changing it requires no energy which ultimately allows a Goldstone mode to exist in the first place. \textcolor{red}{Zitieren!}
+Therefore, this phase may be chosen arbitrarily, and changing it requires no energy which ultimately allows a Goldstone mode to exist in the first place \cite{Goldstone1961,Anderson63}.
 
@@
 \end{equation}
-with $r > 0$ and $u > 0$ if the system is outside of the superconducting phase. \textcolor{red}{Zitieren!}
+with $r > 0$ and $u > 0$ if the system is outside of the superconducting phase. 
 In this case, the only minimum is at $\Delta_\text{SC} = 0$. 
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_V0.pdf}
-    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
-    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
-    The left edge of each plot is at $-0.05$ rather than $0$ in order to improve the visibility of the peaks at $\omega=0$.
-    The shaded area marks the two-particle continuum.
-    For each plot, the parameters are set to $U=-2.5t$, $V=0$, and $N_\gamma = 3000$.
-    Since the ratio of $\Delta_\text{SC}$ to $\Delta_\text{CDW}$ may be chosen arbitrarily, we show in (a) the spectral functions for $\Delta_\text{CDW} = 0$ and in (b) for $\Delta_\text{SC} = 0$.}
-    \label{fig:resolvent_overview_V0}
-\end{figure*}
-
-At $V=0$, both the SC and the CDW phase coexist. 
+At $V=0$, both the SC and the CDW orders coexist. 
 In this phase, the mean-field single-particle energies are given by
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_AFM_CDW.pdf}
-    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
-    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
-    The shaded area marks the two-particle continuum.
-    For each plot, the parameters are set to $V=1t$ and $N_\gamma = 3000$, while $U$ is varied according to the text in the individual panels.
-    The panels (a) and (c) show the spectral functions in the AFM phase, and the panels (b) and (d) in the CDW phase.}
-    \label{fig:resolvent_overview_AFM}
-\end{figure*}
-
 Lastly, we investigate the same spectral functions close to the AFM-CDW phase transition, depicted in \autoref{fig:resolvent_overview_AFM}.
@@
 \subsection{SC-CDW transition}
-
-\begin{figure*}
-    \centering
-    \includegraphics[width=.98\textwidth]{plots/sc_peak_in_cdw.pdf}
-    \caption{The upper panels (a) show double logarithmic plots of the positions $\omega_0$ of the peak in $\spectral{SC}$ in the CDW phase while the lower panels (b) show their respective weights $w_0 = e^{b}$.
-    In the upper panels, the pink markers additionally show the peak position divided by the gap $\omega_0 / \Delta_\text{CDW}$.
-    The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
-    The fits are linear, i.e., $y(V) = c \ln(V/t) + d$, and the parameters are printed on the individual panels.}
-    \label{fig:sc_in_cdw_behavior}
-\end{figure*}
 
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=.98\textwidth]{plots/cdw_peak_in_sc.pdf}
-    \caption{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ in the SC phase, 
-    as well as the position relative to the lower edge of the continuum $\omega_-$.% and in units of $\Delta_\text{SC}$. 
-    The lower panels (b) show their respective weights $w_0 = e^{b}$.
-    The dashed lines represent the value of $\omega_0$ and $w_0$ computed for $U=-2.5t$ and $V=0$ while fixing $\Delta_\text{CDW}=0$.
-    The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
-    The $V$-axis is scaled logarithmically.
-    %The fits are linear, i.e., $y(V) = c \ln|V/t| + d$, and the parameters are printed on the individual panels. \textcolor{red}{ind möglicherweise auch gar nicht sinnvoll.}
-    The left-most values are $V=-0.28t$ for the square lattice and $V=-0.34t$ for the simple cubic lattice.
-    Choosing even smaller values results in $\mathcal{M}$ no longer being positive, i.e., the system is not in thermal equilibrium.}
-    \label{fig:cdw_in_sc_behavior}
-\end{figure*}
-
 As a next step, we want to analyze the peak in $\spectral{CDW}$ that occurs if the system is in the SC phase ($V<0$).
@@
 Both of them smoothly approach a finite value for $|V| \ll 1t$, marked by the dashed line.
-These values are obtained by computing the peaks position and weight for $V=0$ and setting $\Delta_\text{CDW}=0$, see \autoref{fig:resolvent_overview_V0} (a).
+These values are obtained by computing the peaks' position and weight for $V=0$ and setting $\Delta_\text{CDW}=0$, see \autoref{fig:resolvent_overview_V0} (a).
 
-Moving towards smaller $V$, the peaks move toward greater $\omega$, i.e., closer toward the two-particle continuum.
+Moving towards smaller $V$, the peaks move toward greater $\omega$, i.e., closer to the two-particle continuum.
 Additionally, the weights drop off, first with increasing speed and then slowing down.
@@
 Note, that our proof for the nonnegativity is based on the system being in thermal equilibrium.
-Therefore, we conclude that beyond these $V$, the superconducting phase is not the true groundstate of the system.
+Therefore, we conclude that beyond these $V$, the superconducting phase is not the true ground state of the system.
 Specifically, the s-wave superconducting phase on the square lattice seems to be even smaller than first estimated using the $d_{x^2 -y^2}$ data from \cite{Micnas88b}.
-In recent research, there has been evidence for a phase seperated state for negative values of $V$,
+In recent research, there has been evidence for a phase-separated state for negative values of $V$ on a square lattice,
 which would explain our results here \cite{Linner23}.
+It would be reasonable to assume, that this phase occurs in both the 2- and 3-dimensional case.
 The magnitude of $V$ for which our calculation stops working is in the same order as in the referenced paper.
-Note however, that we did our computations at $T=0$ while the reference worked on finite temperature systems.
+Note, however, that we did our computations at $T=0$ while the reference worked on finite temperature systems.
 
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=.98\textwidth]{plots/afm_cdw_peaks_overview.pdf}
-    \caption{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ (orange lines) and $\spectral{AFM}$ (blue lines) close to the corresponding phase transition $U = zV$.
-    The middle panels (b) depict the peak positions relative to the lower edge of the two-particle continuum $\omega_-$, while the bottom panels (c) show their respective weights.
-    The shadings indicate the phase the system is in. Blue represents AFM while orange represents CDW.
-    The left column shows the results for the square and the right column for the simple cubic lattice at $V=-1t$.
-    Note the difference in the scales for the two lattices.}
-    \label{fig:afm_cdw_peaks_overview}
-\end{figure*}
-
-Lastly, we investigate how the modes behave a the system transitions between the CDW and AFM phases.
+Lastly, we investigate how the modes behave as the system transitions between the CDW and AFM phases.
 Similar to the previous subsection, we plot the occurring peaks in $\spectral{CDW}$ and $\spectral{AFM}$ within the respective phase in \autoref{fig:afm_cdw_peaks_overview}.
@@
 
-The panels (a) show the peaks' positions unmodified. They essentially move linearly as $U$ is varied.
-It is noteworthy, that the in the AFM phase, the peak in $\spectral{AFM}$ lies lower than the one in $\spectral{CDW}$.
+The panel (a) shows the peaks' positions unmodified. They essentially move linearly as $U$ is varied.
+It is noteworthy, that in the AFM phase, the peak in $\spectral{AFM}$ lies lower than the one in $\spectral{CDW}$.
 Naturally, this is reversed, if the system is in the CDW phase.
@@
 Additionally, we plot in (b) the peaks' positions relative to the lower edge of the two-particle continuum.
-We see that the lower lying peak, i.e., the peak corresponding to the phase the system is in, 
+We see that the lower-lying peak, i.e., the peak corresponding to the phase the system is in, 
 strays further away from the continuum as the system moves away from the phase boundary.
-The other peak, however, moves evercloser to the aforementioned continuum until they reach it.
-At this point, the weight of said peak also vanishes, see panels (c).
-This occurs around $U=4V \pm 0.4t$ for the square lattice and around $U=6V \pm 1t$ for the simple cubic lattice.
+The other peak, however, moves ever closer to the aforementioned continuum until they reach it.
+At this point, the weight of said peak also vanishes, see panel (c).
+This occurs around $U=4V \pm 0.4t$ for the square lattice and around $U=6V \pm 1.1t$ for the simple cubic lattice.
 
-On the square lattice, the weights of the peak in $\spectral{AFM}$ in the AFM phase (the same applies for CDW) grows as the system moves away from the phase transition.
+On the square lattice, the weights of the peak in $\spectral{AFM}$ in the AFM phase (the same applies for CDW) grow as the system moves away from the phase transition.
 On the simple cubic lattice, however, the weights fall off very slightly.
@@
 
-...
+Ideen für die Zukunft:
+
+Phase-separated state aufnehmen
+
+Ankopplung an das EM-Feld
+
+Mehrbandsysteme
 

### 2024-01-18 paper/main.tex
text

@@
 
-To classify the occurring peaks that lie outside the two-particle continuum, we turn toward the real part of the Green's function.
+To classify the occurring peaks that lie outside the two-particle continuum, we turn towards the real part of the Green's function.
 We plot it in close proximity to the peaks with a double logarithmic scale and fit the result linearly $y = ax + b$ to obtain its power-law behavior.
@@
 
-Moving towards smaller $V$, the peaks move toward greater $\omega$, i.e., closer to the two-particle continuum.
+Moving towards smaller $V$, the peaks move towards greater $\omega$, i.e., closer to the two-particle continuum.
 Additionally, the weights drop off, first with increasing speed and then slowing down.
-They seem to converge toward some value, but we are unable to compute the Green's functions for additional, 
+They seem to converge towards some value, but we are unable to compute the Green's functions for additional, 
 even smaller $V$ because the matrix $\mM$ is not nonnegative anymore after $V\approx -0.28t$ (square lattice) or $V\approx -0.34t$ (simple cubic lattice).

### 2024-01-22 paper/main.tex
paper text

@@
     This renders comprehensive analysis of the behavior of collective excitations possible as the model's parameters are changed across phase transitions.
-    We identify the well-known amplitude (Higgs) and phase (Leggett) modes within the superconducting phase and observe a similar excitation in the CDW phase which shifts towards zero energy as the system approaches the phase transition to the SC phase.
+    We identify the well-known amplitude (Higgs) and phase (Anderson-Bogoliubov) modes within the superconducting phase and observe a similar excitation in the CDW phase which shifts towards zero energy as the system approaches the phase transition to the SC phase.
     In the CDW phase, close to the phase transition to the AFM phase, we find a collective mode that does not change significantly and another mode that becomes soft as the phase boundary is approached.
@@
 
-Collective excitations hold profound scientific interest as they unveil the intricate dynamics of correlated electron systems, offering key insights into the emergent properties of materials.
+Collective excitations hold profound scientific interest as they unveil the intricate dynamics of correlated electron systems, 
+offering key insights into the emergent properties of materials.
 On the theoretical side, the Hubbard model has been employed in a plethora of previous studies. 
@@
 By extension, we also obtain the spectral functions of the investigated systems and discuss the excitations found therein.
-The prominent examples in the SC phase are the well-known phase (Leggett) and amplitude (Higgs) modes \cite{Varma02,Cea14,Measson14,Tsuji15,Krull16,Schwarz20,Fan22}.
+The prominent examples in the SC phase are the well-known phase (Anderson-Bogoliubov) and amplitude (Higgs) modes \cite{Kulik1981,Varma02,Cea14,Measson14,Tsuji15,Krull16,Schwarz20,Fan22}.
 The former is located at zero energy as our model describes neutral superfluids.
@@
 
-In our study, we employ the extended Hubbard model because it encompasses various phases and thereby provides direct access to a rich spectrum of excitation spectra therein.
+In our study, we employ the extended Hubbard model as it encompasses assorted phases and thereby provides direct access to the rich excitation spectra therein.
 Its Hamiltonian is given by
@@
 This holds for both the square lattice ($z=4$) and the simple cubic lattice ($z=6$) and can be seen by comparing \eqref{eqn:delta_cdw} and \eqref{eqn:delta_afm}:
-Crossing the aforementioned line, changes which one of the two prefactors is larger.
+Crossing the aforementioned line, changes which prefactor of the two order parameters is larger.
 
@@
 \end{equation}
+Nevertheless, this does not pose any issue in our calculations.
 We will compute $\mM$ by commutating with the full Hubbard Hamiltonian \eqref{eqn:full_hamiltonian} enabling us to capture collective behavior rather than the one particle dynamics given by the mean-field approximation.
@@
 \end{equation}
-Then, our set is given by $\mathcal{B}_{XP} \coloneqq \{ X_i, P_i \}$.
+Then, our set is given by $\mathcal{B}_{XP} \coloneqq \{ X_i, \ldots, P_i, \ldots \}$.
 If some operators would be 0 ($P_i$ for any $n$-type term) or duplicates (certain $X_i$ for $g$-type terms), we omit them.
@@
     \label{eqn:standard_gf}
-    G_{AB}(\omega + i0^+) = -i \int_0^{\infty} e^{izt} \langle [A(t), B] \rangle \mathrm{d}t\,,
+    G_{AB}(z = \omega + i0^+) = -i \int_0^{\infty} e^{izt} \langle [A(t), B] \rangle \mathrm{d}t\,,
 \end{equation}
@@
 \begin{align}
-    \mathcal{G}_{00}(z = \omega +i0^+) &=  G_{f_{\vk}(t) f_{\vk}^\dagger} (z) \nonumber \\
+    \mathcal{G}_{00}(z = \omega +i0^+) &=  G_{f_{\vk} f_{\vk}^\dagger} (z) \nonumber \\
         &= -i \int_0^{\infty} \langle [f_{\vk}(t), f_{\vk}^\dagger(0)] \rangle e^{izt} \mathrm{d}t\,.
@@
 where $a_i$ and $b_i$ are the Lanczos coefficients \cite{PettiforRecursion,ViswanathRecursion}.
+
 Obtaining a diagonal block of $\mathcal{G}$ is easily achieved by setting $\vec{b}(0) = \vec{a}(0)$.
@@
 To begin, let us describe the spectral functions $\mathcal{A}_i (\omega) = - (1/\pi) \Im [\mathcal{G}_i (\omega + i0^+)]$ with respect to the operators above in the various phases.
-\autoref{fig:resolvent_overview_SC} shows them at $U = -2.5t$ in the SC ($V=-0.1t$) and CDW ($V=0.1t$ and $V=0.5t$) phase, as well as in the SC-CDW coexistence at $V=0$.
+\autoref{fig:resolvent_overview_SC} shows them at $U = -2.5t$ in the SC ($V=-0.1t$) and CDW ($V=0.1t$ and $V=0.5t$) phase.
 
 There are a variety of different features. The difference between the two lattices is mostly quantitative.
-First and foremost, in the SC phase, see panel (a), there is a sharp peak located at $\omega=0$ in $\spectral{Phase}$ and a singularity in $\spectral{Higgs}$ located at $\omega=2\Delta_\text{SC}$.
-We identify them with the well-known Leggett and Higgs modes in superconductors.
-The former can be found at zero energy because our model describes a neutral superfluid wherein there is no coupling of the phase of the order parameter to the electromagnetic potential.
-Therefore, this phase may be chosen arbitrarily, and changing it requires no energy which ultimately allows a Goldstone mode to exist in the first place \cite{Goldstone1961,Anderson63}.
+First and foremost, in the SC phase, see panel (a), 
+there is a sharp peak located at $\omega=0$ in $\spectral{Phase}$ and a singularity in $\spectral{Higgs}$ located at $\omega=2\Delta_\text{SC}$.
+We identify them with the well-known Anderson-Bogoliubov and Higgs modes in superconductors.
+Note, that the former must not have any weight though, because the spectral function is perfectly antisymmetrical.
+The peak itself can be found at zero energy because our model describes a neutral superfluid 
+wherein there is no coupling of the phase of the order parameter to the electromagnetic potential.
+Therefore, this phase may be chosen arbitrarily, and changing it requires no energy 
+which ultimately allows a Goldstone mode to exist in the first place \cite{Goldstone1961,Anderson63}.
 
@@
 This analysis provides that the real part of $\greens{Phase}$ near $\omega=0$ behaves as $1/\omega^2$ indicating that the peak in $\spectral{Phase}$ is the derivative of a $\delta$ distribution.
-Note, that it is located at $\omega=0$ of a perfectly asymmetrical bosonic spectral function and therefore must have 0 weight.
-This is given here, because $\int \delta'(\omega) \mathrm{d}\omega = 0$.
+The weight of such a peak is given by the integral $\int \delta'(\omega) \mathrm{d}\omega = 0$.
+This confirms our previous expectation that this peak cannot have any weight.
 
@@
 Here, $\Delta_\text{CDW}$ and $\Delta_\text{SC}$ can change arbitrarily without affecting the system's energy as long as $\Delta_\text{tot}$ remains constant.
-Note that the degeneracy of both phases is exact due to the SO(4) symmetry \cite{yang90}.
+Note, that the degeneracy of both phases is exact due to the SO(4) symmetry \cite{yang90}.
 
@@
 
-This concludes our proof. Note, that the only assumption made, is that the expectation is to be taken with respect to the thermal equilibrium.
+This concludes our proof. Note, that the only assumption made, is that the expectation value is to be taken with respect to the thermal equilibrium.
 
@@
 \end{equation}
-Computing an integral yields
+Computing an integral numerically yields
 \begin{equation}
@@
 \end{equation}
+
 To give a practical example, let us compute $\greens{Higgs}$ from \eqref{eqn:resolvent_bases}.
@@
 This proves that the imaginary part of such a Fourier-transformed Green's function is antisymmetrical and therefore the same applies to the spectral functions.
-Note that this fully abides by the sum rule $\int_{-\infty}^\infty \mathcal{A}_{A^\dagger A} (\omega) \mathrm{d}\omega = \langle [A^\dagger, A] \rangle = 0$ \cite{rickayzen80}.
+Note, that this fully abides by the sum rule $\int_{-\infty}^\infty \mathcal{A}_{A^\dagger A} (\omega) \mathrm{d}\omega = \langle [A^\dagger, A] \rangle = 0$ \cite{rickayzen80}.
 

### 2024-01-24 paper/main.tex
uni

@@
     \label{fig:phase_diagram}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.48\textwidth]{plots/phase_limits.pdf}
+    \caption{The lower left corner ($U<0$ and $V<0$) of the phase diagram obtained for the extended Hubbard model on 
+    (a) a square lattice and (b) a simple cubic lattice using a mean-field approximation at temperature $T=0$.
+    The blue shading indicates the region where the $s$-wave superconducting phase is the proper ground state of the system.
+    The green shading shows the region that we cannot access because it the discretization $N_\gamma$, which is required to accurately describe the system, is too large.
+    Lastly, the orange shading shows the region in which the dynamical matrix $\mM$ has negative eigenvalues, indicating that there are phases not captured by our methods.}
+    \label{fig:phase_limits}
 \end{figure}

### 2024-01-24 paper/phase_diagram.py

@@ -3,17 +3,21 @@ import matplotlib.pyplot as plt
 
 fig, axs = plt.subplots(nrows=2, sharex=True, figsize=(6.4, 9))
 
+xlims = (-2, 2)
+ylims = (-2, 2)
+alpha = .75
+
 ############################################################################
 ############                  Square lattice                    ############
 ############################################################################
 #Shade s-wave area
-axs[0].fill_between([-2, 0], [0, 0], [-2, -2], color="blue", alpha=.5, label="$s$-wave")
-
-#Shade AFM area
-axs[0].fill_between([0, 2], [0, .5], [-2, -2], color="green", alpha=.5, label="AFM")
+axs[0].fill_between([xlims[0], 0], [0, 0], [ylims[0], ylims[0]], alpha=alpha, label="$s$-wave")
 
 #Shade CDW area
-axs[0].fill_between(np.array([-2, 0, 2]), np.array([0, 0, .5]), np.array([2, 2, 2]), color="orange", alpha=.5, label="CDW")
+axs[0].fill_between(np.array([xlims[0], 0, xlims[1]]), np.array([0, 0, xlims[1] / 4]), np.array([ylims[1], ylims[1], ylims[1]]), alpha=alpha, label="CDW")
+
+#Shade AFM area
+axs[0].fill_between([0, xlims[1]], [0, xlims[1] / 4], [ylims[0], ylims[0]], alpha=alpha, label="AFM")
 
 #Shade d-wave area
 #axs[0].fill_between(micnas_d[0], micnas_d[1], -2 * np.ones(len(micnas_d[0])), color="red", alpha=.5, label="$d_{x^2 - y^2}$-wave")
@@ -21,44 +25,44 @@ axs[0].fill_between(np.array([-2, 0, 2]), np.array([0, 0, .5]), np.array([2, 2, 
 #Plot boundaries
 micnas_d = np.loadtxt("../data/micnas_d_wave.csv").transpose()
 axs[0].plot(micnas_d[0], micnas_d[1], "k--", label="$d_{x^2 - y^2}$-boundary")
-axs[0].plot(np.array([0, 2]), 0.25 * np.array([0, 2]),  "k-")
-axs[0].plot(np.array([-2, 0]),       np.array([0, 0]),  "k-")
-axs[0].plot(np.array([0, 0]),        np.array([0, -2]), "k-")
[…]

### 2024-01-24 paper/phase_limits.py

@@ -1,0 +1,57 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+fig, axs = plt.subplots(nrows=2, sharex=True, figsize=(6.4, 9))
+
+xlims = (-5, 0)
+ylims = (-0.5, 0)
+alpha = .75
+
+############################################################################
+############                  Square lattice                    ############
+############################################################################
+import gzip
+with gzip.open(f"../data/phases/square/T0/unkown_boundary.dat.gz", 'rt') as fp:
+    u_boundary = np.loadtxt(fp)
+
+axs[0].fill_between(u_boundary[0], u_boundary[1], np.full(len(u_boundary[0]), ylims[1]), label="$s$-wave", alpha=alpha)
+axs[0].fill_between(u_boundary[0], u_boundary[1], np.full(len(u_boundary[0]), ylims[0]), label="New phases", alpha=alpha)
+axs[0].fill_between([u_boundary[0][-1], xlims[1]], [ylims[1], ylims[1]], [ylims[0], ylims[0]], label=r"$\Delta$ too small", alpha=alpha)
+axs[0].plot(u_boundary[0], u_boundary[1], "k-")
+axs[0].axvline(u_boundary[0][-1], color="k", linestyle="--")
+
+############################################################################
+############                  Cubic lattice                     ############
+############################################################################
+with gzip.open(f"../data/phases/cube/T0/unkown_boundary.dat.gz", 'rt') as fp:
+    u_boundary = np.loadtxt(fp)
+
+axs[1].fill_between(u_boundary[0], u_boundary[1], np.full(len(u_boundary[0]), ylims[1]), label="$s$-wave", alpha=alpha)
+axs[1].fill_between(u_boundary[0], u_boundary[1], np.full(len(u_boundary[0]), ylims[0]), label="New phases", alpha=alpha)
+axs[1].fill_between([u_boundary[0][-1], xlims[1]], [ylims[1], ylims[1]], [ylims[0], ylims[0]], label=r"$\Delta$ too small", alpha=alpha)
+axs[1].plot(u_boundary[0], u_boundary[1], "k-")
+axs[1].axvline(u_boundary[0][-1], color="k", linestyle="--")
+
+############################################################################
[…]

### 2024-01-26 paper/afm_cdw_peaks_overview.py
text

@@ -15,9 +15,9 @@ import lib.plot_settings as ps
 
 
 Ts = np.array([0.])
-Us_base = np.array([0.0001, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4])
-Us_cube = np.array([0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 1.0, 1.05, 1.1])
-Us = np.concatenate((-Us_base[::-1], Us_base))
+Us_square = np.array([0.0001, 0.025, 0.05, 0.075, 0.1, 0.125, 0.15, 0.175, 0.2, 0.225, 0.25, 0.275, 0.3, 0.325, 0.35, 0.375, 0.4, 0.41, 0.42]) # 0.421 0.422 0.423 0.424
+Us_cube = np.array([0.0001, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 1.0, 1.05, 1.105]) # 1.03, 1.06, 1.07, 1.08, 1.09, 1.1,
+Us = np.array([np.concatenate((-Us_square[::-1], Us_square)), np.concatenate((-Us_cube[::-1], Us_cube))], dtype=object)
 Vs = np.array([1.0])
 
 
@@ -36,10 +36,10 @@ for i in range(2):
         plotters[j][i].set_individual_linestyles(["-", "-"])
         plotters[j][i].set_individual_markerstyles(["v", "^"])
     if i == 0:
-        u_data = 4.0 + Us
+        u_data = 4.0 + Us[0]
     else:
-        u_data = 6.0 + np.concatenate((-Us_cube[::-1], Us, Us_cube))
-    
+        u_data = 6.0 + Us[1]
+
     weights = np.zeros(len(u_data))
     peak_positions = np.zeros(len(u_data))
     peak_positions_to_cont = np.zeros(len(u_data))
@@ -47,12 +47,13 @@ for i in range(2):
     for name_suffix in name_suffices:
         counter = 0
         for T, U, V in iterate_containers(Ts, u_data, Vs):
-            name = f"T={T}/U={U}/V={V}"
+            name = f"T={T}/U={round(U, 4)}/V={V}"
             cont_edges = cf.continuum_edges(f"{folders[i]}{name}", f"higgs_{name_suffix}", True)
[…]

### 2024-01-26 paper/phase_diagram.py

@@ -5,7 +5,7 @@ fig, axs = plt.subplots(nrows=2, sharex=True, figsize=(6.4, 9))
 
 xlims = (-2, 2)
 ylims = (-2, 2)
-alpha = .75
+alpha = .6
 
 ############################################################################
 ############                  Square lattice                    ############

### 2024-01-26 paper/main.tex
text

@@
 
-Collective excitations hold profound scientific interest as they unveil the intricate dynamics of correlated electron systems, 
-offering key insights into the emergent properties of materials.
+The study of collective excitations is of great scientific interest as it sheds light on the intricate dynamics of correlated electron systems, providing crucial insights into emergent material properties.
 On the theoretical side, the Hubbard model has been employed in a plethora of previous studies. 
@@
 encouraging the model's usage for the description of high-temperature superconductivity \cite{yang89}.
-Shortly afterward, an exact SO(4) symmetry was discovered,
-which allows a degeneracy of superconductivity (SC) and a charge-density wave (CDW) governed by an attractive on-site interaction \cite{yang90}.
+Shortly afterward, an exact SO(4) symmetry was discovered, which allows a degeneracy of superconductivity (SC) and a charge-density wave (CDW) governed by an attractive on-site interaction \cite{yang90}.
 This coexistence can be argued by the existence of a particle-hole transformation on bipartite lattices, 
@@
 
-Numerous studies have been performed on equilibrium systems. 
-These investigated the phases and various quantities therein of the said model including various additional interactions with and without doping 
+Numerous studies have investigated the phases and various quantities of the Hubbard model in equilibrium systems, including various additional interactions with and without doping.
 \cite{Micnas88,Micnas88b,Micnas89,Dzierzawa92,Kostyrko92,Eriksson95,Staudt00,Onari04,Toschi05,Brackett16,Paki19,romer20,Sushchyev22}.
-For a long time, works on the dynamics of the superconducting gap parameter focused on its behavior after an instantaneous quench, 
+For a long time, research on the dynamics of the superconducting gap parameter focused on its behavior after an instantaneous quench, 
 yielding damped or persistent oscillations depending on the magnitude of the quench \cite{Volkov73,Yuzbashyan05,Yuzbashyan06,Barankov06,Cui19}.
@@
 In this paper, we will restrict ourselves to the half-filled Hubbard model, including an additional intersite interaction, on a square and a simple cubic lattice.
-\textcolor{red}{Für den 3D Fall finde ich keine Phasendiagramme des extended Hubbard models.
-Es gibt eines zum normalen Hubbard model \cite{Staudt00} und nen Haufen zum Bose-Hubbard-Model, aber das ist halt etwas anderes.}
-The 2D case already exhibits a wide range of possible phases, including CDW, AFM as well as $s$- and $d_{x^2 - y^2}$-wave superconductivity
-\cite{Micnas88b,Tsuchiura95,Su01,Su04,ha11,Huang13,Jiang22}.
-
-In this article, we will first employ a mean-field approximation to the interaction terms 
+The 2D case already exhibits a wide range of possible phases, including CDW, AFM, $s$- and $d_{x^2 - y^2}$-wave superconductivity, and phase-separated states \cite{Micnas88b,Tsuchiura95,Su01,Su04,ha11,Huang13,Jiang22,Linner23}.
+We expand these well-known phase diagrams to the simple cubic lattice where we find a similar structure for CDW, AFM, and $s$-wave SC.
+
+To study this system, we will first employ a mean-field approximation to the interaction terms 
 and then use the methodology from the so-called iterated equations of motion approach (iEoM),
@@
 The functionality of this method has been compared to the density matrix formalism and has proved to be considerably more accurate \cite{Kalthoff17}.
-Additionally, we will show an explicit way to obtain various Green's functions from the aforementioned methodology.
+
+Moreover, we demonstrate an explicit way to obtain various Green's functions from the aforementioned methodology.
 By extension, we also obtain the spectral functions of the investigated systems and discuss the excitations found therein.
@@
     The blue shading indicates the region where the $s$-wave superconducting phase is the proper ground state of the system.
-    The green shading shows the region that we cannot access because it the discretization $N_\gamma$, which is required to accurately describe the system, is too large.
+    The green shading shows the region that we cannot access because the discretization $N_\gamma$, which is required to accurately describe the system, is too large.
     Lastly, the orange shading shows the region in which the dynamical matrix $\mM$ has negative eigenvalues, indicating that there are phases not captured by our methods.}
@@
 
+The matrix $\mM$ is positive semidefinite if the system is in thermal equilibrium.
+We prove this statement in the appendix \autoref{sec:positive_M}.
+We can use this fact to further enhance our ground state phase diagram.
+If $\mM$ has even a single negative eigenvalue for any combination of parameters, we know that the system is not in thermal equilibrium, 
+i.e., our self-consistency did not capture the correct ground state phase.
+This does in fact happen for certain $U<0$ and $V<0$, see the orange shading in \autoref{fig:phase_limits}.
+For finite temperatures, on a square lattice, a phase-separated state as well as the coexistence of a phase-separated state with $s$-wave superconductivity has been found in this region \cite{Linner23}.
+The phase boundary that we propose here is qualitatively in good agreement with the one found in the aforementioned reference.
+We expect a similar set of phases to be present on the simple cubic lattice but cannot prove this statement at this point.
+
+Additionally, note that while the existence of a negative eigenvalue of $\mM$ proves that the system is not in thermal equilibrium, the absence of one does not prove the contrary.
+For example, we do not find any negative eigenvalues of $\mM$ in the $U>0$, $V<0$ region despite previous studies finding $d_{x^2 - y^2}$-wave superconductivity there \cite{Micnas88b,Huang13}.
+
 However, most Hamiltonians do not allow any such operator set to exist as the commutation usually introduces terms of higher order.
@@
 A detailed explanation of the numerics is provided in the appendix \autoref{sec:numerical_ieom}.
+Herein lies the computational restriction of our method.
+If the gap $\Delta_\text{tot}$ is of the same order of magnitude as our discretization $\Delta \gamma$ our numerics become inaccurate.
+This manifests specifically whenever a spectral function has strong features at minuscule energies, e.g., the phase mode in the superconducting phase.
+In this case, the dynamical matrix $\mM$ picks up negative eigenvalues that vanish if $N_\gamma$ is increased so that $\Delta \gamma$ is sufficiently smaller than $\Delta_\text{tot}$.
 
@@
 This condition is fulfilled for all cases investigated in this article.
-Additionally, the matrix $\mM$ is positive semidefinite if the system is in thermal equilibrium.
-We prove this statement in the appendix \autoref{sec:positive_M}.
 
@@
     \includegraphics[width=.98\textwidth]{plots/sc_peak_in_cdw.pdf}
-    \caption{The upper panels (a) show double logarithmic plots of the positions $\omega_0$ of the peak in $\spectral{SC}$ in the CDW phase while the lower panels (b) show their respective weights $w_0 = e^{b}$.
+    \caption{The upper panels (a) show double logarithmic plots of the positions $\omega_0$ of the peak in $\spectral{SC}$ in the CDW phase while the lower panels (b) show their respective weights $W_0 = e^{b}$.
     In the upper panels, the pink markers additionally show the peak position divided by the gap $\omega_0 / \Delta_\text{CDW}$.
@@
     as well as the position relative to the lower edge of the continuum $\omega_-$.% and in units of $\Delta_\text{SC}$. 
-    The lower panels (b) show their respective weights $w_0 = e^{b}$.
-    The dashed lines represent the value of $\omega_0$ and $w_0$ computed for $U=-2.5t$ and $V=0$ while fixing $\Delta_\text{CDW}=0$.
+    The lower panels (b) show their respective weights $W_0 = e^{b}$.
+    The dashed lines represent the value of $\omega_0$ and $W_0$ computed for $U=-2.5t$ and $V=0$ while fixing $\Delta_\text{CDW}=0$.
     The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
@@
 The real part is related to the imaginary part via the Kramers-Kronig relations.
-Specifically, if the imaginary part is a $\delta$ distribution, the real part will be proportional to $1/\omega$, i.e., $a=-1$, and the peak has the weight $w_0 = \exp(b)$.
+Specifically, if the imaginary part is a $\delta$ distribution, the real part will be proportional to $1/\omega$, i.e., $a=-1$, and the peak has the weight $W_0 = \exp(b)$.
 Furthermore, an exponent of $a=-2$ corresponds to the derivative of the $\delta$ distribution, i.e., $\delta'(\omega)$.
@@
 In the SC phase, $\spectral{CDW}$ features a $\delta$ peak below the continuum corresponding to the finite energy necessary to excite this kind of electronic density modulation.
-For moderate-sized values of $V>0$, i.e., in the CDW phase, see panel (b) at $V=0.1t$, the aforementioned spectral function has a singularity at $\omega=2\Delta_\text{CDW}$.
+For moderate-sized values of $V>0$, i.e., in the CDW phase, see panel (b) at $V=0.1t$, the aforementioned spectral function has a singularity at $\omega=2\Delta_\text{CDW}$.% that exhibits a square-root behavior.
 This mode becomes hard and moves outside the two-particle continuum as $V$ is increased, see panel (c) at $V=0.5t$.
@@
 The peak in $\spectral{CDW}$ moves to a very small, yet finite, $\omega$.
+Within the two-particle continuum $\spectral{CDW}$ and $\spectral{Phase}$ are identical.
 
@@
 This peak is described by $\delta'(\omega)$.
-\textcolor{red}{Warum hat Higgs nun einen Peak bei 0, aber CDW hatte einen bei endlichem $\omega$?
-Das müsste ja bedeuten, dass ein Cooper-Paar energtisch kostenfrei ist, aber ein CDW-Exziton kostet uns etwas Energie.}
 
 Lastly, we chose $\Delta_\text{CDW} = \Delta_\text{SC}$ for panel (c).
-Now, $\spectral{Higgs}$ and $\spectral{CDW}$ are identical.
-Note, that this only occurs for this specific ratio of $\Delta_\text{CDW}$ and $\Delta_\text{SC}$, otherwise the occurring peaks differ in magnitude.
+For this specific ratio of $\Delta_\text{CDW}$ and $\Delta_\text{SC}$, $\spectral{Higgs}$ and $\spectral{CDW}$ are identical.
+Choosing a different ratio yields qualitatively the same results, but the peaks differ in magnitude.
 Both spectral functions have a peak at $\omega = 0$, described by $\delta'(\omega)$, and a singularity at the lower edge of the two-particle continuum $\omega = 2\Delta_\text{tot}$.
-\textcolor{red}{TODO: Exponent}
+Each one of the singularities behaves as $1/\sqrt{\omega - 2 \Delta_\text{tot}}$.
 
@@
 First and foremost, we investigate the peak in $\spectral{Phase}$ and $\spectral{Higgs}$ in the CDW phase.
-The evolution of its position $\omega_0$ and its weight $w_0$ as $V$ is varied can be viewed double logarithmically in \autoref{fig:sc_in_cdw_behavior}.
+The evolution of its position $\omega_0$ and its weight $W_0$ as $V$ is varied can be viewed double logarithmically in \autoref{fig:sc_in_cdw_behavior}.
 For $V \ll t$, the position grows with the square root of $V$. This behavior then transitions to a purely linear growth for large $V$.
@@
 
-The peak weights $w_0$ fall off as $1/\sqrt{V}$ for $V \ll t$. 
+The peak weights $W_0$ fall off as $1/\sqrt{V}$ for $V \ll t$. 
 Afterward, it reaches a shallow minimum and rises slightly to reach a constant value.
 
-Specifically, we learn that for $V \ll t$, the peak position follows $\omega_0 = \alpha \sqrt{V}$ and its weight follows $w_0 = \beta / \sqrt{V}$, 
+Specifically, we learn that for $V \ll t$, the peak position follows $\omega_0 = \alpha \sqrt{V}$ and its weight follows $W_0 = \beta / \sqrt{V}$, 
 where $\alpha$ and $\beta$ are some constants.
-This allows us to write $w_0 = \beta / (\alpha \omega_0)$. 
+This allows us to write $W_0 = \beta / (\alpha \omega_0)$. 
 Furthermore, we know that the spectral functions need to be perfectly antisymmetrical about $\omega = 0$, i.e., we can observe
 \begin{align}
-    \mathcal{A}_\text{Phase} (\omega \ll t) &= w_0 (\delta (\omega - \omega_0) - \delta (\omega + \omega_0)) \nonumber \\
+    \mathcal{A}_\text{Phase} (\omega \ll t) &= W_0 (\delta (\omega - \omega_0) - \delta (\omega + \omega_0)) \nonumber \\
         &= - \frac{2\beta}{\alpha} \frac{\delta (\omega + \omega_0) - \delta (\omega - \omega_0)}{2\omega_0} \,.
@@
 As a next step, we want to analyze the peak in $\spectral{CDW}$ that occurs if the system is in the SC phase ($V<0$).
-A plot of its position $\omega_0$ and weight $w_0$ can be seen in \autoref{fig:sc_in_cdw_behavior}.
+A plot of its position $\omega_0$ and weight $W_0$ can be seen in \autoref{fig:sc_in_cdw_behavior}.
 Both of them smoothly approach a finite value for $|V| \ll 1t$, marked by the dashed line.
@@
 At this point, the weight of said peak also vanishes, see panel (c).
-This occurs around $U=4V \pm 0.4t$ for the square lattice and around $U=6V \pm 1.1t$ for the simple cubic lattice.
+This occurs around $U=4V \pm 0.42t$ for the square lattice and around $U=6V \pm 1.105t$ for the simple cubic lattice.
 
@@
 
-\begin{figure}
+\begin{figure*}
     \centering
-    \includegraphics[width=.48\textwidth]{plots/higgs_peak.pdf}
-    \caption{Log-log plot of $\spectral{Higgs}$ near $\omega = \omega_0 = 2\Delta_\text{SC}$ in the SC phase at $U=-2.5t$ and $V=-0.1t$.
-    We additionally plot the difference between $\spectral{Higgs}$ and $\spectral{Phase}$ and fit it, as we interpret the latter as a background within the two-particle continuum.
-    The upper (lower) panel shows the results for the square (simple cubic) lattice.
-    The spectral function behaves as $1 / \sqrt{\omega - \omega_0}$.}
+    \includegraphics[width=.98\textwidth]{plots/higgs_peak.pdf}
+    \caption{Log-log plot of $\spectral{Higgs}$ (a, c) and $\spectral{CDW}$ (b) near $\omega = \omega_0 = 2\Delta_\text{SC}$ at $U=-2.5t$ and $V=0$.
+    The different panels depict the spectral functions for various ratios of $\Delta_\text{SC}$ to $\Delta_\text{CDW}$.
+    We additionally plot the difference between $\spectral{i}$ and $\spectral{Phase}$ and fit it, as we interpret the latter as a background within the two-particle continuum.
+    The left (right) panel shows the results for the square (simple cubic) lattice.
+    The spectral function behaves as $1 / \sqrt{\omega - 2 \Delta_\text{tot}}$.
+    Note, that $\spectral{CDW}$ and $\spectral{Higgs}$ are identical for the choice in panel (c).}
     \label{fig:higgs_peak}
-\end{figure}
+\end{figure*}
 
@@
 
-Continuing, we investigate the divergence at $\omega = 2\Delta$ found in $\spectral{Higgs}$ within the SC phase.
+Continuing, we investigate the divergence at $\omega = 2\Delta$ found in $\spectral{Higgs}$ and $\spectral{CDW}$ at $V=0$.
 It behaves as $1/\sqrt{\omega}$ as shown in \autoref{fig:higgs_peak}.

### 2024-01-26 paper/cdw_peak_in_sc.py

@@ -17,7 +17,7 @@ from scipy.optimize import curve_fit
 
 Ts = np.array([0.])
 Us = np.array([-2.5])
-Vs = np.array([ #"-0.000001", "-0.0000013", "-0.0000015", "-0.0000017", "-0.000002", "-0.0000025", 
+Vs = np.array([ "-0.000001", "-0.0000013", "-0.0000015", "-0.0000017", "-0.000002", "-0.0000025", 
                 "-0.000003", "-0.000004", "-0.000005", "-0.000006", "-0.000007", "-0.000008", "-0.000009",
                 "-0.00001", "-0.000013", "-0.000015", "-0.000017", "-0.00002", "-0.000025", 
                 "-0.00003", "-0.00004", "-0.00005", "-0.00006", "-0.00007", "-0.00008", "-0.00009", 
@@ -99,8 +99,8 @@ axs[1][1].text(0.88, 0.88, "(b.2)", transform = axs[1][1].transAxes)
 
 axs[1][0].set_xlabel(r"$\ln|V / t|$")
 axs[1][1].set_xlabel(r"$\ln|V / t|$")
-axs[1][0].set_ylabel(r"$w_0$")
-axs[0][0].set_ylabel(r"$\omega_0$")
+axs[1][0].set_ylabel(r"$W_0$")
+axs[0][0].set_ylabel(r"$\omega_0 / t$")
 axs[1][1].legend(loc="lower left")
 axs[0][1].legend(loc="upper left")
 fig.tight_layout()

### 2024-01-26 paper/cdw_peak_in_sc_details.py
text

@@ -109,7 +109,7 @@ axs[1][1].text(0.88, 0.88, "(b.2)", transform = axs[1][1].transAxes)
 
 axs[1][0].set_xlabel(r"$\ln|V / t|$")
 axs[1][1].set_xlabel(r"$\ln|V / t|$")
-axs[1][0].set_ylabel(r"$w_0$")
+axs[1][0].set_ylabel(r"$W_0$")
 axs[0][0].set_ylabel(r"$\omega_0$")
 axs[1][1].legend(loc="lower right")
 axs[0][1].legend(loc="lower right")

### 2024-01-29 paper/main.tex
Feierabend

@@
     \includegraphics[width=.98\textwidth]{plots/cdw_peak_in_sc.pdf}
-    \caption{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ in the SC phase, 
-    as well as the position relative to the lower edge of the continuum $\omega_-$.% and in units of $\Delta_\text{SC}$. 
-    The lower panels (b) show their respective weights $W_0 = e^{b}$.
-    The dashed lines represent the value of $\omega_0$ and $W_0$ computed for $U=-2.5t$ and $V=0$ while fixing $\Delta_\text{CDW}=0$.
+    \caption{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ in the SC phase relative to the position of the peak at $V=0$ with $\Delta_\text{CDW} = 0$.
+    The lower panels (b) show their respective weights $W_0 = e^{b}$ relative to the peak's weight at $V=0$.
     The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
@@
     Choosing even smaller values results in $\mathcal{M}$ no longer being positive, i.e., the system is not in thermal equilibrium.
-    \textcolor{red}{Der Fit im unteren Panel ist ein artanh(ln|V|), damit landet man bei sowas wie $(1-V^2)/(1+V^2)$.
-    Darüber muss ich noch etwas nachdenken.}}
+    The fits are $y(x) = a (\tanh (bx - c) + 1)$.}
     \label{fig:cdw_in_sc_behavior}
@@
     \label{fig:afm_cdw_peaks_overview}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=.98\textwidth]{plots/afm_cdw_peaks_details.pdf}
+    \caption{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{AFM}$ relative to the lower edge of the two-particle continuum $\omega_-$.
+    The parameter range depicted here places the system within the CDW phase.
+    The lower panels (b) depict their respective weights $W_0$.
+    The left column shows the results for the square and the right column for the simple cubic lattice at $V=-1t$.
+    All fits are linear, i.e., $y=ax + b$.}
+    \label{fig:afm_cdw_peaks_details}
 \end{figure*}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 As a next step, we want to analyze the peak in $\spectral{CDW}$ that occurs if the system is in the SC phase ($V<0$).
 A plot of its position $\omega_0$ and weight $W_0$ can be seen in \autoref{fig:sc_in_cdw_behavior}.
-Both of them smoothly approach a finite value for $|V| \ll 1t$, marked by the dashed line.
-These values are obtained by computing the peaks' position and weight for $V=0$ and setting $\Delta_\text{CDW}=0$, see \autoref{fig:resolvent_overview_V0} (a).
-
-Moving towards smaller $V$, the peaks move towards greater $\omega$, i.e., closer to the two-particle continuum.
+The quantities are given relative to the respect quantity of the peak in $\spectral{CDW}$ at $V=0$ with $\Delta_\text{CDW} = 0$, see \autoref{fig:resolvent_overview_V0} (a).
+Both of them smoothly approach $0$ for $|V| \ll 1t$.
+This indicates that the peak steadily evolves to the limiting case $V=0$.
+
+Moving towards larger $|V|$, the peaks move towards greater $\omega$, i.e., closer to the two-particle continuum.
 Additionally, the weights drop off, first with increasing speed and then slowing down.
-They seem to converge towards some value, but we are unable to compute the Green's functions for additional, 
-even smaller $V$ because the matrix $\mM$ is not nonnegative anymore after $V\approx -0.28t$ (square lattice) or $V\approx -0.34t$ (simple cubic lattice).
+A fit of the form $y(x) = a (\tanh (bx - c) + 1)$, with $x=\ln|V/t|$ works well for both the peaks' positions and weights.
+Transforming back to the non-logarithmic scale yields
+\begin{equation}
+    y(V) = a \left( \frac{ \xi - \frac{1}{\xi} }{ \xi + \frac{1}{\xi} } \right)\,,\quad \xi \coloneqq e^{-c} |V/t|^b\,.
+\end{equation}
+The fit parameters are printed in the respective panels of \autoref{fig:sc_in_cdw_behavior}.
+This indicates that the peak weights drop off fairly quickly as the system moves away from the phase transition while the peak positions shift towards higher energies.
+It also suggests that there might be a finite saturation value, but we are unable to compute the Green's functions for additional, even larger $|V|$, 
+because the matrix $\mM$ is not nonnegative anymore after $V\approx -0.28t$ (square lattice) or $V\approx -0.34t$ (simple cubic lattice).
 Note, that our proof for the nonnegativity is based on the system being in thermal equilibrium.
-Therefore, we conclude that beyond these $V$, the superconducting phase is not the true ground state of the system.
-Specifically, the s-wave superconducting phase on the square lattice seems to be even smaller than first estimated using the $d_{x^2 -y^2}$ data from \cite{Micnas88b}.
-In recent research, there has been evidence for a phase-separated state for negative values of $V$ on a square lattice,
-which would explain our results here \cite{Linner23}.
+Therefore, we conclude that beyond these values of $V$, the superconducting phase is not the true ground state of the system, see \autoref{fig:phase_limits}.
+Specifically, the $s$-wave superconducting phase on the square lattice seems to be even smaller than first estimated using the $d_{x^2 -y^2}$ data from \cite{Micnas88b}.
+In recent research, there has been evidence for a phase-separated state for negative values of $V$ on a square lattice, which would explain our results here \cite{Linner23}.
 It would be reasonable to assume, that this phase occurs in both the 2- and 3-dimensional case.
@@
 At this point, the weight of said peak also vanishes, see panel (c).
-This occurs around $U=4V \pm 0.42t$ for the square lattice and around $U=6V \pm 1.105t$ for the simple cubic lattice.
+This occurs around $U \approx 4V \pm 0.424t$ for the square lattice and around $U \approx 6V \pm 1.105t$ for the simple cubic lattice.
 
@@
 On the simple cubic lattice, however, the weights fall off very slightly.
+
+In \autoref{fig:afm_cdw_peaks_details}, we revisit panels (b) and (c) from the previous figure.
+This time around the scaling is double-logarithmic and we consider $U$ relative to the phase transition.
+We restrict the analysis to $\spectral{AFM}$ in the CDW phase as the reverse case yields precisely the same data.
+This yields that the peak positions $\omega_0$ (a) behave quadratically as they move into the two-particle continuum,
+while their weights $W_0$ (b) drop off linearly.
 

### 2024-01-29 paper/cdw_peak_in_sc_details.py

@@ -1,119 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-
-import os, sys
-if os.name == "nt":
-    sys.path.append(os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + r"\python")
-else:
-    sys.path.append(os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + "/python")
-
-import lib.continued_fraction as cf
-from lib.iterate_containers import *
-from lib.extract_key import *
-import lib.resolvent_peak as rp
-import lib.plot_settings as ps
-from lib.ez_linear_fit import *
-
-from scipy.optimize import curve_fit
-
-Ts = np.array([0.])
-Us = np.array([-2.5])
-Vs = np.array([ "-0.000001", "-0.0000013", "-0.0000015", "-0.0000017", "-0.000002", "-0.0000025", 
-                "-0.000003", "-0.000004", "-0.000005", "-0.000006", "-0.000007", "-0.000008", "-0.000009",
-                "-0.00001", "-0.000013", "-0.000015", "-0.000017", "-0.00002", "-0.000025", 
-                "-0.00003", "-0.00004", "-0.00005", "-0.00006", "-0.00007", "-0.00008", "-0.00009", 
-                "-0.0001", "-0.00013", "-0.00015", "-0.00017", "-0.0002", "-0.00025", "-0.0003", 
-                "-0.0004", "-0.0005", "-0.0006", "-0.0007", "-0.0008", "-0.0009", 
-                "-0.001", "-0.0013", "-0.0015", "-0.0017", "-0.002", "-0.0025", 
-                "-0.003", "-0.004", "-0.005", "-0.006", "-0.007", "-0.008", "-0.009", 
-                "-0.01", "-0.013", "-0.015", "-0.017", "-0.02", "-0.025", 
-                "-0.03", "-0.04", "-0.05", "-0.06", "-0.07", "-0.08", "-0.09", 
-                "-0.1", "-0.13", "-0.15", "-0.2", "-0.25", "-0.28"
-                ])
-
-folders = ["../data/modes/square/dos_3k/", "../data/modes/cube/dos_3k/"]
-element_names = ["a", "a+b", "a+ib"]
-
-name_suffix = "higgs_CDW"
[…]

### 2024-01-29 paper/afm_cdw_peaks_overview.py
Feierabend

@@ -15,8 +15,8 @@ import lib.plot_settings as ps
 
 
 Ts = np.array([0.])
-Us_square = np.array([0.0001, 0.025, 0.05, 0.075, 0.1, 0.125, 0.15, 0.175, 0.2, 0.225, 0.25, 0.275, 0.3, 0.325, 0.35, 0.375, 0.4, 0.41, 0.42]) # 0.421 0.422 0.423 0.424
-Us_cube = np.array([0.0001, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 1.0, 1.05, 1.105]) # 1.03, 1.06, 1.07, 1.08, 1.09, 1.1,
+Us_square = np.array([0.0001, 0.025, 0.05, 0.075, 0.1, 0.125, 0.15, 0.175, 0.2, 0.225, 0.25, 0.275, 0.3, 0.325, 0.35, 0.375, 0.4, 0.41, 0.42, 0.423])   # there is a peak at 0.424, but our numerical tools start breaking 
+Us_cube = np.array([0.0001, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 1.0, 1.05, 1.105])
 Us = np.array([np.concatenate((-Us_square[::-1], Us_square)), np.concatenate((-Us_cube[::-1], Us_cube))], dtype=object)
 Vs = np.array([1.0])
 
@@ -26,7 +26,7 @@ element_names = ["a", "a+b", "a+ib"]
 
 name_suffices = ["AFM", "CDW"]
 nrows=3
-fig, axs = plt.subplots(nrows=nrows, ncols=2, figsize=(12.8, 8.2), sharex="col", gridspec_kw=dict(hspace=0))
+fig, axs = plt.subplots(nrows=nrows, ncols=2, figsize=(12.8, 6.4), sharex="col", gridspec_kw=dict(hspace=0))
 plotters = np.empty((nrows,2), dtype=ps.CURVEFAMILY)
 
 for i in range(2):
@@ -53,7 +53,7 @@ for i in range(2):
             upper = 13 * float(V) + 2 if 13 * float(V) + 2 < cont_edges[0] else cont_edges[0]
 
[…]

### 2024-01-29 paper/afm_cdw_peaks_details.py
Feierabend

@@ -12,13 +12,13 @@ from lib.iterate_containers import *
 from lib.extract_key import *
 import lib.resolvent_peak as rp
 import lib.plot_settings as ps
-from lib.ez_linear_fit import *
+from lib.ez_fit import *
 
 Ts = np.array([0.])
-Us_square = np.array([0.0001, 0.025, 0.05, 0.075, 0.1, 0.125, 0.15, 0.175, 0.2, 0.225, 0.25, 0.275, 0.3, 0.325, 0.35, 0.375, 0.4, 0.41, 0.42]) # 0.425
-Us_cube = np.array([0.0001, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 1.0, 1.03, 1.05, 1.06, 1.07, 1.08, 1.09, 1.1, 1.105])
-# Find boundary square: 0.41, 0.42, 0.43, 0.44, 0.45
-# Find boundary cube:   1.11, 1.12, 1.13, 1.14, 1.15
+Us_square = np.array([0.225, 0.25, 0.275, 0.3, 0.325, 0.35, 0.375, 0.4, 0.41, 0.42, 0.421, 0.422, 0.423]) # there is a peak at 0.424, but our numerical tools start breaking 
+Us_cube   = np.array([ 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 1.0, 1.03, 1.05, 1.06, 1.07, 1.08, 1.09, 1.1, 1.105])
+# New square: 0.413, 0.415, 0.417, 0.418, 0.419
+# New cube:   1.102, 1.095, 1.085
 Us = np.array([Us_square, Us_cube], dtype=object)
 Vs = np.array([1.0])
 
@@ -28,8 +28,11 @@ element_names = ["a", "a+b", "a+ib"]
 
 name_suffix = "AFM"
 nrows=2
-fig, axs = plt.subplots(nrows=nrows, ncols=2, figsize=(12.8, 8.2), sharex="col", gridspec_kw=dict(hspace=0))
+fig, axs = plt.subplots(nrows=nrows, ncols=2, figsize=(12.8, 6.4), sharex="col", gridspec_kw=dict(hspace=0))
[…]

### 2024-01-29 paper/sc_peak_in_cdw.py

@@ -29,7 +29,8 @@ Vs = np.array(["0.00001", "0.000013", "0.000015", "0.000017", "0.00002", "0.0000
                 "0.01", "0.013", "0.015", "0.017", "0.02", "0.025", 
                 "0.03", "0.04", "0.05", "0.06", "0.07", "0.08", "0.09", 
                 
-                "0.1", "0.13", "0.15", "0.2", "0.25", "0.3", "0.35", "0.4", "0.45", "0.5", "0.6", "0.7", "0.8", "0.9", 
+                "0.1", "0.13", "0.15", "0.2", "0.25", "0.3", "0.35", "0.4", 
+                "0.45", "0.5", "0.6", "0.7", "0.8", "0.9", 
                 "1.0", "1.1", "1.2", "1.3", "1.4", "1.5", "1.6", "1.7", "1.8", "1.9", "2.0", 
                 "2.5", "3.0", "3.5", "4.0", "6.0", "8.0", "10.0", "15.0", "25.0", "50.0"])
 v_data = np.log(np.array([float(v) for v in Vs]))
@@ -65,7 +66,7 @@ for i in range(2):
         lower = 0 if float(V) < 1 else float(V)
         upper = 13 * float(V) + 2 if 13 * float(V) + 2 < cont_edges[0] else cont_edges[0]
         
-        peak_positions[counter], weights[counter] = rp.analyze_peak(f"{folders[i]}{name}", name_suffix, (lower, upper))
+        peak_positions[counter], weights[counter] = rp.analyze_peak(f"{folders[i]}{name}", name_suffix, (lower, upper), begin_offset=1e-7)
         peak_positions_div_delta[counter] = peak_positions[counter] / extract_key(f"{folders[i]}{name}/resolvent_{name_suffix}.dat.gz", "Total Gap")
         counter += 1
 

### 2024-01-30 paper/main.tex
Paper draft

@@
     \includegraphics[width=.98\textwidth]{plots/cdw_peak_in_sc.pdf}
-    \caption{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ in the SC phase relative to the position of the peak at $V=0$ with $\Delta_\text{CDW} = 0$.
-    The lower panels (b) show their respective weights $W_0 = e^{b}$ relative to the peak's weight at $V=0$.
+    \caption{The panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ in the SC phase.
+    Below that, in panels (b), their respective weights are depicted.
+    The dashed lines in both rows show the position or weight computed for $V=0$ with $\Delta_\text{CDW} = 0$.
     The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
-    The $V$-axis is scaled logarithmically.
     The left-most values are $V=-0.28t$ for the square lattice and $V=-0.34t$ for the simple cubic lattice.
     Choosing even smaller values results in $\mathcal{M}$ no longer being positive, i.e., the system is not in thermal equilibrium.
-    The fits are $y(x) = a (\tanh (bx - c) + 1)$.}
+    \newline
+    The lower panels (c) and (d) present the data again, but with logarithmic scaling on the $V$-axis.
+    Additionally, the peak positions and weights are given relative to their value at $V=0$.
+    These data are fitted by $y(x) = a (\tanh (bx - c) + 1)$ with the parameters printed in the individual panel.
+    The panels (a) and (b) feature the same fitting result.}
     \label{fig:cdw_in_sc_behavior}
@@
     \caption{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{AFM}$ relative to the lower edge of the two-particle continuum $\omega_-$.
-    The parameter range depicted here places the system within the CDW phase.
     The lower panels (b) depict their respective weights $W_0$.
     The left column shows the results for the square and the right column for the simple cubic lattice at $V=-1t$.
+    $U_0$ denotes the highest value of $U$ for which there is no peak below the two-particle continuum.
+    For the square lattice it is $U_0 = 3.5775t$ and for the simple cubic lattice it is $U_0 = 4.89t$.
+    The parameter range depicted here places the system within the CDW phase.
     All fits are linear, i.e., $y=ax + b$.}
@@
 In this case, the only minimum is at $\Delta_\text{SC} = 0$. 
-That means that both possible modes have to overcome the same energy to be excited at all. \textcolor{red}{Passt die Beschreibung so?}
+That means that both possible modes have to overcome the same energy to be excited at all.
 
@@
 A plot of its position $\omega_0$ and weight $W_0$ can be seen in \autoref{fig:sc_in_cdw_behavior}.
-The quantities are given relative to the respect quantity of the peak in $\spectral{CDW}$ at $V=0$ with $\Delta_\text{CDW} = 0$, see \autoref{fig:resolvent_overview_V0} (a).
-Both of them smoothly approach $0$ for $|V| \ll 1t$.
+First and foremost, the upper panels (a) and (b) depict the peak positions and weights, respectively.
+The former drops off and the latter grows as $V$ moves to 0, however, both of them smoothly approach a finite value.
+It is the same, as the one that is obtained for $V=0$ while setting $\Delta_\text{CDW}$ to 0, see \autoref{fig:resolvent_overview_V0} (a).
 This indicates that the peak steadily evolves to the limiting case $V=0$.
@@
 Moving towards larger $|V|$, the peaks move towards greater $\omega$, i.e., closer to the two-particle continuum.
-Additionally, the weights drop off, first with increasing speed and then slowing down.
-A fit of the form $y(x) = a (\tanh (bx - c) + 1)$, with $x=\ln|V/t|$ works well for both the peaks' positions and weights.
+Additionally, the weights drop off, first with increasing speed and then slowing down, see panels (c) and (d) for a logarithmic scaling.
+A fit of the form $y(x) = a (\tanh (bx - c) + 1)$, with $x=\ln|V/t|$ works well for both the peak positions and weights.
 Transforming back to the non-logarithmic scale yields
@@
 
-The panel (a) shows the peaks' positions unmodified. They essentially move linearly as $U$ is varied.
+The panel (a) shows the peak positions unmodified. They essentially move linearly as $U$ is varied.
 It is noteworthy, that in the AFM phase, the peak in $\spectral{AFM}$ lies lower than the one in $\spectral{CDW}$.
@@
 
-Additionally, we plot in (b) the peaks' positions relative to the lower edge of the two-particle continuum.
+Additionally, we plot in (b) the peak positions relative to the lower edge of the two-particle continuum.
 We see that the lower-lying peak, i.e., the peak corresponding to the phase the system is in, 
@@
 At this point, the weight of said peak also vanishes, see panel (c).
-This occurs around $U \approx 4V \pm 0.424t$ for the square lattice and around $U \approx 6V \pm 1.105t$ for the simple cubic lattice.
-
-On the square lattice, the weights of the peak in $\spectral{AFM}$ in the AFM phase (the same applies for CDW) grow as the system moves away from the phase transition.
+This occurs around $U \approx 4V \pm 0.4245t$ for the square lattice and around $U \approx 6V \pm 1.11t$ for the simple cubic lattice.
+
+On the square lattice, the weights of the peaks in $\spectral{AFM}$ in the AFM phase (the same applies to $\spectral{CDW}$ in the CDW phase) grow as the system moves away from the phase transition.
 On the simple cubic lattice, however, the weights fall off very slightly.
@@
 In \autoref{fig:afm_cdw_peaks_details}, we revisit panels (b) and (c) from the previous figure.
-This time around the scaling is double-logarithmic and we consider $U$ relative to the phase transition.
 We restrict the analysis to $\spectral{AFM}$ in the CDW phase as the reverse case yields precisely the same data.
+This time around the scaling is double-logarithmic and we consider $U$ relative to those values at which we cannot find a peak in $\spectral{AFM}$.
+This occurs around $U_0 = 3.5755t$ on the square lattice and around $U_0 = 4.89t$ on the simple cubic lattice.
 This yields that the peak positions $\omega_0$ (a) behave quadratically as they move into the two-particle continuum,
@@
 
-Ideen für die Zukunft:
-
-Phase-separated state aufnehmen
-
-Ankopplung an das EM-Feld
-
-Mehrbandsysteme
+We have conducted an analysis of the mean-field phase diagram of the extended Hubbard model in 2D and 3D. 
+Specifically, both systems provide a similar structure of $s$-wave SC, CDW, and AFM.
+Furthermore, we were able to identify an area in which our analysis is incomplete.
+In 2D, this region coincides with a phase-separated state that has already been observed in recent research \cite{Linner23}.
+
+We have also developed a novel method to obtain Fourier transformed Green's functions and analyzed various such functions. 
+We have found collective excitations within the spectral functions $\spectral{Higgs}$, $\spectral{Phase}$, $\spectral{CDW}$, and $\spectral{AFM}$ 
+and examined their behavior as the system approaches phase transitions. 
+In particular, we identified the peak and singularity found in the first two as the well-known phase and amplitude modes in neutral superconductors 
+and thereby provided a technique to obtain them starting from a microscopic description.
+
+We observed the behavior of the peak in the SC-related spectral functions.
+It moves towards 0 energy and attains more weight as the system moves from the CDW phase towards the SC phase. 
+The peak's relative position to the two-particle continuum and its weight plateau as the system moves away from the phase transition.
+
+In the SC phase close to the CDW phase, the peak in $\spectral{CDW}$ is located at a finite energy and and has a finite weight. 
+It moves towards higher energy and its weight drops off as the system moves away from the phase transition.
+
+Around the AFM-CDW phase transition, both $\spectral{AFM}$ and $\spectral{CDW}$ feature a peak. 
+The peak of the former in the AFM phase lies at lower energies than the latter one and vice-versa. 
+Moving away from the phase transition, the higher-lying peak becomes soft as it moves into the two-particle continuum. 
+The peak position relative to the two-particle continuum approaches $0$ quadratically with $U$, and its weight approaches $0$ linearly.
+
+Furthermore, we have found a peak in $\spectral{CDW}$ that appears at large values of $V$, 
+which is most likely the same as the one found close to the CDW-AFM phase transition.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Some possible ideas for future research include incorporating phase-separated states into the mean-field theory.
+This would enable us to peer deeper into the negative $V$ regime of the phase diagrams and provide more analysis of the collective excitations that occur therein.
+
+Moreover, one can fathom to include a coupling of the electronic system to the electromagnetic field.
+This should move the position of the phase mode close to the plasma frequency as explained by the Anderson-Higgs mechanism.
+
+Additionally, one could describe multi-band systems with even richer phases and collective excitations.
 

### 2024-01-30 paper/afm_cdw_peaks_details.py

@@ -15,8 +15,10 @@ import lib.plot_settings as ps
 from lib.ez_fit import *
 
 Ts = np.array([0.])
-Us_square = np.array([0.225, 0.25, 0.275, 0.3, 0.325, 0.35, 0.375, 0.4, 0.41, 0.42, 0.421, 0.422, 0.423]) # there is a peak at 0.424, but our numerical tools start breaking 
-Us_cube   = np.array([ 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 1.0, 1.03, 1.05, 1.06, 1.07, 1.08, 1.09, 1.1, 1.105])
+Us_square = np.array([ 0.0001, 0.025, 0.05, 0.075, 0.1, 0.125, 0.15, 0.175, 0.2, 
+                0.225, 0.25, 0.275, 0.3, 0.325, 0.35, 0.375, 0.4, 0.41, 0.413, 0.415, 0.417, 0.418, 0.419, 0.42, 0.421, 0.422, 0.423, 0.424]) # there is a peak at 0.424, but our numerical tools start breaking 
+Us_cube   = np.array([ 0.0001, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 
+                0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 1.0, 1.03, 1.05, 1.06, 1.07, 1.08, 1.085, 1.09, 1.095, 1.1, 1.102, 1.105])
 # New square: 0.413, 0.415, 0.417, 0.418, 0.419
 # New cube:   1.102, 1.095, 1.085
 Us = np.array([Us_square, Us_cube], dtype=object)
@@ -28,7 +30,7 @@ element_names = ["a", "a+b", "a+ib"]
 
 name_suffix = "AFM"
 nrows=2
-fig, axs = plt.subplots(nrows=nrows, ncols=2, figsize=(12.8, 6.4), sharex="col", gridspec_kw=dict(hspace=0))
+fig, axs = plt.subplots(nrows=nrows, ncols=2, figsize=(12.8, 5.4), sharex="col", gridspec_kw=dict(hspace=0))
 plotters = np.empty((nrows,2), dtype=ps.CURVEFAMILY)
 
 peak_fit_params = [ {"range": 1e-6, "begin_offset": 5e-10, "imaginary_offset": 1e-6},
[…]

### 2024-01-30 paper/sc_peak_in_cdw.py

@@ -53,12 +53,12 @@ for i in range(2):
     plotters[0][i] = ps.CURVEFAMILY(6, axis=axs[0][i])
     plotters[0][i].set_individual_colors("nice")
     plotters[0][i].set_individual_linestyles(["-", "-", "", "", "", ""])
-    plotters[0][i].set_individual_markerstyles(["", "", "x", "x", "v", "1"])
+    plotters[0][i].set_individual_markerstyles(["", "", "^", "^", "v", "1"])
     
     plotters[1][i] = ps.CURVEFAMILY(3, axis=axs[1][i])
     plotters[1][i].set_individual_colors("nice")
     plotters[1][i].set_individual_linestyles(["-", "", ""])
-    plotters[1][i].set_individual_markerstyles(["", "x", "v"])
+    plotters[1][i].set_individual_markerstyles(["", "^", "v"])
     
     for T, U, V in iterate_containers(Ts, Us, Vs):
         name = f"T={T}/U={U}/V={V}"
@@ -76,7 +76,7 @@ for i in range(2):
     
     plotters[1][i].plot(v_lin, rp.linear_function(v_lin, *popt), label="Fit")
     plotters[1][i].plot(v_data[:cut], weights[:cut], label="Fitted data")
-    plotters[1][i].plot(v_data[cut:], weights[cut:], label="Omitted data")
+    plotters[1][i].plot(v_data[cut:], weights[cut:], label="Omitted data", markerfacecolor="None")
     
     axs[1][i].text(0.05, 0.4, f"$c={popt[0]:.4f}$", transform = axs[1][i].transAxes)
     axs[1][i].text(0.05, 0.3, f"$d={popt[1]:.4f}$", transform = axs[1][i].transAxes)
@@ -96,7 +96,7 @@ for i in range(2):
     plotters[0][i].plot(x_lin,  rp.linear_function(x_lin, *popt), label="Fit 2")
     plotters[0][i].plot(v_data[:cut], peak_positions[:cut], label="Data Fit 1")
     plotters[0][i].plot(v_data[cut2:], peak_positions[cut2:], label="Data Fit 2")
-    plotters[0][i].plot(v_data[cut:cut2], peak_positions[cut:cut2], label="Omitted data")
+    plotters[0][i].plot(v_data[cut:cut2], peak_positions[cut:cut2], label="Omitted data", markerfacecolor="None")
[…]

### 2024-01-30 paper/cdw_peak_in_sc.py
Paper draft

@@ -14,39 +14,61 @@ import lib.resolvent_peak as rp
 import lib.plot_settings as ps
 from lib.ez_fit import *
 
-from scipy.optimize import curve_fit
 
 Ts = np.array([0.])
 Us = np.array([-2.5])
 Vs = np.array([ "-0.000001", "-0.0000013", "-0.0000015", "-0.0000017", "-0.000002", "-0.0000025", 
-                "-0.000003", "-0.000004", "-0.000005", "-0.000006", "-0.000007", "-0.000008", "-0.000009",
+                "-0.000003", "-0.000004", "-0.000005", "-0.000006", "-0.000007", "-0.000008", "-0.000009", # last index = 12
                 "-0.00001", "-0.000013", "-0.000015", "-0.000017", "-0.00002", "-0.000025", 
-                "-0.00003", "-0.00004", "-0.00005", "-0.00006", "-0.00007", "-0.00008", "-0.00009", 
-                "-0.0001", "-0.00013", "-0.00015", "-0.00017", "-0.0002", "-0.00025", "-0.0003", 
-                "-0.0004", "-0.0005", "-0.0006", "-0.0007", "-0.0008", "-0.0009", 
-                "-0.001", "-0.0013", "-0.0015", "-0.0017", "-0.002", "-0.0025", 
-                "-0.003", "-0.004", "-0.005", "-0.006", "-0.007", "-0.008", "-0.009", 
+                "-0.00003", "-0.00004", "-0.00005", "-0.00006", "-0.00007", "-0.00008", "-0.00009",  # last index = 25
+                "-0.0001", "-0.00013", "-0.00015", "-0.00017", "-0.0002", "-0.00025", "-0.0003", # last index = 32
+                "-0.0004", "-0.0005", "-0.0006", "-0.0007", "-0.0008", "-0.0009",  # last index = 37
+                "-0.001", "-0.0013", "-0.0015", "-0.0017", "-0.002", "-0.0025", # 43
+                "-0.003", "-0.004", "-0.005", "-0.006", "-0.007", "-0.008", "-0.009", # 50
                 "-0.01", "-0.013", "-0.015", "-0.017", "-0.02", "-0.025", 
[…]

### 2024-02-05 paper/afm_cdw_peaks_overview.py
plot formatting

@@ -80,10 +80,10 @@ axs[1][1].text(0.9, 0.6, "(b.2)", transform = axs[1][1].transAxes)
 axs[2][0].text(0.9, 0.6, "(c.1)", transform = axs[2][0].transAxes)
 axs[2][1].text(0.9, 0.6, "(c.2)", transform = axs[2][1].transAxes)
 
-axs[nrows-1][0].set_xlabel(r"$U / t$")
-axs[nrows-1][1].set_xlabel(r"$U / t$")
-axs[0][0].set_ylabel(r"$\omega_0 / t$")
-axs[1][0].set_ylabel(r"$(\omega_- - \omega_0) / t$")
+axs[nrows-1][0].set_xlabel(r"$U [t]$")
+axs[nrows-1][1].set_xlabel(r"$U [t]$")
+axs[0][0].set_ylabel(r"$\omega_0 [t]$")
+axs[1][0].set_ylabel(r"$(\omega_- - \omega_0) [t]$")
 axs[2][0].set_ylabel(r"$W_0$")
 legend = axs[0][1].legend(loc='upper center')
 fig.tight_layout()

### 2024-02-05 paper/peak_fits.py

@@ -36,16 +36,16 @@ def plot_general_peak(plot_axs, T, U, V, name_suffix, initial_search_bounds, tex
 
 # CDW in SC
 plot_general_peak(axs[0], T=0.0, U=-2.5, V=-0.1, name_suffix="CDW", initial_search_bounds=(0.3, 0.8), reversed=False, text="SC: ")
-axs[0][0].set_ylabel(r"$\ln(\Re[\mathcal{G}_\mathrm{CDW}](\omega))$")
+axs[0][0].set_ylabel(r"$\ln(\Re[\mathcal{G}_\mathrm{CDW}](\omega) \cdot t)$")
 # SC in CDW
 plot_general_peak(axs[1], T=0.0, U=-2.5, V=0.1, name_suffix="higgs_SC", initial_search_bounds=(0.5, 1.5), reversed=False, text="CDW: ")
-axs[1][0].set_ylabel(r"$\ln(\Re[\mathcal{G}_\mathrm{Higgs}](\omega))$")
+axs[1][0].set_ylabel(r"$\ln(\Re[\mathcal{G}_\mathrm{Higgs}](\omega) \cdot t)$")
 #AFM in CDW
 plot_general_peak(axs[2], T=0.0, U=[3.9, 5.9], V=1.0, name_suffix="AFM", initial_search_bounds=(2., "lower_edge"), reversed=True, text="CDW: ")
-axs[2][0].set_ylabel(r"$\ln(\Re[\mathcal{G}_\mathrm{AFM}](\omega))$")
+axs[2][0].set_ylabel(r"$\ln(\Re[\mathcal{G}_\mathrm{AFM}](\omega) \cdot t)$")
 #AFM in AFM
 plot_general_peak(axs[3], T=0.0, U=[4.1, 6.1], V=1.0, name_suffix="AFM", initial_search_bounds=(2., "lower_edge"), reversed=True, text="AFM: ")
-axs[3][0].set_ylabel(r"$\ln(\Re[\mathcal{G}_\mathrm{AFM}](\omega))$")
+axs[3][0].set_ylabel(r"$\ln(\Re[\mathcal{G}_\mathrm{AFM}](\omega) \cdot t)$")
 
 
 legend = axs[0][1].legend(loc='upper center', bbox_to_anchor=(0., 1.25), ncol=2, shadow=True)

### 2024-02-05 paper/zero_peaks.py

@@ -37,7 +37,7 @@ for j, V, g_name, name_suffix in [(0, -0.1, "Phase", "phase_SC"), (1, 0.0, "Higg
         plotters[i].plot(w_log, func_ln(w_log, *popt), label=f"Fit")
         axs[j][i].text(0.05, 0.4, f"$a={popt[0]:.4f}$", transform = axs[j][i].transAxes)
         axs[j][i].text(0.05, 0.29, f"$b={popt[1]:.4f}$", transform = axs[j][i].transAxes)
-    axs[j][0].set_ylabel(rf"$\ln(\Re[\mathcal{{G}}_\mathrm{{{g_name}}}](\omega))$")
+    axs[j][0].set_ylabel(rf"$\ln(\Re[\mathcal{{G}}_\mathrm{{{g_name}}}](\omega) \cdot t)$")
 
 axs[0][0].title.set_text("Square")
 axs[0][1].title.set_text("Simple cubic")

### 2024-02-19 paper/main.tex
plot formatting
Feierabend

@@
 \affiliation{Condensed Matter Theory, TU Dortmund University,
-Otto-Hahn Stra\ss{}e 4, 44221 Dortmund, Germany}
+Otto-Hahn Stra\ss{}e 4, 44227 Dortmund, Germany}
 
@@
     in the extended Hubbard model at zero temperature and half-filling.
-    We employ the iterated equations of motion approach \cite{Kalthoff17,bleicker18} to compute the two-particle Green's functions and by extension, the corresponding spectral densities.
-    This renders comprehensive analysis of the behavior of collective excitations possible as the model's parameters are changed across phase transitions.
+    We employ the iterated equations of motion approach \cite{Kalthoff17,bleicker18} to compute the two-particle Green's functions and their spectral densities.
+    This renders a comprehensive analysis of the behavior of collective excitations possible as the model's parameters are changed across phase transitions.
     We identify the well-known amplitude (Higgs) and phase (Anderson-Bogoliubov) modes within the superconducting phase and observe a similar excitation in the CDW phase which shifts towards zero energy as the system approaches the phase transition to the SC phase.
@@
 
-The study of collective excitations is of great scientific interest as it sheds light on the intricate dynamics of correlated electron systems, providing crucial insights into emergent material properties.
+The study of collective excitations is of great interest as it sheds light on the intricate dynamics of correlated electron systems, providing crucial insight into emergent material properties.
 On the theoretical side, the Hubbard model has been employed in a plethora of previous studies. 
@@
 \cite{Micnas88,Micnas88b,Micnas89,Dzierzawa92,Kostyrko92,Eriksson95,Staudt00,Onari04,Toschi05,Brackett16,Paki19,romer20,Sushchyev22}.
-For a long time, research on the dynamics of the superconducting gap parameter focused on its behavior after an instantaneous quench, 
-yielding damped or persistent oscillations depending on the magnitude of the quench \cite{Volkov73,Yuzbashyan05,Yuzbashyan06,Barankov06,Cui19}.
-More recent experimental and theoretical studies examined the driven systems in the hope of inducing superconductivity \cite{Nicoletti14,Krull14,Moor14,Casandruc15,patel16,sentef17,Buenemann17}.
+Recent studies on the dynamics of the superconducting gap parameter examined quenches, yielding oscillations \cite{Volkov73,Yuzbashyan05,Yuzbashyan06,Barankov06,Cui19}, 
+and driven systems in the hope of inducing superconductivity \cite{Nicoletti14,Krull14,Moor14,Casandruc15,patel16,sentef17,Buenemann17}.
 
 In this paper, we will restrict ourselves to the half-filled Hubbard model, including an additional intersite interaction, on a square and a simple cubic lattice.
-The 2D case already exhibits a wide range of possible phases, including CDW, AFM, $s$- and $d_{x^2 - y^2}$-wave superconductivity, and phase-separated states \cite{Micnas88b,Tsuchiura95,Su01,Su04,ha11,Huang13,Jiang22,Linner23}.
+Specifically, we investigate competing phases, i.e., the behavior of various collective modes around phase transitions.
+To this end, the 2D case already provides a wide range of possible phases, including CDW, AFM, $s$- and $d_{x^2 - y^2}$-wave superconductivity, and phase-separated states \cite{Micnas88b,Tsuchiura95,Su01,Su04,ha11,Huang13,Jiang22,Linner23}.
 We expand these well-known phase diagrams to the simple cubic lattice where we find a similar structure for CDW, AFM, and $s$-wave SC.
@@
 By extension, we also obtain the spectral functions of the investigated systems and discuss the excitations found therein.
-The prominent examples in the SC phase are the well-known phase (Anderson-Bogoliubov) and amplitude (Higgs) modes \cite{Kulik1981,Varma02,Cea14,Measson14,Tsuji15,Krull16,Schwarz20,Fan22}.
-The former is located at zero energy as our model describes neutral superfluids.
+The prominent examples in the SC phase are the well-known phase (Anderson-Bogoliubov) and amplitude (Higgs) modes.
+The former occurs in neutral superfluids at $0$ energy and has been found in the past \cite{Maiti2015,Sun2020,Fan22}.
+We will obtain this mode as well based on a microscopic description that excludes long-range electromagnetic interactions.
+The inclusion of this kind of interaction shifts this mode towards the plasma frequency \cite{Kulik1981}. TODO: Schön
+
+The amplitude mode ... \cite{Varma02,Cea14,Measson14,Tsuji15,Krull16,Schwarz20}
 The latter is found at the lower edge of the two-particle continuum.
@@
 
-In our study, we employ the extended Hubbard model as it encompasses assorted phases and thereby provides direct access to the rich excitation spectra therein.
+In our study, we employ the extended Hubbard model as it encompasses the relevant phases and thereby provides direct access to the rich excitation spectra therein.
 Its Hamiltonian is given by
@@
 
-In this article, we will be using the operator pseudo scalar product
+In this article, we will be using the symplectic product\textcolor{red}{, also referred to as the operator pseudo scalar product,}
 \begin{equation}

### 2024-02-20 paper/main.tex
text

@@
 The matrix $\mM$ is positive semidefinite if the system is in thermal equilibrium.
-We prove this statement in the appendix \autoref{sec:positive_M}.
+We prove this statement in the appendix \ref{sec:positive_M}.
 We can use this fact to further enhance our ground state phase diagram.
@@
 
-We create our operator set on the basis of \eqref{eqn:equal_expecs}.
+\textcolor{red}{To treat the square and simple cubic lattice on equal footing, we utilize the fact \eqref{eqn:equal_expecs} to create our operator set in $\gamma$-space.}
 It consists of operators of the type
@@
 Operators with different indices are put into the set individually, e.g., $n_{\gamma \up}$, and $n_{\gamma \down}$ are distinct operators in our set.
+\textcolor{red}{Additionally, we will include $\tau_{k} \coloneqq c_{k \uparrow}^\dagger c_{k \downarrow}$ and its Hermitian conjugate.
+This will allow us to describe transversal magnons later on.}
 
@@
 Practically, we choose $N_\gamma = 3000$ equally spaced discretization points.
-A detailed explanation of the numerics is provided in the appendix \autoref{sec:numerical_ieom}.
-Herein lies the computational restriction of our method.
+A detailed explanation of the numerics is provided in the appendix \ref{sec:numerical_ieom}.
+\textcolor{red}{Computationally, our method is limited by the number of terms included in our operator set as well in the magnitude of $N_\gamma$.}
 If the gap $\Delta_\text{tot}$ is of the same order of magnitude as our discretization $\Delta \gamma$ our numerics become inaccurate.
@@
 Then, our set is given by $\mathcal{B}_{XP} \coloneqq \{ X_i, \ldots, P_i, \ldots \}$.
-If some operators would be 0 ($P_i$ for any $n$-type term) or duplicates (certain $X_i$ for $g$-type terms), we omit them.
+If some operators would be 0 ($P_i$ for any Hermitian term) or duplicates (certain $X_i$ for $g$-type terms, e.g, $g_{k\sigma} = g_{k+Q\sigma}^\dagger$), we omit them.
 
@@
 Thus, if all occurring expectation values are real, both matrices have large empty blocks.
-This condition is fulfilled for all cases investigated in this article.
+This condition is fulfilled for all cases investigated in this article \textcolor{red}{because our model has inversion symmetry as well as time-reversal symmetry.}
 
@@
 Note, that all of the aforementioned operators are Hermitian. 
-This means that all spectral functions need to be completely antisymmetrical, see appendix \autoref{sec:antisymmetry_spectral}.
+This means that all spectral functions need to be completely antisymmetrical, see appendix \ref{sec:antisymmetry_spectral}.
 For this reason, we will only show the $\omega \geq 0$ in our plots. 
@@
 Furthermore, an exponent of $a=-2$ corresponds to the derivative of the $\delta$ distribution, i.e., $\delta'(\omega)$.
-The fits themselves can be found in appendix \autoref{sec:fit_greens_functions}.
+The fits themselves can be found in appendix \ref{sec:fit_greens_functions}.
 

### 2024-02-28 paper/phase_diagram.py
uni

@@ -2,16 +2,21 @@ import numpy as np
 import matplotlib.pyplot as plt
 
 fig, axs = plt.subplots(nrows=2, sharex=True, figsize=(6.4, 9))
+folder = "T0"
 
-xlims = (-2, 2)
+xlims = (-4, 4)
 ylims = (-2, 2)
 alpha = .6
 
 ############################################################################
 ############                  Square lattice                    ############
 ############################################################################
+import gzip
+with gzip.open(f"../data/phases/square/{folder}/unkown_boundary.dat.gz", 'rt') as fp:
+    u_boundary = np.loadtxt(fp)
+
 #Shade s-wave area
-axs[0].fill_between([xlims[0], 0], [0, 0], [ylims[0], ylims[0]], alpha=alpha, label="$s$-wave")
+axs[0].fill_between(u_boundary[0], u_boundary[1], np.full(len(u_boundary[0]), 0), label="$s$-wave", alpha=alpha)
 
 #Shade CDW area
 axs[0].fill_between(np.array([xlims[0], 0, xlims[1]]), np.array([0, 0, xlims[1] / 4]), np.array([ylims[1], ylims[1], ylims[1]]), alpha=alpha, label="CDW")
@@ -19,8 +24,11 @@ axs[0].fill_between(np.array([xlims[0], 0, xlims[1]]), np.array([0, 0, xlims[1] 
 #Shade AFM area
 axs[0].fill_between([0, xlims[1]], [0, xlims[1] / 4], [ylims[0], ylims[0]], alpha=alpha, label="AFM")
 
-#Shade d-wave area
-#axs[0].fill_between(micnas_d[0], micnas_d[1], -2 * np.ones(len(micnas_d[0])), color="red", alpha=.5, label="$d_{x^2 - y^2}$-wave")
+# unknown regions
+axs[0].fill_between(u_boundary[0], u_boundary[1], np.full(len(u_boundary[0]), ylims[0]), label="Unknown phases", alpha=alpha)
+axs[0].fill_between([u_boundary[0][-1], 0], [0, 0], [ylims[0], ylims[0]], label=r"$\Delta$ too small", alpha=alpha)
+axs[0].plot(u_boundary[0], u_boundary[1], "k-")
[…]

### 2024-02-28 paper/main.tex
uni

@@
 \begin{abstract}
-    We investigate the superconducting (SC), charge-density wave (CDW), and antiferromagnetic (AFM) phases 
-    in the extended Hubbard model at zero temperature and half-filling.
-    We employ the iterated equations of motion approach \cite{Kalthoff17,bleicker18} to compute the two-particle Green's functions and their spectral densities.
+    We investigate the superconducting (SC), charge-density wave (CDW), and antiferromagnetic (AFM) phases in the extended Hubbard model at zero temperature and half-filling. 
+    We employ the iterated equations of motion approach to compute the two-particle Green's functions and their spectral densities. 
     This renders a comprehensive analysis of the behavior of collective excitations possible as the model's parameters are changed across phase transitions. 
-    We identify the well-known amplitude (Higgs) and phase (Anderson-Bogoliubov) modes within the superconducting phase and observe a similar excitation in the CDW phase which shifts towards zero energy as the system approaches the phase transition to the SC phase.
-    In the CDW phase, close to the phase transition to the AFM phase, we find a collective mode that does not change significantly and another mode that becomes soft as the phase boundary is approached.
+    We identify the well-known amplitude (Higgs) and phase (Anderson-Bogoliubov) modes within the superconducting phase 
+    and observe a similar excitation (Cooperon) in the CDW phase which shifts towards zero energy as the system approaches the phase transition to the SC phase. 
+    \textcolor{red}{In the CDW phase, close to the phase transition to the AFM phase, 
+    we find a collective mode (exciton) that does not change significantly and another mode (magnon) that moves into the two-particle continuum. 
+    In the AFM phase we identify both longitudinal and transversal magnons.}
 \end{abstract}
@@
 \cite{Micnas88,Micnas88b,Micnas89,Dzierzawa92,Kostyrko92,Eriksson95,Staudt00,Onari04,Toschi05,Brackett16,Paki19,romer20,Sushchyev22}.
-Recent studies on the dynamics of the superconducting gap parameter examined quenches, yielding oscillations \cite{Volkov73,Yuzbashyan05,Yuzbashyan06,Barankov06,Cui19}, 
-and driven systems in the hope of inducing superconductivity \cite{Nicoletti14,Krull14,Moor14,Casandruc15,patel16,sentef17,Buenemann17}.
+\textcolor{red}{Recent studies on the dynamics of the superconducting gap parameter examined quenches, yielding oscillations \cite{Volkov73,Yuzbashyan05,Yuzbashyan06,Barankov06,Cui19}, 
+and driven systems in the hope of inducing superconductivity \cite{Nicoletti14,Krull14,Moor14,Casandruc15,patel16,sentef17,Buenemann17}.}
 
 In this paper, we will restrict ourselves to the half-filled Hubbard model, including an additional intersite interaction, on a square and a simple cubic lattice.
-Specifically, we investigate competing phases, i.e., the behavior of various collective modes around phase transitions.
-To this end, the 2D case already provides a wide range of possible phases, including CDW, AFM, $s$- and $d_{x^2 - y^2}$-wave superconductivity, and phase-separated states \cite{Micnas88b,Tsuchiura95,Su01,Su04,ha11,Huang13,Jiang22,Linner23}.
+\textcolor{red}{Specifically, we investigate competing phases, i.e., the behavior of various collective modes around phase transitions.
+To this end, the 2D case already provides a wide range of possible phases, including CDW, AFM, $s$- and $d_{x^2 - y^2}$-wave superconductivity, and phase-separated states \cite{Micnas88b,Tsuchiura95,Su01,Su04,ha11,Huang13,Jiang22,Linner23}.}
 We expand these well-known phase diagrams to the simple cubic lattice where we find a similar structure for CDW, AFM, and $s$-wave SC.
@@
 The prominent examples in the SC phase are the well-known phase (Anderson-Bogoliubov) and amplitude (Higgs) modes.
-The former occurs in neutral superfluids at $0$ energy and has been found in the past \cite{Maiti2015,Sun2020,Fan22}.
+\textcolor{red}{The former occurs in neutral superfluids at $0$ energy and has been found in the past \cite{Bogoljubov1958,Anderson58,Brieskorn74,Schmid1975,simanek1975,schoen1976propagating,Maiti2015,Sun2020,Fan22}.
 We will obtain this mode as well based on a microscopic description that excludes long-range electromagnetic interactions.
-The inclusion of this kind of interaction shifts this mode towards the plasma frequency \cite{Kulik1981}. TODO: Schön
-
-The amplitude mode ... \cite{Varma02,Cea14,Measson14,Tsuji15,Krull16,Schwarz20}
-The latter is found at the lower edge of the two-particle continuum.
+The inclusion of this kind of interaction would shift this mode towards the plasma frequency \cite{Anderson58,schoen1976propagating,Kulik1981}.}
+\textcolor{red}{The amplitude mode, on the other hand, is located at the lower edge of the quasiparticle continuum as it represents the energy required to form or break a Cooper pair \cite{Schmid1975,Varma02,Cea14,Measson14,Tsuji15,Krull16,Schwarz20}}
 
@@
 
-In our study, we employ the extended Hubbard model as it encompasses the relevant phases and thereby provides direct access to the rich excitation spectra therein.
+In our study, we employ the extended Hubbard model at half-filling as it encompasses the relevant phases and thereby provides direct access to the rich excitation spectra therein.
 Its Hamiltonian is given by
@@
 with the system's dimension $D$ and the dimensionless momentum $\vk$.
+
+\textcolor{red}{We will investigate this model for various sets of parameters allowing us access to an assortment of phases.
+Namely, the model exhibits antiferromagnetism for positive $U$ and moderately sized $V$.
+At larger $V$ the intersite repulsion takes over and favors a charge-ordered phase.
+In the $U<0$ region, the same phase occurs for any $V>0$.
+Choosing $V=0$ leads to a coexistence of $s$-wave superconductivity and said CDW \cite{yang90}, while moderately sized $V<0$ yield a purely $s$-wave superconducting phase \cite{Micnas88b}.
+In this article, we will explore the AFM-CDW as well as the CDW-SC phase transitions.}
 
@@
     The boundary for the $d_{x^2 - y^2}$-wave SC (dashed line) for the square lattice has been taken from Ref. \cite{Micnas88b}, 
-    as it is not accessible using our formalism.}
+    as it is not accessible using our formalism.
+    \textcolor{red}{The red shading shows the region in which the dynamical matrix $\mM$, see equation \eqref{eqn:heisenberg}, has negative eigenvalues, 
+    indicating that there are phases not captured by our methods.
+    In accordance with literature, we expect to find a phase-separated state \cite{Linner23}.
+    Lastly, the red shading shows the region that we cannot access because the discretization $N_\gamma$, 
+    which is required to accurately describe the system, is too large.}}
     \label{fig:phase_diagram}
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=.48\textwidth]{plots/phase_limits.pdf}
-    \caption{The lower left corner ($U<0$ and $V<0$) of the phase diagram obtained for the extended Hubbard model on 
-    (a) a square lattice and (b) a simple cubic lattice using a mean-field approximation at temperature $T=0$.
-    The blue shading indicates the region where the $s$-wave superconducting phase is the proper ground state of the system.
-    The green shading shows the region that we cannot access because the discretization $N_\gamma$, which is required to accurately describe the system, is too large.
-    Lastly, the orange shading shows the region in which the dynamical matrix $\mM$ has negative eigenvalues, indicating that there are phases not captured by our methods.}
-    \label{fig:phase_limits}
-\end{figure}
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=.48\textwidth]{plots/phase_limits.pdf}
+%    \caption{The lower left corner ($U<0$ and $V<0$) of the phase diagram obtained for the extended Hubbard model on 
+%    (a) a square lattice and (b) a simple cubic lattice using a mean-field approximation at temperature $T=0$.
+%    The blue shading indicates the region where the $s$-wave superconducting phase is the proper ground state of the system.
+%    The green shading shows the region that we cannot access because the discretization $N_\gamma$, which is required to accurately describe the system, is too large.
+%    Lastly, the orange shading shows the region in which the dynamical matrix $\mM$ has negative eigenvalues, indicating that there are phases not captured by our methods.}
+%    \label{fig:phase_limits}
+%\end{figure}
 
@@
 i.e., our self-consistency did not capture the correct ground state phase.
-This does in fact happen for certain $U<0$ and $V<0$, see the orange shading in \autoref{fig:phase_limits}.
+This does in fact happen for certain $U<0$ and $V<0$, see the orange shading in \autoref{fig:phase_diagram}.
 For finite temperatures, on a square lattice, a phase-separated state as well as the coexistence of a phase-separated state with $s$-wave superconductivity has been found in this region \cite{Linner23}.
@@
 
-In this article, we will be using the symplectic product\textcolor{red}{, also referred to as the operator pseudo scalar product,}
+In this article, we will be using the \textcolor{red}{symplectic product,}
 \begin{equation}
@@
 Operators with different indices are put into the set individually, e.g., $n_{\gamma \up}$, and $n_{\gamma \down}$ are distinct operators in our set.
-\textcolor{red}{Additionally, we will include $\tau_{k} \coloneqq c_{k \uparrow}^\dagger c_{k \downarrow}$ and its Hermitian conjugate.
+\textcolor{red}{Additionally, we will include 
+\begin{equation}
+    \tau_{k} \coloneqq c_{k \uparrow}^\dagger c_{k \downarrow}
+\end{equation}
+and its Hermitian conjugate.
 This will allow us to describe transversal magnons later on.}
@@
 If the gap $\Delta_\text{tot}$ is of the same order of magnitude as our discretization $\Delta \gamma$ our numerics become inaccurate.
-This manifests specifically whenever a spectral function has strong features at minuscule energies, e.g., the phase mode in the superconducting phase.
+This manifests specifically if a spectral function has strong features at minuscule energies, e.g., the phase mode in the superconducting phase.
 In this case, the dynamical matrix $\mM$ picks up negative eigenvalues that vanish if $N_\gamma$ is increased so that $\Delta \gamma$ is sufficiently smaller than $\Delta_\text{tot}$.
+This happens if the paremeters are chosen from the purple shaded area in \autoref{fig:phase_diagram}.
+\textcolor{red}{This issue only arises in the SC phase, nevertheless, we expect similar inaccuracies in the AFM region for small $U$.
+However, we did not perfom any computations in that region, hence this does not pose an issue to our analysis.}
 
@@
 The entries of this matrix $\mathcal{G}(z)$ are the Fourier-transformed Green's functions mentioned in \eqref{eqn:standard_gf} with respect to the operators from the initially chosen set.
-For instance, assume the operator in the set is $f_{\vk}$, then the top left element of $\mathcal{G}$ is the Green's function 
-\begin{align}
-    \mathcal{G}_{00}(z = \omega +i0^+) &=  G_{f_{\vk} f_{\vk}^\dagger} (z) \nonumber \\
-        &= -i \int_0^{\infty} \langle [f_{\vk}(t), f_{\vk}^\dagger(0)] \rangle e^{izt} \mathrm{d}t\,.
-\end{align}
+\textcolor{red}{That means, if we index each operator in our set $A_i$, the matrix element $(i,j)$ of $\mathcal{G}$ is the Green's function
+\begin{align}
+    \mathcal{G}_{ij}(z = \omega +i0^+) &=  G_{A_i A_j^\dagger} (z) \nonumber \\
+        &= -i \int_0^{\infty} \langle [A_i(t), A_j^\dagger(0)] \rangle e^{izt} \mathrm{d}t\,.
+\end{align}}
 
@@
 and some other complex-valued vector $\vec{a}$ which has its coefficients set in such a way,
-that $\vec{a} \cdot \vec{A}$ is equal to the desired operator. 
+that \textcolor{red}{$\vec{A} \cdot \vec{a}$} is equal to the desired operator. 
 For instance, $\vec{a} \equiv \vec{e}_1$ in order to represent $A_1$.
@@
 Note, that our proof for the nonnegativity is based on the system being in thermal equilibrium.
-Therefore, we conclude that beyond these values of $V$, the superconducting phase is not the true ground state of the system, see \autoref{fig:phase_limits}.
+Therefore, we conclude that beyond these values of $V$, the superconducting phase is not the true ground state of the system, see the red shading in \autoref{fig:phase_diagram}.
 Specifically, the $s$-wave superconducting phase on the square lattice seems to be even smaller than first estimated using the $d_{x^2 -y^2}$ data from \cite{Micnas88b}.

### 2024-03-04 paper/main.tex
Plakát ty vole

@@
     we find a collective mode (exciton) that does not change significantly and another mode (magnon) that moves into the two-particle continuum. 
-    In the AFM phase we identify both longitudinal and transversal magnons.}
+    In the AFM phase, we identify both longitudinal and transversal magnons.}
 \end{abstract}
@@
 The inclusion of this kind of interaction would shift this mode towards the plasma frequency \cite{Anderson58,schoen1976propagating,Kulik1981}.}
-\textcolor{red}{The amplitude mode, on the other hand, is located at the lower edge of the quasiparticle continuum as it represents the energy required to form or break a Cooper pair \cite{Schmid1975,Varma02,Cea14,Measson14,Tsuji15,Krull16,Schwarz20}}
+\textcolor{red}{The amplitude mode, on the other hand, is located at the lower edge of the quasiparticle continuum as it represents the energy required to form or break a Cooper pair \cite{Schmid1975,Varma02,Cea14,Measson14,Tsuji15,Krull16,Mueller2019,Schwarz20}}
 
@@
     \begin{aligned}
-        n_{k\sigma} &\coloneqq  c_{\vk\sigma}^\dagger c_{\vk\sigma}\,,      &f_k     &\coloneqq  c_{-\vk\down} c_{\vk\up}\,, \\
-        g_{k\sigma} &\coloneqq  c_{\vk\sigma}^\dagger c_{\vk+\vQ\sigma}\,,  &\eta_k  &\coloneqq  c_{-\vk-\vQ\down} c_{\vk\up}\,,
+        n_{k\sigma} &\coloneqq  c_{\vk\sigma}^\dagger c_{\vk\sigma}      &f_k     &\coloneqq  c_{-\vk\down} c_{\vk\up} \\
+        g_{k\sigma} &\coloneqq  c_{\vk\sigma}^\dagger c_{\vk+\vQ\sigma}  &\eta_k  &\coloneqq  c_{-\vk-\vQ\down} c_{\vk\up}
     \end{aligned}
@@
     indicating that there are phases not captured by our methods.
-    In accordance with literature, we expect to find a phase-separated state \cite{Linner23}.
+    In accordance with the literature, we expect to find a phase-separated state \cite{Linner23}.
     Lastly, the red shading shows the region that we cannot access because the discretization $N_\gamma$, 
@@
 Operators with different indices are put into the set individually, e.g., $n_{\gamma \up}$, and $n_{\gamma \down}$ are distinct operators in our set.
-\textcolor{red}{Additionally, we will include 
+\textcolor{red}{Additionally, we will include an analogous expression for
 \begin{equation}
@@
 however, this allows us to obtain good results with drastically smaller matrices compared to a momentum-based operator set and obtain results for a three-dimensional system in the first place.
-Practically, we choose $N_\gamma = 3000$ equally spaced discretization points.
+Practically, we choose $N_\gamma = 6000$ equally spaced discretization points.
 A detailed explanation of the numerics is provided in the appendix \ref{sec:numerical_ieom}.
@@
 In this case, the dynamical matrix $\mM$ picks up negative eigenvalues that vanish if $N_\gamma$ is increased so that $\Delta \gamma$ is sufficiently smaller than $\Delta_\text{tot}$.
-This happens if the paremeters are chosen from the purple shaded area in \autoref{fig:phase_diagram}.
+This happens if the parameters are chosen from the purple shaded area in \autoref{fig:phase_diagram}.
 \textcolor{red}{This issue only arises in the SC phase, nevertheless, we expect similar inaccuracies in the AFM region for small $U$.
-However, we did not perfom any computations in that region, hence this does not pose an issue to our analysis.}
+However, we did not perform any computations in that region, hence this does not pose an issue to our analysis.}
 
@@
     The shaded area marks the two-particle continuum.
-    For each plot, the parameters are set to $U=-2.5t$ and $N_\gamma = 3000$, while $V$ is varied according to the text in the individual panels.
+    For each plot, the parameters are set to $U=-2.5t$ and $N_\gamma = 6000$, while $V$ is varied according to the text in the individual panels.
     The panels show the spectral functions in the (a) SC phase and the (b and c) CDW phase, respectively.}
@@
     The shaded area marks the two-particle continuum.
-    For each plot, the parameters are set to $U=-2.5t$, $V=0$, and $N_\gamma = 3000$.
+    For each plot, the parameters are set to $U=-2.5t$, $V=0$, and $N_\gamma = 6000$.
     Since the ratio of $\Delta_\text{SC}$ to $\Delta_\text{CDW}$ may be chosen arbitrarily, we show in (a) the spectral functions for $\Delta_\text{CDW} = 0$ and in (b) for $\Delta_\text{SC} = 0$.}
@@
     The shaded area marks the two-particle continuum.
-    For each plot, the parameters are set to $V=1t$ and $N_\gamma = 3000$, while $U$ is varied according to the text in the individual panels.
+    For each plot, the parameters are set to $V=1t$ and $N_\gamma = 6000$, while $U$ is varied according to the text in the individual panels.
     The panels (a) and (c) show the spectral functions in the AFM phase, and the panels (b) and (d) in the CDW phase.}
@@
     \newline
-    The lower panels (c) and (d) present the data again, but with logarithmic scaling on the $V$-axis.
+    The lower panels (c) and (d) present the data again but with logarithmic scaling on the $V$-axis.
     Additionally, the peak positions and weights are given relative to their value at $V=0$.
@@
     $U_0$ denotes the highest value of $U$ for which there is no peak below the two-particle continuum.
-    For the square lattice it is $U_0 = 3.5775t$ and for the simple cubic lattice it is $U_0 = 4.89t$.
+    For the square lattice, it is $U_0 = 3.5775t$ and for the simple cubic lattice, it is $U_0 = 4.89t$.
     The parameter range depicted here places the system within the CDW phase.
@@
         A_\text{CDW}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} + g_{\vk \down} \right) = \int \dgamma \left( g_{\gamma \up} + g_{\gamma \down} \right) \,,\\
-        A_\text{AFM}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} - g_{\vk \down} \right) = \int \dgamma \left( g_{\gamma \up} - g_{\gamma \down} \right) \,,
+        A_\text{l.AFM}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} - g_{\vk \down} \right) = \int \dgamma \left( g_{\gamma \up} - g_{\gamma \down} \right) \,, \\
+        A_\text{t.AFM}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( \tau_{\vk} + \tau_{\vk}^\dagger \right) = \int \dgamma \left( \tau_{\gamma \up} + \tau_{\gamma \down} \right) \,,
     \end{align}
@@
 
-We have also developed a novel method to obtain Fourier transformed Green's functions and analyzed various such functions. 
+We have also developed a novel method to obtain Fourier-transformed Green's functions and analyzed various such functions. 
 We have found collective excitations within the spectral functions $\spectral{Higgs}$, $\spectral{Phase}$, $\spectral{CDW}$, and $\spectral{AFM}$ 
@@
 
-Moreover, one can fathom to include a coupling of the electronic system to the electromagnetic field.
+Moreover, one can fathom including a coupling of the electronic system to the electromagnetic field.
 This should move the position of the phase mode close to the plasma frequency as explained by the Anderson-Higgs mechanism.

### 2024-03-04 Poster DPG/poster.tex
Plakát ty vole

\documentclass [portrait,a0, 25pt]{a0poster}

\usepackage{theoposter_tudo}	% Do explicitly use the local version of theoposter.sty
\usepackage{xspace}
\usepackage{fontawesome}	% icons

% MRW Packages
\usepackage{multicol}
\usepackage{bm}
\usepackage{braket}
\usepackage{dsfont}
\usepackage{siunitx}
\usepackage{nicefrac}

\usepackage[mode=buildnew]{standalone}% requires -shell-escape

%MRW commands
\newcommand{\vect}[1]{\ensuremath{  \bm{#1}  } }
\newcommand{\Vint}[2]{\ensuremath{\mathcal{V}^{#1}_{\scriptscriptstyle #2}}}
\newcommand{\Veff}[2]{\ensuremath{\tilde{\mathcal{V}}^{#1}_{\scriptscriptstyle #2}}}

\newcommand{\im}{\mathrm{i}}

\newcommand{\highlightNat}[1]{\textbf{\textcolor{tugreen}{#1}}}
\newcommand{\highlightDarkNat}[1]{\textbf{\textcolor{tudarkgreen}{#1}}}

\newcommand{\highlightOne}[1]{\highlightNat{#1}}

\newcommand{\ddt}{\frac{\mathrm{d}}{\mathrm{d}t}}
\newcommand{\dgamma}{\mathrm{d}\gamma}

\newcommand{\mM}{\mathcal{M}}
\newcommand{\mN}{\mathcal{N}}

\newcommand{\greens}[1]{\mathcal{G}_\text{#1} (\omega)}
\newcommand{\spectral}[1]{\mathcal{A}_\text{#1}  (\omega)}

% For more tikz
\usetikzlibrary{arrows.meta}

\begin{document}%
\fontsize{22}{22} % 10pt is the standard size

\begin{tikzpicture}[overlay, inner sep=0pt, outer sep=0pt]
	\posterhead%
		{ % title
        Collective excitations in competing phases \\ in two and three dimensions
        }
		{ % authors % set a normal space after an abbreviation, instead of an inter-sentence space
            \underline{Joshua Alt\"user}\textsuperscript{1},
            Götz S.\ Uhrig\textsuperscript{1},
        }	% underline the name of the presenting author
		{ % affiliations
            \textsuperscript{1}Condensed Matter Theory, Technische Universität Dortmund, Otto-Hahn-Str.\ 4, 44227 Dortmund, Germany\\
		}
\newcommand*\TikZ{Ti\textit{k}Z\xspace}

\posterbox{2cm}{26cm}{38cm}{Introduction}
{%
\begin{itemize}
    \item Study of collective behavior of many particles rather than individual ones
    \item Complex interplay of various degrees of freedom
    \item Governs many structural, magnetic, and electronic phenomena
\end{itemize}

\highlightOne{ Investigated phases } \\
\begin{itemize}
    \item $s$-wave superconductivity (SC), Charge-density wave (CDW), and antiferromagnetism (AFM) (nesting vector $\vec{Q} = (\pi, \ldots)$)
\end{itemize}

\begin{minipage}{0.64\textwidth}
    \highlightOne{ Investigated excitations } \\
    \begin{itemize}
        \item (CDW) Exciton: $1/N \sum_{k} \left( g_{\vec{k}\uparrow} + g_{\vec{k}\downarrow} \right),\qquad g_{\vec{k}\sigma}$
        \item (AFM) Longitudinal magnon: $1/N \sum_{k} \left( g_{\vec{k}\uparrow} - g_{\vec{k}\downarrow} \right)$
        \item (AFM) Transversal magnon: $1/N \sum_{k} \left( \tau_{\vec{k}} + \tau_{\vec{k}}^\dagger \right)$
        \item (SC) Amplitude (Higgs) mode: $1/N \sum_{k} \left( f_{\vec{k}} + f_{\vec{k}}^\dagger \right)$
        \item (SC) Phase (Anderson-Bogoliubov) mode: $\im /N \sum_{k} \left( f_{\vec{k}} - f_{\vec{k}}^\dagger \right) $
    \end{itemize}
\end{minipage}
\hfill
\begin{minipage}{0.35\textwidth}
\highlightOne{ Abbreviations }
\begin{equation*}
    \label{eqn:operators}
    \begin{aligned}
        n_{k\sigma} &\coloneqq  c_{\vec{k}\sigma}^\dagger c_{\vec{k}\sigma}\,,          \\
        f_k     &\coloneqq  c_{-\vec{k}\downarrow} c_{\vec{k}\uparrow}\,, \\
        g_{k\sigma} &\coloneqq  c_{\vec{k}\sigma}^\dagger c_{\vec{k}+\vec{Q}\sigma}\,,  \\
        \tau_k  &\coloneqq  c_{\vec{k}\uparrow}^\dagger c_{\vec{k}\downarrow}\,,
    \end{aligned}
\end{equation*}
\end{minipage}
}

\posterbox{2cm}{45cm}{38cm}{Method: Iterated equations of motion (iEoM) \cite{Kalthoff17,Bleicker18}}
{%
\highlightOne{ Key ideas }
\begin{itemize}
\item Consider a time-dependent operator $\hat{a}(t) = \sum_j c_j(t) \hat{A}_j$ and the symplectic product $(\hat{A} | \hat{B}) \coloneqq \langle [\hat{A}^\dagger, \hat{B}] \rangle$
\item Write the Heisenberg EoM as matrix-vector EoM
\begin{equation*}
    \label{eqn:heisenberg}
    \begin{aligned}
        \ddt \hat{a}(t) = \sum_j \ddt c_j(t) \hat{A}_j &= i \sum_j c_j(t) [H, \hat{A}_j] \\
        \Rightarrow \sum_j \underbrace{(\hat{A}_i | \hat{A}_j)}_{\coloneqq \mN_{ij}} \ddt c_j(t) &= i \sum_j \underbrace{(\hat{A}_i | [\hat{H}, \hat{A}_j])}_{\coloneqq \mM_{ij}} c_j(t) \\
        \Rightarrow \mN \ddt \vec{c}(t) &= i \mM \vec{c}(t)\,.
    \end{aligned}
\end{equation*}
\item Generalized eigenvalue problem $\omega \mN \vec{v} = \mM \vec{v}$, real solutions if either $\mM$ or $\mN$ is nonnegative.
\begin{itemize}
    \item $\mM$ is nonnegative is thermal equilibrium
\end{itemize}
\end{itemize}

\highlightOne{ Green's functions }
\begin{itemize}
    \item Elements of the matrix $\greens{ } \coloneqq \mN [-(\omega + \im 0^+) \mN - \mM]^{-1} \mN$ are Fourier-transformed Green's functions
    \item Specifically
    \begin{equation*}
        \mathcal{G}_{ij}(\omega) = G_{\hat{A}_i \hat{A}_j^\dagger} (\omega) = -\im \int_0^{\infty} \langle [A_i(t), A_j^\dagger(0)] \rangle e^{\im (\omega + \im 0^+) t} \mathrm{d}t
    \end{equation*}
    \item Lengthy calculations yield a quadratic form
    \begin{equation*}
        \frac{1}{-(\omega + \im 0^+) \mN - \mM} \to \check{N}^{-1/2} \frac{1}{(\omega + \im 0^+)^2 - \check{M}} \check{N}^{-1/2}
    \end{equation*}
    \item Matrix inverse by tridiagonalization and subsequent continued fraction expansion with square-root terminator
\end{itemize}
}

\posterbox{2cm}{72.5cm}{38cm}{Model}
{%
\begin{minipage}{0.59\textwidth}
    \highlightOne{ Hamiltonian: Extended Hubbard model }
    \begin{equation*}
        \label{eqn:full_hamiltonian}
        \begin{aligned}
            H = &-t \sum_{\langle i, j \rangle, \sigma} \left( c_{i\sigma}^\dagger c_{j\sigma} + \text{h.c.} \right) 
            + \mu \sum_{i,\sigma} n_{i\sigma} \\
            &+ U \sum_{i} n_{i\uparrow} n_{i\downarrow} 
            + \frac{V}{2} \sum_{\langle i, j\rangle, \sigma} n_{i\sigma} n_{j\sigma}\,,
        \end{aligned}
    \end{equation*}
    \begin{itemize}
        \item Half-filling, on both a square and a simple cubic lattice, temperature $T=0$
    \end{itemize}
    \highlightOne{ Static mean-field theory }
    \begin{itemize}
        \item Used to deal with the interaction terms and to obtain expectation values for iEoM
        \item Terms depend on $\hat{\gamma}(\vec{k}) \coloneqq \frac{1}{D} \sum_{\alpha=1}^D \cos(k_\alpha)$ \\
        $\Rightarrow$ DOS based description $\rho \coloneqq \frac{1}{N} \sum_{\vec{k}} \delta(\gamma - \hat{\gamma}(\vec{k}))$
        \begin{align*}
            \Delta_\text{CDW} &= \left(\frac{U}{2N} - \frac{zV}{N}\right) \sum_{\sigma} \int \langle g_{\sigma} (\gamma) \rangle \dgamma\\\ 
            \Delta_\text{SC} &= \frac{U}{N} \int \langle f(\gamma) \rangle \dgamma\\
            \Delta_\text{AFM} &= \frac{U}{2N} \int \left( \langle g_{\uparrow} (\gamma) \rangle - \langle g_{\downarrow} (\gamma) \rangle \right) \dgamma\\ 
            \Delta_n &= \frac{V}{N} \sum_{\sigma} \int \gamma \langle n_{\sigma} (\gamma) \rangle \dgamma
        \end{align*}
        \item Allows us to tackle both 2D and 3D systems
    \end{itemize}
\end{minipage}
\hfill
\begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{plots/phase_diagram.pdf}
    \center{\textcolor{tudarkgreen}{Mean-field phase diagram of the extended Hubbard model. 
    (a) Square lattice (b) simple cubic lattice. $d_{x^2-y^2}$ from Ref. \cite{Micnas88b}.}}
\end{minipage}
\highlightOne{ Phase diagram }
\begin{itemize}
    \item Mostly the same for both lattices, $d_{x^2 -y^2}$-wave SC for $V<0$ on the square lattice is inaccessible to us
    \item Red region: Mean-field self-consistency converges to $s$-wave SC, but $\mM$ is not nonnegative $\Rightarrow$ not the true groundstate.
    Literature suggests a phase-separated state. \cite{Linner23}
    \item Purple region: Inaccuracies due to finite discretization dominate; here the gap is of the same order of magnitude as our gap
\end{itemize}
}

\posterbox{42cm}{26cm}{38cm}{Spectral functions}
{%
\highlightOne{Close to SC-CDW phase transition} \\
\begin{minipage}{0.65\textwidth}
    \includegraphics[width=\textwidth]{plots/resolvent_overview_SC_CDW.pdf} % NV sketch
\end{minipage}
\hfill
\begin{minipage}{0.34\textwidth}
    \begin{itemize}
        \item SC phase:
        \begin{itemize}
            \item Peak at $0$: Anderson-Bogoliubov mode, $\propto \delta'(\omega)$
            \item Singularity at $2\Delta$: Higgs mode, \\$\propto 1/\sqrt{\omega - 2\Delta}$
            \item CDW spectral function has a peak below the two-particle continuum
        \end{itemize}
        \item CDW phase:
        \begin{itemize}
            \item Phase and amplitude SC spectral functions are identical
            \item Both have a peak below the two-particle continuum
            \item For moderate $V$: singularity in the CDW spectral function, \\$\propto 1/\sqrt{\omega - 2\Delta}$
            \item For larger $V$: peak below the continuum
        \end{itemize}
    \end{itemize}
\end{minipage}

\highlightOne{CDW-SC coexistence at $V=0$} \\
\begin{minipage}{0.65\textwidth}
    \includegraphics[width=\textwidth]{plots/resolvent_overview_V0.pdf} % NV sketch
\end{minipage}
\hfill
\begin{minipage}{0.34\textwidth}
    \begin{itemize}
        \item The ratio $\Delta_\text{CDW} / \Delta_\text{SC}$ may be chosen arbitrarily as long as $\Delta_\text{tot} \coloneqq \sqrt{\Delta_\text{CDW}^2 + \Delta_\text{SC}^2} = \text{const}$
        \item Anderson-Bogoliubov mode always exits
        \item For $\Delta_\text{CDW} = 0$, the Higgs mode exists at $\omega = 2\Delta_\text{tot}$, while the CDW spectral function has a peak at $\omega=0$
        \item The reverse applies for $\Delta_\text{SC} = 0$
        \item $\Delta_\text{CDW} = \Delta_\text{SC}$ yields a mixture of the two
    \end{itemize}
\end{minipage}

\highlightOne{Close to AFM-CDW phase transition} \\
\begin{minipage}{0.65\textwidth}
    \includegraphics[width=\textwidth]{plots/resolvent_overview_AFM_CDW.pdf} % NV sketch
    \center{\textcolor{tudarkgreen}{Spectral functions for various collective excitations.}}
\end{minipage}
\hfill
\begin{minipage}{0.34\textwidth}
    \begin{itemize}
        \item AFM phase: Transversal AFM spectral function has a peak at $0$
        \item Longitudinal AFM spectral function behaves just like the CDW spectral function
        \item Close to the phase transition: Both have a peak below the continuum
        \item Further away: Only the spectral function corresponding to the phase has a peak below the continuum
    \end{itemize}
\end{minipage}
}

\posterbox{42cm}{78cm}{38cm}{Behavior of the peaks}
{%
\begin{minipage}{0.49\textwidth}
    \includegraphics[width=\textwidth]{plots/sc_peak_in_cdw.pdf} % NV sketch
    \center{\textcolor{tudarkgreen}{Weight and position of the peak in the SC spectral functions in the CDW phase.}}
\end{minipage}
\hfill
\begin{minipage}{0.49\textwidth}
    \includegraphics[width=\textwidth]{plots/cdw_peak_in_sc.pdf} % NV sketch
    \center{\textcolor{tudarkgreen}{Weight and position of the peak in the CDW spectral functions in the SC phase.}}
\end{minipage}
\begin{itemize}
    \item Double-logarithmic plots
    \item The weights diverge as $1/\sqrt{|V|}$ while the peak positions move to $0$ as $\sqrt{|V|}$
    \item For $V\gg t$, the weights become constant. The position grows linearly and the position in units of the gap becomes constant.
\end{itemize}

\begin{minipage}{0.49\textwidth}
    \includegraphics[width=\textwidth]{plots/afm_cdw_peaks_overview.pdf} % NV sketch
    \center{\textcolor{tudarkgreen}{Weight and position of the peak in the AFM and CDW spectral functions close to the phase transition.}}
\end{minipage}
\hfill
\begin{minipage}{0.49\textwidth}
    \begin{itemize}
        \item Orange region: System is in the CDW phase, blue region: System is in the AFM phase
        \item Peak position grows linearly with $U$ as the system moves away from the phase transition
        \item But it moves into the continuum (b) quadratically
        \item At the same time, the weights also vanish
    \end{itemize}
\end{minipage}

}

\posterbox{2cm}{106cm}{38cm}{Possible outlook}
{%
\begin{itemize}
\item Incorporating phase-separated states into the mean-field theory, thereby providing deeper analysis of the negative $V$ regime of phase diagrams and collective excitations
\item Coupling the electronic system to the electromagnetic field to include the Anderson-Higgs mechanism for superconductors
\item Describing multi-band systems with even richer phases and collective excitations
\end{itemize}
}

\posterbox{42cm}{110cm}{38cm}{References}
{%
\begingroup
\renewcommand{\section}[2]{}	% for removing the bibliography title
\begin{thebibliography}{99}
    %\begin{multicols}{2}
    \bibitem{Kalthoff17} M. Kalthoff, F. Keim, H. Krull, and G. S. Uhrig, The European Physical Journal B 90, 97 (2017).
    \bibitem{Bleicker18} P. Bleicker and G. S. Uhrig, Phys. Rev. A 98, 033602 (2018).
    \bibitem{Micnas88b} R. Micnas, J. Ranninger, S. Robaszkiewicz, and S. Tabor, Phys. Rev. B 37, 9410 (1988).
    \bibitem{Linner23} E. Linnér, C. Dutreix, S. Biermann, and E. A. Stepanov, Phys. Rev. B 108, 205156 (2023).
    %\end{multicols}          
\end{thebibliography}
\endgroup
}

% Do not remove this, for the sake of archeology!
\node [anchor=north] at ($(\paperwidth-1cm,.9cm-\paperheight)$) {\tiny \the\year};
\end{tikzpicture}

\end{document}

### 2024-03-04 paper/resolvent_overview_SC_CDW.py

@@ -24,15 +24,15 @@ plotters = np.empty((nrows, ncols), dtype=ps.CURVEFAMILY)
 for i in range(nrows):
     for j in range(ncols):
         axs[i][j].set_ylim(0, .99)
-        plotters[i][j] = ps.CURVEFAMILY(4, axis=axs[i][j])
-        plotters[i][j].set_individual_colors("nice")
-        plotters[i][j].set_individual_dashes([ [1,0], [3,6,3,0], [1.5, 2], [3,5,1.5,5,3,0] ])
+        plotters[i][j] = ps.CURVEFAMILY(5, axis=axs[i][j])
+        plotters[i][j].set_individual_colors("GPT")
+        plotters[i][j].set_individual_dashes([ [1,0], [1.5,1.5], [3, 1.5], [5,2,1,2], [7,3,2,2,3,2] ])
+
+name_suffices = ["phase_SC", "higgs_SC", "CDW", "AFM", "higgs_AFM_trans"]
+labels = ["Phase", "Higgs", "CDW", "l.AFM", "t.AFM"]
 
 plot_lower_lim = -0.05
 plot_upper_lim = 4.25
-
-name_suffices = ["phase_SC", "higgs_SC", "CDW", "AFM"]
-labels = ["Phase", "Higgs", "CDW", "AFM"]
 
 for j, folder in enumerate(folders):
     usage_upper_lim = 2 * plot_upper_lim if j == 0 else 3 * plot_upper_lim
@@ -47,22 +47,22 @@ for j, folder in enumerate(folders):
         axs[i][j].set_xlim(plot_lower_lim, usage_upper_lim)
         if i == 2:
             cont = np.sqrt(resolvents[0].roots[0])
-            zommed_xlim = (cont - 0.08, cont + 0.03) 
-            axins = create_zoom(axs[i][j], 0.1, 0.29, 0.275, 0.66, zommed_xlim, ylim=(0, 0.55), 
+            zoomed_xlim = (cont - 0.08, cont + 0.03) 
+            axins = create_zoom(axs[i][j], 0.1, 0.29, 0.275, 0.66, zoomed_xlim, ylim=(0, 0.55), 
                                 y_funcs=[lambda x, res=res: res.spectral_density(x + 1e-5j) for res in resolvents],
[…]

### 2024-03-04 Poster DPG/poster.tex
a
x

u

Paper stuff

data

stuff

tex

stuff

@@
 \usepackage[mode=buildnew]{standalone}% requires -shell-escape
-
-%MRW commands
-\newcommand{\vect}[1]{\ensuremath{  \bm{#1}  } }
-\newcommand{\Vint}[2]{\ensuremath{\mathcal{V}^{#1}_{\scriptscriptstyle #2}}}
-\newcommand{\Veff}[2]{\ensuremath{\tilde{\mathcal{V}}^{#1}_{\scriptscriptstyle #2}}}
 
@@
 
-\posterbox{2cm}{45cm}{38cm}{Method: Iterated equations of motion (iEoM) \cite{Kalthoff17,Bleicker18}}
+\posterbox{2cm}{46cm}{38cm}{Method: Iterated equations of motion (iEoM) \cite{Kalthoff17,Bleicker18}}
 {%
@@
 
-\posterbox{2cm}{72.5cm}{38cm}{Model}
+\posterbox{2cm}{74.8cm}{38cm}{Model}
 {%
@@
         \end{align*}
+        \item The iEoM utilize the same description
         \item Allows us to tackle both 2D and 3D systems
@@
 \end{minipage}
+
 \highlightOne{ Phase diagram }
@@
 \begin{itemize}
-    \item Double-logarithmic plots
+    \item Double-logarithmic plots $\Rightarrow y(V) = e^d |V|^c$
     \item The weights diverge as $1/\sqrt{|V|}$ while the peak positions move to $0$ as $\sqrt{|V|}$
@@
 
-\begin{minipage}{0.49\textwidth}
+\begin{minipage}{0.55\textwidth}
     \includegraphics[width=\textwidth]{plots/afm_cdw_peaks_overview.pdf} % NV sketch
@@
 \hfill
-\begin{minipage}{0.49\textwidth}
+\begin{minipage}{0.44\textwidth}
     \begin{itemize}
@@
 
-\posterbox{2cm}{106cm}{38cm}{Possible outlook}
+\posterbox{2cm}{110.35cm}{38cm}{Possible outlook}
 {%
 \begin{itemize}
-\item Incorporating phase-separated states into the mean-field theory, thereby providing deeper analysis of the negative $V$ regime of phase diagrams and collective excitations
+\item Incorporating phase-separated states into the mean-field theory
+\begin{itemize}
+    \item thereby providing deeper analysis of the negative $V$ regime of phase diagrams and collective excitations
+\end{itemize}
 \item Coupling the electronic system to the electromagnetic field to include the Anderson-Higgs mechanism for superconductors
@@
 
-\posterbox{42cm}{110cm}{38cm}{References}
+\posterbox{42cm}{111cm}{38cm}{References}
 {%

### 2024-03-04 paper/main.tex
a
x

u

Paper stuff

data

stuff

tex

stuff

@@
 \newcommand{\kminusQ}{-\vk-\vQ}
+\newcommand{\im}{\mathrm{i}}
 
@@
 \begin{equation}
+    \label{eqn:time_dependent_operator}
     a(t) = \sum_j c_j(t) A_j\,,
@@
     \begin{aligned}
-        \ddt a(t) = \sum_j \ddt c_j(t) A_j &= i \sum_j c_j(t) [H, A_j] \\
-        \Rightarrow \sum_j \underbrace{(A_i | A_j)}_{\coloneqq \mN_{ij}} \ddt c_j(t) &= i \sum_j \underbrace{(A_i | [H, A_j])}_{\coloneqq \mM_{ij}} c_j(t) \\
-        \Rightarrow \mN \ddt \vec{c}(t) &= i \mM \vec{c}(t)\,.
+        \ddt a(t) = \sum_j \ddt c_j(t) A_j &= \im \sum_j c_j(t) [H, A_j] \\
+        \Rightarrow \sum_j \underbrace{(A_i | A_j)}_{\coloneqq \mN_{ij}} \ddt c_j(t) &= \im \sum_j \underbrace{(A_i | [H, A_j])}_{\coloneqq \mM_{ij}} c_j(t) \\
+        \Rightarrow \mN \ddt \vec{c}(t) &= \im \mM \vec{c}(t)\,.
     \end{aligned}
@@
 \begin{equation}
-    G_{AB}^\text{ret} (t) = - i \langle [A(t), B] \rangle \Theta(t)\,,
+    G_{AB}^\text{ret} (t) = - \im \langle [A(t), B] \rangle \Theta(t)\,,
 \end{equation}
@@
     \label{eqn:standard_gf}
-    G_{AB}(z = \omega + i0^+) = -i \int_0^{\infty} e^{izt} \langle [A(t), B] \rangle \mathrm{d}t\,,
+    G_{AB}(z = \omega + \im 0^+) = -\im \int_0^{\infty} e^{\im z t} \langle [A(t), B] \rangle \mathrm{d}t\,,
 \end{equation}
@@
     \label{eqn:green_function}
-    \mathcal{G}(z &= \omega + i0^+) = \mN \frac{1}{-z \mN - \mM} \mN \\
+    \mathcal{G}(z &= \omega + \im 0^+) = \mN \frac{1}{-z \mN - \mM} \mN \\
         &\coloneqq  -\mN \mathcal{R}(z) \mN\,,
@@
 The entries of this matrix $\mathcal{G}(z)$ are the Fourier-transformed Green's functions mentioned in \eqref{eqn:standard_gf} with respect to the operators from the initially chosen set.
-\textcolor{red}{That means, if we index each operator in our set $A_i$, the matrix element $(i,j)$ of $\mathcal{G}$ is the Green's function
-\begin{align}
-    \mathcal{G}_{ij}(z = \omega +i0^+) &=  G_{A_i A_j^\dagger} (z) \nonumber \\
-        &= -i \int_0^{\infty} \langle [A_i(t), A_j^\dagger(0)] \rangle e^{izt} \mathrm{d}t\,.
+\textcolor{red}{That means, if we index each operator in our set $A_i$, the matrix element $(j,i)$ of $\mathcal{G}$ is the Green's function
+\begin{align}
+    \mathcal{G}_{ji}(z = \omega +\im 0^+) &=  G_{A_j A_i^\dagger} (z) \nonumber \\
+        &= -\im \int_0^{\infty} \langle [A_j(t), A_i^\dagger(0)] \rangle e^{\im z t} \mathrm{d}t\,.
 \end{align}}
@@
 In the following, we will derive this relation.
-For that, consider the Fourier-transformed Green's function \eqref{eqn:standard_gf} with respect to two operators $A$ and $B^\dagger$ that are included in our operator set
-\begin{align}
-    G_{AB^\dagger} (z) &= - i \int_0^\infty \exp(i z t) \langle [ A(t), B^\dagger(0) ] \rangle \mathrm{d}t
-\end{align}
-Since $A$ and $B$ are included in the operator set, we can rewrite them as dot products of the vector
-\begin{equation}
-    \vec{A} \coloneqq  \left( A_1, A_2, \dots, A_N \right)\,, \quad
-    \vec{A}^\dagger \coloneqq  \begin{pmatrix}
-        A_1^\dagger \\ A_2^\dagger \\ \vdots \\ A_N^\dagger
-    \end{pmatrix}\,,
-\end{equation}
-and some other complex-valued vector $\vec{a}$ which has its coefficients set in such a way,
-that \textcolor{red}{$\vec{A} \cdot \vec{a}$} is equal to the desired operator. 
-For instance, $\vec{a} \equiv \vec{e}_1$ in order to represent $A_1$.
-
+\textcolor{red}{For that, consider the Fourier-transformed Green's function above.
+We rewrite both operators in the same manner as in \eqref{eqn:time_dependent_operator} to obtain
+\begin{align}
+    G_{AB^\dagger} (z) &= \im \int_0^\infty e^{\im z t} \langle [ A_i^\dagger(0), A_j(t) ] \rangle \mathrm{d}t \nonumber \\
+        &= \im \int_0^\infty e^{\im z t} \langle [ \sum_m a_{j,m}^*(0) A_m^\dagger, \sum_n a_{i,n}(t) A_n ] \rangle \mathrm{d}t \nonumber \\
+        &= \im \int_0^\infty \sum_{mn} e^{\im z t} a_{j,m}^*(0) \underbrace{\langle [ A_m^\dagger, A_n ] \rangle}_{\equiv \mN_{mn}} a_{i,n}(t) \mathrm{d}t \nonumber \\
+        &= \im \int_0^\infty e^{\im z t} \vec{a}_{j}^\dagger (0) \mN \vec{a}_{i}(t) \mathrm{d}t\,.
+\end{align}
 Furthermore, assuming, that $\mN$ is invertible, we can easily solve the differential equation \eqref{eqn:heisenberg} to obtain
 \begin{equation}
-    \vec{c}(t) = \exp \left( i \mN^{-1} \mM t \right) \vec{c}(0)\,.
+    \vec{a}_{i}(t) = \exp \left( \im \mN^{-1} \mM t \right) \vec{a}_{i}(0)\,.
 \end{equation}
@@
     \label{eqn:green_derivation}
-    G_{AB^\dagger} (z) &= i \int_0^\infty \exp(izt) \langle [ (\vec{A \cdot} \vec{b}(0))^\dagger, \vec{A} \cdot \vec{a}(t) ] \rangle\ \mathrm{d}t \nonumber \\
-        &= i \int_0^\infty \exp(izt) \vec{b}^\dagger(0) \underbrace{\langle [ \vec{A}^\dagger, \vec{A} ] \rangle}_{\equiv \mN} \vec{a}(t) \mathrm{d}t \nonumber \\
-        &= i  \int_0^\infty \vec{b}^\dagger(0) \mN \exp \left( i \left(\mN^{-1} \mM + z \right) t \right) \vec{a}(0) \mathrm{d}t  \nonumber \\
-        &= - \vec{b}^\dagger(0) \left[ \mN \frac{1}{\mN^{-1} \mM + z} \right] \vec{a}(0) \nonumber \\
-        &= - \vec{b}^\dagger(0) \left[ \mN \frac{1}{ \underbrace{\mM + z \mN}}_{\equiv \mathcal{R}(z)} \mN \right] \vec{a}(0)\,,
-\end{align}
-where $\vec{a}(0)$ and $\vec{b}(0)$ are chosen such, that their product with $\vec{A}$ yields $A(0)$ and $B(0)$, respectively.
-The task at hand is finding the resolvent as $\mathcal{R}$.
-
-To do that, we embrace this matrix structure in \eqref{eqn:xp_set} and assume that all matrix entries are real.
+    G_{AB^\dagger} (z) &= \im  \int_0^\infty \vec{a}_{j}^\dagger (0) \mN \exp \left( \im \left(\mN^{-1} \mM + z \right) t \right) \vec{a}_{i}(0) \mathrm{d}t  \nonumber \\
+        &= - \vec{a}_{j}^\dagger (0) \left[ \mN \frac{1}{\mN^{-1} \mM + z} \right] \vec{a}_{i}(0) \nonumber \\
+        &= - \vec{a}_{j}^\dagger (0) \left[ \mN \frac{1}{ \underbrace{\mM + z \mN}}_{\equiv \mathcal{R}(z)} \mN \right] \vec{a}_{i}(0)\,,
+\end{align}
+where $\vec{a}_i(0)$ and $\vec{a}_j^\dagger (0)$ need to be chosen such, that $A_i = \sum_n a_{i,n} A_n$ and $A_j^\dagger = \sum_n a_{j,n}^* A_n^\dagger$ hold.
+The task at hand is finding the resolvent as $\mathcal{R}$.}
+
+To do that, we embrace this matrix structure in \eqref{eqn:xp_set} and assume that all matrix entries are real \textcolor{red}{so that $\kappa_ij = \Lambda_{\pm,ij} = 0$ holds}.
 Then, with $\mathcal{R}|_X$ denoting the block of a matrix $\mathcal{R}$ corresponding to the $X$-operators, we can calculate
@@
 \begin{equation}
+    \label{eqn:rx}
     r_X (z) = -\check{N}^{-1/2} \frac{1}{z^2 - \check{N}^{-1/2} \mathcal{K}_+ \check{N}^{-1/2}} \check{N}^{-1/2}\,.
@@
 The matrix $\check{M} \coloneqq \check{N}^{-1/2} \mathcal{K}_+ \check{N}^{-1/2}$ is positive semidefinite and Hermitian by the previous arguments.
-If $\check{N}$ has a singular part, the inverse can be replaced by the pseudo-inverse.
+If $\check{N}$ has a singular part, the inverse can be replaced by the Moore-Penrose pseudo-inverse.
+\textcolor{red}{A possible way to compute this is to diagonalize $\check{N} = \mathcal{V} \mathcal{D} \mathcal{V}^\dagger$, with a diagonal matrix $\mathcal{D}$ and a unitary transformation matrix $\mathcal{V}$.
+Now, the pseudo-inverse can be defined as
+\begin{equation}
+    \check{N}^+ \coloneqq \mathcal{V} \mathcal{D}^+ \mathcal{V}^\dagger
+\end{equation}
+with
+\begin{equation}
+    (\mathcal{D}^+)_{ij} = \begin{cases}
+        1/\mathcal{D}_{ij} & \mathcal{D}_{ij} \neq 0 \\ 0 & \text{otherwise}
+    \end{cases}\,.
+\end{equation}
+Note, that this definition yields the standard inverse for invertible matrices.}
+
 The same calculation can be repeated by exchanging $X$ with $P$, yielding the relation for the remaining block.
@@
         G_{AB^\dagger} \vert_P (z) &= - \left[ \vec{b}^\dagger (0) \right]_P \mathcal{L}^\dagger r_X (z) \mathcal{L} \left[ \vec{a}(0) \right]_P\,, \\
-        G_{AB^\dagger} \vert_X (z) &= - \left[ \vec{b}^\dagger (0) \right]_X \mathcal{L} r_P (z) \mathcal{L}^\dagger \left[ \vec{a}(0) \right]_X\,.
+        G_{AB^\dagger} \vert_X (z) &= - \left[ \vec{b}^\dagger (0) \right]_X \mathcal{L} r_P (z) \mathcal{L}^\dagger \left[ \vec{a}(0) \right]_X\,,
     \end{align}
 \end{subequations}
+\textcolor{red}{where $r_X (z)$ is given in \eqref{eqn:rx} and 
+\begin{equation}
+    r_P (z) = -\check{N}_P^{-1/2} \frac{1}{z^2 - \check{M}_P} \check{N}_P^{-1/2}\,.
+\end{equation}}
+
+Now, the task at hand is finding the inverse $1/(z^2 - \check{M})$ for all $z$.
+This can be achieved using a Lanczos tridiagonalization and subsequently, a continued fraction expansion in terms of the Lanczos coefficients $a_i$ and $b_i$ \cite{PettiforRecursion,ViswanathRecursion}.
+In the single-band case, the coefficients approach the limit
+\begin{equation}
+    \label{eqn:inf_lanczos}
+    a_\infty = \frac{\omega_+ + \omega_-}{2}\text{  and  } b_\infty = \frac{\omega_+ - \omega_-}{4}\,,
+\end{equation}
+where $\omega_\pm$ represents the upper and lower band edge, respectively \cite{PettiforRecursion}.
+This behavior allows us to terminate the continued fraction, once the coefficients have converged close enough to these values, using the so-called square root terminator
+\begin{equation}
+    T(\omega) = \frac{1}{2b_\infty^2} \left( \omega - a_\infty \mp \sqrt{(\omega - a_\infty)^2 - 4 b_\infty^2} \right)\,,
+\end{equation}
+where the negative sign is to be chosen for $\omega - a_\infty > 2b_\infty$ and $|\omega - a_\infty| < 2b_\infty$ and the positive one otherwise.
+It is to be noted, that the coefficients start to drop off from this limit as more and more Lanczos iterations are performed \cite{ViswanathRecursion}.
+Therefore, we terminate the continued fraction with the aforementioned terminator at the coefficient pair that has the least deviation from $a_\infty$ and $b_\infty$.
 
@@
     \includegraphics[width=.98\textwidth]{plots/resolvent_overview_SC_CDW.pdf}
-    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
+    \caption{Spectral functions with respect to the operators listed in Eq.~\eqref{eqn:resolvent_bases}.
     The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
@@
     The shaded area marks the two-particle continuum.
-    For each plot, the parameters are set to $U=-2.5t$ and $N_\gamma = 6000$, while $V$ is varied according to the text in the individual panels.
+    For each plot, the parameters are set to $U=-2.5t$ and $N_\gamma = 6000$, while $V$ is varied, see the legend.
     The panels show the spectral functions in the (a) SC phase and the (b and c) CDW phase, respectively.}
@@
     \includegraphics[width=.98\textwidth]{plots/resolvent_overview_V0.pdf}
-    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
-    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
-    The left edge of each plot is at $-0.05$ rather than $0$ in order to improve the visibility of the peaks at $\omega=0$.
-    The shaded area marks the two-particle continuum.
-    For each plot, the parameters are set to $U=-2.5t$, $V=0$, and $N_\gamma = 6000$.
+    \caption{\textcolor{red}{Same as \autoref{fig:resolvent_overview_SC}, except that we set $V=0$, i.e, SC and CDW order coexist.}
     Since the ratio of $\Delta_\text{SC}$ to $\Delta_\text{CDW}$ may be chosen arbitrarily, we show in (a) the spectral functions for $\Delta_\text{CDW} = 0$ and in (b) for $\Delta_\text{SC} = 0$.}
@@
     \includegraphics[width=.98\textwidth]{plots/resolvent_overview_AFM_CDW.pdf}
-    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
-    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
-    The shaded area marks the two-particle continuum.
-    For each plot, the parameters are set to $V=1t$ and $N_\gamma = 6000$, while $U$ is varied according to the text in the individual panels.
+    \caption{\textcolor{red}{Same as \autoref{fig:resolvent_overview_SC}, except that we are now looking at the system near the AFM-CDW phase transition.
+    For the square lattice, we set $V=1.2t$ and for the simple cubic lattice, we set $V=0.8t$. This choice yields the phase boundary at $U=4.8t$ for both lattices.}
     The panels (a) and (c) show the spectral functions in the AFM phase, and the panels (b) and (d) in the CDW phase.}
@@
     \includegraphics[width=.98\textwidth]{plots/sc_peak_in_cdw.pdf}
-    \caption{The upper panels (a) show double logarithmic plots of the positions $\omega_0$ of the peak in $\spectral{SC}$ in the CDW phase while the lower panels (b) show their respective weights $W_0 = e^{b}$.
+    \caption{The upper panels (a) show double logarithmic plots of the positions $\omega_0$ of the peak in $\spectral{SC}$ in the CDW phase while the lower panels (b) show their respective weights $W_0$.
     In the upper panels, the pink markers additionally show the peak position divided by the gap $\omega_0 / \Delta_\text{CDW}$.
     The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
-    The fits are linear, i.e., $y(V) = c \ln(V/t) + d$, and the parameters are printed on the individual panels.}
+    \textcolor{red}{The fits are linear, i.e., $y(V) = e^d V^c$, and the parameters are printed on the individual panels.}}
     \label{fig:sc_in_cdw_behavior}
@@
     \includegraphics[width=.98\textwidth]{plots/cdw_peak_in_sc.pdf}
-    \caption{The panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ in the SC phase.
-    Below that, in panels (b), their respective weights are depicted.
-    The dashed lines in both rows show the position or weight computed for $V=0$ with $\Delta_\text{CDW} = 0$.
-    The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
-    The left-most values are $V=-0.28t$ for the square lattice and $V=-0.34t$ for the simple cubic lattice.
-    Choosing even smaller values results in $\mathcal{M}$ no longer being positive, i.e., the system is not in thermal equilibrium.
-    \newline
-    The lower panels (c) and (d) present the data again but with logarithmic scaling on the $V$-axis.
-    Additionally, the peak positions and weights are given relative to their value at $V=0$.
-    These data are fitted by $y(x) = a (\tanh (bx - c) + 1)$ with the parameters printed in the individual panel.
-    The panels (a) and (b) feature the same fitting result.}
+    \caption{\textcolor{red}{Same as \autoref{fig:sc_in_cdw_behavior} but for the peak in $\spectral{CDW}$ within the SC phase, i.e., $V<0$.}}
     \label{fig:cdw_in_sc_behavior}
@@
     \includegraphics[width=.98\textwidth]{plots/afm_cdw_peaks_overview.pdf}
-    \caption{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ (orange lines) and $\spectral{AFM}$ (blue lines) close to the corresponding phase transition $U = zV$.
-    The middle panels (b) depict the peak positions relative to the lower edge of the two-particle continuum $\omega_-$, while the bottom panels (c) show their respective weights.
+    \caption{\textcolor{red}{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ (orange lines) and $\spectral{l.AFM}$ (blue lines) close to the corresponding phase transition $U = 4.8t$.
+    Again, we chose $V=1.2t$ for the square lattice (left column) and $V=0.8t$ for the simple cubic lattice (right column) respectively.
+    The middle panels (b) depict the peak positions relative to the lower edge of the two-particle continuum $\omega_-$, while the bottom panels (c) show their respective weights.}
     The shadings indicate the phase the system is in. Blue represents AFM while orange represents CDW.
-    The left column shows the results for the square and the right column for the simple cubic lattice at $V=-1t$.
     Note the difference in the scales for the two lattices.}
@@
     \includegraphics[width=.98\textwidth]{plots/afm_cdw_peaks_details.pdf}
-    \caption{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{AFM}$ relative to the lower edge of the two-particle continuum $\omega_-$.
+    \caption{The upper panels (a) show double logarithmic plots of the positions $\omega_0$ of the peak in $\spectral{l.AFM}$ relative to the lower edge of the two-particle continuum $\omega_-$.
     The lower panels (b) depict their respective weights $W_0$.
-    The left column shows the results for the square and the right column for the simple cubic lattice at $V=-1t$.
+    Again, we chose $V=1.2t$ for the square lattice (left column) and $V=0.8t$ for the simple cubic lattice (right column) respectively.
     $U_0$ denotes the highest value of $U$ for which there is no peak below the two-particle continuum.
-    For the square lattice, it is $U_0 = 3.5775t$ and for the simple cubic lattice, it is $U_0 = 4.89t$.
+    For the square lattice, it is $U_0 \approx 3.372t$ and for the simple cubic lattice, it is $U_0 \approx 4.479t$.
     The parameter range depicted here places the system within the CDW phase.
-    All fits are linear, i.e., $y=ax + b$.}
+    The fits are of the same fashion as in \autoref{fig:sc_in_cdw_behavior}.}
     \label{fig:afm_cdw_peaks_details}
@@
 
-Now, the task at hand is finding the inverse $1/(z^2 - \check{M})$ for all $z$.
-This can be achieved using a Lanczos tridiagonalization and subsequently a continued fraction expansion in the form of
-
-\begin{widetext}
-\begin{equation}
-    \left( z^2 - \begin{pmatrix}
-        a_0 & b_1 & 0 & 0 & \cdots \\
-        b_1 & a_1 & b_2 & 0 & \cdots \\
-        0 & b_2 & a_2 & b_3 & \cdots \\
-        0 & 0 & b_3 & a_3 & \cdots \\
-        \vdots & \vdots & \vdots & \vdots & \ddots
-    \end{pmatrix} \right)_{00}^{-1} = \dfrac{1}{z^2 - a_0 - \dfrac{b_1^2}{z^2 - a_1 - \dfrac{b_2^2}{ z^2 - a_2 - \hdots}}}\,\,
-\end{equation}
-\end{widetext}
-
-where $a_i$ and $b_i$ are the Lanczos coefficients \cite{PettiforRecursion,ViswanathRecursion}.
-
-Obtaining a diagonal block of $\mathcal{G}$ is easily achieved by setting $\vec{b}(0) = \vec{a}(0)$.
-Obtaining an off-diagonal block requires linear combinations in the form of 
-\begin{align}
-    \vec{a}^\dagger \mathcal{G} \vec{b} &= \frac{1}{4} \Big\{ 
-        \underbrace{\left[ (\vec{a} + \vec{b})^\dagger \mathcal{G} (\vec{a} + \vec{b}) - (\vec{a} - \vec{b})^\dagger \mathcal{G} (\vec{a} - \vec{b}) \right]}_{ = 2 \vec{a}^\dagger \mathcal{G} \vec{b} + 2 \vec{b}^\dagger \mathcal{G} \vec{a}} \\
-    &-i \underbrace{\left[ (\vec{a} + i \vec{b})^\dagger \mathcal{G} (\vec{a} + i \vec{b}) - (\vec{a} - i \vec{b})^\dagger \mathcal{G} (\vec{a} - i \vec{b}) \right]}_{= 2i \vec{a}^\dagger \mathcal{G} \vec{b} - 2i \vec{b}^\dagger \mathcal{G} \vec{a}} \Big\}\,, \nonumber
-\end{align}
-i.e., one computes the four diagonal blocks and then simply adds them as described above.
-
-In the single-band case, the coefficients approach the limit
-\begin{equation}
-    \label{eqn:inf_lanczos}
-    a_\infty = \frac{\omega_+ + \omega_-}{2}\text{  and  } b_\infty = \frac{\omega_+ - \omega_-}{4}\,,
-\end{equation}
-where $\omega_\pm$ represents the upper and lower band edge, respectively \cite{PettiforRecursion}.
-This behavior allows us to terminate the continued fraction, once the coefficients have converged close enough to these values, using the so-called square root terminator
-\begin{equation}
-    T(\omega) = \frac{1}{2b_\infty^2} \left( \omega - a_\infty \mp \sqrt{(\omega - a_\infty)^2 - 4 b_\infty^2} \right)\,,
-\end{equation}
-where the negative sign is to be chosen for $\omega - a_\infty > 2b_\infty$ and $|\omega - a_\infty| < 2b_\infty$ and the positive one otherwise.
-It is to be noted, that the coefficients start to drop off from this limit as more and more Lanczos iterations are performed \cite{ViswanathRecursion}.
-Therefore, we terminate the continued fraction with the aforementioned terminator at the coefficient pair that has the least deviation from $a_\infty$ and $b_\infty$.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In this section, we will be investigating four different diagonal Green's functions $G_{AA^\dagger}(\omega + i0^+)$, namely with
+In this section, we will be investigating four different diagonal Green's functions $G_{AA^\dagger}(\omega + \im 0^+)$, namely with
 \begin{subequations}
@@
 The remaining two capture the collective behavior of the CDW and AFM states, respectively.
-In the following, we will refer to the Green's functions generated by these operators as $\mathcal{G}_{i}(\omega) = G_{A_i A_i^\dagger}(\omega)$.
+In the following, we will refer to the Green's functions generated by these operators as \textcolor{red}{$\mathcal{G}_{\alpha}(\omega) = G_{A_\alpha A_\alpha^\dagger}(\omega)$ 
+with $\alpha \in \{ \text{Higgs}, \text{Phase}, \text{CDW}, \text{l.AFM}, \text{t.AFM} \}$.}
 
 Note, that all of the aforementioned operators are Hermitian. 
-This means that all spectral functions need to be completely antisymmetrical, see appendix \ref{sec:antisymmetry_spectral}.
+This means that all spectral functions need to be completely antisymmetrical \cite{rickayzen80}.%, see appendix \ref{sec:antisymmetry_spectral}.
 For this reason, we will only show the $\omega \geq 0$ in our plots. 
@@
 
-To begin, let us describe the spectral functions $\mathcal{A}_i (\omega) = - (1/\pi) \Im [\mathcal{G}_i (\omega + i0^+)]$ with respect to the operators above in the various phases.
+To begin, let us describe the spectral functions $\mathcal{A}_\alpha (\omega) = - (1/\pi) \Im [\mathcal{G}_\alpha (\omega + \im 0^+)]$ with respect to the operators above in the various phases.
 \autoref{fig:resolvent_overview_SC} shows them at $U = -2.5t$ in the SC ($V=-0.1t$) and CDW ($V=0.1t$ and $V=0.5t$) phase.
@@
 there is a sharp peak located at $\omega=0$ in $\spectral{Phase}$ and a singularity in $\spectral{Higgs}$ located at $\omega=2\Delta_\text{SC}$.
-We identify them with the well-known Anderson-Bogoliubov and Higgs modes in superconductors.
+We identify them with the well-known Anderson-Bogoliubov and Higgs modes in superconductors \cite{Bogoljubov1958,Anderson58,Brieskorn74,Schmid1975,simanek1975,schoen1976propagating,Kulik1981,Maiti2015,Sun2020,Fan22,Schmid1975,Varma02,Cea14,Measson14,Tsuji15,Krull16,Mueller2019,Schwarz20}.
 Note, that the former must not have any weight though, because the spectral function is perfectly antisymmetrical.
@@
 
-To classify the occurring peaks that lie outside the two-particle continuum, we turn towards the real part of the Green's function.
+To characterize the occurring peaks that lie outside the two-particle continuum, we turn towards the real part of the Green's function.
 We plot it in close proximity to the peaks with a double logarithmic scale and fit the result linearly $y = ax + b$ to obtain its power-law behavior.
@@
 Previous studies on the dynamics of the order parameter found damped oscillations after a quench.
-These have the frequency $\Omega = 2 \Delta_\text{SC}$ and fall off as $1/\sqrt{t}$ \cite{Yuzbashyan06}.
+These have the frequency $\Omega = 2 \Delta_\text{SC}$ and fall off as $1/\sqrt{t}$ \cite{Volkov73,Kulik1981,Yuzbashyan06}.
 An inverse Fourier transform of $\spectral{Higgs}$ yields precisely the same behavior, thereby reinforcing the validity of our results.
@@
 In the CDW phase, see panels (b) and (c), both of $\spectral{Higgs}$ and $\spectral{Phase}$ become identical and form a $\delta$ peak below the two-particle continuum.
+\textcolor{red}{In this case, both modes describe the condensation of a Cooperon, i.e., a bound state of two electrons.}
 Following the Landau theory for continuous phase transitions, this is to be expected as the free energy is expanded in terms of the order parameter as
@@
 with $r > 0$ and $u > 0$ if the system is outside of the superconducting phase. 
-In this case, the only minimum is at $\Delta_\text{SC} = 0$. 
+In this case, the only minimum is at $\Delta_\text{SC} = 0$ \cite{Coleman2015}. 
 That means that both possible modes have to overcome the same energy to be excited at all.
@@
 In the SC phase, $\spectral{CDW}$ features a $\delta$ peak below the continuum corresponding to the finite energy necessary to excite this kind of electronic density modulation.
+\textcolor{red}{This mode corresponds to the creation of an exciton.}
 For moderate-sized values of $V>0$, i.e., in the CDW phase, see panel (b) at $V=0.1t$, the aforementioned spectral function has a singularity at $\omega=2\Delta_\text{CDW}$.% that exhibits a square-root behavior.
-This mode becomes hard and moves outside the two-particle continuum as $V$ is increased, see panel (c) at $V=0.5t$.
-
-$\spectral{AFM}$ is restricted to the continuum for both phases and both lattices.
-For the square lattice, however, there is a singularity located at the upper edge of the two-particle continuum.
+\textcolor{red}{This mode moves out of the two-particle continuum as $V$ is increased and becomes a proper $\delta$ peak, see panel (c) at $V=0.5t$.}
+
+\textcolor{red}{$\spectral{t.AFM}$ and $\spectral{l.AFM}$ are identical and restricted to the continuum for both phases and both lattices.
+The former statement can be understood by the same argument why $\spectral{Phase}$ and $\spectral{Higgs}$ are identical outside of the SC phase:
+If no AFM order is present, the same amount of energy is required to create any such excitation, in this case, a magnon.}
+For the square lattice, there is a singularity located at the upper edge of the two-particle continuum.
 
@@
 This results in a purely superconducting phase with the same features as in \autoref{fig:resolvent_overview_SC} panel (a).
-The peak in $\spectral{CDW}$ moves to a very small, yet finite, $\omega$.
-Within the two-particle continuum $\spectral{CDW}$ and $\spectral{Phase}$ are identical.
+\textcolor{red}{The peak in $\spectral{CDW}$ moves to $\omega=0$. In fact, $\spectral{CDW}$ and $\spectral{Phase}$ are identical.}
 
@@
 Each one of the singularities behaves as $1/\sqrt{\omega - 2 \Delta_\text{tot}}$.
-
-We associate the peak at $\omega=0$ with this shifting of order parameters, i.e., diminishing one and increasing the other while keeping $\Delta_\text{tot}$ constant.
-The singularity at the lower edge of the two-particle continuum can be interpreted similarly to the Higgs mode in a pure superconductor.
-It captures the change of $\Delta_\text{tot}$ by changing either one of the composing order parameters.
+\textcolor{red}{Essentially, varying the ratio of the two gap parameters smoothly switches $\spectral{Higgs}$ and $\spectral{CDW}$.}
+
+\textcolor{red}{We associate the peak in the amplitude-related spectral functions at $\omega=0$ with this shifting of order parameters, i.e., diminishing one and increasing the other while keeping $\Delta_\text{tot}$ constant.
+Specifically, in the pure SC phase, we find this peak only in $\spectral{CDW}$.
+This can be understood as follows: The operator $A_\text{CDW}$ in \eqref{eqn:resolvent_bases} creates an exciton and thereby increases $|\Delta_\text{CDW}|$.
+This can in essence be achieved without any external energy by lowering $\Delta_\text{SC}$.
+However, the converse is not true: Since $\Delta_\text{CDW}$ is already 0, creating another Cooper pair by virtue of $A_\text{Higgs}$ will always increase $\Delta_\text{tot}$ and therefore requires a minimum energy of $2 \Delta_\text{tot}$.
+The same argument can be made for the pure CDW phase.
+If, however, both orders are present, the system can shift between them arbitrarily by creating either kind of excitation.
+Hence, in this case, we find a peak at $\omega=0$ in both spectral functions.}
 
@@
 Lastly, we investigate the same spectral functions close to the AFM-CDW phase transition, depicted in \autoref{fig:resolvent_overview_AFM}.
-We choose $V=1t$ for both lattices and $U=zV \pm 0.1t$, where $z$ is the coordination number, see panels (a) and (b).
+\textcolor{red}{We choose $V=1.2t$ for the square lattice and $V=0.8t$ for the simple cubic lattice.
+This yields that the phase transition is located at $U=4.8t$ for both cases. 
+The panels (a) and (b) show the system close to the phase transition at $U=4.8t \pm 0.1t$.}
 Again, both SC-related spectral functions are identical in both the CDW and AFM phases.
 Within the continuum their weight is shifted towards the upper edge and on the square lattice only, there is a peak above the continuum.
-In the AFM phase, both $\spectral{AFM}$ and $\spectral{CDW}$ have a peak close, but yet below, the two-particle continuum.
+In the AFM phase, both $\spectral{l.AFM}$ and $\spectral{CDW}$ have a peak close, but yet below, the two-particle continuum.
 The peak of the former is at a lower energy than the peak of the latter.
@@
 Using the same analysis as before, we conclude that each of these peaks is a $\delta$ peak.
-Moving further away from the phase transition, here $U=z(V+0.2t)$ in panels (c) and (d), the upper peak becomes soft as it shifts into the two-particle continuum.
+\textcolor{red}{Moving further away from the phase transition, here $U=4.8t \pm 1.4t$ in panels (c) and (d), the upper peak moves into the two-particle continuum while the other one persists.
+Both close and far away from the phase transition, but only in the AFM phase, $\spectral{t.AFM}$ exhibits a $\delta'$ peak at $\omega=0$.
+This represents a transversal magnon and is the Goldstone boson for the AFM phase.}
 
@@
 First and foremost, the upper panels (a) and (b) depict the peak positions and weights, respectively.
-The former drops off and the latter grows as $V$ moves to 0, however, both of them smoothly approach a finite value.
-It is the same, as the one that is obtained for $V=0$ while setting $\Delta_\text{CDW}$ to 0, see \autoref{fig:resolvent_overview_V0} (a).
-This indicates that the peak steadily evolves to the limiting case $V=0$.
-
-Moving towards larger $|V|$, the peaks move towards greater $\omega$, i.e., closer to the two-particle continuum.
-Additionally, the weights drop off, first with increasing speed and then slowing down, see panels (c) and (d) for a logarithmic scaling.
-A fit of the form $y(x) = a (\tanh (bx - c) + 1)$, with $x=\ln|V/t|$ works well for both the peak positions and weights.
-Transforming back to the non-logarithmic scale yields
-\begin{equation}
-    y(V) = a \left( \frac{ \xi - \frac{1}{\xi} }{ \xi + \frac{1}{\xi} } \right)\,,\quad \xi \coloneqq e^{-c} |V/t|^b\,.
-\end{equation}
-The fit parameters are printed in the respective panels of \autoref{fig:sc_in_cdw_behavior}.
-This indicates that the peak weights drop off fairly quickly as the system moves away from the phase transition while the peak positions shift towards higher energies.
-It also suggests that there might be a finite saturation value, but we are unable to compute the Green's functions for additional, even larger $|V|$, 
-because the matrix $\mM$ is not nonnegative anymore after $V\approx -0.28t$ (square lattice) or $V\approx -0.34t$ (simple cubic lattice).
-Note, that our proof for the nonnegativity is based on the system being in thermal equilibrium.
+\textcolor{red}{For $|V| \ll t$, the behavior of both the weight and the position of the peak is the same as for the previously discussed peak in $\spectral{SC}$ within the CDW phase.}
+
+\textcolor{red}{Moving towards larger $|V|$, the growth of the peak position slows down, while the weights start to drop off rapidly.
+However, we are unable to compute the Green's functions for additional, even larger $|V|$ because the matrix $\mM$ is not nonnegative anymore after $V\approx -0.28t$ (square lattice) or $V\approx -0.34t$ (simple cubic lattice).
+Note, that our proof for the nonnegativity is based on the system being in thermal equilibrium.}
 Therefore, we conclude that beyond these values of $V$, the superconducting phase is not the true ground state of the system, see the red shading in \autoref{fig:phase_diagram}.
@@
 At this point, the weight of said peak also vanishes, see panel (c).
-This occurs around $U \approx 4V \pm 0.4245t$ for the square lattice and around $U \approx 6V \pm 1.11t$ for the simple cubic lattice.
+This occurs around $U \approx 4.8t \pm 1.428t$ for the square lattice and around $U \approx 4.8t \pm 0.321t$ for the simple cubic lattice.
 
@@
 
-\section{Antisymmetry of the spectral functions}
-\label{sec:antisymmetry_spectral}
-
-Consider any Hermitian operator $A$. 
-We compute the Fourier-transformed Green's function for positive and negative $\omega$
-\begin{align}
-    G_{AA}(\omega) &= -i \int_0^\infty e^{i \omega t} \langle [A(t), A] \rangle \mathrm{d}t\,, \nonumber \\
-    G_{AA}(- \omega) &= -i \int_0^\infty e^{-i \omega t} \langle [A(t), A] \rangle \mathrm{d}t\,.
-\end{align}
-We also compute the complex conjugate of the former
-\begin{align}
-    G_{AA}^* (\omega) &= i \int_0^\infty e^{-i \omega t} \langle [A(t), A] \rangle^* \mathrm{d}t \nonumber \\
-        &= i \int_0^\infty e^{-i \omega t} \langle [A^\dagger, A^\dagger(t)] \rangle \\
-        &= -i \int_0^\infty e^{-i \omega t} \langle [A(t), A] \rangle \\
-        &= G_{AA}(- \omega)
-\end{align}
-Taking the imaginary part reveals
-\begin{align}
-    \Im [ G_{AA}^* (\omega) ] = - \Im [G_{AA} (\omega) ] = \Im [G_{AA} (-\omega)]\,.
-\end{align}
-This proves that the imaginary part of such a Fourier-transformed Green's function is antisymmetrical and therefore the same applies to the spectral functions.
-Note, that this fully abides by the sum rule $\int_{-\infty}^\infty \mathcal{A}_{A^\dagger A} (\omega) \mathrm{d}\omega = \langle [A^\dagger, A] \rangle = 0$ \cite{rickayzen80}.
-
 \bibliography{sn-bibliography}

### 2024-03-04 paper/afm_cdw_peaks_overview.py
a
x

u

Paper stuff

data

stuff

tex

stuff

@@ -13,13 +13,13 @@ from lib.extract_key import *
 import lib.resolvent_peak as rp
 import lib.plot_settings as ps
 
-Us_square = np.array([0.0001, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 1, 1.05, 1.1, 1.15, 1.2, 1.24, 1.25])
-#, 1.27, 1.3, 1.32, 1.35, 1.37, 1.4, 1.42, 1.45, 1.47, 1.5
+Us_square = np.array([  0.0001, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 0.5, 0.55, 0.6, 
+                        0.65, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 1, 1.05, 1.1, 1.15, 1.2, 1.25, 1.3, 1.35, 1.4, 1.428])#, 1.43, 1.432, 1.434, 1.436, 1.438, 1.44, 1.45, 1.47, 1.5
 
-Us_cube = np.array([0.0001, 0.01, 0.02, 0.03, 0.04, 0.05, 0.06, 0.07, 0.08, 0.09, 0.1, 0.11, 0.12, 0.13, 0.14, 0.15, 0.16, 0.17, 0.18, 0.19, 0.2, 0.21, 0.22, 0.23, 0.24, 0.25, 0.26, 0.27, 0.28, 0.29, 0.295, 0.299])
-#, 0.3, 0.302, 0.305, 0.307, 0.31, 0.312, 0.315, 0.317, 0.32, 0.322, 0.325
+Us_cube = np.array([0.0001, 0.01, 0.02, 0.03, 0.04, 0.05, 0.06, 0.07, 0.08, 0.09, 0.1, 0.11, 0.12, 0.13, 0.14, 0.15, 
+                    0.16, 0.17, 0.18, 0.19, 0.2, 0.21, 0.22, 0.23, 0.24, 0.25, 0.26, 0.27, 0.28, 0.29, 0.3, 0.31, 0.321])#, 0.322, 0.325
 
-#for p in [1.27, 1.3, 1.32, 1.35, 1.37, 1.4, 1.42, 1.45, 1.47, 1.5]:
+#for p in [0.321]:
 #    print(f"0 {round(4.8 + p, 4)} 1.2")
 
[…]

### 2024-03-04 paper/resolvent_overview_AFM_CDW.py

@@ -17,10 +17,10 @@ params = [  [ [0., 4.85, 1.2], [0., 4.75, 1.2], [0., 6.2, 1.2], [0., 3.4, 1.2] ]
             [ [0., 4.85, 0.8], [0., 4.75, 0.8], [0., 6.2, 0.8], [0., 3.4, 0.8] ]]
 
 folders = ["../data/modes/square/dos_6000/", "../data/modes/cube/dos_6000/"]
-nrows = 4
+nrows = 3
 ncols = 2
 # ax = axs[row][col]
-fig, axs = plt.subplots(nrows=nrows, ncols=ncols, figsize=(12.8, 10), sharey=True, sharex="col", gridspec_kw=dict(hspace=0, wspace=0))
+fig, axs = plt.subplots(nrows=nrows, ncols=ncols, figsize=(12.8, 8), sharey=True, sharex="col", gridspec_kw=dict(hspace=0, wspace=0))
 
 plotters = np.empty((nrows, ncols), dtype=ps.CURVEFAMILY)
 for i in range(nrows):
@@ -78,10 +78,10 @@ axs[0][1].text(10.6, 0.6, "(a.2) AFM\n$U = 6.2t$")
 axs[1][1].text(10.6, 0.6, "(b.2) CDW\n$U = 3.4t$")
 axs[1][0].text(7.6, 0.6, "(b.1) CDW\n$U = 4.75t$")
 
-axs[2][0].text(7.6, 0.6, "(c.1) AFM\n$U = 4.85t$")
+axs[2][0].text(7.6, 0.6, "(c.1) AFM\n$U = 6.2t$")
 axs[2][1].text(10.6, 0.6, "(c.2) AFM\n$U = 6.2t$")
 
-if nrows > 3: axs[3][0].text(7.6, 0.6, "(d.1) CDW\n$U = 4.75t$")
+if nrows > 3: axs[3][0].text(7.6, 0.6, "(d.1) CDW\n$U = 3.4t$")
 if nrows > 3: axs[3][1].text(10.6, 0.6, "(d.2) CDW\n$U = 3.4t$")
 
 fig.tight_layout()

### 2024-03-05 paper/main.tex
Paper stuff

@@
     $U_0$ denotes the highest value of $U$ for which there is no peak below the two-particle continuum.
-    For the square lattice, it is $U_0 \approx 3.372t$ and for the simple cubic lattice, it is $U_0 \approx 4.479t$.
+    For the square lattice, it is $U_0 = 3.38$ and for the simple cubic lattice, it is $U_0 = 4.48t$.
     The parameter range depicted here places the system within the CDW phase.
@@
 At this point, the weight of said peak also vanishes, see panel (c).
-This occurs around $U \approx 4.8t \pm 1.428t$ for the square lattice and around $U \approx 4.8t \pm 0.321t$ for the simple cubic lattice.
+This occurs around $U \approx 4V \pm 0.4245t$ for the square lattice and around $U \approx 6V \pm 1.11t$ for the simple cubic lattice.
 

### 2024-03-05 paper/resolvent_overview_AFM_CDW.py
Paper stuff

@@ -78,10 +78,10 @@ axs[0][1].text(10.6, 0.6, "(a.2) AFM\n$U = 6.2t$")
 axs[1][1].text(10.6, 0.6, "(b.2) CDW\n$U = 3.4t$")
 axs[1][0].text(7.6, 0.6, "(b.1) CDW\n$U = 4.75t$")
 
-axs[2][0].text(7.6, 0.6, "(c.1) AFM\n$U = 4.85t$")
+axs[2][0].text(7.6, 0.6, "(c.1) AFM\n$U = 6.2t$")
 axs[2][1].text(10.6, 0.6, "(c.2) AFM\n$U = 6.2t$")
 
-if nrows > 3: axs[3][0].text(7.6, 0.6, "(d.1) CDW\n$U = 4.75t$")
+if nrows > 3: axs[3][0].text(7.6, 0.6, "(d.1) CDW\n$U = 3.4t$")
 if nrows > 3: axs[3][1].text(10.6, 0.6, "(d.2) CDW\n$U = 3.4t$")
 
 fig.tight_layout()

### 2024-03-05 paper/zero_peaks.py

@@ -39,8 +39,8 @@ for j, V, g_name, name_suffix in [(0, -0.1, "Phase", "phase_SC"), (1, 0.0, "Higg
         axs[j][i].text(0.05, 0.29, f"$b={popt[1]:.4f}$", transform = axs[j][i].transAxes)
     axs[j][0].set_ylabel(rf"$\ln(\Re[\mathcal{{G}}_\mathrm{{{g_name}}}](\omega) \cdot t)$")
 
-axs[0][0].title.set_text("Square")
-axs[0][1].title.set_text("Simple cubic")
+axs[0][0].title.set_text("Square lattice")
+axs[0][1].title.set_text("Simple cubic lattice")
 axs[0][0].legend()
 axs[1][0].set_xlabel(r"$\ln(\omega / t)$")
 axs[1][1].set_xlabel(r"$\ln(\omega / t)$")

### 2024-03-05 paper/phase_diagram.py
Paper stuff

@@ -2,7 +2,7 @@ import numpy as np
 import matplotlib.pyplot as plt
 
 fig, axs = plt.subplots(nrows=2, sharex=True, figsize=(6.4, 9))
-folder = "T0"
+folder = "u_bound_1"
 
 xlims = (-4, 4)
 ylims = (-2, 2)

### 2024-03-05 paper/afm_cdw_peaks_details.py
Paper stuff

@@ -78,8 +78,8 @@ for i in range(2):
     axs[0][i].text(0.05, 0.7, f"b = {popt1[1]:.4f}", transform = axs[0][i].transAxes)
     axs[1][i].text(0.05, 0.7, f"b = {popt2[1]:.4f}", transform = axs[1][i].transAxes)
 
-axs[0][0].title.set_text("Square")
-axs[0][1].title.set_text("Simple cubic")
+axs[0][0].title.set_text("Square lattice")
+axs[0][1].title.set_text("Simple cubic lattice")
 
 axs[0][0].text(0.89, 0.7, "(a.1)", transform = axs[0][0].transAxes)
 axs[0][1].text(0.89, 0.7, "(a.2)", transform = axs[0][1].transAxes)
@@ -88,8 +88,8 @@ axs[1][1].text(0.89, 0.7, "(b.2)", transform = axs[1][1].transAxes)
 
 axs[nrows-1][0].set_xlabel(r"$\ln((U - U_0) / t)$")
 axs[nrows-1][1].set_xlabel(r"$\ln((U - U_0) / t)$")
-axs[0][0].set_ylabel(r"$(\omega_- - \omega_0) [t]$")
-axs[1][0].set_ylabel(r"$W_0$")
+axs[0][0].set_ylabel(r"$\ln ((\omega_- - \omega_0) / t)$")
+axs[1][0].set_ylabel(r"$\ln(W_0)$")
 legend = axs[0][1].legend(loc='lower right')
 fig.tight_layout()
 

### 2024-03-05 paper/afm_cdw_peaks_overview.py

@@ -73,8 +73,8 @@ for i in range(2):
 #axs[1][1].set_ylim(0, 0.11)
 #axs[2][1].set_ylim(0, 0.18)
 
-axs[0][0].title.set_text("Square")
-axs[0][1].title.set_text("Simple cubic")
+axs[0][0].title.set_text("Square lattice")
+axs[0][1].title.set_text("Simple cubic lattice")
 
 axs[0][0].text(0.9, 0.6, "(a.1)", transform = axs[0][0].transAxes)
 axs[0][1].text(0.9, 0.6, "(a.2)", transform = axs[0][1].transAxes)

### 2024-03-06 paper/resolvent_overview_V0.py
mm

@@ -62,12 +62,12 @@ for i in range(nrows):
 axs[0][0].set_title("Square lattice", pad=22)
 axs[0][1].set_title("Simple cubic lattice", pad=22)
 
-axs[0][0].text(6.4, 0.6, "(a.1)\n$\Delta_\\mathrm{CDW} = 0$")
-axs[1][0].text(6.4, 0.6, "(b.1)\n$\Delta_\\mathrm{SC} = 0$")
-axs[2][0].text(6.4, 0.6, "(c.1)\n$\Delta_\\mathrm{SC} = \Delta_\\mathrm{CDW}$")
-axs[0][1].text(9.4, 0.6, "(a.2)\n$\Delta_\\mathrm{CDW} = 0$")
-axs[1][1].text(9.4, 0.6, "(b.2)\n$\Delta_\\mathrm{SC} = 0$")
-axs[2][1].text(9.4, 0.6, "(c.2)\n$\Delta_\\mathrm{SC} = \Delta_\\mathrm{CDW}$")
+axs[0][0].text(0.7, 0.6, "(a.1)\n$\Delta_\\mathrm{CDW} = 0$", transform = axs[0][0].transAxes)
+axs[1][0].text(0.7, 0.6, "(b.1)\n$\Delta_\\mathrm{SC} = 0$", transform = axs[1][0].transAxes)
+axs[2][0].text(0.7, 0.6, "(c.1)\n$\Delta_\\mathrm{SC} = \Delta_\\mathrm{CDW}$", transform = axs[2][0].transAxes)
+axs[0][1].text(0.7, 0.6, "(a.2)\n$\Delta_\\mathrm{CDW} = 0$", transform = axs[0][1].transAxes)
+axs[1][1].text(0.7, 0.6, "(b.2)\n$\Delta_\\mathrm{SC} = 0$", transform = axs[1][1].transAxes)
+axs[2][1].text(0.7, 0.6, "(c.2)\n$\Delta_\\mathrm{SC} = \Delta_\\mathrm{CDW}$", transform = axs[2][1].transAxes)
 
 fig.tight_layout()
 plt.savefig(f"plots/{os.path.basename(__file__).split('.')[0]}.pdf")

### 2024-03-06 paper/cdw_peak_in_sc.py
mm

@@ -71,16 +71,14 @@ for i in range(2):
     popt, pcov = ez_linear_fit(v_data[:cut], peak_positions[:cut], plotters[0][i], ez_lin_space(v_data), label="Fit")
     plotters[0][i].plot(v_data[:cut], peak_positions[:cut], label="Fitted data")
     plotters[0][i].plot(v_data[cut:], peak_positions[cut:], label="Omitted data", markerfacecolor="None")
-    axs[0][i].text(0.15, 0.88, f"$c={popt[0]:.4f}$", transform = axs[0][i].transAxes)
-    axs[0][i].text(0.15, 0.77, f"$d={popt[1]:.4f}$", transform = axs[0][i].transAxes)
+    axs[0][i].text(0.15, 0.8, f"$c={popt[0]:.4f}$\n$d={popt[1]:.4f}$", transform = axs[0][i].transAxes)
     
     # Plot and fit W_0
     cut = len(v_data) - cutoffs[1][i]
     popt, pcov = ez_linear_fit(v_data[:cut], weights[:cut], plotters[1][i], ez_lin_space(v_data), label="Fit")
     plotters[1][i].plot(v_data[:cut], weights[:cut], label="Data")
     plotters[1][i].plot(v_data[cut:], weights[cut:], label="Omitted data", markerfacecolor="None")
-    axs[1][i].text(0.15, 0.88, f"$c={popt[0]:.4f}$", transform = axs[1][i].transAxes)
-    axs[1][i].text(0.15, 0.77, f"$d={popt[1]:.4f}$", transform = axs[1][i].transAxes)
+    axs[1][i].text(0.15, 0.8, f"$c={popt[0]:.4f}$\n$d={popt[1]:.4f}$", transform = axs[1][i].transAxes)
 
 axs[0][0].title.set_text("Square lattice")
 axs[0][1].title.set_text("Simple cubic lattice")

### 2024-03-06 paper/main.tex
mm

--- 2024-03-04 paper/main.tex
@@
 
+\def\hmath$#1${\texorpdfstring{{\rmfamily\textit{#1}}}{#1}}
+
 \begin{document}
@@
     In accordance with the literature, we expect to find a phase-separated state \cite{Linner23}.
-    Lastly, the red shading shows the region that we cannot access because the discretization $N_\gamma$, 
-    which is required to accurately describe the system, is too large.}}
+    Lastly, the striped area shows the region that we cannot access because the discretization $N_\gamma$, 
+    which is required to accurately describe the system, is too large. However, we expect to find a superconducting state here.}}
     \label{fig:phase_diagram}
@@
 In this case, the dynamical matrix $\mM$ picks up negative eigenvalues that vanish if $N_\gamma$ is increased so that $\Delta \gamma$ is sufficiently smaller than $\Delta_\text{tot}$.
-This happens if the parameters are chosen from the purple shaded area in \autoref{fig:phase_diagram}.
+This happens if the parameters are chosen from the striped area in \autoref{fig:phase_diagram}.
 \textcolor{red}{This issue only arises in the SC phase, nevertheless, we expect similar inaccuracies in the AFM region for small $U$.
@@
     The middle panels (b) depict the peak positions relative to the lower edge of the two-particle continuum $\omega_-$, while the bottom panels (c) show their respective weights.}
-    The shadings indicate the phase the system is in. Blue represents AFM while orange represents CDW.
+    The shadings indicate the phase the system is in. Green represents AFM while orange represents CDW.
     Note the difference in the scales for the two lattices.}
@@
 Additionally, we will add a small imaginary part of $10^{-5}t$ to $\omega$ in order to visualize the occurring $\delta$ peaks.
+\textcolor{red}{Furthermore, we provide a brief analysis of the effect of choosing different numbers of discretization points $N_\gamma$ in appendix \ref{sec:finite_size}.}
 
@@
 \end{align}
-For $\mM$ to be positive semidefinite the expression above must not be negative.
-Therefore, we need to show, that any diagonal element of $\mM$ is nonnegative.
-To do this, we expand the commutators and the thermal expectation value $\langle O \rangle = \frac{1}{Z} \Trace [\exp(-\beta H_\text{MF}) O]$, 
-where $\beta$ is the inverse temperature and $Z$ the partition function.
-This procedure yields
-
-\begin{widetext}
-    \begin{align}
-        \langle [B^\dagger, [H, B]] \rangle &= \frac{1}{Z} \Trace [\exp(-\beta H) [B^\dagger, [H, B]]] \nonumber \\
-            &= \frac{1}{Z} \sum_j e^{-\beta \epsilon_j} \bra{\psi_j} [B^\dagger, [H, B]] \ket{\psi_j} \nonumber \\
-            &= \frac{1}{Z} \sum_j e^{-\beta \epsilon_j} \left[ \bra{\psi_j} B^\dagger (H - \epsilon_j) B \ket{\psi_j} + \bra{\psi_j} B (H - \epsilon_j) B^\dagger \ket{\psi_j} \right] \nonumber \\
-            &= \frac{1}{Z} \sum_{ij} e^{-\beta \epsilon_j} \left[ \bra{\psi_j} B^\dagger \ket{\psi_i} (\epsilon_i - \epsilon_j) \bra{\psi_i} B \ket{\psi_j} + \bra{\psi_j} B \ket{\psi_i} (\epsilon_i - \epsilon_j) \bra{\psi_i} B^\dagger \ket{\psi_j} \right] \nonumber \\
-            &= \frac{1}{Z} \sum_{ij} e^{-\beta \epsilon_j} (\epsilon_i - \epsilon_j) \underbrace{ \left[ \bra{\psi_j} B^\dagger \ket{\psi_i} \bra{\psi_i} B \ket{\psi_j} + \bra{\psi_j} B \ket{\psi_i} \bra{\psi_i} B^\dagger \ket{\psi_j} \right]}_{\coloneqq C_{ij} = C_{ji} \geq 0} \nonumber \\
-            &= \frac{1}{2Z} \left[ \sum_{ij} C_{ij} e^{-\beta \epsilon_j} (\epsilon_i - \epsilon_j) - \sum_{ij} C_{ij} e^{-\beta \epsilon_i} (\epsilon_i - \epsilon_j) \right] \nonumber \\
-            &= \frac{1}{2Z} \sum_{ij} C_{ij} \left( e^{-\beta \epsilon_j} - e^{-\beta \epsilon_i} \right) \left( \epsilon_i - \epsilon_j \right) \geq 0 \,.
-    \end{align}
-\end{widetext}
-
-This concludes our proof. Note, that the only assumption made, is that the expectation value is to be taken with respect to the thermal equilibrium.
+For $\mM$ to be positive semidefinite the expression above must not be negative,
+\textcolor{red}{which has already been proven in Refs. \cite{Dyson1978,mermin66}.}
 
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=.98\textwidth]{plots/higgs_peak.pdf}
-    \caption{Log-log plot of $\spectral{Higgs}$ (a, c) and $\spectral{CDW}$ (b) near $\omega = \omega_0 = 2\Delta_\text{SC}$ at $U=-2.5t$ and $V=0$.
-    The different panels depict the spectral functions for various ratios of $\Delta_\text{SC}$ to $\Delta_\text{CDW}$.
-    We additionally plot the difference between $\spectral{i}$ and $\spectral{Phase}$ and fit it, as we interpret the latter as a background within the two-particle continuum.
-    The left (right) panel shows the results for the square (simple cubic) lattice.
-    The spectral function behaves as $1 / \sqrt{\omega - 2 \Delta_\text{tot}}$.
-    Note, that $\spectral{CDW}$ and $\spectral{Higgs}$ are identical for the choice in panel (c).}
-    \label{fig:higgs_peak}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \includegraphics[width=0.98\textwidth]{plots/peak_fits.pdf}
-    \caption{Log-log plot of the real part of various Green's functions, the labels indicate its type and the text in the panels indicate the phase.
-        The results for both lattice types are shown but are qualitatively identical.
-        The power-law exponent is $a=-1$ in all cases, indicating that these peaks are $\delta$ distributions.}
-        \label{fig:peak_fits}
-\end{figure*}
-
-In this appendix section, we show fits to the real and imaginary parts of various Green's functions in the different phases.
+In this appendix section, we discuss fits to the real and imaginary parts of various Green's functions in the different phases.
 All fits are linear of the type $y = ax + b$ in double logarithmic plots, i.e., $a$ describes the power-law behavior of the functions.
-Firstly, the real part of $\greens{Phase}$ in the SC phase is shown in panel (a) of \autoref{fig:zero_peaks}.
+An example plot of the real part of $\greens{Phase}$ in the SC phase is shown in panel (a) of \autoref{fig:zero_peaks}.
 It behaves as $1/\omega^2$ indicating that the peak we find in the spectral function at $\omega=0$ corresponds to the derivative of a $\delta$ distribution.
-The same results are obtained for the peak in $\spectral{Higgs}$ and $\spectral{CDW}$ in the coexistence phase.
-
-Continuing, we investigate the divergence at $\omega = 2\Delta$ found in $\spectral{Higgs}$ and $\spectral{CDW}$ at $V=0$.
-It behaves as $1/\sqrt{\omega}$ as shown in \autoref{fig:higgs_peak}.
-
-Lastly, we show all the remaining peaks in \autoref{fig:peak_fits}.
+The same results are obtained for the peak in $\spectral{Higgs}$ and $\spectral{CDW}$ in the coexistence phase as well as in $\spectral{t.AFM}$ within the AFM phase.
+
+Continuing, we investigate the divergence at $\omega = 2\Delta$ found in $\spectral{Higgs}$ and $\spectral{CDW}$ at $V=0$. It behaves as $1/\sqrt{\omega}$.
+
+Lastly, all remaining peaks below the two-particle continuum behave identical.
 The real part of each one of them behaves as $1/\omega$ in close vicinity to the peak position.
 This indicates that the peaks are $\delta$ distributions.
-The peaks of $\spectral{AFM}$ and $\spectral{CDW}$ close the the phase transition are identical when swapped, i.e., $\spectral{AFM}$ in the CDW phase is the same as $\spectral{CDW}$ in the AFM phase.
-
-\section{Numerical treatment of the iEoM matrices}
+The peaks of $\spectral{AFM}$ and $\spectral{CDW}$ close the the phase transition are identical when swapped, 
+i.e., $\spectral{AFM}$ in the CDW phase is the same as $\spectral{CDW}$ in the AFM phase.
+
+\section{Numerical treatment of the iEoM matrices in \hmath $\gamma$-space}
 \label{sec:numerical_ieom}
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=0.48\textwidth]{plots/finite_size.pdf}
+    \caption{Effect of changing the number of discretization points $N_\gamma$ on the absolute position of the peak in $\spectral{Phase}$ for $U=-2.5t$ and $V=-0.1t$.
+    On the simple cubic lattice, the peak already lies properly at $\omega=0$.
+    On the square lattice, its position approaches $0$ with $\sqrt{1/N_\gamma}$.}
+    \label{fig:finite_size}
+\end{figure}
+
 To give a practical example, let us compute $\greens{Higgs}$ from \eqref{eqn:resolvent_bases}.
@@
 
+\section{Dependence of the results on the discretization}
+\label{sec:finite_size}
+
+Most of our data barely depends on the number of discretization points $N_\gamma$ at all.
+However, specifically features that lie at very small energies, e.g., the peak in $\spectral{Phase}$ within the SC phase, can be difficult to properly resolve.
+We show this effect in \autoref{fig:finite_size}.
+Neglecting minor fluctuations, this peak is properly located at $\omega=0$ for the simple cubic lattice.
+On the square lattice, however, it follows a $\sqrt{1/N_\gamma}$ behavior, i.e., also approaching $0$.
+This behavior can be observed for the other peaks at $\omega=0$ as well.
+How far away they are from $0$, or whether they are at all, depends on the spectral function as well as on the system parameters.
+
 \bibliography{sn-bibliography}

### 2024-03-06 Poster DPG/poster.tex
Paper stuff
mm

@@
 
+\newcommand{\boxwidth}{38cm}
+\newcommand{\boxmargin}{2cm} % (82cm - 2 * boxwidth) / 3
+\newcommand{\firstbox}{25.5cm}
+
 % For more tikz
@@
 		{ % authors % set a normal space after an abbreviation, instead of an inter-sentence space
-            \underline{Joshua Alt\"user}\textsuperscript{1},
+            \underline{Joshua Alth\"user}\textsuperscript{1},
             Götz S.\ Uhrig\textsuperscript{1},
@@
 
-\posterbox{2cm}{26cm}{38cm}{Introduction}
+\posterbox{\boxmargin}{\dimexpr\firstbox}{\boxwidth}{Introduction}
 {%
@@
 
-\highlightOne{ Investigated phases } \\
+\highlightOne{ Phases of interest } \\
 \begin{itemize}
-    \item $s$-wave superconductivity (SC), Charge-density wave (CDW), and antiferromagnetism (AFM) (nesting vector $\vec{Q} = (\pi, \ldots)$)
+    \item $s$-wave superconductivity (SC), charge-density wave (CDW), and antiferromagnetism (AFM)
+    \item Nesting vectors (lattice constant $=1$): $\vec{Q} = (\pi, \pi)$ (square lattice), $\vec{Q} = (\pi, \pi, \pi)$ (sc lattice)
 \end{itemize}
@@
 \begin{minipage}{0.64\textwidth}
-    \highlightOne{ Investigated excitations } \\
+    \highlightOne{ Observables of excitations of interest } \\
     \begin{itemize}
@@
 
-\posterbox{2cm}{46cm}{38cm}{Method: Iterated equations of motion (iEoM) \cite{Kalthoff17,Bleicker18}}
-{%
-\highlightOne{ Key ideas }
-\begin{itemize}
-\item Consider a time-dependent operator $\hat{a}(t) = \sum_j c_j(t) \hat{A}_j$ and the symplectic product $(\hat{A} | \hat{B}) \coloneqq \langle [\hat{A}^\dagger, \hat{B}] \rangle$
-\item Write the Heisenberg EoM as matrix-vector EoM
-\begin{equation*}
-    \label{eqn:heisenberg}
-    \begin{aligned}
-        \ddt \hat{a}(t) = \sum_j \ddt c_j(t) \hat{A}_j &= i \sum_j c_j(t) [H, \hat{A}_j] \\
-        \Rightarrow \sum_j \underbrace{(\hat{A}_i | \hat{A}_j)}_{\coloneqq \mN_{ij}} \ddt c_j(t) &= i \sum_j \underbrace{(\hat{A}_i | [\hat{H}, \hat{A}_j])}_{\coloneqq \mM_{ij}} c_j(t) \\
-        \Rightarrow \mN \ddt \vec{c}(t) &= i \mM \vec{c}(t)\,.
-    \end{aligned}
-\end{equation*}
-\item Generalized eigenvalue problem $\omega \mN \vec{v} = \mM \vec{v}$, real solutions if either $\mM$ or $\mN$ is nonnegative.
-\begin{itemize}
-    \item $\mM$ is nonnegative is thermal equilibrium
-\end{itemize}
-\end{itemize}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\highlightOne{ Green's functions }
-\begin{itemize}
-    \item Elements of the matrix $\greens{ } \coloneqq \mN [-(\omega + \im 0^+) \mN - \mM]^{-1} \mN$ are Fourier-transformed Green's functions
-    \item Specifically
-    \begin{equation*}
-        \mathcal{G}_{ij}(\omega) = G_{\hat{A}_i \hat{A}_j^\dagger} (\omega) = -\im \int_0^{\infty} \langle [A_i(t), A_j^\dagger(0)] \rangle e^{\im (\omega + \im 0^+) t} \mathrm{d}t
-    \end{equation*}
-    \item Lengthy calculations yield a quadratic form
-    \begin{equation*}
-        \frac{1}{-(\omega + \im 0^+) \mN - \mM} \to \check{N}^{-1/2} \frac{1}{(\omega + \im 0^+)^2 - \check{M}} \check{N}^{-1/2}
-    \end{equation*}
-    \item Matrix inverse by tridiagonalization and subsequent continued fraction expansion with square-root terminator
-\end{itemize}
-}
-
-\posterbox{2cm}{74.8cm}{38cm}{Model}
+\posterbox{\boxmargin}{\dimexpr\firstbox + 19.2cm}{\boxwidth}{Model}
 {%
@@
         \item Half-filling, on both a square and a simple cubic lattice, temperature $T=0$
+        \item A simple model exhibiting a rich phase diagram
     \end{itemize}
@@
         \item Terms depend on $\hat{\gamma}(\vec{k}) \coloneqq \frac{1}{D} \sum_{\alpha=1}^D \cos(k_\alpha)$ \\
-        $\Rightarrow$ DOS based description $\rho \coloneqq \frac{1}{N} \sum_{\vec{k}} \delta(\gamma - \hat{\gamma}(\vec{k}))$
+        $\Rightarrow$ density of states $\rho(\gamma) \coloneqq \frac{1}{N} \sum_{\vec{k}} \delta(\gamma - \hat{\gamma}(\vec{k}))$
         \begin{align*}
-            \Delta_\text{CDW} &= \left(\frac{U}{2N} - \frac{zV}{N}\right) \sum_{\sigma} \int \langle g_{\sigma} (\gamma) \rangle \dgamma\\\ 
-            \Delta_\text{SC} &= \frac{U}{N} \int \langle f(\gamma) \rangle \dgamma\\
-            \Delta_\text{AFM} &= \frac{U}{2N} \int \left( \langle g_{\uparrow} (\gamma) \rangle - \langle g_{\downarrow} (\gamma) \rangle \right) \dgamma\\ 
-            \Delta_n &= \frac{V}{N} \sum_{\sigma} \int \gamma \langle n_{\sigma} (\gamma) \rangle \dgamma
+            \Delta_\text{CDW} &= \left(\frac{U}{2N} - \frac{zV}{N}\right) \sum_{\sigma} \int \rho(\gamma) \langle g_{\sigma} (\gamma) \rangle \dgamma\\\ 
+            \Delta_\text{SC} &= \frac{U}{N} \int \rho(\gamma) \langle f(\gamma) \rangle \dgamma\\
+            \Delta_\text{AFM} &= \frac{U}{2N} \int \rho(\gamma) \left( \langle g_{\uparrow} (\gamma) \rangle - \langle g_{\downarrow} (\gamma) \rangle \right) \dgamma\\ 
+            \Delta_n &= \frac{V}{N} \sum_{\sigma} \int \rho(\gamma) \gamma \langle n_{\sigma} (\gamma) \rangle \dgamma
         \end{align*}
-        \item The iEoM utilize the same description
         \item Allows us to tackle both 2D and 3D systems
@@
     \includegraphics[width=\textwidth]{plots/phase_diagram.pdf}
-    \center{\textcolor{tudarkgreen}{Mean-field phase diagram of the extended Hubbard model. 
+    \center{\textcolor{tudarkgreen}{Mean-field phase diagram of the extended Hubbard model at $T=0$. 
     (a) Square lattice (b) simple cubic lattice. $d_{x^2-y^2}$ from Ref. \cite{Micnas88b}.}}
@@
     Literature suggests a phase-separated state. \cite{Linner23}
-    \item Purple region: Inaccuracies due to finite discretization dominate; here the gap is of the same order of magnitude as our gap
+    \item Striped region: Inaccuracies due to finite discretization dominate; here the gap is of the same order of magnitude as our gap
 \end{itemize}
@@
 
-\posterbox{42cm}{26cm}{38cm}{Spectral functions}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\posterbox{\boxmargin}{\dimexpr\firstbox + 53.2cm}{\boxwidth}{Method: Iterated equations of motion (iEoM) \cite{Kalthoff17,Bleicker18}}
+{%
+\highlightOne{ Key ideas }
+\begin{itemize}
+    \item Objective: capture collective excitations
+\item Consider a time-dependent operator $\hat{a}(t) = \sum_j c_j(t) \hat{A}_j$ and the symplectic product $(\hat{A} | \hat{B}) \coloneqq \langle [\hat{A}^\dagger, \hat{B}] \rangle$
+\item Write the Heisenberg EoM as matrix-vector EoM (w.r.t. to full interaction Hamiltonian)
+\begin{equation*}
+    \label{eqn:heisenberg}
+    \begin{aligned}
+        \ddt \hat{a}(t) = \sum_j \ddt c_j(t) \hat{A}_j &= \im \sum_j c_j(t) [H, \hat{A}_j] \\
+        \Rightarrow \sum_j \underbrace{(\hat{A}_i | \hat{A}_j)}_{\coloneqq \mN_{ij}} \ddt c_j(t) &= \im \sum_j \underbrace{(\hat{A}_i | [\hat{H}, \hat{A}_j])}_{\coloneqq \mM_{ij}} c_j(t) \\
+        \Rightarrow \mN \ddt \vec{c}(t) &= \im \mM \vec{c}(t)\,.
+    \end{aligned}
+\end{equation*}
+\item Generalized eigenvalue problem $\omega \mN \vec{v} = \mM \vec{v}$, real solutions if either $\mM$ or $\mN$ is nonnegative.
+\begin{itemize}
+    \item[$\rightarrow$] $\mM$ is nonnegative is thermal equilibrium
+\end{itemize}
+\end{itemize}
+
+\highlightOne{ Green's functions }
+\begin{itemize}
+    \item Elements of the matrix $\greens{ } \coloneqq \mN [-(\omega + \im 0^+) \mN - \mM]^{-1} \mN$ are Fourier-transformed Green's functions
+    \item Specifically
+    \begin{equation*}
+        \mathcal{G}_{ij}(\omega) = G_{\hat{A}_i \hat{A}_j^\dagger} (\omega) = -\im \int_0^{\infty} \langle [A_i(t), A_j^\dagger(0)] \rangle e^{\im (\omega + \im 0^+) t} \mathrm{d}t
+    \end{equation*}
+    \item The matrices $\mN$ and $\mM$, and therefore also $\mathcal{G}(\omega)$, exhibit a block structure
+    \item Lengthy calculations yield a quadratic form for the two blocks, denoted $|_X$ and $|_P$
+    \begin{align*}
+        \mathcal{G}(z = \omega + \im 0^+) &= \mathcal{N} \frac{1}{-z \mN - \mM} \mathcal{N} \\
+        \to \mathcal{G}|_X (z) = - \mathcal{L}^\dagger \check{N}_X^{-1/2} \frac{1}{z^2 - \check{M}_X} \check{N}_X^{-1/2} \mathcal{L}\,&,\qquad
+        \mathcal{G}|_P (z) = - \mathcal{L} \check{N}_P^{-1/2} \frac{1}{z^2 - \check{M}_P} \check{N}_P^{-1/2} \mathcal{L}^\dagger
+    \end{align*}
+    \item Matrix inverse by tridiagonalization and subsequent continued fraction expansion with square-root terminator
+\end{itemize}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\posterbox{ \boxwidth + \boxmargin + \boxmargin}{\dimexpr\firstbox}{\boxwidth}{Spectral functions}
 {%
@@
     \begin{itemize}
+        \item $U=-2.5t$
         \item SC phase:
@@
     \begin{itemize}
+        \item Coexistence is the result of an SO(4) symmetry of the Hubbard model at half-filling \cite{yang90}
         \item The ratio $\Delta_\text{CDW} / \Delta_\text{SC}$ may be chosen arbitrarily as long as $\Delta_\text{tot} \coloneqq \sqrt{\Delta_\text{CDW}^2 + \Delta_\text{SC}^2} = \text{const}$
@@
     \includegraphics[width=\textwidth]{plots/resolvent_overview_AFM_CDW.pdf} % NV sketch
-    \center{\textcolor{tudarkgreen}{Spectral functions for various collective excitations.}}
 \end{minipage}
@@
     \begin{itemize}
+        \item $V=1.2t$ (square lattice) and $V=0.8t$ (simple cubic lattice) $\Rightarrow$ phase transition at $U=4.8t$
         \item AFM phase: Transversal AFM spectral function has a peak at $0$
@@
 
-\posterbox{42cm}{78cm}{38cm}{Behavior of the peaks}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\posterbox{ \boxwidth + \boxmargin + \boxmargin}{\dimexpr\firstbox + 52cm}{\boxwidth}{Behavior of the peaks}
 {%
@@
 \end{minipage}
-
 }
 
-\posterbox{2cm}{110.35cm}{38cm}{Possible outlook}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\posterbox{\boxmargin}{109.7cm}{\boxwidth}{Possible outlook}
 {%
@@
 \item Coupling the electronic system to the electromagnetic field to include the Anderson-Higgs mechanism for superconductors
+\item Incorporating different fillings
 \item Describing multi-band systems with even richer phases and collective excitations
@@
 
-\posterbox{42cm}{111cm}{38cm}{References}
+\posterbox{\boxwidth + \boxmargin + \boxmargin}{110.4cm}{\boxwidth}{References}
 {%
@@
     \bibitem{Linner23} E. Linnér, C. Dutreix, S. Biermann, and E. A. Stepanov, Phys. Rev. B 108, 205156 (2023).
+    \bibitem{yang90} C. N. Yang and S. Zhang, Modern Physics Letters B 04, 759 (1990).
     %\end{multicols}          

### 2024-03-06 paper/phase_diagram.py
mm

@@ -25,8 +25,9 @@ axs[0].fill_between(np.array([xlims[0], 0, xlims[1]]), np.array([0, 0, xlims[1] 
 axs[0].fill_between([0, xlims[1]], [0, xlims[1] / 4], [ylims[0], ylims[0]], alpha=alpha, label="AFM")
 
 # unknown regions
-axs[0].fill_between(u_boundary[0], u_boundary[1], np.full(len(u_boundary[0]), ylims[0]), label="Unknown phases", alpha=alpha)
-axs[0].fill_between([u_boundary[0][-1], 0], [0, 0], [ylims[0], ylims[0]], label=r"$\Delta$ too small", alpha=alpha)
+axs[0].fill_between(u_boundary[0], u_boundary[1], np.full(len(u_boundary[0]), ylims[0]), label="Likely PS", alpha=alpha)
+axs[0].fill_between([u_boundary[0][-1], 0], [0, 0], [ylims[0], ylims[0]], label=r"$\Delta$ too small", 
+                    alpha=alpha, facecolor="C0", edgecolor="black", hatch="///", linewidth=0.0)
 axs[0].plot(u_boundary[0], u_boundary[1], "k-")
 axs[0].axvline(u_boundary[0][-1], ymin=0, ymax=0.5, color="k", linestyle=":")
 
@@ -53,8 +54,9 @@ axs[1].fill_between(np.array([xlims[0], 0, xlims[1]]), np.array([0, 0, xlims[1] 
 axs[1].fill_between([0, xlims[1]], [0, xlims[1] / 6], [ylims[0], ylims[0]], alpha=alpha, label="AFM")
 
 # unknown regions
-axs[1].fill_between(u_boundary[0], u_boundary[1], np.full(len(u_boundary[0]), ylims[0]), label="Unknown phases", alpha=alpha)
-axs[1].fill_between([u_boundary[0][-1], 0], [0, 0], [ylims[0], ylims[0]], label=r"$\Delta$ too small", alpha=alpha)
+axs[1].fill_between(u_boundary[0], u_boundary[1], np.full(len(u_boundary[0]), ylims[0]), label="Likely PS", alpha=alpha)
+axs[1].fill_between([u_boundary[0][-1], 0], [0, 0], [ylims[0], ylims[0]], label=r"$\Delta$ too small", 
+                    alpha=alpha, facecolor="C0", edgecolor="black", hatch="///", linewidth=0.0)
[…]

### 2024-03-06 paper/resolvent_overview_AFM_CDW.py

@@ -72,14 +72,12 @@ for i in range(nrows):
 axs[0][0].set_title("Square lattice", pad=22)
 axs[0][1].set_title("Simple cubic lattice", pad=22)
 
-axs[0][0].text(7.6, 0.6, "(a.1) AFM\n$U = 4.85t$")
-axs[0][1].text(10.6, 0.6, "(a.2) AFM\n$U = 6.2t$")
-
-axs[1][1].text(10.6, 0.6, "(b.2) CDW\n$U = 3.4t$")
-axs[1][0].text(7.6, 0.6, "(b.1) CDW\n$U = 4.75t$")
-
-axs[2][0].text(7.6, 0.6, "(c.1) AFM\n$U = 6.2t$")
-axs[2][1].text(10.6, 0.6, "(c.2) AFM\n$U = 6.2t$")
+axs[0][0].text(0.7, 0.6, "(a.1) AFM\n$U = 4.85t$", transform = axs[0][0].transAxes)
+axs[0][1].text(0.7, 0.6, "(a.2) AFM\n$U = 4.85t$", transform = axs[0][1].transAxes)
+axs[1][1].text(0.7, 0.6, "(b.2) CDW\n$U = 4.75t$", transform = axs[1][1].transAxes)
+axs[1][0].text(0.7, 0.6, "(b.1) CDW\n$U = 4.75t$", transform = axs[1][0].transAxes)
+axs[2][0].text(0.7, 0.6, "(c.1) AFM\n$U = 6.2t$" , transform = axs[2][0].transAxes)
+axs[2][1].text(0.7, 0.6, "(c.2) AFM\n$U = 6.2t$" , transform = axs[2][1].transAxes)
 
 if nrows > 3: axs[3][0].text(7.6, 0.6, "(d.1) CDW\n$U = 3.4t$")
 if nrows > 3: axs[3][1].text(10.6, 0.6, "(d.2) CDW\n$U = 3.4t$")

### 2024-03-07 paper/phase_diagram.py
data
plots

poster

paper

Poster

@@ -27,9 +27,9 @@ axs[0].fill_between([0, xlims[1]], [0, xlims[1] / 4], [ylims[0], ylims[0]], alph
 # unknown regions
 axs[0].fill_between(u_boundary[0], u_boundary[1], np.full(len(u_boundary[0]), ylims[0]), label="Likely PS", alpha=alpha)
 axs[0].fill_between([u_boundary[0][-1], 0], [0, 0], [ylims[0], ylims[0]], label=r"$\Delta$ too small", 
-                    alpha=alpha, facecolor="C0", edgecolor="black", hatch="///", linewidth=0.0)
+                    alpha=alpha, facecolor="C0", edgecolor="black", hatch="///", linewidth=2.0)
 axs[0].plot(u_boundary[0], u_boundary[1], "k-")
-axs[0].axvline(u_boundary[0][-1], ymin=0, ymax=0.5, color="k", linestyle=":")
+#axs[0].axvline(u_boundary[0][-1], ymin=0, ymax=0.5, color="k", linestyle=":")
 
 #Plot boundaries
 micnas_d = np.loadtxt("../data/micnas_d_wave.csv").transpose()
@@ -56,9 +56,9 @@ axs[1].fill_between([0, xlims[1]], [0, xlims[1] / 6], [ylims[0], ylims[0]], alph
 # unknown regions
 axs[1].fill_between(u_boundary[0], u_boundary[1], np.full(len(u_boundary[0]), ylims[0]), label="Likely PS", alpha=alpha)
 axs[1].fill_between([u_boundary[0][-1], 0], [0, 0], [ylims[0], ylims[0]], label=r"$\Delta$ too small", 
-                    alpha=alpha, facecolor="C0", edgecolor="black", hatch="///", linewidth=0.0)
+                    alpha=alpha, facecolor="C0", edgecolor="black", hatch="///", linewidth=2.0)
 axs[1].plot(u_boundary[0], u_boundary[1], "k-")
-axs[1].axvline(u_boundary[0][-1], ymin=0, ymax=0.5, color="k", linestyle=":")
+#axs[1].axvline(u_boundary[0][-1], ymin=0, ymax=0.5, color="k", linestyle="-")
 
 #Plot boundaries
 axs[1].plot(np.array([0, xlims[1]]), np.array([0, xlims[1]]) / 6,  "k-")
@@ -79,7 +79,7 @@ axs[1].set_xlabel("$U [t]$")
[…]

### 2024-03-07 Poster DPG/poster.tex
data
plots

poster

paper

Poster

@@
     \begin{itemize}
-        \item (CDW) Exciton: $1/N \sum_{k} \left( g_{\vec{k}\uparrow} + g_{\vec{k}\downarrow} \right),\qquad g_{\vec{k}\sigma}$
+        \item (CDW) Exciton: $1/N \sum_{k} \left( g_{\vec{k}\uparrow} + g_{\vec{k}\downarrow} \right)$
         \item (AFM) Longitudinal magnon: $1/N \sum_{k} \left( g_{\vec{k}\uparrow} - g_{\vec{k}\downarrow} \right)$
@@
     \begin{aligned}
-        n_{k\sigma} &\coloneqq  c_{\vec{k}\sigma}^\dagger c_{\vec{k}\sigma}\,,          \\
-        f_k     &\coloneqq  c_{-\vec{k}\downarrow} c_{\vec{k}\uparrow}\,, \\
-        g_{k\sigma} &\coloneqq  c_{\vec{k}\sigma}^\dagger c_{\vec{k}+\vec{Q}\sigma}\,,  \\
-        \tau_k  &\coloneqq  c_{\vec{k}\uparrow}^\dagger c_{\vec{k}\downarrow}\,,
+        n_{k\sigma} &\coloneqq  c_{\vec{k}\sigma}^\dagger c_{\vec{k}\sigma} \\
+        f_k     &\coloneqq  c_{-\vec{k}\downarrow} c_{\vec{k}\uparrow} \\
+        g_{k\sigma} &\coloneqq  c_{\vec{k}\sigma}^\dagger c_{\vec{k}+\vec{Q}\sigma} \\
+        \tau_k  &\coloneqq  c_{\vec{k}\uparrow}^\dagger c_{\vec{k}\downarrow}
     \end{aligned}
@@
 
-\posterbox{\boxmargin}{\dimexpr\firstbox + 53.2cm}{\boxwidth}{Method: Iterated equations of motion (iEoM) \cite{Kalthoff17,Bleicker18}}
+\posterbox{\boxmargin}{\dimexpr\firstbox + 53.2cm}{\boxwidth}{Method: Iterated equations of motion (iEoM)}
 {%
-\highlightOne{ Key ideas }
+\highlightOne{ Key ideas \cite{Kalthoff17,Bleicker18}}
 \begin{itemize}
@@
     \begin{itemize}
-        \item Orange region: System is in the CDW phase, blue region: System is in the AFM phase
+        \item Orange shading: System is in the CDW phase, green shading: System is in the AFM phase
         \item Peak position grows linearly with $U$ as the system moves away from the phase transition
@@
 
-\posterbox{\boxmargin}{109.7cm}{\boxwidth}{Possible outlook}
+\posterbox{\boxmargin}{109.77cm}{\boxwidth}{Possible outlook}
 {%

### 2024-03-07 paper/cdw_peak_in_sc.py

@@ -71,21 +71,21 @@ for i in range(2):
     popt, pcov = ez_linear_fit(v_data[:cut], peak_positions[:cut], plotters[0][i], ez_lin_space(v_data), label="Fit")
     plotters[0][i].plot(v_data[:cut], peak_positions[:cut], label="Fitted data")
     plotters[0][i].plot(v_data[cut:], peak_positions[cut:], label="Omitted data", markerfacecolor="None")
-    axs[0][i].text(0.15, 0.8, f"$c={popt[0]:.4f}$\n$d={popt[1]:.4f}$", transform = axs[0][i].transAxes)
+    axs[0][i].text(0.15, 0.78, f"$c={popt[0]:.4f}$\n$d={popt[1]:.4f}$", transform = axs[0][i].transAxes)
     
     # Plot and fit W_0
     cut = len(v_data) - cutoffs[1][i]
     popt, pcov = ez_linear_fit(v_data[:cut], weights[:cut], plotters[1][i], ez_lin_space(v_data), label="Fit")
     plotters[1][i].plot(v_data[:cut], weights[:cut], label="Data")
     plotters[1][i].plot(v_data[cut:], weights[cut:], label="Omitted data", markerfacecolor="None")
-    axs[1][i].text(0.15, 0.8, f"$c={popt[0]:.4f}$\n$d={popt[1]:.4f}$", transform = axs[1][i].transAxes)
+    axs[1][i].text(0.15, 0.78, f"$c={popt[0]:.4f}$\n$d={popt[1]:.4f}$", transform = axs[1][i].transAxes)
 
-axs[0][0].title.set_text("Square lattice")
-axs[0][1].title.set_text("Simple cubic lattice")
+axs[0][0].set_title("Square lattice"      , pad=13)
+axs[0][1].set_title("Simple cubic lattice", pad=13)
 
-for i in range(ncols):
-    axs[0][i].text(0.88, 0.75, f"(a.{i+1})", transform = axs[0][i].transAxes)
-    axs[1][i].text(0.88, 0.75, f"(b.{i+1})", transform = axs[1][i].transAxes)
+for i in range(2):
+    axs[0][i].text(0.87, 0.75, f"(a.{i+1})", transform = axs[0][i].transAxes)
+    axs[1][i].text(0.87, 0.75, f"(b.{i+1})", transform = axs[1][i].transAxes)
 
 axs[1][0].set_ylim(axs[1][0].get_ylim()[0], axs[1][0].get_ylim()[1] + 1.1)
 

### 2024-03-07 paper/sc_peak_in_cdw.py

@@ -83,31 +83,31 @@ for i in range(2):
     peak_positions_div_delta = np.log(peak_positions_div_delta)
     popt1, pcov1 = curve_fit(rp.linear_function, v_data[:cut], peak_positions[:cut])
     x_lin = np.linspace(np.min(v_data), np.max(v_data), 2000)
-    fit1, = plotters[0][i].plot(x_lin, rp.linear_function(x_lin, *popt), label="Fit 1")
+    fit1, = plotters[0][i].plot(x_lin, rp.linear_function(x_lin, *popt1), label="Fit 1")
 
     cut2 = len(Vs) - 27
     popt2, pcov2 = curve_fit(rp.linear_function, v_data[cut2:], peak_positions[cut2:])
-    axs[0][i].text(0.05, 0.6, f"$c_1={popt[0]:.4f}$\n$d_1={popt[1]:.4f}$\n$c_2={popt2[0]:.4f}$\n$d_2={popt2[1]:.4f}$", transform = axs[0][i].transAxes)
-    fit2, = plotters[0][i].plot(x_lin,  rp.linear_function(x_lin, *popt), label="Fit 2")
+    axs[0][i].text(0.05, 0.54, f"$c_1={popt[0]:.4f}$\n$d_1={popt[1]:.4f}$\n$c_2={popt2[0]:.4f}$\n$d_2={popt2[1]:.4f}$", transform = axs[0][i].transAxes)
+    fit2, = plotters[0][i].plot(x_lin,  rp.linear_function(x_lin, *popt2), label="Fit 2")
     data1, = plotters[0][i].plot(v_data[:cut], peak_positions[:cut], label="Data Fit 1")
     data2, = plotters[0][i].plot(v_data[cut2:], peak_positions[cut2:], label="Data Fit 2")
     omitted, = plotters[0][i].plot(v_data[cut:cut2], peak_positions[cut:cut2], label="Omitted data", markerfacecolor="None")
     div_delta, = plotters[0][i].plot(v_data, peak_positions_div_delta, label=r"$\omega_0 / \Delta_\mathrm{CDW}$")
 
-axs[0][0].title.set_text("Square lattice")
-axs[0][1].title.set_text("Simple cubic lattice")
+axs[0][0].set_title("Square lattice"      , pad=13)
+axs[0][1].set_title("Simple cubic lattice", pad=13)
 
 for i in range(2):
[…]

### 2024-03-07 paper/main.tex
paper

@@
     We identify the well-known amplitude (Higgs) and phase (Anderson-Bogoliubov) modes within the superconducting phase 
-    and observe a similar excitation (Cooperon) in the CDW phase which shifts towards zero energy as the system approaches the phase transition to the SC phase. 
+    and observe a similar excitation (cooperon) in the CDW phase which shifts towards zero energy as the system approaches the phase transition to the SC phase. 
     \textcolor{red}{In the CDW phase, close to the phase transition to the AFM phase, 
@@
 
-%\begin{figure}
-%    \centering
-%    \includegraphics[width=.48\textwidth]{plots/phase_limits.pdf}
-%    \caption{The lower left corner ($U<0$ and $V<0$) of the phase diagram obtained for the extended Hubbard model on 
-%    (a) a square lattice and (b) a simple cubic lattice using a mean-field approximation at temperature $T=0$.
-%    The blue shading indicates the region where the $s$-wave superconducting phase is the proper ground state of the system.
-%    The green shading shows the region that we cannot access because the discretization $N_\gamma$, which is required to accurately describe the system, is too large.
-%    Lastly, the orange shading shows the region in which the dynamical matrix $\mM$ has negative eigenvalues, indicating that there are phases not captured by our methods.}
-%    \label{fig:phase_limits}
-%\end{figure}
-
 We observe that the entire Hamiltonian and thus all expectation values only depend on
@@
     \includegraphics[width=.98\textwidth]{plots/afm_cdw_peaks_overview.pdf}
-    \caption{\textcolor{red}{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ (orange lines) and $\spectral{l.AFM}$ (blue lines) close to the corresponding phase transition $U = 4.8t$.
+    \caption{\textcolor{red}{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ (orange lines) and $\spectral{l.AFM}$ (green lines) close to the corresponding phase transition $U = 4.8t$.
     Again, we chose $V=1.2t$ for the square lattice (left column) and $V=0.8t$ for the simple cubic lattice (right column) respectively.
@@
 In the CDW phase, see panels (b) and (c), both of $\spectral{Higgs}$ and $\spectral{Phase}$ become identical and form a $\delta$ peak below the two-particle continuum.
-\textcolor{red}{In this case, both modes describe the condensation of a Cooperon, i.e., a bound state of two electrons.}
+\textcolor{red}{In this case, both modes describe the condensation of a cooperon, i.e., a bound state of two electrons.}
 Following the Landau theory for continuous phase transitions, this is to be expected as the free energy is expanded in terms of the order parameter as
@@
 Lastly, we investigate how the modes behave as the system transitions between the CDW and AFM phases.
-Similar to the previous subsection, we plot the occurring peaks in $\spectral{CDW}$ and $\spectral{AFM}$ within the respective phase in \autoref{fig:afm_cdw_peaks_overview}.
-On the right side of each panel, i.e., for $U > zV$, the system is in the AFM phase (blue shading).
+Similar to the previous subsection, we plot the occurring peaks in $\spectral{CDW}$ and $\spectral{l.AFM}$ within the respective phase in \autoref{fig:afm_cdw_peaks_overview}.
+On the right side of each panel, i.e., for $U > zV$, the system is in the AFM phase (green shading).
 On the left side, it is in the CDW phase (orange shading).
-In general, the peak in $\spectral{AFM}$ behaves exactly as the peak in $\spectral{CDW}$ if the phases are swapped.
+In general, the peak in $\spectral{l.AFM}$ behaves exactly as the peak in $\spectral{CDW}$ if the phases are swapped.
 
 The panel (a) shows the peak positions unmodified. They essentially move linearly as $U$ is varied.
-It is noteworthy, that in the AFM phase, the peak in $\spectral{AFM}$ lies lower than the one in $\spectral{CDW}$.
+It is noteworthy, that in the AFM phase, the peak in $\spectral{l.AFM}$ lies lower than the one in $\spectral{CDW}$.
 Naturally, this is reversed, if the system is in the CDW phase.
@@
 
-On the square lattice, the weights of the peaks in $\spectral{AFM}$ in the AFM phase (the same applies to $\spectral{CDW}$ in the CDW phase) grow as the system moves away from the phase transition.
+On the square lattice, the weights of the peaks in $\spectral{l.AFM}$ in the AFM phase (the same applies to $\spectral{CDW}$ in the CDW phase) grow as the system moves away from the phase transition.
 On the simple cubic lattice, however, the weights fall off very slightly.
@@
 In \autoref{fig:afm_cdw_peaks_details}, we revisit panels (b) and (c) from the previous figure.
-We restrict the analysis to $\spectral{AFM}$ in the CDW phase as the reverse case yields precisely the same data.
-This time around the scaling is double-logarithmic and we consider $U$ relative to those values at which we cannot find a peak in $\spectral{AFM}$.
-This occurs around $U_0 = 3.5755t$ on the square lattice and around $U_0 = 4.89t$ on the simple cubic lattice.
-This yields that the peak positions $\omega_0$ (a) behave quadratically as they move into the two-particle continuum,
-while their weights $W_0$ (b) drop off linearly.
+We restrict the analysis to $\spectral{l.AFM}$ in the CDW phase as the reverse case yields precisely the same data.
+This time around the scaling is double-logarithmic and we consider $U$ relative to those values at which we cannot find a peak in $\spectral{l.AFM}$.
+This occurs around $U_0 = 3.372t$ on the square lattice and around $U_0 = 4.479t$ on the simple cubic lattice.
+This yields that the peak positions $\omega_0$ (a) behave quadratically as they move into the two-particle continuum, i.e., $\omega_0 \propto (U-U_0)^2$,
+while their weights $W_0$ (b) drop off linearly, i.e., $W_0 \propto (U-U_0)$.
 
@@
 We have also developed a novel method to obtain Fourier-transformed Green's functions and analyzed various such functions. 
-We have found collective excitations within the spectral functions $\spectral{Higgs}$, $\spectral{Phase}$, $\spectral{CDW}$, and $\spectral{AFM}$ 
+We have found collective excitations within the spectral functions $\spectral{Higgs}$, $\spectral{Phase}$, $\spectral{CDW}$, $\spectral{l.AFM}$, and $\spectral{t.AFM}$ 
 and examined their behavior as the system approaches phase transitions. 
@@
 
-We observed the behavior of the peak in the SC-related spectral functions.
+We observed the behavior of the peak in the SC-related spectral functions, \textcolor{red}{corresponding to a cooperon}.
 It moves towards 0 energy and attains more weight as the system moves from the CDW phase towards the SC phase. 
@@
 
-In the SC phase close to the CDW phase, the peak in $\spectral{CDW}$ is located at a finite energy and and has a finite weight. 
-It moves towards higher energy and its weight drops off as the system moves away from the phase transition.
-
-Around the AFM-CDW phase transition, both $\spectral{AFM}$ and $\spectral{CDW}$ feature a peak. 
+In the SC phase close to the CDW phase, the peak in $\spectral{CDW}$, \textcolor{red}{corresponding to an exciton}, is located at a finite energy and and has a finite weight. 
+\textcolor{red}{It behaves in the same manner as the previously discussed peak}.
+
+Around the AFM-CDW phase transition, both $\spectral{l.AFM}$ and $\spectral{CDW}$ feature a peak. 
+\textcolor{red}{The former corresponds to a longitudinal magnon, while the latter represents an exciton.}
 The peak of the former in the AFM phase lies at lower energies than the latter one and vice-versa. 
-Moving away from the phase transition, the higher-lying peak becomes soft as it moves into the two-particle continuum. 
+Moving away from the phase transition, the higher-lying peak moves into the two-particle continuum. 
 The peak position relative to the two-particle continuum approaches $0$ quadratically with $U$, and its weight approaches $0$ linearly.
@@
 which is most likely the same as the one found close to the CDW-AFM phase transition. 
+\textcolor{red}{It is also reasonable to assume, that this peak is always located outside of the two-particle continuum, even for small values of $V$.
+In this case however, it would lie very close to the continuum, which we cannot resolve due to the limited accuracy of our numerics.
+Therefore, it appears as a singularity at $2\Delta$.}
 
@@
 
-Moreover, one can fathom including a coupling of the electronic system to the electromagnetic field.
+\textcolor{red}{Specifically for the SC related quantities, one can fathom including a coupling of the electronic system to the electromagnetic field.}
 This should move the position of the phase mode close to the plasma frequency as explained by the Anderson-Higgs mechanism.
@@
 This indicates that the peaks are $\delta$ distributions.
-The peaks of $\spectral{AFM}$ and $\spectral{CDW}$ close the the phase transition are identical when swapped, 
-i.e., $\spectral{AFM}$ in the CDW phase is the same as $\spectral{CDW}$ in the AFM phase.
+The peaks of $\spectral{l.AFM}$ and $\spectral{CDW}$ close the the phase transition are identical when swapped, 
+i.e., $\spectral{l.AFM}$ in the CDW phase is the same as $\spectral{CDW}$ in the AFM phase.
 

### 2024-03-07 paper/sc_peak_in_cdw.py
Poster

@@ -106,8 +106,8 @@ axs[1][1].set_xlabel(r"$\ln(V / t)$")
 axs[1][0].set_ylabel(r"$\ln(W_0)$")
 axs[0][0].set_ylabel(r"$\ln(\omega_0 / t)$")
 axs[1][1].legend(loc="lower right", ncol=3, columnspacing=1)
-axs[0][0].legend(handles=[fit1, fit2, div_delta], loc="lower right", bbox_to_anchor=(1.02, -0.04))
-axs[0][1].legend(handles=[data1, data2, omitted], loc="lower right", bbox_to_anchor=(1.02, -0.04))
+axs[0][0].legend(handles=[fit1, fit2, div_delta], loc="lower right", bbox_to_anchor=(1. - 0.02, 0.02))
+axs[0][1].legend(handles=[data1, data2, omitted], loc="lower right", bbox_to_anchor=(1. - 0.02, 0.02))
 #axs[0][1].legend(loc="lower right", ncol=2)
 fig.tight_layout()
 

### 2024-03-07 paper/main.tex
Poster

@@
 \textcolor{red}{It is also reasonable to assume, that this peak is always located outside of the two-particle continuum, even for small values of $V$.
-In this case however, it would lie very close to the continuum, which we cannot resolve due to the limited accuracy of our numerics.
+In this case, however, it would lie very close to the continuum, which we cannot resolve due to the limited accuracy of our numerics.
 Therefore, it appears as a singularity at $2\Delta$.}
@@
 
-\textcolor{red}{Specifically for the SC related quantities, one can fathom including a coupling of the electronic system to the electromagnetic field.}
+\textcolor{red}{Specifically for the SC-related quantities, one can fathom including a coupling of the electronic system to the electromagnetic field.}
 This should move the position of the phase mode close to the plasma frequency as explained by the Anderson-Higgs mechanism.
@@
 \begin{acknowledgments} 
-    ....
+    \textcolor{red}{This research was partially funded by the MERCUR Kooperation.
+    We would like to thank the members of our group for various useful discussions.
+    [Oder hier lieber alle mal beim Namen nennen? Ich hab mich ja mit allen mal unterhalten]
+    [Götz Seibold zu danken klingt meines Erachtens auch sinnig, mit dem hast du ja viel gesprochen.
+    Lido habe ich nicht verwendet.]}
 \end{acknowledgments}
@@
 
-Lastly, all remaining peaks below the two-particle continuum behave identical.
+Lastly, all remaining peaks below the two-particle continuum behave identically.
 The real part of each one of them behaves as $1/\omega$ in close vicinity to the peak position.
 This indicates that the peaks are $\delta$ distributions.
-The peaks of $\spectral{l.AFM}$ and $\spectral{CDW}$ close the the phase transition are identical when swapped, 
+The peaks of $\spectral{l.AFM}$ and $\spectral{CDW}$ close the phase transition are identical when swapped, 
 i.e., $\spectral{l.AFM}$ in the CDW phase is the same as $\spectral{CDW}$ in the AFM phase.

### 2024-03-12 cpp/FermionCommute/sources/Operator.hpp
uni

@@ -3,9 +3,6 @@
 #include "IndexWrapper.hpp"
 
 namespace SymbolicOperators {
-	//const std::string SpinUp = "\\uparrow";
-	//const std::string SpinDown = "\\downarrow";
-
 	struct Operator {
 		Momentum momentum;
 		// Contains all indizes, standard: first index = spin, all others arbitrary, e.g., orbitals, bands etc

### 2024-03-12 cpp/FermionCommute/sources/Coefficient.hpp
uni

@@ -11,8 +11,8 @@ namespace SymbolicOperators {
 		// if Coeff(k) = Coeff(-k)
 		bool translationalInvariance = true;
 		// if Coeff(k+Q) = -Coeff(k)
-		bool Q_changes_sign;
-		bool isDaggered;
+		bool Q_changes_sign{};
+		bool isDaggered{};
 
 		template<class Archive>
 		void serialize(Archive& ar, const unsigned int version) {

### 2024-03-12 cpp/FermionCommute/sources/WickTerm.cpp

@@ -31,7 +31,7 @@ namespace SymbolicOperators {
 			reciever_list.push_back(std::get<WickTerm>(buffer));
 			return;
 		}
-		for (size_t i = 1; i < remaining.size(); i++)
+		for (size_t i = 1U; i < remaining.size(); ++i)
 		{
 			if (std::holds_alternative<Term>(buffer)) {
 				WickTerm temp(std::get<Term>(buffer));
@@ -80,7 +80,7 @@ namespace SymbolicOperators {
 			reciever.insert(reciever.end(), buffer_list.begin(), buffer_list.end());
 		}
 
-		for (size_t i = 0; i < reciever.size();)
+		for (size_t i = 0U; i < reciever.size();)
 		{
 			if (reciever[i].handled()) {
 				++i;
@@ -102,9 +102,9 @@ namespace SymbolicOperators {
 		std::vector<WickTerm> these_copies;
 		these_copies.push_back(*this);
 
-		auto setDeltas = [&](const Operator& left, const Operator& right, bool sc_type, size_t index) {
+		auto setDeltas = [&](const Operator& left, const Operator& right, size_t index) {
 			Momentum copy_momentum = left.momentum;
-			if (sc_type) copy_momentum.flipMomentum();
+			if (left.isDaggered == right.isDaggered) copy_momentum.flipMomentum();
 
 			for (size_t k = 1U; k < left.indizes.size(); ++k)
 			{
@@ -117,7 +117,7 @@ namespace SymbolicOperators {
 			this_copy.delta_momenta.push_back(make_delta(copy_momentum, right.momentum));
 			};
 
-		for (size_t i = 0U; i < temporary_operators.size(); i += 2)
+		for (size_t i = 0U; i < temporary_operators.size(); i += 2U)
 		{
 			size_t copies_size = these_copies.size();
 			for (size_t j = 0U; j < copies_size; ++j)
@@ -138,7 +138,7 @@ namespace SymbolicOperators {
 							this_copy.delta_indizes.push_back(these_copies[j].delta_indizes.back());
 						}
 						// Due to the dagger we need to swap left and right
-						setDeltas(RIGHT, LEFT, true, j);
+						setDeltas(RIGHT, LEFT, j);
 
 						these_copies[j].operators.push_back(WickOperator(SC_Type, true, LEFT.momentum));
 						if (LEFT.indizes.size() > 1) {
@@ -159,7 +159,7 @@ namespace SymbolicOperators {
[…]

### 2024-03-15 paper/main.tex
Feierabend

@@
 
+\newcommand{\markEdited}{red}
+
 \def\hmath$#1${\texorpdfstring{{\rmfamily\textit{#1}}}{#1}}
@@
     and observe a similar excitation (cooperon) in the CDW phase which shifts towards zero energy as the system approaches the phase transition to the SC phase. 
-    \textcolor{red}{In the CDW phase, close to the phase transition to the AFM phase, 
+    \textcolor{\markEdited}{In the CDW phase, close to the phase transition to the AFM phase, 
     we find a collective mode (exciton) that does not change significantly and another mode (magnon) that moves into the two-particle continuum. 
@@
 \cite{Micnas88,Micnas88b,Micnas89,Dzierzawa92,Kostyrko92,Eriksson95,Staudt00,Onari04,Toschi05,Brackett16,Paki19,romer20,Sushchyev22}.
-\textcolor{red}{Recent studies on the dynamics of the superconducting gap parameter examined quenches, yielding oscillations \cite{Volkov73,Yuzbashyan05,Yuzbashyan06,Barankov06,Cui19}, 
+\textcolor{\markEdited}{Recent studies on the dynamics of the superconducting gap parameter examined quenches, yielding oscillations \cite{Volkov73,Yuzbashyan05,Yuzbashyan06,Barankov06,Cui19}, 
 and driven systems in the hope of inducing superconductivity \cite{Nicoletti14,Krull14,Moor14,Casandruc15,patel16,sentef17,Buenemann17}.}
@@
 In this paper, we will restrict ourselves to the half-filled Hubbard model, including an additional intersite interaction, on a square and a simple cubic lattice.
-\textcolor{red}{Specifically, we investigate competing phases, i.e., the behavior of various collective modes around phase transitions.
+\textcolor{\markEdited}{Specifically, we investigate competing phases, i.e., the behavior of various collective modes around phase transitions.
 To this end, the 2D case already provides a wide range of possible phases, including CDW, AFM, $s$- and $d_{x^2 - y^2}$-wave superconductivity, and phase-separated states \cite{Micnas88b,Tsuchiura95,Su01,Su04,ha11,Huang13,Jiang22,Linner23}.}
@@
 The prominent examples in the SC phase are the well-known phase (Anderson-Bogoliubov) and amplitude (Higgs) modes.
-\textcolor{red}{The former occurs in neutral superfluids at $0$ energy and has been found in the past \cite{Bogoljubov1958,Anderson58,Brieskorn74,Schmid1975,simanek1975,schoen1976propagating,Maiti2015,Sun2020,Fan22}.
+\textcolor{\markEdited}{The former occurs in neutral superfluids at $0$ energy and has been found in the past \cite{Bogoljubov1958,Anderson58,Brieskorn74,Schmid1975,simanek1975,schoen1976propagating,Maiti2015,Sun2020,Fan22}.
 We will obtain this mode as well based on a microscopic description that excludes long-range electromagnetic interactions.
 The inclusion of this kind of interaction would shift this mode towards the plasma frequency \cite{Anderson58,schoen1976propagating,Kulik1981}.}
-\textcolor{red}{The amplitude mode, on the other hand, is located at the lower edge of the quasiparticle continuum as it represents the energy required to form or break a Cooper pair \cite{Schmid1975,Varma02,Cea14,Measson14,Tsuji15,Krull16,Mueller2019,Schwarz20}}
+\textcolor{\markEdited}{The amplitude mode, on the other hand, is located at the lower edge of the quasiparticle continuum as it represents the energy required to form or break a Cooper pair \cite{Schmid1975,Varma02,Cea14,Measson14,Tsuji15,Krull16,Mueller2019,Schwarz20}}
 
@@
 
-\textcolor{red}{We will investigate this model for various sets of parameters allowing us access to an assortment of phases.
+\textcolor{\markEdited}{We will investigate this model for various sets of parameters allowing us access to an assortment of phases.
 Namely, the model exhibits antiferromagnetism for positive $U$ and moderately sized $V$.
@@
     as it is not accessible using our formalism.
-    \textcolor{red}{The red shading shows the region in which the dynamical matrix $\mM$, see equation \eqref{eqn:heisenberg}, has negative eigenvalues, 
+    \textcolor{\markEdited}{The red shading shows the region in which the dynamical matrix $\mM$, see equation \eqref{eqn:heisenberg}, has negative eigenvalues, 
     indicating that there are phases not captured by our methods.
@@
 
-In this article, we will be using the \textcolor{red}{symplectic product,}
+In this article, we will be using the \textcolor{\markEdited}{symplectic product,}
 \begin{equation}
@@
 
-\textcolor{red}{To treat the square and simple cubic lattice on equal footing, we utilize the fact \eqref{eqn:equal_expecs} to create our operator set in $\gamma$-space.}
+\textcolor{\markEdited}{To treat the square and simple cubic lattice on equal footing, we utilize the fact \eqref{eqn:equal_expecs} to create our operator set in $\gamma$-space.}
 It consists of operators of the type
@@
 Operators with different indices are put into the set individually, e.g., $n_{\gamma \up}$, and $n_{\gamma \down}$ are distinct operators in our set.
-\textcolor{red}{Additionally, we will include an analogous expression for
+\textcolor{\markEdited}{Additionally, we will include an analogous expression for
 \begin{equation}
@@
 A detailed explanation of the numerics is provided in the appendix \ref{sec:numerical_ieom}.
-\textcolor{red}{Computationally, our method is limited by the number of terms included in our operator set as well in the magnitude of $N_\gamma$.}
+\textcolor{\markEdited}{Computationally, our method is limited by the number of terms included in our operator set as well in the magnitude of $N_\gamma$.}
 If the gap $\Delta_\text{tot}$ is of the same order of magnitude as our discretization $\Delta \gamma$ our numerics become inaccurate.
@@
 This happens if the parameters are chosen from the striped area in \autoref{fig:phase_diagram}.
-\textcolor{red}{This issue only arises in the SC phase, nevertheless, we expect similar inaccuracies in the AFM region for small $U$.
+\textcolor{\markEdited}{This issue only arises in the SC phase, nevertheless, we expect similar inaccuracies in the AFM region for small $U$.
 However, we did not perform any computations in that region, hence this does not pose an issue to our analysis.}
@@
 Thus, if all occurring expectation values are real, both matrices have large empty blocks.
-This condition is fulfilled for all cases investigated in this article \textcolor{red}{because our model has inversion symmetry as well as time-reversal symmetry.}
+This condition is fulfilled for all cases investigated in this article \textcolor{\markEdited}{because our model has inversion symmetry as well as time-reversal symmetry.}
 
@@
 The entries of this matrix $\mathcal{G}(z)$ are the Fourier-transformed Green's functions mentioned in \eqref{eqn:standard_gf} with respect to the operators from the initially chosen set.
-\textcolor{red}{That means, if we index each operator in our set $A_i$, the matrix element $(j,i)$ of $\mathcal{G}$ is the Green's function
+\textcolor{\markEdited}{That means, if we index each operator in our set $A_i$, the matrix element $(j,i)$ of $\mathcal{G}$ is the Green's function
 \begin{align}
@@
 In the following, we will derive this relation.
-\textcolor{red}{For that, consider the Fourier-transformed Green's function above.
+\textcolor{\markEdited}{For that, consider the Fourier-transformed Green's function above.
 We rewrite both operators in the same manner as in \eqref{eqn:time_dependent_operator} to obtain
 \begin{align}
-    G_{AB^\dagger} (z) &= \im \int_0^\infty e^{\im z t} \langle [ A_i^\dagger(0), A_j(t) ] \rangle \mathrm{d}t \nonumber \\
-        &= \im \int_0^\infty e^{\im z t} \langle [ \sum_m a_{j,m}^*(0) A_m^\dagger, \sum_n a_{i,n}(t) A_n ] \rangle \mathrm{d}t \nonumber \\
-        &= \im \int_0^\infty \sum_{mn} e^{\im z t} a_{j,m}^*(0) \underbrace{\langle [ A_m^\dagger, A_n ] \rangle}_{\equiv \mN_{mn}} a_{i,n}(t) \mathrm{d}t \nonumber \\
-        &= \im \int_0^\infty e^{\im z t} \vec{a}_{j}^\dagger (0) \mN \vec{a}_{i}(t) \mathrm{d}t\,.
+    G_{A_j A_i^\dagger} (z) &= \im \int_0^\infty e^{\im z t} \langle [ A_i^\dagger(0), A_j(t) ] \rangle \mathrm{d}t \nonumber \\
+        &= \im \int_0^\infty e^{\im z t} \langle [ \sum_m a_{i,m}^*(0) A_m^\dagger, \sum_n a_{j,n}(t) A_n ] \rangle \mathrm{d}t \nonumber \\
+        &= \im \int_0^\infty \sum_{mn} e^{\im z t} a_{i,m}^*(0) \underbrace{\langle [ A_m^\dagger, A_n ] \rangle}_{\equiv \mN_{mn}} a_{j,n}(t) \mathrm{d}t \nonumber \\
+        &= \im \int_0^\infty e^{\im z t} \vec{a}_{i}^\dagger (0) \mN \vec{a}_{j}(t) \mathrm{d}t\,.
 \end{align}
@@
 \begin{equation}
-    \vec{a}_{i}(t) = \exp \left( \im \mN^{-1} \mM t \right) \vec{a}_{i}(0)\,.
+    \vec{a}_{j}(t) = \exp \left( \im \mN^{-1} \mM t \right) \vec{a}_{j}(0)\,.
 \end{equation}
@@
     \label{eqn:green_derivation}
-    G_{AB^\dagger} (z) &= \im  \int_0^\infty \vec{a}_{j}^\dagger (0) \mN \exp \left( \im \left(\mN^{-1} \mM + z \right) t \right) \vec{a}_{i}(0) \mathrm{d}t  \nonumber \\
-        &= - \vec{a}_{j}^\dagger (0) \left[ \mN \frac{1}{\mN^{-1} \mM + z} \right] \vec{a}_{i}(0) \nonumber \\
-        &= - \vec{a}_{j}^\dagger (0) \left[ \mN \frac{1}{ \underbrace{\mM + z \mN}}_{\equiv \mathcal{R}(z)} \mN \right] \vec{a}_{i}(0)\,,
-\end{align}
-where $\vec{a}_i(0)$ and $\vec{a}_j^\dagger (0)$ need to be chosen such, that $A_i = \sum_n a_{i,n} A_n$ and $A_j^\dagger = \sum_n a_{j,n}^* A_n^\dagger$ hold.
+    G_{A_j A_i^\dagger} (z) &= \im  \int_0^\infty \vec{a}_{i}^\dagger (0) \mN \exp \left( \im \left(\mN^{-1} \mM + z \right) t \right) \vec{a}_{j}(0) \mathrm{d}t  \nonumber \\
+        &= - \vec{a}_{i}^\dagger (0) \left[ \mN \frac{1}{\mN^{-1} \mM + z} \right] \vec{a}_{j}(0) \nonumber \\
+        &= - \vec{a}_{i}^\dagger (0) \left[ \mN \frac{1}{ \underbrace{\mM + z \mN}}_{\equiv \mathcal{R}(z)} \mN \right] \vec{a}_{j}(0)\,,
+\end{align}
+where $\vec{a}_j(0)$ and $\vec{a}_i^\dagger (0)$ need to be chosen such, that $A_j = \sum_n a_{j,n} A_n$ and $A_i^\dagger = \sum_n a_{i,n}^* A_n^\dagger$ hold.
 The task at hand is finding the resolvent as $\mathcal{R}$.}
 
-To do that, we embrace this matrix structure in \eqref{eqn:xp_set} and assume that all matrix entries are real \textcolor{red}{so that $\kappa_ij = \Lambda_{\pm,ij} = 0$ holds}.
+To do that, we embrace this matrix structure in \eqref{eqn:xp_set} and assume that all matrix entries are real \textcolor{\markEdited}{so that $\kappa_{ij} = \Lambda_{\pm,ij} = 0$ holds}.
 Then, with $\mathcal{R}|_X$ denoting the block of a matrix $\mathcal{R}$ corresponding to the $X$-operators, we can calculate
@@
 If $\check{N}$ has a singular part, the inverse can be replaced by the Moore-Penrose pseudo-inverse.
-\textcolor{red}{A possible way to compute this is to diagonalize $\check{N} = \mathcal{V} \mathcal{D} \mathcal{V}^\dagger$, with a diagonal matrix $\mathcal{D}$ and a unitary transformation matrix $\mathcal{V}$.
+\textcolor{\markEdited}{A possible way to compute this is to diagonalize $\check{N} = \mathcal{V} \mathcal{D} \mathcal{V}^\dagger$, with a diagonal matrix $\mathcal{D}$ and a unitary transformation matrix $\mathcal{V}$.
 Now, the pseudo-inverse can be defined as
@@
 \end{subequations}
-\textcolor{red}{where $r_X (z)$ is given in \eqref{eqn:rx} and 
+\textcolor{\markEdited}{where $r_X (z)$ is given in \eqref{eqn:rx} and 
 \begin{equation}
@@
     \includegraphics[width=.98\textwidth]{plots/resolvent_overview_V0.pdf}
-    \caption{\textcolor{red}{Same as \autoref{fig:resolvent_overview_SC}, except that we set $V=0$, i.e, SC and CDW order coexist.}
+    \caption{\textcolor{\markEdited}{Same as \autoref{fig:resolvent_overview_SC}, except that we set $V=0$, i.e, SC and CDW order coexist.}
     Since the ratio of $\Delta_\text{SC}$ to $\Delta_\text{CDW}$ may be chosen arbitrarily, we show in (a) the spectral functions for $\Delta_\text{CDW} = 0$ and in (b) for $\Delta_\text{SC} = 0$.}
@@
     \includegraphics[width=.98\textwidth]{plots/resolvent_overview_AFM_CDW.pdf}
-    \caption{\textcolor{red}{Same as \autoref{fig:resolvent_overview_SC}, except that we are now looking at the system near the AFM-CDW phase transition.
+    \caption{\textcolor{\markEdited}{Same as \autoref{fig:resolvent_overview_SC}, except that we are now looking at the system near the AFM-CDW phase transition.
     For the square lattice, we set $V=1.2t$ and for the simple cubic lattice, we set $V=0.8t$. This choice yields the phase boundary at $U=4.8t$ for both lattices.}
@@
     The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
-    \textcolor{red}{The fits are linear, i.e., $y(V) = e^d V^c$, and the parameters are printed on the individual panels.}}
+    \textcolor{\markEdited}{The fits are linear, i.e., $y(V) = e^d V^c$, and the parameters are printed on the individual panels.}}
     \label{fig:sc_in_cdw_behavior}
@@
     \includegraphics[width=.98\textwidth]{plots/cdw_peak_in_sc.pdf}
-    \caption{\textcolor{red}{Same as \autoref{fig:sc_in_cdw_behavior} but for the peak in $\spectral{CDW}$ within the SC phase, i.e., $V<0$.}}
+    \caption{\textcolor{\markEdited}{Same as \autoref{fig:sc_in_cdw_behavior} but for the peak in $\spectral{CDW}$ within the SC phase, i.e., $V<0$.}}
     \label{fig:cdw_in_sc_behavior}
@@
     \includegraphics[width=.98\textwidth]{plots/afm_cdw_peaks_overview.pdf}
-    \caption{\textcolor{red}{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ (orange lines) and $\spectral{l.AFM}$ (green lines) close to the corresponding phase transition $U = 4.8t$.
+    \caption{\textcolor{\markEdited}{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ (orange lines) and $\spectral{l.AFM}$ (green lines) close to the corresponding phase transition $U = 4.8t$.
     Again, we chose $V=1.2t$ for the square lattice (left column) and $V=0.8t$ for the simple cubic lattice (right column) respectively.
@@
 The remaining two capture the collective behavior of the CDW and AFM states, respectively.
-In the following, we will refer to the Green's functions generated by these operators as \textcolor{red}{$\mathcal{G}_{\alpha}(\omega) = G_{A_\alpha A_\alpha^\dagger}(\omega)$ 
+In the following, we will refer to the Green's functions generated by these operators as \textcolor{\markEdited}{$\mathcal{G}_{\alpha}(\omega) = G_{A_\alpha A_\alpha^\dagger}(\omega)$ 
 with $\alpha \in \{ \text{Higgs}, \text{Phase}, \text{CDW}, \text{l.AFM}, \text{t.AFM} \}$.}
@@
 Additionally, we will add a small imaginary part of $10^{-5}t$ to $\omega$ in order to visualize the occurring $\delta$ peaks.
-\textcolor{red}{Furthermore, we provide a brief analysis of the effect of choosing different numbers of discretization points $N_\gamma$ in appendix \ref{sec:finite_size}.}
+\textcolor{\markEdited}{Furthermore, we provide a brief analysis of the effect of choosing different numbers of discretization points $N_\gamma$ in appendix \ref{sec:finite_size}.}
 
@@
 In the CDW phase, see panels (b) and (c), both of $\spectral{Higgs}$ and $\spectral{Phase}$ become identical and form a $\delta$ peak below the two-particle continuum.
-\textcolor{red}{In this case, both modes describe the condensation of a cooperon, i.e., a bound state of two electrons.}
+\textcolor{\markEdited}{In this case, both modes describe the condensation of a cooperon, i.e., a bound state of two electrons.}
 Following the Landau theory for continuous phase transitions, this is to be expected as the free energy is expanded in terms of the order parameter as
@@
 In the SC phase, $\spectral{CDW}$ features a $\delta$ peak below the continuum corresponding to the finite energy necessary to excite this kind of electronic density modulation.
-\textcolor{red}{This mode corresponds to the creation of an exciton.}
+\textcolor{\markEdited}{This mode corresponds to the creation of an exciton.}
 For moderate-sized values of $V>0$, i.e., in the CDW phase, see panel (b) at $V=0.1t$, the aforementioned spectral function has a singularity at $\omega=2\Delta_\text{CDW}$.% that exhibits a square-root behavior.
-\textcolor{red}{This mode moves out of the two-particle continuum as $V$ is increased and becomes a proper $\delta$ peak, see panel (c) at $V=0.5t$.}
-
-\textcolor{red}{$\spectral{t.AFM}$ and $\spectral{l.AFM}$ are identical and restricted to the continuum for both phases and both lattices.
+\textcolor{\markEdited}{This mode moves out of the two-particle continuum as $V$ is increased and becomes a proper $\delta$ peak, see panel (c) at $V=0.5t$.}
+
+\textcolor{\markEdited}{$\spectral{t.AFM}$ and $\spectral{l.AFM}$ are identical and restricted to the continuum for both phases and both lattices.
 The former statement can be understood by the same argument why $\spectral{Phase}$ and $\spectral{Higgs}$ are identical outside of the SC phase:
@@
 This results in a purely superconducting phase with the same features as in \autoref{fig:resolvent_overview_SC} panel (a).
-\textcolor{red}{The peak in $\spectral{CDW}$ moves to $\omega=0$. In fact, $\spectral{CDW}$ and $\spectral{Phase}$ are identical.}
+\textcolor{\markEdited}{The peak in $\spectral{CDW}$ moves to $\omega=0$. In fact, $\spectral{CDW}$ and $\spectral{Phase}$ are identical.}
 
@@
 Each one of the singularities behaves as $1/\sqrt{\omega - 2 \Delta_\text{tot}}$.
-\textcolor{red}{Essentially, varying the ratio of the two gap parameters smoothly switches $\spectral{Higgs}$ and $\spectral{CDW}$.}
-
-\textcolor{red}{We associate the peak in the amplitude-related spectral functions at $\omega=0$ with this shifting of order parameters, i.e., diminishing one and increasing the other while keeping $\Delta_\text{tot}$ constant.
+\textcolor{\markEdited}{Essentially, varying the ratio of the two gap parameters smoothly switches $\spectral{Higgs}$ and $\spectral{CDW}$.}
+
+\textcolor{\markEdited}{We associate the peak in the amplitude-related spectral functions at $\omega=0$ with this shifting of order parameters, i.e., diminishing one and increasing the other while keeping $\Delta_\text{tot}$ constant.
 Specifically, in the pure SC phase, we find this peak only in $\spectral{CDW}$.
@@
 Lastly, we investigate the same spectral functions close to the AFM-CDW phase transition, depicted in \autoref{fig:resolvent_overview_AFM}.
-\textcolor{red}{We choose $V=1.2t$ for the square lattice and $V=0.8t$ for the simple cubic lattice.
+\textcolor{\markEdited}{We choose $V=1.2t$ for the square lattice and $V=0.8t$ for the simple cubic lattice.
 This yields that the phase transition is located at $U=4.8t$ for both cases. 
@@
 Using the same analysis as before, we conclude that each of these peaks is a $\delta$ peak.
-\textcolor{red}{Moving further away from the phase transition, here $U=4.8t \pm 1.4t$ in panels (c) and (d), the upper peak moves into the two-particle continuum while the other one persists.
+\textcolor{\markEdited}{Moving further away from the phase transition, here $U=4.8t \pm 1.4t$ in panels (c) and (d), the upper peak moves into the two-particle continuum while the other one persists.
 Both close and far away from the phase transition, but only in the AFM phase, $\spectral{t.AFM}$ exhibits a $\delta'$ peak at $\omega=0$.
@@
 First and foremost, the upper panels (a) and (b) depict the peak positions and weights, respectively.
-\textcolor{red}{For $|V| \ll t$, the behavior of both the weight and the position of the peak is the same as for the previously discussed peak in $\spectral{SC}$ within the CDW phase.}
-
-\textcolor{red}{Moving towards larger $|V|$, the growth of the peak position slows down, while the weights start to drop off rapidly.
+\textcolor{\markEdited}{For $|V| \ll t$, the behavior of both the weight and the position of the peak is the same as for the previously discussed peak in $\spectral{SC}$ within the CDW phase.}
+
+\textcolor{\markEdited}{Moving towards larger $|V|$, the growth of the peak position slows down, while the weights start to drop off rapidly.
 However, we are unable to compute the Green's functions for additional, even larger $|V|$ because the matrix $\mM$ is not nonnegative anymore after $V\approx -0.28t$ (square lattice) or $V\approx -0.34t$ (simple cubic lattice).
@@
 
-We observed the behavior of the peak in the SC-related spectral functions, \textcolor{red}{corresponding to a cooperon}.
+We observed the behavior of the peak in the SC-related spectral functions, \textcolor{\markEdited}{corresponding to a cooperon}.
 It moves towards 0 energy and attains more weight as the system moves from the CDW phase towards the SC phase. 
@@
 
-In the SC phase close to the CDW phase, the peak in $\spectral{CDW}$, \textcolor{red}{corresponding to an exciton}, is located at a finite energy and and has a finite weight. 
-\textcolor{red}{It behaves in the same manner as the previously discussed peak}.
+In the SC phase close to the CDW phase, the peak in $\spectral{CDW}$, \textcolor{\markEdited}{corresponding to an exciton}, is located at a finite energy and and has a finite weight. 
+\textcolor{\markEdited}{It behaves in the same manner as the previously discussed peak}.
 
 Around the AFM-CDW phase transition, both $\spectral{l.AFM}$ and $\spectral{CDW}$ feature a peak. 
-\textcolor{red}{The former corresponds to a longitudinal magnon, while the latter represents an exciton.}
+\textcolor{\markEdited}{The former corresponds to a longitudinal magnon, while the latter represents an exciton.}
 The peak of the former in the AFM phase lies at lower energies than the latter one and vice-versa. 
@@
 which is most likely the same as the one found close to the CDW-AFM phase transition. 
-\textcolor{red}{It is also reasonable to assume, that this peak is always located outside of the two-particle continuum, even for small values of $V$.
+\textcolor{\markEdited}{It is also reasonable to assume, that this peak is always located outside of the two-particle continuum, even for small values of $V$.
 In this case, however, it would lie very close to the continuum, which we cannot resolve due to the limited accuracy of our numerics.
@@
 
-\textcolor{red}{Specifically for the SC-related quantities, one can fathom including a coupling of the electronic system to the electromagnetic field.}
+\textcolor{\markEdited}{Specifically for the SC-related quantities, one can fathom including a coupling of the electronic system to the electromagnetic field.}
 This should move the position of the phase mode close to the plasma frequency as explained by the Anderson-Higgs mechanism.
@@
 \begin{acknowledgments} 
-    \textcolor{red}{This research was partially funded by the MERCUR Kooperation.
+    \textcolor{\markEdited}{This research was partially funded by the MERCUR Kooperation.
     We would like to thank the members of our group for various useful discussions.
@@
 For $\mM$ to be positive semidefinite the expression above must not be negative,
-\textcolor{red}{which has already been proven in Refs. \cite{Dyson1978,mermin66}.}
+\textcolor{\markEdited}{which has already been proven in Refs. \cite{Dyson1978,mermin66}.}
 

### 2024-03-15 cpp/FermionCommute/sources/Momentum.cpp

@@ -44,7 +44,9 @@ namespace SymbolicOperators {
 				this->momentum_list.push_back(rhs.momentum_list[i]);
 			}
 		}
-
+		this->sort();
+		if (this->momentum_list.empty()) return *this;
+		if (this->momentum_list.front().first < 0) this->flipMomentum();
 		return *this;
 	}
 	Momentum& Momentum::operator-=(const Momentum& rhs)
@@ -69,7 +71,9 @@ namespace SymbolicOperators {
 				this->momentum_list.push_back(std::make_pair(-rhs.momentum_list[i].first, rhs.momentum_list[i].second));
 			}
 		}
-
+		this->sort();
+		if (this->momentum_list.empty()) return *this;
+		if (this->momentum_list.front().first < 0) this->flipMomentum();
 		return *this;
 	}
 	void Momentum::addInPlace(const Momentum& rhs)

### 2024-03-15 cpp/FermionCommute/sources/FermionCommute.cpp
Feierabend

@@ -1,5 +1,6 @@
 #include "Term.hpp"
 #include "WickTerm.hpp"
+#include "WickOperatorTemplate.hpp"
 #include <fstream>
 #include <sstream>
 
@@ -23,6 +24,18 @@ int main(int argc, char** argv) {
 	// transversal magnon
 	const Operator c_k_Q_down_dagger('k', 1, true, SpinDown, true);
 	const Operator c_k_Q_down('k', 1, true, SpinDown, false);
+
+	if (std::strcmp(argv[1], "test") == 0) {
+		const WickOperatorTemplate sc_temp{ {IndexComparison{false, SpinDown, SpinUp}}, Momentum(), SC_Type, true };
+		WickTerm wick;
+		wick.multiplicity = 1;
+		wick.temporary_operators = { c_minus_k, c_k };
+		auto wick_results = identifyWickOperators(wick, sc_temp);
+
+		std::cout << wick_results << std::endl;
+
+		return 0;
+	}
 
 	const Term H_T(1, Coefficient("\\epsilon_0", 'q'), MomentumSum({ 'q' }), Sigma, op_vec({
 		Operator('q', 1, false, Sigma, true), Operator('q', 1, false, Sigma, false)

### 2024-03-15 cpp/FermionCommute/sources/WickTerm.hpp

@@ -1,6 +1,7 @@
 #pragma once
 #include "Term.hpp"
 #include "WickOperator.hpp"
+#include "WickOperatorTemplate.hpp"
 #include <algorithm>
 
 namespace SymbolicOperators {
@@ -8,7 +9,7 @@ namespace SymbolicOperators {
 
 	struct WickTerm
 	{
-		int multiplicity;
+		int multiplicity{};
 		std::vector<Coefficient> coefficients;
 		MomentumSum sum_momenta;
 		IndexSum sum_indizes;
@@ -33,7 +34,8 @@ namespace SymbolicOperators {
 
 		explicit WickTerm(const Term* base);
 		explicit WickTerm(const Term& base);
-		WickTerm();
+		WickTerm() = default;
+		WickTerm(const WickTerm& base, const TemplateResult::SingleResult& result);
 
 		inline bool includesType(const OperatorType operator_type) const {
 			return std::any_of(this->operators.begin(), this->operators.end(),
@@ -123,6 +125,8 @@ namespace SymbolicOperators {
 	};
 
 	void wicks_theorem(const Term& term, std::vector<WickTerm>& reciever);
+	std::vector<WickTerm> identifyWickOperators(const WickTerm& source, const WickOperatorTemplate& operator_template);
+	
 	void clearEtas(std::vector<WickTerm>& terms);
 	void cleanWicks(std::vector<WickTerm>& terms);
 

### 2024-03-18 cpp/FermionCommute/sources/WickOperatorTemplate.cpp
wip

@@ -43,8 +43,24 @@ namespace SymbolicOperators {
 		KroneckerDelta<Momentum> momentum_delta{ this->momentum_difference, momentum_diff };
 
 		std::vector<KroneckerDelta<Index>> index_delta;
+		
+		TemplateResult result(1U, this->type, left.momentum);
+ 		result.results.front().op.isDaggered = false;
+		result.momentum_delta = make_delta(this->momentum_difference, momentum_diff);
 
-		return {};
+	for (size_t i = 0U; i < indexComparison.size(); ++i)
+		{
+			if (indexComparison[i].any_identical) {
+				result.add_index_delta(make_delta(left.indizes[i], right.indizes[i]));
+			}
+			else {
+				const size_t previous_size{ result.create_branch() };
+				result.add_index_delta_range(make_delta(left.indizes[i], indexComparison[i].base), 0U, previous_size);
+				result.add_index_delta_range(make_delta(right.indizes[i], indexComparison[i].other), 0U, previous_size);
+			}
+		}
+
+		return result;
 	}
 
 	TemplateResult WickOperatorTemplate::createFromOperators(const Operator& left, const Operator& right) const {
@@ -56,6 +72,9 @@ namespace SymbolicOperators {
 
 		if (left.isDaggered == right.isDaggered)
 			return {};
+		// The input needs to be normal ordered.
+		// This means that if right is not daggered, left cannot be daggered either
+		assert(! left.isDaggered);
 		return this->_handle_num_type(left, right);
 	}
 }

### 2024-03-18 cpp/FermionCommute/sources/FermionCommute.cpp
wip

@@ -27,12 +27,16 @@ int main(int argc, char** argv) {
 
 	if (std::strcmp(argv[1], "test") == 0) {
 		const WickOperatorTemplate sc_temp{ {IndexComparison{false, SpinDown, SpinUp}}, Momentum(), SC_Type, true };
+		const WickOperatorTemplate cdw_temp{ {IndexComparison{true}}, Momentum({}, true), CDW_Type, false };
 		WickTerm wick;
 		wick.multiplicity = 1;
-		wick.temporary_operators = { c_minus_k, c_k };
+		wick.temporary_operators = { c_minus_k_Q, c_k_Q };
 		auto wick_results = identifyWickOperators(wick, sc_temp);
 
-		std::cout << wick_results << std::endl;
+		std::cout << "Pre clean:  " << wick_results << std::endl;
+		cleanWicks(wick_results);
+		std::cout << "Post clean: " << wick_results << std::endl;
+
 
 		return 0;
 	}

### 2024-03-25 cpp/FermionCommute/sources/FermionCommute.cpp
savbe

@@ -25,7 +25,40 @@ int main(int argc, char** argv) {
 	const Operator c_k_Q_down_dagger('k', 1, true, SpinDown, true);
 	const Operator c_k_Q_down('k', 1, true, SpinDown, false);
 
+	const Term H_T(1, Coefficient("\\epsilon_0", 'q'), SumContainer{ MomentumSum({ 'q' }), Sigma },
+		op_vec({
+			Operator('q', 1, false, Sigma, true), Operator('q', 1, false, Sigma, false)
+			}));
+
+	const Term H_U(1, Coefficient("\\frac{U}{N}"), MomentumSum({ 'r', 'p', 'q' }), op_vec({
+		Operator('r', 1, false, SpinUp, true), Operator('p', 1, false, SpinDown, true),
+		Operator(momentum_pairs({ std::make_pair(1, 'p'), std::make_pair(-1, 'q') }), SpinDown, false),
+		Operator(momentum_pairs({ std::make_pair(1, 'r'), std::make_pair(1, 'q') }), SpinUp, false),
+		}));
+
+	const Term H_V(1, Coefficient("\\tilde{V}", Momentum('q'), true),
+		SumContainer{ MomentumSum({ 'r', 'p', 'q' }), IndexSum({ Sigma, SigmaPrime }) },
+		op_vec({
+			Operator('r', 1, false, Sigma, true),
+			Operator('p', 1, false, SigmaPrime, true),
+			Operator(momentum_pairs({ std::make_pair(1, 'p'), std::make_pair(-1, 'q') }), SigmaPrime, false),
+			Operator(momentum_pairs({ std::make_pair(1, 'r'), std::make_pair(1, 'q') }), Sigma, false),
+			}));
+
+	const term_vec H = { H_T, H_U, H_V };//
+
+	if (argc < 2) {
+		std::cerr << "Which basis?" << std::endl;
+		return 1;
+	}
 	if (std::strcmp(argv[1], "test") == 0) {
+		term_vec commute_with_H;
+		Term base_f(1, { c_minus_k, c_k });
+		commutator(commute_with_H, H_T, base_f);
+		//cleanUp(commute_with_H);
+		std::cout << "\\begin{align*}\n\t[ H, " << toStringWithoutPrefactor({ base_f }) << " ] ="
+			<< commute_with_H << "\\end{align*}" << std::endl;
+
 		const std::vector<WickOperatorTemplate> templates = {
[…]

### 2024-03-25 cpp/FermionCommute/sources/IndexWrapper.cpp
savbe

@@ -12,10 +12,10 @@ namespace SymbolicOperators {
 			os << "\\downarrow";
 			break;
 		case Sigma:
-			os << Sigma;
+			os << "\\sigma";
 			break;
 		case SigmaPrime:
-			os << SigmaPrime;
+			os << "\\sigma'";
 			break;
 		default:
 			os << "ERROR_INDEX";

### 2024-03-25 cpp/FermionCommute/sources/Term.cpp

@@ -1,27 +1,25 @@
-#define append_vector(a, b) a.insert(a.end(), b.begin(), b.end())
-
 #include "Term.hpp"
+#include "../../Utility/sources/RangeUtility.hpp"
+//#include "KroneckerDeltaUtility.hpp"
 #include <sstream>
 
 namespace SymbolicOperators {
-	Term::Term(int _multiplicity, Coefficient _coefficient, const MomentumSum& _sum_momenta, const IndexSum& _sum_indizes, const std::vector<Operator>& _operators)
-		: coefficients(1, _coefficient), sum_momenta(_sum_momenta), sum_indizes(_sum_indizes), operators(_operators), multiplicity(_multiplicity) {}
+	Term::Term(int _multiplicity, Coefficient _coefficient, const SumContainer& _sums, const std::vector<Operator>& _operators)
+		: coefficients(1, _coefficient), sums(_sums), operators(_operators), multiplicity(_multiplicity) {}
 	Term::Term(int _multiplicity, Coefficient _coefficient, const MomentumSum& _sum_momenta, const std::vector<Operator>& _operators)
-		: coefficients(1, _coefficient), sum_momenta(_sum_momenta), operators(_operators), multiplicity(_multiplicity) {}
+		: coefficients(1, _coefficient), sums{ _sum_momenta, {} }, operators(_operators), multiplicity(_multiplicity) {}
 	Term::Term(int _multiplicity, Coefficient _coefficient, const IndexSum& _sum_indizes, const std::vector<Operator>& _operators)
-		: coefficients(1, _coefficient), sum_indizes(_sum_indizes), operators(_operators), multiplicity(_multiplicity) {}
+		: coefficients(1, _coefficient), sums{ {}, _sum_indizes }, operators(_operators), multiplicity(_multiplicity) {}
 	Term::Term(int _multiplicity, Coefficient _coefficient, const std::vector<Operator>& _operators)
 		: coefficients(1, _coefficient), operators(_operators), multiplicity(_multiplicity) {}
-	Term::Term(int _multiplicity, const MomentumSum& _sum_momenta, const IndexSum& _sum_indizes, const std::vector<Operator>& _operators)
-		: coefficients(), sum_momenta(_sum_momenta), sum_indizes(_sum_indizes), operators(_operators), multiplicity(_multiplicity) {}
[…]

### 2024-03-25 cpp/FermionCommute/sources/WickCleaner.cpp

@@ -1,15 +1,21 @@
 #include "WickTerm.hpp"
 #include <map>
+//#include "KroneckerDeltaUtility.hpp"
 
 namespace SymbolicOperators {
 	bool WickTerm::setDeltas()
 	{
+		 //remove_delta_squared(this->delta_indizes);
+		 //remove_delta_squared(this->delta_momenta);
+		 //remove_delta_is_one(this->delta_indizes);
+		 //remove_delta_is_one(this->delta_momenta);
+
 		// Erase delta_k,k etc
 		for (auto it = delta_momenta.begin(); it != delta_momenta.end();)
 		{
 			// k = k + Q can never be achieved
 			if (it->first.differsOnlyInQ(it->second)) return false;
-
+		
 			if (it->first == it->second) {
 				it = delta_momenta.erase(it);
 			}
@@ -110,7 +116,7 @@ namespace SymbolicOperators {
 				delta.second -= delta.first;
 				delta.first.momentum_list.clear();
 
-				for (auto m : sum_momenta)
+				for (auto m : sums.momenta)
 				{
 					index = delta.second.isUsed(m);
 					if (index >= 0) {
@@ -170,6 +176,12 @@ namespace SymbolicOperators {
 				}
 			}
 		}
+
+
+		//remove_delta_squared(this->delta_indizes);
+		//remove_delta_squared(this->delta_momenta);
+		//remove_delta_is_one(this->delta_indizes);
+		//remove_delta_is_one(this->delta_momenta);
 		// Remove delta^2
 		for (int i = 0; i < delta_momenta.size(); i++)
 		{
@@ -180,7 +192,7 @@ namespace SymbolicOperators {
 					--i;
 					break;
 				}
-
+		
 				auto delta_buffer = delta_momenta[j];
 				delta_buffer.first.flipMomentum();
 				delta_buffer.second.flipMomentum();
@@ -202,13 +214,13 @@ namespace SymbolicOperators {
 				}
 			}
 		}
-
+		
 		// Erase delta_k,k etc
 		for (auto it = delta_momenta.begin(); it != delta_momenta.end();)
 		{
 			// k = k + Q can never be achieved
 			if (it->first.differsOnlyInQ(it->second)) return false;
-
+		
 			if (it->first == it->second) {
 				it = delta_momenta.erase(it);
 			}
@@ -216,12 +228,14 @@ namespace SymbolicOperators {
 				++it;
 			}
 		}
+
+		//return !is_always_zero(this->delta_indizes);
[…]

### 2024-03-25 cpp/FermionCommute/sources/WickOperatorTemplate.hpp

@@ -20,9 +20,10 @@ namespace SymbolicOperators {
 			std::vector<KroneckerDelta<Index>> index_deltas;
 
 			inline void clear_delta_equals_one(){
-				std::remove_if(this->index_deltas.begin(), this->index_deltas.end(), [](const KroneckerDelta<Index>& delta){
+				auto new_end = std::remove_if(this->index_deltas.begin(), this->index_deltas.end(), [](const KroneckerDelta<Index>& delta){
 					return delta.first == delta.second;
 				});
+				this->index_deltas.erase(new_end, this->index_deltas.end());
 			};
 			inline bool contains_impossible_delta() const {
 				return std::any_of(this->index_deltas.begin(), this->index_deltas.end(), [](const KroneckerDelta<Index>& delta){
@@ -64,9 +65,10 @@ namespace SymbolicOperators {
 		}
 
 		inline void clear_impossible(){
-			std::remove_if(this->results.begin(), this->results.end(), [](const SingleResult& result){
+			auto new_end = std::remove_if(this->results.begin(), this->results.end(), [](const SingleResult& result){
 				return result.contains_impossible_delta();
 			});
+			this->results.erase(new_end, this->results.end());
 		};
 		inline void clean_up(){
 			for(auto& result : results){

### 2024-03-26 paper/main.tex
wip
savbe
Introduction

@@
 \usepackage{chronology}
-\usepackage{lipsum}
 \usepackage{amssymb}
@@
 \usepackage[normalem]{ulem}
-\usepackage{mhchem}
+%\usepackage{mhchem}
 
@@
 \newcommand{\greens}[1]{\mathcal{G}_\text{#1} (\omega)}
+\newcommand{\green}[1]{\mathcal{G}_\text{#1}}
 \newcommand{\spectral}[1]{\mathcal{A}_\text{#1}  (\omega)}
@@
 \newcommand{\markEdited}{red}
+
+\newcommand{\bs}{\begin{subequations}}
+\newcommand{\es}{\end{subequations}}
+\newcommand{\be}{\begin{equation}}
+\newcommand{\ee}{\end{equation}}
+
+\newcommand{\red}[1]{\textcolor{red}{#1}}
+\newcommand{\blue}[1]{\textcolor{blue}{#1}}
 
@@
 \begin{abstract}
-    We investigate the superconducting (SC), charge-density wave (CDW), and antiferromagnetic (AFM) phases in the extended Hubbard model at zero temperature and half-filling. 
-    We employ the iterated equations of motion approach to compute the two-particle Green's functions and their spectral densities. 
-    This renders a comprehensive analysis of the behavior of collective excitations possible as the model's parameters are changed across phase transitions. 
-    We identify the well-known amplitude (Higgs) and phase (Anderson-Bogoliubov) modes within the superconducting phase 
-    and observe a similar excitation (cooperon) in the CDW phase which shifts towards zero energy as the system approaches the phase transition to the SC phase. 
-    \textcolor{\markEdited}{In the CDW phase, close to the phase transition to the AFM phase, 
-    we find a collective mode (exciton) that does not change significantly and another mode (magnon) that moves into the two-particle continuum. 
-    In the AFM phase, we identify both longitudinal and transversal magnons.}
+    We investigate the superconducting (SC), charge-density wave (CDW), and antiferromagnetic (AFM) phases in the 
+		extended Hubbard model at zero temperature and half-filling. 
+    We employ the iterated equations of motion approach to compute the two-particle Green's functions and their
+		spectral densities. 
+    This renders a comprehensive analysis of the behavior of collective excitations possible as the 
+		model's parameters are tuned across phase transitions. 
+    We identify the well-known amplitude (Higgs) and phase (Anderson-Bogoliubov) modes within the 
+		superconducting phase and observe a similar excitation (cooperon) in the CDW phase which shifts towards 
+		zero energy as the system approaches the phase transition to the SC phase. 
+    In the CDW phase, close to the phase transition to the AFM phase, 
+    we find a collective mode, an exciton, that does not change significantly 
+    and another mode, a longitudinal magnon, that emerges from the two-particle continuum as the system approaches the phase transition to the AFM phase. 
+    \red{Habe ich geaendert - stimmt es so?} \blue{Nicht ganz, das Magnon verschwindet, wenn man weg von der Phasengrenze geht, also zu kleineren U/größeren V. 
+    Umgekehrt in der AFM phase, verschwindet das Exziton, bei dem analogen Prozess, also zu großem U/kleinen V. Des Weiteren sind beide Magnonen außerhalb der AFM Phase identisch.
+    Ist es dann richtig, hier nur von dem longitudinalen zu sprechen?}
+		In the AFM phase, we identify both a longitudinal (amplitude) and a 
+		transversal Goldstone magnon; the latter is located at zero energy.
 \end{abstract}
@@
 The study of collective excitations is of great interest as it sheds light on the intricate dynamics of correlated electron systems, providing crucial insight into emergent material properties.
-On the theoretical side, the Hubbard model has been employed in a plethora of previous studies. 
-Early studies proved the existence of eigenstates to the Hubbard Hamiltonian that exhibit off-diagonal long-range order,
-encouraging the model's usage for the description of high-temperature superconductivity \cite{yang89}.
-Shortly afterward, an exact SO(4) symmetry was discovered, which allows a degeneracy of superconductivity (SC) and a charge-density wave (CDW) governed by an attractive on-site interaction \cite{yang90}.
-This coexistence can be argued by the existence of a particle-hole transformation on bipartite lattices, 
-that maps the attractive Hubbard model exactly onto the repulsive one, exhibiting antiferromagnetism (AFM) \cite{Hirsch85}.
-The previously mentioned SC and CDW phases map to different spin operators \cite{zitko15,lieb89}.
-
-Numerous studies have investigated the phases and various quantities of the Hubbard model in equilibrium systems, including various additional interactions with and without doping.
+We are in particular interested in the behavior of the collective excitations in the vicinity of phase transitions.
+Do they signal these transitions, for instance by softening? 
+How does the competition of different phases manifest in the energies and weights of the collective excitations?
+These questions set the context of the present article.
+
+On the theoretical side, we choose a paradigmatic, but simple model which displays competing phases.
+The Hubbard model has been employed in a plethora of previous studies and competing phases are established in its extensions. 
+Early studies proved the existence of eigenstates of the Hubbard Hamiltonian that exhibit off-diagonal long-range order, encouraging the model's usage for the description of high-temperature superconductivity \cite{yang89}.
+Shortly afterward, an exact SO(4) symmetry was discovered, which induces a degeneracy of 
+superconductivity (SC) and a charge-density wave (CDW) governed by an attractive on-site interaction \cite{yang90}.
+This coexistence stems from the existence of a particle-hole transformation on bipartite lattices, 
+that maps the attractive Hubbard model rigorously onto the repulsive one, 
+exhibiting antiferromagnetism (AFM) \cite{Hirsch85}.
+The order parameters of the previously mentioned SC and CDW phases map to different spin expectation values \cite{zitko15,lieb89}.
+\blue{Den vorigen Satz verstehe ich leider gar nicht: phase = spin operator? Ja, das war ungenau. So ist es vermutlich besser?}
+
+Numerous studies investigated the phases and various quantities of the Hubbard model in equilibrium systems, including additional interactions with and without doping
 \cite{Micnas88,Micnas88b,Micnas89,Dzierzawa92,Kostyrko92,Eriksson95,Staudt00,Onari04,Toschi05,Brackett16,Paki19,romer20,Sushchyev22}. 
-\textcolor{\markEdited}{Recent studies on the dynamics of the superconducting gap parameter examined quenches, yielding oscillations \cite{Volkov73,Yuzbashyan05,Yuzbashyan06,Barankov06,Cui19}, 
-and driven systems in the hope of inducing superconductivity \cite{Nicoletti14,Krull14,Moor14,Casandruc15,patel16,sentef17,Buenemann17}.}
-
-In this paper, we will restrict ourselves to the half-filled Hubbard model, including an additional intersite interaction, on a square and a simple cubic lattice.
-\textcolor{\markEdited}{Specifically, we investigate competing phases, i.e., the behavior of various collective modes around phase transitions.
-To this end, the 2D case already provides a wide range of possible phases, including CDW, AFM, $s$- and $d_{x^2 - y^2}$-wave superconductivity, and phase-separated states \cite{Micnas88b,Tsuchiura95,Su01,Su04,ha11,Huang13,Jiang22,Linner23}.}
-We expand these well-known phase diagrams to the simple cubic lattice where we find a similar structure for CDW, AFM, and $s$-wave SC.
-
-To study this system, we will first employ a mean-field approximation to the interaction terms 
-and then use the methodology from the so-called iterated equations of motion approach (iEoM),
-which has already seen success in the handling of interaction quenches \cite{uhrig09,hamerla13,hamerla14,bleicker18}.
-Here, one commutes operators from a suitable operator basis with the Hamiltonian and adds the newly occurring terms to it.
-Naturally, a truncation is necessary for most practical applications, however, the approximation becomes better the more terms are included within the basis.
-The functionality of this method has been compared to the density matrix formalism and has proved to be considerably more accurate \cite{Kalthoff17}.
-
-Moreover, we demonstrate an explicit way to obtain various Green's functions from the aforementioned methodology.
-By extension, we also obtain the spectral functions of the investigated systems and discuss the excitations found therein.
-The prominent examples in the SC phase are the well-known phase (Anderson-Bogoliubov) and amplitude (Higgs) modes.
-\textcolor{\markEdited}{The former occurs in neutral superfluids at $0$ energy and has been found in the past \cite{Bogoljubov1958,Anderson58,Brieskorn74,Schmid1975,simanek1975,schoen1976propagating,Maiti2015,Sun2020,Fan22}.
-We will obtain this mode as well based on a microscopic description that excludes long-range electromagnetic interactions.
-The inclusion of this kind of interaction would shift this mode towards the plasma frequency \cite{Anderson58,schoen1976propagating,Kulik1981}.}
-\textcolor{\markEdited}{The amplitude mode, on the other hand, is located at the lower edge of the quasiparticle continuum as it represents the energy required to form or break a Cooper pair \cite{Schmid1975,Varma02,Cea14,Measson14,Tsuji15,Krull16,Mueller2019,Schwarz20}}
-
-The remainder of this paper is organized as follows:
-In \autoref{sec:model} we will introduce the model and its Hamiltonian as well as our mean-field theory for the ground state.
-We give a brief overview of the iterated equations of motion approach and derive a rigorous link to Green's functions in \autoref{sec:ieom}.
-Next, we show our results in \autoref{sec:results}.
-Lastly, in \autoref{sec:conclusion}, we will discuss our results.
+Recent studies on the dynamics of the superconducting gap parameter examined quenches, yielding oscillations \cite{Volkov73,Yuzbashyan05,Yuzbashyan06,Barankov06,Cui19}, 
+and driven systems motivated by the goal to induce superconductivity \cite{Nicoletti14,Krull14,Moor14,Casandruc15,patel16,sentef17,Buenemann17}.
+
+In this paper, we restrict ourselves to the half-filled Hubbard model 
+including an additional nearest neighbor, intersite interaction on the square and the simple cubic lattice at zero temperature.
+Specifically, we investigate competing phases, i.e., the behavior of various collective modes close to phase transitions between these phases.
+To this end, the case in two dimensions (2D) already displays a wide range of possible phases
+including CDW, AFM, $s$- and $d_{x^2 - y^2}$-wave superconductivity as well as 
+phase-separated states \cite{Micnas88b,Tsuchiura95,Su01,Su04,ha11,Huang13,Jiang22,Linner23}.
+We extend the corresponding established phase diagrams to the simple cubic lattice in three dimensions
+(3D) where we find a qualitatively similar phase diagran for CDW, AFM, $s$-wave SC phases, and
+indications of phase separation.
+
+First, we employ a mean-field approximation to the interaction terms to determine the phases.
+Second, we use the iterated equations of motion approach (iEoM)
+which has already seen success in the handling of interaction quenches \cite{uhrig09,hamerla13,hamerla14,bleicker18}
+to compute the collective excitations.
+The basic idea is to start in the Heisenberg picture from a suitable operator basis which is extended
+upon commuting its operators with the Hamiltonian and including the appearing additional operators to the basis. 
+Of course, a truncation is necessary for most practical applications, however, the approximation becomes better the more terms are included within the basis.
+The applicability of this method was compared successfully to the results of the density matrix formalism \cite{Kalthoff17}.
+
+Moreover, we demonstrate an explicit way to compute various Green's functions by this approach.
+By extension, the corresponding spectral functions of the investigated systems can be computed and 
+we discuss the signatures of collective excitations in the spectral functions. \blue{within these?}
+The most prominent examples in the SC phase are the well-known phase mode (Anderson-Bogoliubov) and 
+the amplitude (Higgs) modes. The former occurs in neutral superfluids at zero energy and was found
+in a large number of studies \cite{Bogoljubov1958,Anderson58,Brieskorn74,Schmid1975,simanek1975,schon76,Maiti2015,Sun2020,Fan22} which we cannot list exhaustively here.
+We obtain this mode based on a microscopic description without long-range electromagnetic interactions.
+The inclusion of this kind of interaction would shift this mode towards the plasma frequency 
+\cite{Anderson58,schon76,Kulik1981} which is, however, beyond the scope of the present 
+paper. The amplitude mode, on the other hand, is located at the lower edge of the quasiparticle continuum.
+The corresponding energy is the energy required to break up a Cooper pair 
+\cite{Schmid1975,Varma02,Cea14,Measson14,Tsuji15,Krull16,Mueller2019,Schwarz20}.
+This Higgs mode is not charged so that it does not couple to the electromagnetic fields.
+
+This paper is organized as follows:
+In \autoref{sec:model} we introduce the model and its Hamiltonian as well as the employed mean-field theory for the ground state.
+We give a brief overview of the iterated equations of motion approach and 
+derive a rigorous relation to Green's functions in \autoref{sec:ieom}.
+Next, we show and discuss results in \autoref{sec:results}.
+Lastly, in \autoref{sec:conclusion}, we summarize the results, draw the conclusions, and provide
+an outlook.
 

### 2024-03-26 paper/afm_cdw_peaks_overview.py
model

@@ -77,6 +77,7 @@ axs[0][1].set_title("Simple cubic lattice")
 for i in range(2):
     axs[0][i].text(0.87, 0.5, f"(a.{i+1})", transform = axs[0][i].transAxes)
     axs[1][i].text(0.87, 0.5, f"(b.{i+1})", transform = axs[1][i].transAxes)
+    axs[2][i].text(0.87, 0.5, f"(c.{i+1})", transform = axs[2][i].transAxes)
 
 axs[nrows-1][0].set_xlabel(r"$U [t]$")
 axs[nrows-1][1].set_xlabel(r"$U [t]$")

### 2024-03-26 paper/main.tex
model

@@
 The inclusion of this kind of interaction would shift this mode towards the plasma frequency 
-\cite{Anderson58,schon76,Kulik1981} which is, however, beyond the scope of the present 
-paper. The amplitude mode, on the other hand, is located at the lower edge of the quasiparticle continuum.
+\cite{Anderson58,schon76,Kulik1981} which is, however, beyond the scope of the present paper. 
+The amplitude mode, on the other hand, is located at the lower edge of the quasiparticle continuum.
 The corresponding energy is the energy required to break up a Cooper pair 
@@
 
-In our study, we employ the extended Hubbard model at half-filling as it encompasses the relevant phases and thereby provides direct access to the rich excitation spectra therein.
+In our study, we employ the extended Hubbard model at half-filling as it hosts
+the relevant phases and thereby provides direct access to the rich excitation spectra therein.
 Its Hamiltonian is given by
-\begin{equation}
-    \label{eqn:full_hamiltonian}
-    \begin{aligned}
+\begin{align}
+\nonumber
         H = &-t \sum_{\langle i, j \rangle, \sigma} \left( c_{i\sigma}^\dagger c_{j\sigma} + \text{h.c.} \right) 
         + \mu \sum_{i,\sigma} n_{i\sigma} \\
-        &+ U \sum_{i} n_{i\uparrow} n_{i\downarrow} 
-        + \frac{V}{2} \sum_{\langle i, j\rangle, \sigma} n_{i\sigma} n_{j\sigma}\,,
-    \end{aligned}
-\end{equation}
+        & + U \sum_{i} n_{i\uparrow} n_{i\downarrow} 
+        + \frac{V}{2} \sum_{\langle i, j\rangle, \sigma} n_{i\sigma} n_{j\sigma},
+				    \label{eqn:full_hamiltonian}
+\end{align}
 where $c_{i\sigma}^{(\dagger)}$ annihilates (creates) an electron with spin $\sigma$ on lattice site $i$ 
-and $\langle i, j\rangle$ denotes the summation over the next neighbors.
+and $\langle i, j\rangle$ denotes the summation over nearest neighbor sites.
 The parameters are the hopping amplitude $t$, the onsite interaction $U$, the intersite interaction $V$, and the chemical potential $\mu$.
-Applying a Fourier transform into $k$ space yields the single-particle dispersion 
-\begin{equation}
-    \epsilon_0 (\vk) = -2t \sum_{\alpha=1}^D \cos(k_\alpha)\,,\quad k_\alpha \in [-\pi, \pi)\,,
-\end{equation}
-with the system's dimension $D$ and the dimensionless momentum $\vk$.
-
-\textcolor{\markEdited}{We will investigate this model for various sets of parameters allowing us access to an assortment of phases.
-Namely, the model exhibits antiferromagnetism for positive $U$ and moderately sized $V$.
-At larger $V$ the intersite repulsion takes over and favors a charge-ordered phase.
-In the $U<0$ region, the same phase occurs for any $V>0$.
-Choosing $V=0$ leads to a coexistence of $s$-wave superconductivity and said CDW \cite{yang90}, while moderately sized $V<0$ yield a purely $s$-wave superconducting phase \cite{Micnas88b}.
-In this article, we will explore the AFM-CDW as well as the CDW-SC phase transitions.}
+Applying a Fourier transform passing to $k$ space yields the single-particle dispersion 
+\begin{equation}
+    \epsilon_0 (\vk) = -2t \sum_{\alpha=1}^D \cos(k_\alpha), \quad k_\alpha \in [-\pi, \pi)\,,
+\end{equation}
+with the system's dimension $D$ and the dimensionless wave vector $\vk$ where we set the lattice constant to unity.
+
+We investigate this model for various sets of parameters allowing us access to a variety of phases.
+The model exhibits antiferromagnetism for positive $U$ and moderate values of $V$.
+At larger $V$, the intersite repulsion takes over and favors a charge-ordered phase, i.e., a CDW.
+In the $U<0$ region, the CDW occurs for any $V>0$.
+Choosing $V=0$ leads to a coexistence of $s$-wave superconductivity and said CDW \cite{yang90}, while moderate
+values of  $V<0$ yield an $s$-wave superconducting phase \cite{Micnas88b}.
+In this article, we explore the AFM-CDW as well as the CDW-SC phase transitions.
+For $U<0$ and $V<0$, signs of phase separation occur as one would expect.
 
@@
 
-Next, we decouple the interaction terms.
-We define 
-\begin{equation}
+Next, we decouple the interaction terms according to Wick's theorem.
+We define short hands for the operators
+\bs
+\begin{align}
     \label{eqn:operators}
-    \begin{aligned}
         n_{k\sigma} &\coloneqq  c_{\vk\sigma}^\dagger c_{\vk\sigma}      &f_k     &\coloneqq  c_{-\vk\down} c_{\vk\up} \\
         g_{k\sigma} &\coloneqq  c_{\vk\sigma}^\dagger c_{\vk+\vQ\sigma}  &\eta_k  &\coloneqq  c_{-\vk-\vQ\down} c_{\vk\up}
-    \end{aligned}
-\end{equation}
-where $\vQ \coloneqq  (\pi, ...)$ defines the nesting vector for the CDW and AFM phases, see Ref. \cite{sentef17}.
-We use the following abbreviations to write down the mean-field parameters
+\end{align}
+\es
+where $\vQ \coloneqq  (\pi, \pi)$ in 2D and $\vQ \coloneqq  (\pi, \pi,\pi)$ in 3D
+defines the nesting vector for the CDW and AFM phases. We use the following abbreviations to write down the mean-field parameters
 \begin{subequations}
@@
         \label{eqn:delta_cdw}
-        \Delta_\text{CDW} &= \left(\frac{U}{2N} - \frac{zV}{N}\right) \sum_{\vk\sigma} \langle g_{\vk\sigma} \rangle\,, \\
+        \Delta_\text{CDW} &= \left(\frac{U}{2N} - 
+				\frac{zV}{N}\right) \sum_{\vk\sigma} \langle g_{\vk\sigma} \rangle \\
         \label{eqn:delta_afm}
-        \Delta_\text{AFM} &= \frac{U}{2N} \sum_{\vk} \left( \langle g_{k\uparrow} \rangle - \langle g_{\vk\downarrow} \rangle \right)\,, \\
-        \Delta_\text{SC} &= \frac{U}{N} \sum_{\vk} \langle f_{\vk} \rangle\,, \\
-        \Delta_\eta &= \frac{U}{N} \sum_{\vk} \langle \eta_{\vk} \rangle\,, \\
-        \Delta_n &= \frac{V}{N} \sum_{\vk,\sigma} \sum_{\alpha=1}^D \cos k_\alpha \langle n_{\vk\sigma} \rangle\,,
+        \Delta_\text{AFM} &= \frac{U}{2N} \sum_{\vk} \left( \langle g_{k\uparrow} \rangle - \langle g_{\vk\downarrow} \rangle \right), \\
+        \Delta_\text{SC} &= \frac{U}{N} \sum_{\vk} \langle f_{\vk} \rangle, \\
+        \Delta_\eta &= \frac{U}{N} \sum_{\vk} \langle \eta_{\vk} \rangle, \\
+        \Delta_n &= \frac{V}{N} \sum_{\vk,\sigma} \sum_{\alpha=1}^D \cos k_\alpha \langle n_{\vk\sigma} \rangle,
     \end{align}
@@
 where $z$ denotes the coordination number of the lattice.
-The last parameter, $\Delta_n$, renormalizes the hopping term to
+The last parameter, $\Delta_n$, renormalizes the hopping term according to 
 \begin{equation}
@@
 \end{equation}
-and 
+and the matrix
 \begin{equation}
@@
     \includegraphics[width=.48\textwidth]{plots/phase_diagram.pdf}
-    \caption{The phase diagram obtained for the extended Hubbard model on 
-    (a) a square lattice and (b) a simple cubic lattice using a mean-field approximation at temperature $T=0$.
+    \caption{The phase diagram obtained for the extended Hubbard model \eqref{eqn:full_hamiltonian} on 
+    (a) a square lattice and (b) a simple cubic lattice using a mean-field approximation at $T=0$.
     The CDW-AFM boundary lies at $U = zV$, where $z$ is the coordination number. 
-    For $U<0$ and $V=0$, there is a coexistence of CDW and $s$-wave SC.
-    The boundary for the $d_{x^2 - y^2}$-wave SC (dashed line) for the square lattice has been taken from Ref. \cite{Micnas88b}, 
-    as it is not accessible using our formalism.
-    \textcolor{\markEdited}{The red shading shows the region in which the dynamical matrix $\mM$, see equation \eqref{eqn:heisenberg}, has negative eigenvalues, 
-    indicating that there are phases not captured by our methods.
-    In accordance with the literature, we expect to find a phase-separated state \cite{Linner23}.
-    Lastly, the striped area shows the region that we cannot access because the discretization $N_\gamma$, 
-    which is required to accurately describe the system, is too large. However, we expect to find a superconducting state here.}}
+    For $U<0$ and $V=0$,  CDW and $s$-wave SC coexist.
+    The boundary for the $d_{x^2 - y^2}$-wave SC (dashed line) for the square lattice is  taken from Ref.\
+		\cite{Micnas88b} since it is not accessible within our formalism, see below.
+    However, the red shading indicates the region in which the dynamical matrix $\mM$ in 
+		Eq.\ \eqref{eqn:heisenberg}, has negative eigenvalues indicating the instability of the assumed phase.
+    In view of the attractive interactions, we expect a separation of phases \cite{Linner23}.
+    Lastly, the striped area shows the region that we cannot access numerically
+		because the gap values are too small for any tractable discretization. 
+    Yet an SC phase is expected.}
     \label{fig:phase_diagram}
@@
 
-We observe that the entire Hamiltonian and thus all expectation values only depend on
-\begin{equation}
-    \hat{\gamma}(\vk) \coloneqq \frac{1}{D} \sum_{\alpha=1}^D \cos(k_\alpha)\,,
-\end{equation}
-i.e., for any operator $\hat{O}$ the following relation holds 
+We observe that  the entire Hamiltonian and all expectation values in the considered phases only depend on
+\begin{equation}
+    \widehat{\gamma}(\vk) \coloneqq \frac{1}{D} \sum_{\alpha=1}^D \cos(k_\alpha),
+\end{equation}
+i.e., for any operator $\widehat{O}$ the following relation holds 
 \begin{equation}
     \label{eqn:equal_expecs}
-    \langle \hat{O}_{\vk} \rangle = \langle \hat{O}_{\vk'} \rangle \eqqcolon \langle \hat{O}( \gamma ) \rangle\,,
-\end{equation}
-if $\hat{\gamma}(\vk) = \hat{\gamma}(\vk')$.
-While two-dimensional systems around the size of $100\times100$ lattice sites can still be solved by using momentum sums,
+    \langle \widehat{O}_{\vk} \rangle = \langle \widehat{O}_{\vk'} \rangle \eqqcolon \langle \widehat{O}( \gamma ) \rangle\,,
+\end{equation}
+if $\gamma= \widehat{\gamma}(\vk) = \widehat{\gamma}(\vk')$.
+While 2D systems  of about $100\times100$ lattice sites can still be solved by evaluating sums over  wave vectors,
 computing solutions for large three-dimensional systems becomes impossible due to the $N=L^3$ scaling.
-This issue can be resolved by using the aforementioned fact and replacing the momentum sums with energy integrals using the bare density of states (DOS)
-\begin{equation}
-    \rho(\gamma) \coloneqq  \frac{1}{N} \sum_{\vk} \delta \left(\gamma - \hat{\gamma} (\vk) \right)\,.
+This issue can be resolved by using the aforementioned fact and replacing the wave vector sums 
+by energy integrals using the density of states (DOS) for $\gamma$ defined by
+\begin{equation}
+    \rho(\gamma) \coloneqq  \frac{1}{N} \sum_{\vk} \delta \left(\gamma - \widehat{\gamma} (\vk) \right)\,.
 \end{equation}
@@
 \end{equation}
-We will be using the exact densities of states for the square and the simple cubic lattice found in Ref. \cite{Hanisch97}.
-This allows us to access both two- and three-dimensional models on equal footing.
-We can compute any phase as long as it does not introduce another kind of momentum dependence.
+Henceforth, we use the exact DOS for the square and the simple cubic lattice provided 
+in Ref.\ \cite{Hanisch97}. 
+This allows us to access both 2D and 3D models on equal footing.
+We can compute any phase as long as it does not introduce another kind of wave vector dependence.
 
 We solve the mean-field equations self-consistently.
-The $\gamma$-integrals are approximated numerically using a $\tanh$-$\sinh$ quadrature \cite{takahasi73}, 
-terminating once $|1 - \int \dgamma \rho(\gamma)| < 10^{-13}$ and reusing the computed points and weights.
-This method excels at dealing with the singularities in the DOS, 
+The $\gamma$ integrals are approximated numerically using a $\tanh$-$\sinh$ quadrature \cite{takahasi73} 
+terminating once $|1 - \int \dgamma \rho(\gamma)| < 10^{-13}$ is achieved
+and reusing the computed sampling points and weights.
+This method excels at dealing with the singularities in the DOS 
 requiring merely a few hundred function evaluations to achieve the desired accuracy.
 
-This procedure yields the ground state phase diagram at temperature $T=0$ shown in \autoref{fig:phase_diagram}.
-The CDW-AFM boundary is located at $U = zV$, where $z$ is the coordination.
-This holds for both the square lattice ($z=4$) and the simple cubic lattice ($z=6$) and can be seen by comparing \eqref{eqn:delta_cdw} and \eqref{eqn:delta_afm}:
-Crossing the aforementioned line, changes which prefactor of the two order parameters is larger.
-
-Note, that the $d_{x^2 - y^2}$-superconducting state, which has been confirmed for the square lattice \cite{Micnas88b,Huang13}, cannot be described by our method. 
-This is due to our restriction to terms that are proportional to $\hat{\gamma}(\vk)$.
+This procedure yields the ground state phase diagram at $T=0$ shown in Fig.\ 
+\ref{fig:phase_diagram}.
+The CDW-AFM boundary is located at $U = zV$, where $z$ is the coordination number.
+This holds for both the square lattice ($z=4$) and the simple cubic lattice ($z=6$) and can be seen by comparing the prefactors in Eqs.\ \eqref{eqn:delta_cdw} and \eqref{eqn:delta_afm}:
+Crossing $U = zV$ changes which prefactor of the two order parameters is larger.
+
+Note, that the $d_{x^2 - y^2}$-superconducting state, which has been confirmed for the square lattice 
+\cite{Micnas88b,Huang13}, cannot be described by our method because it would require to 
+deal with expectations values which do not depend only on $\widehat{\gamma}(\vk)$.
 

### 2024-03-26 paper/afm_cdw_peaks_details.py

@@ -85,8 +85,6 @@ axs[0][0].text(0.89, 0.66, "(a.1)", transform = axs[0][0].transAxes)
 axs[0][1].text(0.89, 0.66, "(a.2)", transform = axs[0][1].transAxes)
 axs[1][0].text(0.89, 0.66, "(b.1)", transform = axs[1][0].transAxes)
 axs[1][1].text(0.89, 0.66, "(b.2)", transform = axs[1][1].transAxes)
-axs[2][0].text(0.89, 0.66, "(c.1)", transform = axs[1][0].transAxes)
-axs[2][1].text(0.89, 0.66, "(c.2)", transform = axs[1][1].transAxes)
 
 axs[nrows-1][0].set_xlabel(r"$\ln((U - U_0) / t)$")
 axs[nrows-1][1].set_xlabel(r"$\ln((U - U_0) / t)$")

### 2024-03-26 paper/main.tex
method + plots

@@
 
-\section{Iterated equations of motion and Green's functions}\label{sec:ieom}
-
-So far we have discussed the static mean-field equations that essentially describe the static ground state.
-These results will be used to compute the quantities, namely expectation values, necessary for the iterated equations of motion approach \cite{uhrig09,hamerla13,hamerla14,bleicker18}.
-With it, we can describe two-particle quantities like the various collective excitations of the system.
-
-We start with some operator set $\mathcal{B}$ that is complete with respect to commutation with a Hamiltonian $H$, 
-i.e., any commutator $[H, A]$ for any $A \in \mathcal{B}$ can be represented by linear combinations of operators in $\mathcal{B}$.
-We can then express any time-dependent operator from this set as
+\section{Iterated equations of motion and Green's functions}
+\label{sec:ieom}
+
+So far we discussed the static mean-field equations that describe the ground state.
+These results are used to compute the quantities, namely the expectation values, necessary for the iterated equations of motion approach \cite{uhrig09,hamerla13,hamerla14,bleicker18}.
+On this basis, we can describe two-particle quantities such as the various collective excitations of the system.
+
+We start with an operator set $\mathcal{B}$ that ideally is complete with respect to commutation with 
+the Hamiltonian $H$, i.e., any commutator $[H, A]$ for any $A \in \mathcal{B}$ can be represented by linear combinations of operators in $\mathcal{B}$.
+Then, we can express any time-dependent operator in this set by
 \begin{equation}
     \label{eqn:time_dependent_operator}
-    a(t) = \sum_j c_j(t) A_j\,,
-\end{equation}
-where $c_j(t)$ captures the entire time dependence. 
-Inserting this into the Heisenberg equation of motion and applying an operator scalar product $(A_i|\cdot)$ to both sides of the equation yields
-\begin{equation}
+    A(t) = \sum_n a_n(t) A_n,
+\end{equation}
+where the coefficients $c_j(t)$ capture the entire time dependence. 
+Inserting this into the Heisenberg equation of motion and applying a sort of operator scalar product $(A_i|\cdot)$ 
+on both sides of the equation yields
+\bs
+\begin{align}
+        \ddt A(t) = \sum_n \ddt a_n(t) A_n &= \im \sum_n a_n(t) [H, A_n] \\
+        \Rightarrow \sum_n \underbrace{(A_i | A_n)}_{\coloneqq \mN_{in}} \ddt a_n(t) &= 
+				\im \sum_n \underbrace{(A_i | [H, A_n])}_{\coloneqq \mM_{in}} a_n(t) \\
+        \Rightarrow \mN \ddt \vec{a}(t) &= \im \mM \vec{a}(t).
 				    \label{eqn:heisenberg}
-    \begin{aligned}
-        \ddt a(t) = \sum_j \ddt c_j(t) A_j &= \im \sum_j c_j(t) [H, A_j] \\
-        \Rightarrow \sum_j \underbrace{(A_i | A_j)}_{\coloneqq \mN_{ij}} \ddt c_j(t) &= \im \sum_j \underbrace{(A_i | [H, A_j])}_{\coloneqq \mM_{ij}} c_j(t) \\
-        \Rightarrow \mN \ddt \vec{c}(t) &= \im \mM \vec{c}(t)\,.
-    \end{aligned}
-\end{equation}
-The matrices $\mN$ and $\mM$ contain all the dynamics and energetic properties of the system.
-The former is referred to as a dynamical matrix while the latter is called a norm matrix.
-The advantage is that one can now handle simple matrices rather than operators acting on an enormous Hilbert space.
-The size of these matrices depends entirely on the set of operators.
-
-The matrix $\mM$ is positive semidefinite if the system is in thermal equilibrium.
-We prove this statement in the appendix \ref{sec:positive_M}.
-We can use this fact to further enhance our ground state phase diagram.
-If $\mM$ has even a single negative eigenvalue for any combination of parameters, we know that the system is not in thermal equilibrium, 
-i.e., our self-consistency did not capture the correct ground state phase.
-This does in fact happen for certain $U<0$ and $V<0$, see the orange shading in \autoref{fig:phase_diagram}.
-For finite temperatures, on a square lattice, a phase-separated state as well as the coexistence of a phase-separated state with $s$-wave superconductivity has been found in this region \cite{Linner23}.
-The phase boundary that we propose here is qualitatively in good agreement with the one found in the aforementioned reference.
-We expect a similar set of phases to be present on the simple cubic lattice but cannot prove this statement at this point.
-
-Additionally, note that while the existence of a negative eigenvalue of $\mM$ proves that the system is not in thermal equilibrium, the absence of one does not prove the contrary.
-For example, we do not find any negative eigenvalues of $\mM$ in the $U>0$, $V<0$ region despite previous studies finding $d_{x^2 - y^2}$-wave superconductivity there \cite{Micnas88b,Huang13}.
-
-However, most Hamiltonians do not allow any such operator set to exist as the commutation usually introduces terms of higher order.
-For instance, commuting a bilinear term with a quartic Hamiltonian yields, quartic terms. Repeating the commutation yields hexartic ones and so on.
-Therefore, one repeats this commutation process and includes the occurring terms within a bigger set,
-hoping to get better results as the set size increases.
-
-In this article, we will be using the \textcolor{\markEdited}{symplectic product,}
+\end{align}
+\es
+where $\vec{a}:=(a_1, a_2, a_3,\ldots)^\top$.
+The matrices $\mN$ and $\mM$ contain all the energetic and dynamic properties of the system.
+The former is referred to as norm matrix while the latter is called the dynamic matrix.
+The advantage is that one can now handle simple matrices rather than operators 
+acting on an enormous Hilbert space.
+The dimension of these matrices depends on the number of operators in the set $\mathcal{B}$.
+
+The dynamical matrix $\mM$ is positive semidefinite if the system is in thermal equilibrium.
+We derive this statement in  App.\ \ref{sec:positive_M}.
+We use this fact to further enhance our ground state phase diagram.
+If $\mM$ has even a single negative eigenvalue for a combination of parameters, 
+we know that the assumed phase does not represent a true ground state.
+Physically, this means that there are ``excitations'' which in fact lower the energy. 
+Thus, the assumed ground state is not the lowest state and therefore unstable.
+This happens for certain values $U<0$ and $V<0$, see the red shading in Fig.\ \ref{fig:phase_diagram}.
+For finite temperatures on the square lattice, a phase-separated state as well as the coexistence of a phase-separated state with $s$-wave superconductivity has been found in this region \cite{Linner23}.
+The phase boundary that we propose here agrees qualitatively well with the one found in the aforementioned reference.
+We expect a similar set of phases to be present on the simple cubic lattice. \red{This is indicated by
+the negative eigenvalues of the corresponding dynamical matrix.
+Stimmt das so, Joshua?} \blue{ja.
+Ich überlege gerade, ob dieser Absatz evtl.
+mehr Sinn nach dem Einführen des symplektischen Produktes hat?}
+
+While the existence of a negative eigenvalue of $\mM$ proves that the assumed phase is
+not in thermal equilibrium, the absence of negative eigenvalues does not imply absolute stability,
+but only local stability with respect to the considered operators.
+For example, we do not find any negative eigenvalues of $\mM$ in the $U>0$, $V<0$ region despite previous studies indicating $d_{x^2 - y^2}$-wave superconductivity \cite{Micnas88b,Huang13}.
+
+In practice, however, generic Hamiltonians do not allow for
+a complete operator set $\mathcal{B}$ to exist because the commutations usually introduce terms which are not 
+yet in $\mathcal{B}$, e.g., because they are of higher order.
+For instance, commuting a bilinear term with a quartic Hamiltonian yields quartic terms. 
+Iterating the commutation yields hexatic ones and so on.
+One can include such additional terms and generically the results will improve the more
+terms are considered in $\mathcal{B}$. In practice, one has to restrict the operators
+to a suitable class of terms, thereby truncating certain terms. Here, we will restrict ourselves
+to bilinear operators to capture the leading effects of collective behavior.
+
+Furthermore, we use the symplectic product as operator product
 \begin{equation}
@@
 \end{equation}
-where the expectation values are taken with respect to the thermal equilibrium of the mean-field Hamiltonian \eqref{eqn:mf_hamiltonian}.
-Note, that this is not a proper scalar product, as a norm defined using it can also be negative.
-For example, assume that for some operator $A$
-\begin{equation}
-    ||A|| = (A | A) = \langle [A^\dagger, A] \rangle > 0\,,
+where the expectation values are taken with respect to the assumed phase of the mean-field Hamiltonian 
+\eqref{eqn:mf_hamiltonian}.
+Note that this is not a proper scalar product since it is not positive semidefinite.
+For example, let us assume that for some operator $A$
+\bs
+\begin{equation}
+(A | A) = \langle [A^\dagger, A] \rangle > 0,
 \end{equation}
@@
 \begin{equation}
-    ||A^\dagger|| = (A^\dagger | A^\dagger) = \langle [A, A^\dagger] \rangle = - ||A|| < 0\,.
-\end{equation}
-Nevertheless, this does not pose any issue in our calculations.
-We will compute $\mM$ by commutating with the full Hubbard Hamiltonian \eqref{eqn:full_hamiltonian} enabling us to capture collective behavior rather than the one particle dynamics given by the mean-field approximation.
-
-\textcolor{\markEdited}{To treat the square and simple cubic lattice on equal footing, we utilize the fact \eqref{eqn:equal_expecs} to create our operator set in $\gamma$-space.}
-It consists of operators of the type
+(A^\dagger | A^\dagger) = \langle [A, A^\dagger] \rangle = - (A | A)  < 0.
+\end{equation}
+\es
+This does not pose a serious issue in our calculations but must be kept in mind.
+In particular, it implies that the norm matrix is \emph{not positive} as one might have expected.
+We emphasize, that the dynamical matrix  $\mM$ is computed
+by commuting with the \emph{full} Hubbard Hamiltonian \eqref{eqn:full_hamiltonian} 
+enabling us to capture collective behavior 
+rather than using only the mean-field Hamiltonian \eqref{eqn:mf_hamiltonian}
+which captures the one-particle dynamics, but misses
+the two-body dynamics.
+
+In order to treat the square and the simple cubic lattice on equal footing, we exploit 
+\eqref{eqn:equal_expecs} to define the operator set in $\gamma$ space
 \begin{equation}
     \label{eqn:ieom_basis_operator}
-    A_\gamma \coloneqq \frac{1}{\sqrt{N}} \sum_{\vk} \delta (\gamma - \hat{\gamma}( \vk )) A_{\vk}\,,
-\end{equation}
-where $A_{\vk}$ represents each type of operator in \eqref{eqn:operators} and their Hermitian conjugates.
-Operators with different indices are put into the set individually, e.g., $n_{\gamma \up}$, and $n_{\gamma \down}$ are distinct operators in our set.
-\textcolor{\markEdited}{Additionally, we will include an analogous expression for
+    A_\gamma \coloneqq \frac{1}{\sqrt{N}} \sum_{\vk} \delta (\gamma - \widehat{\gamma}( \vk )) A_{\vk},
+\end{equation}
+where $A_{\vk}$ represents each type of operator defined in Eqs.~\eqref{eqn:operators} or
+their Hermitian conjugates if the operators are not Hermitian themselves.
+Operators with different indices are treated separately, e.g., $n_{\gamma \up}$ and $n_{\gamma \down}$ 
+are distinct operators in the studied set $\mathcal{B}$.
+Additionally, we consider an analogous expression for the operator
 \begin{equation}
@@
 and its Hermitian conjugate.
-This will allow us to describe transversal magnons later on.}
-
-Naturally, we have to discretize $\gamma$, 
-however, this allows us to obtain good results with drastically smaller matrices compared to a momentum-based operator set and obtain results for a three-dimensional system in the first place.
-Practically, we choose $N_\gamma = 6000$ equally spaced discretization points.
-A detailed explanation of the numerics is provided in the appendix \ref{sec:numerical_ieom}.
-\textcolor{\markEdited}{Computationally, our method is limited by the number of terms included in our operator set as well in the magnitude of $N_\gamma$.}
-If the gap $\Delta_\text{tot}$ is of the same order of magnitude as our discretization $\Delta \gamma$ our numerics become inaccurate.
-This manifests specifically if a spectral function has strong features at minuscule energies, e.g., the phase mode in the superconducting phase.
-In this case, the dynamical matrix $\mM$ picks up negative eigenvalues that vanish if $N_\gamma$ is increased so that $\Delta \gamma$ is sufficiently smaller than $\Delta_\text{tot}$.
-This happens if the parameters are chosen from the striped area in \autoref{fig:phase_diagram}.
-\textcolor{\markEdited}{This issue only arises in the SC phase, nevertheless, we expect similar inaccuracies in the AFM region for small $U$.
-However, we did not perform any computations in that region, hence this does not pose an issue to our analysis.}
-
-Next, we order these operators in a way reminiscent of the $x$- and $p$-terms in the harmonic oscillator, i.e.,
-\begin{equation}
-    X_i \coloneqq  A_i + A_i^\dagger\,,\quad P_i \coloneqq  A_i - A_i^\dagger\,.
-\end{equation}
-Then, our set is given by $\mathcal{B}_{XP} \coloneqq \{ X_i, \ldots, P_i, \ldots \}$.
-If some operators would be 0 ($P_i$ for any Hermitian term) or duplicates (certain $X_i$ for $g$-type terms, e.g, $g_{k\sigma} = g_{k+Q\sigma}^\dagger$), we omit them.
-
-Due to this choice of set, the matrices occurring in \eqref{eqn:heisenberg} have a special block structure
+This will allow us to describe transversal magnons, i.e., perpendicular 
+deviations from the staggered magnetization in the AFM phase.
+
+For the numerical treatment, we have to discretize $\gamma$.
+Still, this allows us to obtain accurate results with drastically smaller matrices 
+compared to an operator set based on a discretization of wave vectors.
+This is crucial for dealing with three-dimensional lattices.
+Practically, we choose $N_\gamma = 6000$ equally spaced sampling points.
+A detailed explanation of the numerics is provided in the App.\ \ref{sec:numerical_ieom}.
+Computationally, our method is limited by the number of terms included in our operator set 
+as well as by the value of $N_\gamma$.
+If the gap $\Delta_\text{tot}$ is of the same order of magnitude as the discretization $t \Delta \gamma$ the numerics become inaccurate.
+This manifests specifically if a spectral function has strong features at minute energies, e.g., 
+the phase mode in the superconducting phase.
+In this case, the dynamical matrix $\mM$ spuriously displays negative eigenvalues that vanish if 
+$N_\gamma$ is increased so that $\Delta \gamma$ is sufficiently smaller than $\Delta_\text{tot}$.
+This happens if the parameters are chosen from the striped region in Fig.\ \ref{fig:phase_diagram}.
+We observe that this issue only arises in the SC phase;
+nevertheless, we expect similar inaccuracies in the AFM region for small values of $U$.
+
+In the next step, we rearrange these operators in a way reminiscent of the $x$ and $p$ operators
+of a harmonic oscillator
+\begin{equation}
+    X_i \coloneqq  A_i + A_i^\dagger\,,\quad P_i \coloneqq  A_i - A_i^\dagger.
+\end{equation}
+Then, the studied operator set is given by $\mathcal{B}_{XP} \coloneqq \{ X_i, \ldots, P_i, \ldots \}$.
+If some operators would be 0, e.g., $P_i$ for any Hermitian $A_i$, or duplicate, e.g., certain $X_i$ for $g$-type terms where $g_{k\sigma} = g_{k+Q\sigma}^\dagger$, we omit these redundant operators.
+
+Due to this particular choice of operators, the matrices occurring in \eqref{eqn:heisenberg} acquire a block structure
 \begin{equation}
@@
         \Lambda_+ & \mathcal{L} \\ \mathcal{L}^\dagger & \Lambda_-
-    \end{pmatrix}\,,
-\end{equation}
-where the upper block refers to all $X_i$ and the lower block to all $P_i$.
+    \end{pmatrix},
+\end{equation}
+where the upper block refers to all $X_i$ operators and the lower block to all $P_i$ operators.
 Furthermore, due to symmetry, the relations $\Im [\mathcal{K}_\pm] = \Re [\kappa] = 0$ and $\Re [\Lambda_\pm] = \Im [\mathcal{L}] = 0$ hold.
-Thus, if all occurring expectation values are real, both matrices have large empty blocks.
-This condition is fulfilled for all cases investigated in this article \textcolor{\markEdited}{because our model has inversion symmetry as well as time-reversal symmetry.}
-
-To study the collective excitations, we investigate various retarded Green's functions 
+Since the mean-field Hamiltonian is real, all ensuing expectation values are real
+and we can conclude both matrices have large empty blocks with zero elements: $\kappa=0$ and $\Lambda_\pm=0$.
+This condition is fulfilled for all cases investigated in this article because the model displays
+inversion symmetry and time-reversal symmetry \red{or at least the combination of both in the AFM phase}.
+
+To study the collective excitations quantitatively, we investigate various retarded Green's functions 
+\bs
 \begin{equation}
@@
 \end{equation}
-and their Fourier-transformed
+where $\Theta(t)$ is the Heaviside function and their Fourier transforms
 \begin{equation}
     \label{eqn:standard_gf}
-    G_{AB}(z = \omega + \im 0^+) = -\im \int_0^{\infty} e^{\im z t} \langle [A(t), B] \rangle \mathrm{d}t\,,
-\end{equation}
-where $\Theta(t)$ is the Heaviside function.
-Our previous choice of pseudo scalar product enables us to write down a matrix-valued Green's functions in terms of the aforementioned matrices
+    G_{AB}(z = \omega + \im 0^+) = -\im \int_0^{\infty} e^{\im z t} \langle [A(t), B] \rangle \mathrm{d}t.
+\end{equation}
+\es
+The choice of the symplectic operator product enables us to write down the
+matrix-valued Green's functions in terms of the introduced norm and dynamical matrix
+\bs
 \begin{align}
@@
     \mathcal{G}(z &= \omega + \im 0^+) = \mN \frac{1}{-z \mN - \mM} \mN \\
-        &\coloneqq  -\mN \mathcal{R}(z) \mN\,,
-\end{align}
-where we used the resolvent
+        &\coloneqq  -\mN \mathcal{R}(z) \mN,
+\end{align}
+where we introduced the resolvent
 \begin{equation}
     \label{eqn:resolvent}
-    \mathcal{R}(z) \coloneqq  \frac{1}{z \mN + \mM}\,.
-\end{equation}
-The entries of this matrix $\mathcal{G}(z)$ are the Fourier-transformed Green's functions mentioned in \eqref{eqn:standard_gf} with respect to the operators from the initially chosen set.
-\textcolor{\markEdited}{That means, if we index each operator in our set $A_i$, the matrix element $(j,i)$ of $\mathcal{G}$ is the Green's function
-\begin{align}
-    \mathcal{G}_{ji}(z = \omega +\im 0^+) &=  G_{A_j A_i^\dagger} (z) \nonumber \\
-        &= -\im \int_0^{\infty} \langle [A_j(t), A_i^\dagger(0)] \rangle e^{\im z t} \mathrm{d}t\,.
-\end{align}}
-
-In the following, we will derive this relation.
-\textcolor{\markEdited}{For that, consider the Fourier-transformed Green's function above.
-We rewrite both operators in the same manner as in \eqref{eqn:time_dependent_operator} to obtain
-\begin{align}
-    G_{A_j A_i^\dagger} (z) &= \im \int_0^\infty e^{\im z t} \langle [ A_i^\dagger(0), A_j(t) ] \rangle \mathrm{d}t \nonumber \\
-        &= \im \int_0^\infty e^{\im z t} \langle [ \sum_m a_{i,m}^*(0) A_m^\dagger, \sum_n a_{j,n}(t) A_n ] \rangle \mathrm{d}t \nonumber \\
-        &= \im \int_0^\infty \sum_{mn} e^{\im z t} a_{i,m}^*(0) \underbrace{\langle [ A_m^\dagger, A_n ] \rangle}_{\equiv \mN_{mn}} a_{j,n}(t) \mathrm{d}t \nonumber \\
-        &= \im \int_0^\infty e^{\im z t} \vec{a}_{i}^\dagger (0) \mN \vec{a}_{j}(t) \mathrm{d}t\,.
-\end{align}
-Furthermore, assuming, that $\mN$ is invertible, we can easily solve the differential equation \eqref{eqn:heisenberg} to obtain
-\begin{equation}
-    \vec{a}_{j}(t) = \exp \left( \im \mN^{-1} \mM t \right) \vec{a}_{j}(0)\,.
-\end{equation}
-This allows us to finally obtain
+    \mathcal{R}(z) \coloneqq  \frac{1}{z \mN + \mM}.
+\end{equation}
+\es
+The entries of this matrix $\mathcal{G}(z)$ are the Fourier-transformed Green's functions given in 
+\eqref{eqn:standard_gf} with respect to the studied operators. For simplicity, we formulate the
+relation between the Green's functions and the matrices for the operators $A_j$. Eventually, we 
+use the block representation resulting for the operators $X_i$ and $P_i$. \red{Wird das klar?}
+The matrix element $(j,i)$ refers to
+\bs
+\begin{align}
+    \mathcal{G}_{ji}(z = \omega +\im 0^+) &=  G_{A_j A_i^\dagger} (z) \\
+        &= -\im \int_0^{\infty} \langle [A_j(t), A_i^\dagger(0)] \rangle e^{\im z t} \mathrm{d}t.
+\end{align}
+\es
+
+Performing the  Fourier transformation yields
+\bs
+\begin{align}
+    G_{A_j A_i^\dagger} (z) &= \im \int_0^\infty e^{\im z t} \langle [ A_i^\dagger(0), A_j(t) ] \rangle \mathrm{d}t \
+		\\
+        &= \im \int_0^\infty e^{\im z t} 
+				\langle [ \sum_m a_{i,m}^*(0) A_m^\dagger, \sum_n a_{j,n}(t) A_n ] \rangle \mathrm{d}t 
+		\\
+        &= \im \int_0^\infty \sum_{mn} e^{\im z t} a_{i,m}^*(0) \underbrace{\langle [ A_m^\dagger, A_n ] \rangle}_{\equiv \mN_{mn}} a_{j,n}(t) \mathrm{d}t 
+    \\
+        &= \im \int_0^\infty e^{\im z t} \vec{a}_{i}^\dagger (0) \mN \vec{a}_{j}(t) \mathrm{d}t,
+\end{align}
+\es
+where $\vec{a}_j(0)$ and $\vec{a}_i^\dagger (0)$ embody the initial conditions $A_j = \sum_n a_{j,n} A_n$ 
+and $A_i^\dagger = \sum_n a_{i,n}^* A_n^\dagger$.
+Assuming that $\mN$ is invertible we solve the differential equation \eqref{eqn:heisenberg} 
+\begin{equation}
+    \vec{a}_{j}(t) = \exp \left( \im \mN^{-1} \mM t \right) \vec{a}_{j}(0).
+\end{equation}
+Then, the final result reads
+\bs
 \begin{align}
     \label{eqn:green_derivation}
-    G_{A_j A_i^\dagger} (z) &= \im  \int_0^\infty \vec{a}_{i}^\dagger (0) \mN \exp \left( \im \left(\mN^{-1} \mM + z \right) t \right) \vec{a}_{j}(0) \mathrm{d}t  \nonumber \\
-        &= - \vec{a}_{i}^\dagger (0) \left[ \mN \frac{1}{\mN^{-1} \mM + z} \right] \vec{a}_{j}(0) \nonumber \\
-        &= - \vec{a}_{i}^\dagger (0) \left[ \mN \frac{1}{ \underbrace{\mM + z \mN}}_{\equiv \mathcal{R}(z)} \mN \right] \vec{a}_{j}(0)\,,
-\end{align}
-where $\vec{a}_j(0)$ and $\vec{a}_i^\dagger (0)$ need to be chosen such, that $A_j = \sum_n a_{j,n} A_n$ and $A_i^\dagger = \sum_n a_{i,n}^* A_n^\dagger$ hold.
-The task at hand is finding the resolvent as $\mathcal{R}$.}
-
-To do that, we embrace this matrix structure in \eqref{eqn:xp_set} and assume that all matrix entries are real \textcolor{\markEdited}{so that $\kappa_{ij} = \Lambda_{\pm,ij} = 0$ holds}.
-Then, with $\mathcal{R}|_X$ denoting the block of a matrix $\mathcal{R}$ corresponding to the $X$-operators, we can calculate
-\begin{align}
-    r_X (z) &\coloneqq \mathcal{R}(z)|_X = \left. \frac{1}{\mM + z \mN} \right\vert_X \nonumber \\
-        &= \left[ \frac{1}{\mM} - \frac{1}{\mM} z \mN \frac{1}{\mM} + \frac{1}{\mM} z \mN \frac{1}{\mM} z \mN \frac{1}{\mM} - \cdots \right]_X \nonumber \\
-        &= \left. \frac{1}{\mM} \sum_{j=0}^\infty \left( -z \mN \frac{1}{\mM} \right)^j \right\vert_X \,.
-\end{align}
-We may omit every second element of the sum, as we want to obtain the upper left block of the matrix, and $\mN$ always swaps the upper left and lower right block.
-Thus, we obtain
-\begin{align}
-    r_X (z) &= \left. \frac{1}{\mM} \sum_{j=0}^\infty z^{2j} \left( \mN \frac{1}{\mM} \right)^{2j} \right\vert_X \nonumber \\
-        &= \left. \frac{1}{\mM - z^2 \mN \mM^{-1} \mN} \right\vert_X \nonumber \\
-        &= \frac{1}{\mathcal{K}_+ - z^2 \mathcal{L} \mathcal{K}_-^{-1} \mathcal{L}^\dagger}\,.
-\end{align}
-Next, we define $\check{N} \coloneqq \mathcal{L} \mathcal{K}_-^{-1} \mathcal{L}^\dagger$ for brevity.
-Since $\mathcal{M}$ is positive semidefinite and block diagonal, its blocks $\mathcal{K}_\pm$ must be positive semidefinite as well.
-Therefore, $\check{N}$ is also positive semidefinite and we can define its square root.
-We obtain
+    G_{A_j A_i^\dagger} (z) &= \im  \int_0^\infty \vec{a}_{i}^\dagger (0) \mN 
+		\exp \left( \im \left(\mN^{-1} \mM + z \right) t \right) \vec{a}_{j}(0) \mathrm{d}t 
+		\\
+        &= - \vec{a}_{i}^\dagger (0) \left[ \mN \frac{1}{\mN^{-1} \mM + z} \right] \vec{a}_{j}(0) 
+				\\
+        &= - \vec{a}_{i}^\dagger (0) \left[ 
+				\mN \mathcal{R}(z) \mN \right] \vec{a}_{j}(0)
+\end{align}
+\es
+with the resolvent $\mathcal{R}(z)$ from \eqref{eqn:resolvent}.
+Obviously, the key task is computing the resolvent $\mathcal{R}$ efficiently.
+
+To this end, we exploit the matrix structure in \eqref{eqn:xp_set} and assume that all matrix entries are real so that $\kappa_{ij} = \Lambda_{\pm,ij} = 0$ holds. \red{Stimmt das so?}
+Then, with $r_X(z)\coloneqq\mathcal{R}|_{XX}$ denoting the upper left block of a matrix $\mathcal{R}$ which 
+refers to the $X$-operators, we can calculate
+\bs
+\begin{align}
+    r_X (z) & = \left. \frac{1}{\mM + z \mN} \right\vert_{XX} \\
+        &= \left[ \frac{1}{\mM} - \frac{1}{\mM} z \mN \frac{1}{\mM} + 
+				\frac{1}{\mM} z \mN \frac{1}{\mM} z \mN \frac{1}{\mM} - \cdots \right]_{XX}  \\
+        &= \left. \frac{1}{\mM} \sum_{j=0}^\infty \left( -z \mN \frac{1}{\mM} \right)^j \right\vert_{XX} .
+\end{align}
+\es
+We can safely omit every second term of the sum since we want to obtain the upper left block of the matrix only
+and $\mN$ always swaps between the upper left and lower right block. Thus, we obtain
+\bs
+\begin{align}
+    r_X (z) &= \left. \frac{1}{\mM} \sum_{j=0}^\infty z^{2j} \left( \mN \frac{1}{\mM} \right)^{2j} \right\vert_{XX} 
+		\\
+        &= \left. \frac{1}{\mM - z^2 \mN \mM^{-1} \mN} \right\vert_{XX} 
+				\\
+        &= \frac{1}{\mathcal{K}_+ - z^2 \mathcal{L} \mathcal{K}_-^{-1} \mathcal{L}^\dagger}.
+\end{align}
+\es
+For brevity, we define $\check{N}_X \coloneqq \mathcal{L} \mathcal{K}_-^{-1} \mathcal{L}^\dagger$.
+Since $\mathcal{M}$ is positive semidefinite and block diagonal its blocks $\mathcal{K}_\pm$ are positive semidefinite as well.
+Therefore, $\check{N}_X$ is also positive semidefinite and Hermitian so that its square root can be defined.
+Then, the resolvent $r_X(z)$ can be expressed by
 \begin{equation}
     \label{eqn:rx}
-    r_X (z) = -\check{N}^{-1/2} \frac{1}{z^2 - \check{N}^{-1/2} \mathcal{K}_+ \check{N}^{-1/2}} \check{N}^{-1/2}\,.
-\end{equation}
-The matrix $\check{M} \coloneqq \check{N}^{-1/2} \mathcal{K}_+ \check{N}^{-1/2}$ is positive semidefinite and Hermitian by the previous arguments.
-If $\check{N}$ has a singular part, the inverse can be replaced by the Moore-Penrose pseudo-inverse.
-\textcolor{\markEdited}{A possible way to compute this is to diagonalize $\check{N} = \mathcal{V} \mathcal{D} \mathcal{V}^\dagger$, with a diagonal matrix $\mathcal{D}$ and a unitary transformation matrix $\mathcal{V}$.
-Now, the pseudo-inverse can be defined as
-\begin{equation}
-    \check{N}^+ \coloneqq \mathcal{V} \mathcal{D}^+ \mathcal{V}^\dagger
-\end{equation}
-with
-\begin{equation}
-    (\mathcal{D}^+)_{ij} = \begin{cases}
+    r_X (z) = -\check{N}_X^{-1/2} \frac{1}{z^2 - \check{N}_X^{-1/2} \mathcal{K}_+ \check{N}_X^{-1/2}} 
+		\check{N}_X^{-1/2},
+\end{equation}
+where the matrix $\check{M}_X \coloneqq \check{N}_X^{-1/2} \mathcal{K}_+ \check{N}_X^{-1/2}$ is used; it is
+positive semidefinite and Hermitian by the previous arguments.
+
+If $\check{N}_X$ has a singular part, for instance, due to numerical inaccuracies \blue{Das kann auch völlig analytisch auftreten}, the inverse can be replaced by the Moore-Penrose pseudo-inverse. 
+A possible way to compute this inverse is to diagonalize 
+$\check{N}_X = \mathcal{V} \mathcal{D} \mathcal{V}^\dagger$ yielding a diagonal matrix $\mathcal{D}$ and a unitary transformation matrix $\mathcal{V}$. 
+Then, the pseudo-inverse can be defined by
+\begin{equation}
+    \check{N}^{-1} \coloneqq \mathcal{V} \mathcal{D}^{-1} \mathcal{V}^\dagger
+\end{equation}
+with \red{Ich habe das hoch + in ein hoch -1 geaendert, weil mir das "`+"' zu sehr an Transposition erinnerte.}
+\begin{equation}
+    (\mathcal{D}^{-1})_{ij} = \begin{cases}
         1/\mathcal{D}_{ij} & \mathcal{D}_{ij} \neq 0 \\ 0 & \text{otherwise}
-    \end{cases}\,.
-\end{equation}
-Note, that this definition yields the standard inverse for invertible matrices.}
-
-The same calculation can be repeated by exchanging $X$ with $P$, yielding the relation for the remaining block.
-Then, the definitions of the matrices above change in the following way
-\begin{equation}
-    \check{N}_P \coloneqq \mathcal{L}^\dagger \mathcal{K}_+^{-1} \mathcal{L}\,,\quad \check{M}_P \coloneqq \check{N}_P^{-1/2} \mathcal{K}_- \check{N}_P^{-1/2}\,.
-\end{equation}
-In conclusion, the Green's function is given by
+    \end{cases}.
+\end{equation}
+Note that this definition recovers the standard inverse for invertible matrices.
+
+The same calculation can be repeated by exchanging $X$ with $P$, yielding the relation for the lower right block.
+The relevant matrices turn out to be 
+\bs
+\begin{align}
+    \check{N}_P &\coloneqq \mathcal{L}^\dagger \mathcal{K}_+^{-1} \mathcal{L}
+		\\
+		\check{M}_P &\coloneqq \check{N}_P^{-1/2} \mathcal{K}_- \check{N}_P^{-1/2}\,.
+\end{align}
+\es
+Summarizing, the Green's function is given by
 \begin{subequations}
     \begin{align}
-        G_{AB^\dagger} \vert_P (z) &= - \left[ \vec{b}^\dagger (0) \right]_P \mathcal{L}^\dagger r_X (z) \mathcal{L} \left[ \vec{a}(0) \right]_P\,, \\
-        G_{AB^\dagger} \vert_X (z) &= - \left[ \vec{b}^\dagger (0) \right]_X \mathcal{L} r_P (z) \mathcal{L}^\dagger \left[ \vec{a}(0) \right]_X\,,
+        G_{X_j,X_i}  (z) &= - \left[ \vec{x}_j^\dagger (0) \right]_X \mathcal{L}^\dagger r_X (z) \mathcal{L} \left[ \vec{x}_i(0) \right]_X, 
+				\\
+        G_{P_j,P_i} (z) &= \red{+} \left[ \vec{p}_j^\dagger (0) \right]_P \mathcal{L} r_P (z) \mathcal{L}^\dagger \left[ \vec{p}_i(0) \right]_P\,,
     \end{align}
 \end{subequations}
-\textcolor{\markEdited}{where $r_X (z)$ is given in \eqref{eqn:rx} and 
-\begin{equation}
-    r_P (z) = -\check{N}_P^{-1/2} \frac{1}{z^2 - \check{M}_P} \check{N}_P^{-1/2}\,.
-\end{equation}}
-
-Now, the task at hand is finding the inverse $1/(z^2 - \check{M})$ for all $z$.
-This can be achieved using a Lanczos tridiagonalization and subsequently, a continued fraction expansion in terms of the Lanczos coefficients $a_i$ and $b_i$ \cite{PettiforRecursion,ViswanathRecursion}.
+\blue{Brauchen/wollen wir die $[]_{X/P}$ noch? Und ich bin mir ziemlich sicher, dass das in beiden Fällen ein Minus sein sollte.}
+where the vectors $x_j(0)$ and $x_i(0)$ describe the initial conditions for the operators
+$X_j$ and $X_i$, respectively and $p_j(0)$ and $p_i(0)$ correspondingly for the operators
+$P_j$ and $P_i$. The resolvent $r_X (z)$ is given in \eqref{eqn:rx} and 
+\begin{equation}
+    r_P (z) = -\check{N}_P^{-1/2} \frac{1}{z^2 - \check{M}_P} \check{N}_P^{-1/2} .
+\end{equation}
+\red{@ Joshua: Bitte noch einmal sorgfaeltig alles pruefen, da ich doch einiges angepasst habe.}
+
+The remaining task consists of finding the inverse $1/(z^2 - \check{M})$ for all $z$.
+This, however, can be achieved efficiently using a Lanczos tridiagonalization and
+a continued fraction expansion in terms of the Lanczos coefficients $a_i$ and $b_i$ 
+\cite{PettiforRecursion,ViswanathRecursion}.
 In the single-band case, the coefficients approach the limit
@@
 where $\omega_\pm$ represents the upper and lower band edge, respectively \cite{PettiforRecursion}.
-This behavior allows us to terminate the continued fraction, once the coefficients have converged close enough to these values, using the so-called square root terminator
-\begin{equation}
-    T(\omega) = \frac{1}{2b_\infty^2} \left( \omega - a_\infty \mp \sqrt{(\omega - a_\infty)^2 - 4 b_\infty^2} \right)\,,
-\end{equation}
-where the negative sign is to be chosen for $\omega - a_\infty > 2b_\infty$ and $|\omega - a_\infty| < 2b_\infty$ and the positive one otherwise.
-It is to be noted, that the coefficients start to drop off from this limit as more and more Lanczos iterations are performed \cite{ViswanathRecursion}.
-Therefore, we terminate the continued fraction with the aforementioned terminator at the coefficient pair that has the least deviation from $a_\infty$ and $b_\infty$.
+The continued fraction is truncated at some depth when the coefficients $a_i$ and $b_i$ are sufficiently
+close to the limits \eqref{eqn:inf_lanczos}. Then, the truncated continued fraction can be terminated by the
+square root terminator
+\begin{equation}
+\label{eqn:terminator}
+    T(\omega) = \frac{1}{2b_\infty^2} 
+		\left( \omega - a_\infty \mp \sqrt{(\omega - a_\infty)^2 - 4 b_\infty^2} \right),
+\end{equation}
+where the negative sign is to be chosen for $\omega - a_\infty > 2b_\infty$ and the positive sign for
+$\omega - a_\infty < -2b_\infty$. For $|\omega - a_\infty| < 2b_\infty$, the square root in \eqref{eqn:terminator}
+is replaced by $+\im\sqrt{4 b_\infty^2 - (\omega - a_\infty)^2}$.
+
+Note that the coefficients start to deviate from the limits \eqref{eqn:inf_lanczos} as more and more Lanczos iterations are performed \cite{ViswanathRecursion}.
+Therefore, we terminate the continued fraction with the aforementioned terminator when the pair of coefficients 
+occurs in the fraction which deviates the least from $a_\infty$ and $b_\infty$.
 
@@
     \includegraphics[width=.98\textwidth]{plots/resolvent_overview_SC_CDW.pdf}
-    \caption{Spectral functions with respect to the operators listed in Eq.~\eqref{eqn:resolvent_bases}.
-    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
-    The left edge of each plot is at $-0.05$ rather than $0$ in order to improve the visibility of the phase peak.
-    The shaded area marks the two-particle continuum.
-    For each plot, the parameters are set to $U=-2.5t$ and $N_\gamma = 6000$, while $V$ is varied, see the legend.
-    The panels show the spectral functions in the (a) SC phase and the (b and c) CDW phase, respectively.}
+    \caption{Spectral functions of the operators listed in Eq.~\eqref{eqn:resolvent_bases}.
+    The left column shows the results for the square lattice and the right column for the simple cubic lattice.
+    The left edge of each plot is at $-0.05t$  in order to improve the visibility of the phase peak at zero frequency
+		($\hbar$ is set to unity). The gray area marks the two-particle continuum.
+    The parameters are set to $U=-2.5t$ and $N_\gamma = 6000$, while $V$ is varied according to the legends.
+    The panels show the spectral functions in the SC phase (a) and in the CDW phase, (b) and (c), respectively.}
     \label{fig:resolvent_overview_SC}
@@
     \includegraphics[width=.98\textwidth]{plots/resolvent_overview_V0.pdf}
-    \caption{\textcolor{\markEdited}{Same as \autoref{fig:resolvent_overview_SC}, except that we set $V=0$, i.e, SC and CDW order coexist.}
-    Since the ratio of $\Delta_\text{SC}$ to $\Delta_\text{CDW}$ may be chosen arbitrarily, we show in (a) the spectral functions for $\Delta_\text{CDW} = 0$ and in (b) for $\Delta_\text{SC} = 0$.}
+    \caption{Same as Fig.\ \ref{fig:resolvent_overview_SC} except that  $V=0$, i.e., 
+		SC and CDW order can coexist due to the SO(4) symmetry.
+    Since the ratio of $\Delta_\text{SC}$ to $\Delta_\text{CDW}$ can be chosen arbitrarily, 
+    we show in (a) the spectral functions for $\Delta_\text{CDW} = 0$ and in (b) for $\Delta_\text{SC} = 0$ while we distribute the gap equally in (c).}
     \label{fig:resolvent_overview_V0}
@@
     \includegraphics[width=.98\textwidth]{plots/resolvent_overview_AFM_CDW.pdf}
-    \caption{\textcolor{\markEdited}{Same as \autoref{fig:resolvent_overview_SC}, except that we are now looking at the system near the AFM-CDW phase transition.
-    For the square lattice, we set $V=1.2t$ and for the simple cubic lattice, we set $V=0.8t$. This choice yields the phase boundary at $U=4.8t$ for both lattices.}
-    The panels (a) and (c) show the spectral functions in the AFM phase, and the panels (b) and (d) in the CDW phase.}
+    \caption{\red{Die ersten beiden Reihen muessen getauscht werden. Stimmt dann der Text?} 
+    \blue{Ich hab dir offenbar tatsächlich den falschen Plot geschickt... 
+    Das ist der Plot der auf dem Poster ist, hier hatte ich eigentlich einen 4 Zeilen-Plot angedacht.}
+		Same as Fig.\ \ref{fig:resolvent_overview_SC} except that we are focusing 
+		on the AFM-CDW phase transition.
+    For the square lattice, we set $V=1.2t$, and for the simple cubic lattice, $V=0.8t$. 
+		This choice yields the phase transition at $U=4.8t$ for both lattices.
+    The panels (a) and (c) show the spectral functions in the AFM phase and the 
+		panels (b) and (d) in the CDW phase.}
     \label{fig:resolvent_overview_AFM}
@@
     \includegraphics[width=.98\textwidth]{plots/sc_peak_in_cdw.pdf}
-    \caption{The upper panels (a) show double logarithmic plots of the positions $\omega_0$ of the peak in $\spectral{SC}$ in the CDW phase while the lower panels (b) show their respective weights $W_0$.
+    \caption{The upper panels (a) show double logarithmic plots of the positions $\omega_0$ of the peak in $\spectral{SC}$ in the CDW phase 
+    while the lower panels (b) show their respective weights $W_0$.
     In the upper panels, the pink markers additionally show the peak position divided by the gap $\omega_0 / \Delta_\text{CDW}$. 
-    The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
-    \textcolor{\markEdited}{The fits are linear, i.e., $y(V) = e^d V^c$, and the parameters are printed on the individual panels.}}
+    The left column shows the results for the square lattice and the right column for the simple cubic lattice at $U=-2.5t$. 
+    The fits are linear in the double logarithmic plot, i.e., $y(V) = e^d V^c$, and the parameters are indicated in the panels.}
     \label{fig:sc_in_cdw_behavior}
@@
     \includegraphics[width=.98\textwidth]{plots/cdw_peak_in_sc.pdf}
-    \caption{\textcolor{\markEdited}{Same as \autoref{fig:sc_in_cdw_behavior} but for the peak in $\spectral{CDW}$ within the SC phase, i.e., $V<0$.}}
+    \caption{Same as in Fig.\ \ref{fig:sc_in_cdw_behavior}, but for the peak in $\spectral{CDW}$ 
+		in the SC phase, i.e., for $V<0$.}
     \label{fig:cdw_in_sc_behavior}
@@
     \includegraphics[width=.98\textwidth]{plots/afm_cdw_peaks_overview.pdf}
-    \caption{\textcolor{\markEdited}{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ (orange lines) and $\spectral{l.AFM}$ (green lines) close to the corresponding phase transition $U = 4.8t$.
-    Again, we chose $V=1.2t$ for the square lattice (left column) and $V=0.8t$ for the simple cubic lattice (right column) respectively.
-    The middle panels (b) depict the peak positions relative to the lower edge of the two-particle continuum $\omega_-$, while the bottom panels (c) show their respective weights.}
-    The shadings indicate the phase the system is in. Green represents AFM while orange represents CDW.
+    \caption{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ (orange lines) 
+		and $\spectral{l.AFM}$ (green lines) close to the corresponding phase transition 
+		at $U = 4.8t$.   Again, we choose $V=1.2t$ for the square lattice (left column) and $V=0.8t$ for the simple cubic lattice (right column), respectively.
+    The middle panels (b) depict the peak positions relative to the lower edge of the two-particle continuum 
+		$\omega_-$, while the bottom panels (c) show the peak weights.
+    The shadings indicate the phase in which the system is. Green represents AFM while orange represents CDW.
     Note the difference in the scales for the two lattices.}
@@
     \includegraphics[width=.98\textwidth]{plots/afm_cdw_peaks_details.pdf}
-    \caption{The upper panels (a) show double logarithmic plots of the positions $\omega_0$ of the peak in $\spectral{l.AFM}$ relative to the lower edge of the two-particle continuum $\omega_-$.
-    The lower panels (b) depict their respective weights $W_0$.
-    Again, we chose $V=1.2t$ for the square lattice (left column) and $V=0.8t$ for the simple cubic lattice (right column) respectively.
-    $U_0$ denotes the highest value of $U$ for which there is no peak below the two-particle continuum.
-    For the square lattice, it is $U_0 \approx 3.372t$ and for the simple cubic lattice, it is $U_0 \approx 4.479t$.
+    \caption{\red{Muss es im log-Argument nicht $U_0-U$ heissen, um klar zu sein?} 
+		The upper panels (a) show double logarithmic plots of the positions $\omega_0$ 
+		of the peak in $\spectral{l.AFM}$ relative to the lower edge of the two-particle continuum $\omega_-$.
+    The lower panels (b) depict the respective weights $W_0$.
+    Again, we choose $V=1.2t$ for the square lattice (left column) and 
+		$V=0.8t$ for the simple cubic lattice (right column), respectively.
+    The interaction $U_0$ denotes the highest value of $U$ for which 
+		there is no peak below the two-particle continuum, i.e., for $U> U_0$ a peak occurs.
+		\red{Ja, was gilt? Wann gibt's einen Peak, wann nicht? Bitte konsistent im ganzen Artikel bezeichnen.}
+    For the square lattice, we find $U_0 \approx 3.372t$ and for the simple cubic lattice $U_0 \approx 4.479t$.
     The parameter range depicted here places the system within the CDW phase.
-    The fits are of the same fashion as in \autoref{fig:sc_in_cdw_behavior}.}
+    The fits are of the same kind as in Fig.\ \ref{fig:sc_in_cdw_behavior}.}
     \label{fig:afm_cdw_peaks_details}

### 2024-03-26 paper/resolvent_overview_AFM_CDW.py
method + plots

@@ -26,7 +26,7 @@ folders = ["../data/modes/square/dos_6000/", "../data/modes/cube/dos_6000/"]
 nrows = 3 if poster_plot else 4
 ncols = 2
 # ax = axs[row][col]
-fig, axs = plt.subplots(nrows=nrows, ncols=ncols, figsize=(12.8, 8), sharey=True, sharex="col", gridspec_kw=dict(hspace=0, wspace=0))
+fig, axs = plt.subplots(nrows=nrows, ncols=ncols, figsize=(12.8, 8 if poster_plot else 10), sharey=True, sharex="col", gridspec_kw=dict(hspace=0, wspace=0))
 
 plotters = np.empty((nrows, ncols), dtype=ps.CURVEFAMILY)
 for i in range(nrows):

### 2024-03-26 paper/main.tex
Results 1

@@
 
-\section{Results}\label{sec:results}
-
-In this section, we will be investigating four different diagonal Green's functions $G_{AA^\dagger}(\omega + \im 0^+)$, namely with
+\section{Results}
+\label{sec:results}
+
+We investigate four different diagonal Green's functions $G_{AA^\dagger}(\omega + \im 0^+)$ with
 \begin{subequations}
@@
         A_\text{Higgs} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} + f_{\vk}^\dagger \right)  
-            = \int \dgamma \left( f_{\gamma} + f_{\gamma}^\dagger \right) \,,\\
-        A_\text{Phase} &= \frac{i}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} - f_{\vk}^\dagger \right) = \int \dgamma \left( f_{\gamma} - f_{\gamma}^\dagger \right) \,,\\
-        A_\text{CDW}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} + g_{\vk \down} \right) = \int \dgamma \left( g_{\gamma \up} + g_{\gamma \down} \right) \,,\\
-        A_\text{l.AFM}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} - g_{\vk \down} \right) = \int \dgamma \left( g_{\gamma \up} - g_{\gamma \down} \right) \,, \\
-        A_\text{t.AFM}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( \tau_{\vk} + \tau_{\vk}^\dagger \right) = \int \dgamma \left( \tau_{\gamma \up} + \tau_{\gamma \down} \right) \,,
+            = \int_{-1}^1 \dgamma \left( f_{\gamma} + f_{\gamma}^\dagger \right) ,\\
+        A_\text{Phase} &= \frac{i}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} - f_{\vk}^\dagger \right) = 
+				\int_{-1}^1 \dgamma \left( f_{\gamma} - f_{\gamma}^\dagger \right) ,\\
+        A_\text{CDW}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} + g_{\vk \down} \right) = 
+				\int_{-1}^1 \dgamma \left( g_{\gamma \up} + g_{\gamma \down} \right) ,\\
+        A_\text{l.AFM}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} - g_{\vk \down} \right) = 
+				\int_{-1}^1 \dgamma \left( g_{\gamma \up} - g_{\gamma \down} \right) , \\
+        A_\text{t.AFM}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( \tau_{\vk} + \tau_{\vk}^\dagger \right) = 
+				\int_{-1}^1 \dgamma \left( \tau_{\gamma \up} + \tau_{\gamma \down} \right) ,
     \end{align}
@@
 where $N$ is the number of lattice sites in the system. 
-Each one of these operators generates a different kind of collective mode.
-The first operator captures the amplitude mode of the $s$-wave superconducting state, while the second one catches the phase mode \cite{Fan22}.
-The remaining two capture the collective behavior of the CDW and AFM states, respectively.
-In the following, we will refer to the Green's functions generated by these operators as \textcolor{\markEdited}{$\mathcal{G}_{\alpha}(\omega) = G_{A_\alpha A_\alpha^\dagger}(\omega)$ 
-with $\alpha \in \{ \text{Higgs}, \text{Phase}, \text{CDW}, \text{l.AFM}, \text{t.AFM} \}$.}
-
-Note, that all of the aforementioned operators are Hermitian. 
-This means that all spectral functions need to be completely antisymmetrical \cite{rickayzen80}.%, see appendix \ref{sec:antisymmetry_spectral}.
-For this reason, we will only show the $\omega \geq 0$ in our plots. 
-Additionally, we will add a small imaginary part of $10^{-5}t$ to $\omega$ in order to visualize the occurring $\delta$ peaks.
-\textcolor{\markEdited}{Furthermore, we provide a brief analysis of the effect of choosing different numbers of discretization points $N_\gamma$ in appendix \ref{sec:finite_size}.}
+Each of these operators generates a different kind of collective mode.
+The first operator excites the amplitude mode of the $s$-wave superconducting state
+while the second one excites the phase mode \cite{Fan22}.
+The remaining two operators induce the collective behavior of the CDW and AFM order, respectively.
+This means these Green's functions are the susceptibilities towards alternating local potential (CDW) or
+alternating magnetic field (AFM).
+Below, we refer to the Green's functions of these operators by
+$\mathcal{G}_{\alpha}(\omega) = G_{A_\alpha A_\alpha^\dagger}(\omega)$ 
+with $\alpha \in \{ \text{Higgs}, \text{Phase}, \text{CDW}, \text{l.AFM}, \text{t.AFM} \}$.
+Furthermore, we use $\text{SC}$ when the Higgs and phase mode yield the same spectral function and
+$\text{AFM}$ when longitudinal and transversal magnons yield the same spectral function.
+
+The operators in \eqref{eqn:resolvent_bases} are Hermitian and of bosonic character. 
+This means that all spectral functions are antisymmetric \cite{rickayzen80}.
+For this reason, we only show the part  $\omega \geq 0$ in our plots. 
+Additionally, we add a small positive imaginary part of $10^{-5}t$ to $\omega$ 
+in order to plot the $\delta$ peaks as Lorentzians.
+We analyze the effect of different numbers of sampling points $N_\gamma$ in App.\ \ref{sec:finite_size}.
 
@@
 
-To begin, let us describe the spectral functions $\mathcal{A}_\alpha (\omega) = - (1/\pi) \Im [\mathcal{G}_\alpha (\omega + \im 0^+)]$ with respect to the operators above in the various phases.
-\autoref{fig:resolvent_overview_SC} shows them at $U = -2.5t$ in the SC ($V=-0.1t$) and CDW ($V=0.1t$ and $V=0.5t$) phase.
-
-There are a variety of different features. The difference between the two lattices is mostly quantitative.
-First and foremost, in the SC phase, see panel (a), 
-there is a sharp peak located at $\omega=0$ in $\spectral{Phase}$ and a singularity in $\spectral{Higgs}$ located at $\omega=2\Delta_\text{SC}$.
-We identify them with the well-known Anderson-Bogoliubov and Higgs modes in superconductors \cite{Bogoljubov1958,Anderson58,Brieskorn74,Schmid1975,simanek1975,schoen1976propagating,Kulik1981,Maiti2015,Sun2020,Fan22,Schmid1975,Varma02,Cea14,Measson14,Tsuji15,Krull16,Mueller2019,Schwarz20}.
-Note, that the former must not have any weight though, because the spectral function is perfectly antisymmetrical.
-The peak itself can be found at zero energy because our model describes a neutral superfluid 
-wherein there is no coupling of the phase of the order parameter to the electromagnetic potential.
+Let us describe the spectral functions 
+$\mathcal{A}_\alpha (\omega) = - (1/\pi) \Im [\mathcal{G}_\alpha (\omega + \im 0^+)]$ of
+the operators above in the various phases.
+Fig.\ \ref{fig:resolvent_overview_SC} shows them at $U = -2.5t$ in the SC ($V=-0.1t$) and  in the 
+CDW ($V=0.1t$ and $V=0.5t$) phase.
+
+There are a variety of different features. 
+The results for the lattices in 2D and 3D are very similar and differ only quantitatively.
+In the SC phase, see Fig.\ \ref{fig:resolvent_overview_SC}(a), 
+there is a sharp peak located at $\omega=0$ in $\spectral{Phase}$ and a 
+singularity in $\spectral{Higgs}$ located at $\omega=2\Delta_\text{SC}$.
+We identify them with the well-known Anderson-Bogoliubov mode and Higgs mode, respectively, in superconductors 
+\cite{Bogoljubov1958,Anderson58,Brieskorn74,Schmid1975,simanek1975,schon76,Kulik1981,Maiti2015,Sun2020,Fan22,Schmid1975,Varma02,Cea14,Measson14,Tsuji15,Krull16,Mueller2019,Schwarz20}.
+The former must not have any weight because of the antisymmetry of the spectral function.
+The peak itself is located at zero energy because the model \eqref{eqn:full_hamiltonian} 
+describes a neutral superfluid without coupling of the phase of the order parameter to the electromagnetic fields.
 Therefore, this phase may be chosen arbitrarily, and changing it requires no energy 
-which ultimately allows a Goldstone mode to exist in the first place \cite{Goldstone1961,Anderson63}.
-
-To characterize the occurring peaks that lie outside the two-particle continuum, we turn towards the real part of the Green's function.
-We plot it in close proximity to the peaks with a double logarithmic scale and fit the result linearly $y = ax + b$ to obtain its power-law behavior.
+which ultimately induces a Goldstone mode to exist \cite{Goldstone1961,Anderson63}.
+
+To characterize the occurring peaks that lie outside the two-particle continuum, we inspect the real part of the Green's function.
+We plot it in the vicinity of the peaks with a double logarithmic scale and fit 
+the result linearly $y = ax + b$ to obtain its power-law behavior.
 The real part is related to the imaginary part via the Kramers-Kronig relations.
 Specifically, if the imaginary part is a $\delta$ distribution, the real part will be proportional to $1/\omega$, i.e., $a=-1$, and the peak has the weight $W_0 = \exp(b)$.
-Furthermore, an exponent of $a=-2$ corresponds to the derivative of the $\delta$ distribution, i.e., $\delta'(\omega)$.
-The fits themselves can be found in appendix \ref{sec:fit_greens_functions}.
-
-This analysis provides that the real part of $\greens{Phase}$ near $\omega=0$ behaves as $1/\omega^2$ indicating that the peak in $\spectral{Phase}$ is the derivative of a $\delta$ distribution.
-The weight of such a peak is given by the integral $\int \delta'(\omega) \mathrm{d}\omega = 0$.
-This confirms our previous expectation that this peak cannot have any weight.
-
-The singularity in $\spectral{Higgs}$ behaves as $1/\sqrt{\omega - 2 \Delta_\text{SC}}$.
-Previous studies on the dynamics of the order parameter found damped oscillations after a quench.
-These have the frequency $\Omega = 2 \Delta_\text{SC}$ and fall off as $1/\sqrt{t}$ \cite{Volkov73,Kulik1981,Yuzbashyan06}.
-An inverse Fourier transform of $\spectral{Higgs}$ yields precisely the same behavior, thereby reinforcing the validity of our results.
-
-In the CDW phase, see panels (b) and (c), both of $\spectral{Higgs}$ and $\spectral{Phase}$ become identical and form a $\delta$ peak below the two-particle continuum.
-\textcolor{\markEdited}{In this case, both modes describe the condensation of a cooperon, i.e., a bound state of two electrons.}
-Following the Landau theory for continuous phase transitions, this is to be expected as the free energy is expanded in terms of the order parameter as
-\begin{equation}
-    f(\Delta_\text{SC}) \approx r |\Delta_\text{SC}|^2 + \frac{u}{2} |\Delta_\text{SC}|^4\,,
-\end{equation}
-with $r > 0$ and $u > 0$ if the system is outside of the superconducting phase. 
-In this case, the only minimum is at $\Delta_\text{SC} = 0$ \cite{Coleman2015}. 
-That means that both possible modes have to overcome the same energy to be excited at all.
-
-In the SC phase, $\spectral{CDW}$ features a $\delta$ peak below the continuum corresponding to the finite energy necessary to excite this kind of electronic density modulation.
-\textcolor{\markEdited}{This mode corresponds to the creation of an exciton.}
-For moderate-sized values of $V>0$, i.e., in the CDW phase, see panel (b) at $V=0.1t$, the aforementioned spectral function has a singularity at $\omega=2\Delta_\text{CDW}$.% that exhibits a square-root behavior.
-\textcolor{\markEdited}{This mode moves out of the two-particle continuum as $V$ is increased and becomes a proper $\delta$ peak, see panel (c) at $V=0.5t$.}
-
-\textcolor{\markEdited}{$\spectral{t.AFM}$ and $\spectral{l.AFM}$ are identical and restricted to the continuum for both phases and both lattices.
-The former statement can be understood by the same argument why $\spectral{Phase}$ and $\spectral{Higgs}$ are identical outside of the SC phase:
-If no AFM order is present, the same amount of energy is required to create any such excitation, in this case, a magnon.}
+Furthermore, an exponent of $a=-2$ corresponds to the 
+derivative of the $\delta$ distribution, i.e., $\delta'(\omega)$.
+The fits themselves are given in App.\ \ref{sec:fit_greens_functions}.
+
+This analysis yields that the real part of $\greens{Phase}$ near $\omega=0$ behaves like
+$1/\omega^2$ showing that the peak in $\spectral{Phase}$ is the derivative of a $\delta$ distribution.
+The weight of such a peak is given by the integral $\int \delta'(\omega) \mathrm{d}\omega = 0$ and thus
+vanishes in accordance with expectations.
+
+The singularity in $\spectral{Higgs}$ behaves like $1/\sqrt{\omega - 2 \Delta_\text{SC}}$.
+Previous studies on the dynamics of the order parameter found dephasing oscillations after a quench.
+These oscillations have the frequency $\Omega = 2 \Delta_\text{SC}$ and fall off like
+$1/\sqrt{t}$ \cite{Volkov73,Kulik1981,Yuzbashyan06}.
+An inverse Fourier transform of $\spectral{Higgs}$ yields precisely this behavior, 
+thereby corroborating our results.
+
+In the CDW phase, see panels (b) and (c) of Fig.\ \ref{fig:resolvent_overview_SC},
+both spectral functions $\spectral{Higgs}$ and $\spectral{Phase}$ become identical and display a $\delta$ peak below the two-particle continuum.
+In this case, both modes describe a cooperon, i.e., a bound state of two electrons or two holes.
+Following the Landau theory for continuous phase transitions, it is to be expected 
+that both excitations show the same spectral behavior. 
+If the free energy is expanded in powers of the order parameter 
+\begin{equation}
+    f(\Delta_\text{SC}) \approx r |\Delta_\text{SC}|^2 + \frac{u}{2} |\Delta_\text{SC}|^4,
+\end{equation}
+with  $u > 0$. For $r<0$, the system is in the SC phase and $\Delta_\text{SC}$ is finite.
+Then it makes a difference if one excites \emph{along} $\Delta_\text{SC}$ in the complex plane (Higgs mode)
+or \emph{perpendicular} to it (phase mode). For $r>0$, however, the order vanishes, $\Delta_\text{SC}=0$,
+and no distinction between Higgs and phase mode can be made \cite{Coleman2015}. 
+Both possible excitation processes have to overcome the same energy.
+
+In the SC phase, $\spectral{CDW}$ features a $\delta$ peak below the continuum corresponding to the finite energy necessary to excite the electronic density modulation of CDW type.
+This mode corresponds to the creation of an exciton since it results from a bilinear operator with
+creation and annihilation fermionic operator so that it represents a bound electron-hole pair.
+For moderate values of $V>0$, i.e., in the CDW phase, see panel (b) at $V=0.1t$, the CDW spectral function 
+shows a singularity at $\omega=2\Delta_\text{CDW}$.
+This mode moves out of the two-particle continuum upon increasing $V$ 
+and becomes a proper $\delta$ peak, see panel (c) of Fig.\ \ref{fig:resolvent_overview_SC} at $V=0.5t$.
+
+The spectral functions $\spectral{t.AFM}$ and $\spectral{l.AFM}$ are identical and restricted to 
+the continuum for both phases and both lattices.
+This can be understood by the same argument used for the identity of 
+$\spectral{Phase}$ and $\spectral{Higgs}$ outside of the SC phase:
+If no AFM order is present, there is no distinction between a longitudinal and a transversal excitation. 
+The same amount of energy is required to create any such excitation which is a magnon
+or paramagnon if there is no long-range AFM order.
 For the square lattice, there is a singularity located at the upper edge of the two-particle continuum.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-At $V=0$, both the SC and the CDW orders coexist. 
+But this does not occur in the 3D case. Including lifetime effects, sharp features at the upper
+edge of the continuum are expected to be smeared out anyway.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+At $V=0$, the SC and the CDW order can coexist due to the SO(4) symmetry. 
 In this phase, the mean-field single-particle energies are given by
 \begin{equation}
-    E_{\pm} = \pm \sqrt{\epsilon^2 + |\Delta_\text{CDW}|^2 + |\Delta_\text{SC}|^2}\,.
-\end{equation}
-This means that the proper order parameter is $\Delta_\text{tot} \coloneqq \sqrt{|\Delta_\text{CDW}|^2 + |\Delta_\text{SC}|^2}$.
+    E_{\pm} = \pm \sqrt{\epsilon^2 + |\Delta_\text{CDW}|^2 + |\Delta_\text{SC}|^2}.
+\end{equation}
+This means that the proper order parameter is $\Delta_\text{tot} 
+\coloneqq \sqrt{|\Delta_\text{CDW}|^2 + |\Delta_\text{SC}|^2}$.
 Here, $\Delta_\text{CDW}$ and $\Delta_\text{SC}$ can change arbitrarily without affecting the system's energy as long as $\Delta_\text{tot}$ remains constant.
-Note, that the degeneracy of both phases is exact due to the SO(4) symmetry \cite{yang90}.
-
-In \autoref{fig:resolvent_overview_V0}, we show the spectral functions for $U=-2.5t$ and $V=0$.
+This degeneracy of both phases is rigorously exact due to the SO(4) symmetry \cite{yang90}.
+
+In Fig.\ \ref{fig:resolvent_overview_V0}, we show the spectral functions for $U=-2.5t$ and $V=0$.
 The different panels correspond to different choices for $\Delta_\text{CDW}$ and $\Delta_\text{SC}$.
 First, in panel (a), we set $\Delta_\text{CDW} = 0$.
-This results in a purely superconducting phase with the same features as in \autoref{fig:resolvent_overview_SC} panel (a).
-\textcolor{\markEdited}{The peak in $\spectral{CDW}$ moves to $\omega=0$. In fact, $\spectral{CDW}$ and $\spectral{Phase}$ are identical.}
-
-Secondly, panel (b) shows the spectral functions for $\Delta_\text{SC} = 0$, i.e., in a purely charge-ordered phase.
-Similar to before, there is not much change compared to \autoref{fig:resolvent_overview_SC} panel (b).
-The spectral functions $\spectral{Higgs}$ and $\spectral{Phase}$ are still identical, however, both exhibit a sharp peak at $\omega=0$.
-This peak is described by $\delta'(\omega)$.
-
-Lastly, we chose $\Delta_\text{CDW} = \Delta_\text{SC}$ for panel (c).
-For this specific ratio of $\Delta_\text{CDW}$ and $\Delta_\text{SC}$, $\spectral{Higgs}$ and $\spectral{CDW}$ are identical.
+This results in a purely superconducting phase with the same features as in 
+Fig.\ \ref{fig:resolvent_overview_SC}(a).
+The peak in $\spectral{CDW}$ moves to $\omega=0$ because it does not cost energy to enhance the CDW order parameter
+if it is compensated by a reduction of the SC order parameter. 
+In fact, $\spectral{CDW}$ and $\spectral{Phase}$ are identical since they are linked by the SO(4) symmetry.
+
+Second, panel (b) shows the spectral functions for $\Delta_\text{SC} = 0$, i.e., in a purely charge-ordered phase.
+Similar to before, there is not much change compared to Fig.\ \ref{fig:resolvent_overview_SC}(b).
+The spectral functions $\spectral{Higgs}$ and $\spectral{Phase}$ are still identical since no
+SC order is present. Both exhibit a sharp peak at $\omega=0$ proportional to $\delta'(\omega)$
+which reflects that an SC order can be introduced without energy cost if compensated by a reduction of the CDW order.
+
+Last, we choose $\Delta_\text{CDW} = \Delta_\text{SC}$ in panel (c).
+For this specific ratio of $\Delta_\text{CDW}$ and $\Delta_\text{SC}$, 
+$\spectral{Higgs}$ and $\spectral{CDW}$ are identical.
 Choosing a different ratio yields qualitatively the same results, but the peaks differ in magnitude.
-Both spectral functions have a peak at $\omega = 0$, described by $\delta'(\omega)$, and a singularity at the lower edge of the two-particle continuum $\omega = 2\Delta_\text{tot}$.
-Each one of the singularities behaves as $1/\sqrt{\omega - 2 \Delta_\text{tot}}$.
-\textcolor{\markEdited}{Essentially, varying the ratio of the two gap parameters smoothly switches $\spectral{Higgs}$ and $\spectral{CDW}$.}
-
-\textcolor{\markEdited}{We associate the peak in the amplitude-related spectral functions at $\omega=0$ with this shifting of order parameters, i.e., diminishing one and increasing the other while keeping $\Delta_\text{tot}$ constant.
-Specifically, in the pure SC phase, we find this peak only in $\spectral{CDW}$.
-This can be understood as follows: The operator $A_\text{CDW}$ in \eqref{eqn:resolvent_bases} creates an exciton and thereby increases $|\Delta_\text{CDW}|$.
-This can in essence be achieved without any external energy by lowering $\Delta_\text{SC}$.
-However, the converse is not true: Since $\Delta_\text{CDW}$ is already 0, creating another Cooper pair by virtue of $A_\text{Higgs}$ will always increase $\Delta_\text{tot}$ and therefore requires a minimum energy of $2 \Delta_\text{tot}$.
-The same argument can be made for the pure CDW phase.
-If, however, both orders are present, the system can shift between them arbitrarily by creating either kind of excitation.
-Hence, in this case, we find a peak at $\omega=0$ in both spectral functions.}
-
-$\spectral{Phase}$ behaves just as it does in the pure SC phase. It has only a peak at $\omega = 0$ that can be associated with the change of the phase of $\Delta_\text{SC}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Lastly, we investigate the same spectral functions close to the AFM-CDW phase transition, depicted in \autoref{fig:resolvent_overview_AFM}.
-\textcolor{\markEdited}{We choose $V=1.2t$ for the square lattice and $V=0.8t$ for the simple cubic lattice.
-This yields that the phase transition is located at $U=4.8t$ for both cases. 
-The panels (a) and (b) show the system close to the phase transition at $U=4.8t \pm 0.1t$.}
-Again, both SC-related spectral functions are identical in both the CDW and AFM phases.
-Within the continuum their weight is shifted towards the upper edge and on the square lattice only, there is a peak above the continuum.
-In the AFM phase, both $\spectral{l.AFM}$ and $\spectral{CDW}$ have a peak close, but yet below, the two-particle continuum.
+Both spectral functions have a peak at $\omega = 0$ proportional to $\delta'(\omega)$
+and a singularity at the lower edge of the two-particle continuum $\omega = 2\Delta_\text{tot}$.
+These singularities behave like $1/\sqrt{\omega - 2 \Delta_\text{tot}}$.
+Varying the ratio of the two gap parameters allows one to
+switch between $\spectral{Higgs}$ and $\spectral{CDW}$ continuously.
+
+We attribute the peak in the amplitude spectral functions at $\omega=0$ 
+to the freedom to vary the order parameters, i.e., 
+diminishing one and increasing the other while keeping $\Delta_\text{tot}$ 
+constant so that the system stays in its ground states. 
+In the pure SC phase, we find this peak only in $\spectral{CDW}$.
+This can be understood as follows: The operator $A_\text{CDW}$ in \eqref{eqn:resolvent_bases} 
+creates an exciton and thereby increases $|\Delta_\text{CDW}|$.
+This can be achieved without increasing the energy by lowering $\Delta_\text{SC}$.
+However, the reversed argument is not true: Since $\Delta_\text{CDW}$ is already 0, 
+creating another Cooper pair by virtue of $A_\text{Higgs}$ always increases $\Delta_\text{tot}$ and thus 
+requires a minimum energy of $2 \Delta_\text{tot}$.
+The analogous argument holds for the pure CDW phase.
+If, however, both orders are present, the system can shift between them arbitrarily 
+by creating either kind of excitation.
+Hence, in this case, we find a peak at $\omega=0$ in both spectral functions.
+
+The spectral function $\spectral{Phase}$ behaves as it does in the pure SC phase. 
+It has only a peak at $\omega = 0$ that is associated with the freedom of choice
+of the phase of $\Delta_\text{SC}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Finally, we investigate the same spectral functions close to the AFM-CDW phase transition
+as depicted in Fig.\ \ref{fig:resolvent_overview_AFM}.
+We choose $V=1.2t$ for the square lattice and $V=0.8t$ for the simple cubic lattice so that
+the phase transition is located at $U=4.8t$ in both cases. 
+The panels (a) and (b) show the system close to the phase transition at $U=4.8t \pm 0.05t$.
+Again, the SC-related spectral functions are identical in the CDW and the AFM phases
+due to the absence of a finite SC order.
+Within the continuum, their weight is shifted towards the upper edge.
+On the square lattice only, there is a peak above the continuum.
+It is likely to be smeared out if lifetime effects were included.
+In the AFM phase, both $\spectral{l.AFM}$ and $\spectral{CDW}$ have a peak close to, but yet below, the two-particle continuum. 
 The peak of the former is at a lower energy than the peak of the latter.
-In the CDW phase, this behavior is reversed, i.e., the peak in $\spectral{CDW}$ lies lower.
-Using the same analysis as before, we conclude that each of these peaks is a $\delta$ peak.
-\textcolor{\markEdited}{Moving further away from the phase transition, here $U=4.8t \pm 1.4t$ in panels (c) and (d), the upper peak moves into the two-particle continuum while the other one persists.
-Both close and far away from the phase transition, but only in the AFM phase, $\spectral{t.AFM}$ exhibits a $\delta'$ peak at $\omega=0$.
-This represents a transversal magnon and is the Goldstone boson for the AFM phase.}
+In the CDW phase, this behavior is reversed, i.e., the peak of $\spectral{CDW}$ lies lower
+than the one in $\spectral{l.AFM}$.
+Analyzing the power-law behavior of the real part described above, see also
+App.\ \ref{sec:fit_greens_functions}, we confirm that these peaks are $\delta$ peaks.
+Moving further away from the phase transition, here $U=6.2t$ in panels (c) \blue{and $U=3.4t$ in panels(d)}
+\red{Im Text war (d) benannt, aber das existiert ja nicht.}, 
+the upper peak merges with the two-particle continuum while the lower one persists.
+We emphasize that the spectral function of the transverse magnon $\spectral{t.AFM}$ always 
+displays a $\delta'$ peak at $\omega=0$, independent of how far away the parameters are chosen
+from the phase transition. This is the expected behavior of a Goldstone boson.
 

### 2024-03-26 paper/main.tex
results

@@
     \includegraphics[width=.98\textwidth]{plots/afm_cdw_peaks_details.pdf}
-    \caption{\red{Muss es im log-Argument nicht $U_0-U$ heissen, um klar zu sein?} 
+    \caption{\red{Muss es im log-Argument nicht $U_0-U$ heissen, um klar zu sein?}  \blue{Wir plotten $U\in(U_0, 4.8t)$, also $U_0 < U$}
 		The upper panels (a) show double logarithmic plots of the positions $\omega_0$ 
@@
 App.\ \ref{sec:fit_greens_functions}, we confirm that these peaks are $\delta$ peaks.
-Moving further away from the phase transition, here $U=6.2t$ in panels (c) \blue{and $U=3.4t$ in panels(d)}
+Moving further away from the phase transition, here $U=6.2t$ in panels (c) \blue{and $U=3.4t$ in panels (d)}
 \red{Im Text war (d) benannt, aber das existiert ja nicht.}, 
@@
 
-With the prevalent peaks discussed, we turn towards their behavior as the system approaches the phase transition at $V=0$ for $U=-2.5t$.
-First and foremost, we investigate the peak in $\spectral{Phase}$ and $\spectral{Higgs}$ in the CDW phase.
-The evolution of its position $\omega_0$ and its weight $W_0$ as $V$ is varied can be viewed double logarithmically in \autoref{fig:sc_in_cdw_behavior}.
-For $V \ll t$, the position grows with the square root of $V$. This behavior then transitions to a purely linear growth for large $V$.
-Dividing $\omega_0$ by the gap $\Delta_\text{CDW}$ results in a plateau for large $V$ while leaving the square root behavior at the beginning mostly unchanged.
-
-The peak weights $W_0$ fall off as $1/\sqrt{V}$ for $V \ll t$. 
-Afterward, it reaches a shallow minimum and rises slightly to reach a constant value.
-
-Specifically, we learn that for $V \ll t$, the peak position follows $\omega_0 = \alpha \sqrt{V}$ and its weight follows $W_0 = \beta / \sqrt{V}$, 
-where $\alpha$ and $\beta$ are some constants.
-This allows us to write $W_0 = \beta / (\alpha \omega_0)$. 
-Furthermore, we know that the spectral functions need to be perfectly antisymmetrical about $\omega = 0$, i.e., we can observe
-\begin{align}
-    \mathcal{A}_\text{Phase} (\omega \ll t) &= W_0 (\delta (\omega - \omega_0) - \delta (\omega + \omega_0)) \nonumber \\
-        &= - \frac{2\beta}{\alpha} \frac{\delta (\omega + \omega_0) - \delta (\omega - \omega_0)}{2\omega_0} \,.
-\end{align} 
-Taking the limit of $V \to 0$ corresponds to the limit $\omega_0 \to 0$, i.e., leading to an expression reminiscent of symmetric derivative
-\begin{equation}
-    \lim_{h \to 0} \frac{f(x + h) - f(x - h)}{2h} = f'(x)\,,
-\end{equation}
-where the equality holds for any differentiable $f$.
-Applying this to our case yields
-\begin{align}
-    \lim_{\omega_0 \to 0} \mathcal{A}_\text{Phase} (\omega \ll t) = - \frac{2 \beta}{\alpha} \delta'(\omega)\,.
-\end{align}
-This analysis reinforces our previous identification of the phase peak as $\delta' (\omega)$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-As a next step, we want to analyze the peak in $\spectral{CDW}$ that occurs if the system is in the SC phase ($V<0$).
-A plot of its position $\omega_0$ and weight $W_0$ can be seen in \autoref{fig:sc_in_cdw_behavior}.
-First and foremost, the upper panels (a) and (b) depict the peak positions and weights, respectively.
-\textcolor{\markEdited}{For $|V| \ll t$, the behavior of both the weight and the position of the peak is the same as for the previously discussed peak in $\spectral{SC}$ within the CDW phase.}
-
-\textcolor{\markEdited}{Moving towards larger $|V|$, the growth of the peak position slows down, while the weights start to drop off rapidly.
-However, we are unable to compute the Green's functions for additional, even larger $|V|$ because the matrix $\mM$ is not nonnegative anymore after $V\approx -0.28t$ (square lattice) or $V\approx -0.34t$ (simple cubic lattice).
-Note, that our proof for the nonnegativity is based on the system being in thermal equilibrium.}
-Therefore, we conclude that beyond these values of $V$, the superconducting phase is not the true ground state of the system, see the red shading in \autoref{fig:phase_diagram}.
-Specifically, the $s$-wave superconducting phase on the square lattice seems to be even smaller than first estimated using the $d_{x^2 -y^2}$ data from \cite{Micnas88b}.
-In recent research, there has been evidence for a phase-separated state for negative values of $V$ on a square lattice, which would explain our results here \cite{Linner23}.
-It would be reasonable to assume, that this phase occurs in both the 2- and 3-dimensional case.
-The magnitude of $V$ for which our calculation stops working is in the same order as in the referenced paper.
-Note, however, that we did our computations at $T=0$ while the reference worked on finite temperature systems.
+Having discussed the dominant peaks, we address their behavior when 
+the system approaches the phase transition \blue{between the SC and CDW phase} at $V=0$ for $U=-2.5t$.
+First, we investigate the identical peak in $\spectral{Phase}$ and $\spectral{Higgs}$, respectively, in the CDW phase.
+The evolution of its position $\omega_0$ and its weight $W_0$ as a function of $V$ is depicted
+double logarithmically in Fig.\ \ref{fig:sc_in_cdw_behavior}.
+For $V \ll t$, the position increases with the square root of $V$. 
+This behavior crosses over to a purely linear growth for large $V$.
+The gap position $\omega_0$ relative to the gap $\Delta_\text{CDW}$ shows a plateau for large $V$ 
+while leaving the square root behavior for small values of $V$ hardly altered.
+The peak's weight $W_0$ decreases like $1/\sqrt{V}$ for $V \ll t$,
+reaching a shallow minimum for intermediate valus of $V$, and 
+eventually saturating at a constant value.
+
+Summarizing, we see that for $V \ll t$ the peak position follows 
+$\omega_0 = \alpha \sqrt{V}$ and its weight  $W_0 = \beta / \sqrt{V}$, 
+where $\alpha$ and $\beta$ are some constants. Thus, we conclude $W_0 = \beta / (\alpha \omega_0)$. 
+Furthermore, we know that the spectral functions are antisymmetric, i.e., we find
+\bs
+\begin{align}
+    \mathcal{A}_\text{Phase} (\omega \ll t) &= W_0 (\delta (\omega - \omega_0) - \delta (\omega + \omega_0)) 
+		\\
+    &= - \frac{2\beta}{\alpha} \frac{\delta (\omega + \omega_0) - \delta (\omega - \omega_0)}{2\omega_0}.
+\end{align} 
+\es
+Taking the limit $V \to 0$ corresponds to the limit $\omega_0 \to 0$, i.e., leading to a ratio tending to the
+derivative
+\begin{equation}
+    \lim_{h \to 0} \frac{f(x + h) - f(x - h)}{2h} = f'(x).
+\end{equation}
+Applying this to the spectral peak yields
+\begin{align}
+    \lim_{\omega_0 \to 0} \mathcal{A}_\text{Phase} (\omega \ll t) = - \frac{2 \beta}{\alpha} \delta'(\omega),
+\end{align}
+confirming our previous analysis of the phase peak being proportional to  $\delta' (\omega)$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Next, we analyze the peak in $\spectral{CDW}$ occurring if the system is in the SC phase for $V<0$.
+A plot of its position $\omega_0$ and weight $W_0$ is given in Fig.\ \ref{fig:cdw_in_sc_behavior}.
+The upper panels (a) and (b) depict the peak position and weight, respectively.
+For $|V| \ll t$, the behavior of both of them is the same as for the 
+previously discussed peak in $\spectral{SC}$ in the CDW phase.
+Increasing $|V|$, the increase of the peak position slows down while the weights start to drop rapidly.
+We cannot compute the Green's functions for even larger $|V|$ with $V<0$ because the dynamical matrix $\mM$ 
+acquires negative eigenvalues below $V\approx -0.28t$ (square lattice) or $V\approx -0.34t$ (simple cubic lattice). 
+We recall that this indicates that the assumed phase, i.e., the SC phase is not stable. 
+Therefore, we conclude that for sufficiently negative values of $V$, 
+the superconducting phase is not the true ground state as indicated by the red shading in Fig.\ \ref{fig:phase_diagram}.
+Specifically, the region of the SC phase on the square lattice 
+appears to be even smaller than shown by the $d_{x^2 -y^2}$ data from Ref.\ \cite{Micnas88b}.
+Recently, there has been evidence for phase separation for negative values of $V$ 
+on the square lattice, at least at finite temperature \cite{Linner23}. 
+Thus, we interpret the negative eigenvalues in the dynamical matrix as indicators of phase separation. 
+Physically, a strong attractive interaction clearly favors phase separation since the particles prefer to stay close together 
+so it is highly plausible that they gather in one region of the sample while leaving the remainder essentially empty.
+\red{Was ist in 3D - gibt es da nicht auch negative Eigenwerte usw.? Das solten wir dann hier
+ebenfalls besprechen. Wo wollten wir denn die Diskussion des Tricks von Biermann publizieren?}
 
@@
 
-Lastly, we investigate how the modes behave as the system transitions between the CDW and AFM phases.
-Similar to the previous subsection, we plot the occurring peaks in $\spectral{CDW}$ and $\spectral{l.AFM}$ within the respective phase in \autoref{fig:afm_cdw_peaks_overview}.
-On the right side of each panel, i.e., for $U > zV$, the system is in the AFM phase (green shading).
-On the left side, it is in the CDW phase (orange shading).
-In general, the peak in $\spectral{l.AFM}$ behaves exactly as the peak in $\spectral{CDW}$ if the phases are swapped.
-
-The panel (a) shows the peak positions unmodified. They essentially move linearly as $U$ is varied.
-It is noteworthy, that in the AFM phase, the peak in $\spectral{l.AFM}$ lies lower than the one in $\spectral{CDW}$.
-Naturally, this is reversed, if the system is in the CDW phase.
-This is to be expected, as creating an AFM excitation should be energetically more favorable if the system is already in said phase.
-
-Additionally, we plot in (b) the peak positions relative to the lower edge of the two-particle continuum.
-We see that the lower-lying peak, i.e., the peak corresponding to the phase the system is in, 
-strays further away from the continuum as the system moves away from the phase boundary.
-The other peak, however, moves ever closer to the aforementioned continuum until they reach it.
-At this point, the weight of said peak also vanishes, see panel (c).
-This occurs around $U \approx 4.8t \pm 1.428t$ for the square lattice and around $U \approx 4.8t \pm 0.321t$ for the simple cubic lattice.
-
-On the square lattice, the weights of the peaks in $\spectral{l.AFM}$ in the AFM phase (the same applies to $\spectral{CDW}$ in the CDW phase) grow as the system moves away from the phase transition.
-On the simple cubic lattice, however, the weights fall off very slightly.
-
-In \autoref{fig:afm_cdw_peaks_details}, we revisit panels (b) and (c) from the previous figure.
-We restrict the analysis to $\spectral{l.AFM}$ in the CDW phase as the reverse case yields precisely the same data.
-This time around the scaling is double-logarithmic and we consider $U$ relative to those values at which we cannot find a peak in $\spectral{l.AFM}$.
-This occurs around $U_0 = 3.372t$ on the square lattice and around $U_0 = 4.479t$ on the simple cubic lattice.
-This yields that the peak positions $\omega_0$ (a) behave quadratically as they move into the two-particle continuum, i.e., $\omega_0 \propto (U-U_0)^2$,
-while their weights $W_0$ (b) drop off linearly, i.e., $W_0 \propto (U-U_0)$.
+Last, we investigate how the modes behave as the system passes from the CDW to the AFM phase.
+As in the previous subsection, we plot the occurring peaks in $\spectral{CDW}$ and 
+$\spectral{l.AFM}$ in the respective phases in Fig.\ \ref{fig:afm_cdw_peaks_overview}.
+On the right-hand side of each panel, i.e., for $U > zV$, the system is in the AFM phase (green shading);
+on the left-hand side, it is in the CDW phase (orange shading).
+Qualitatively, the peak in $\spectral{l.AFM}$ behaves like the peak in 
+$\spectral{CDW}$ if the phases are swapped. \red{Ist das exakt oder nur ungefaehr so?} \blue{tatsächlich exakt.}
+
+Panel (a) shows the peak positions which shift essentially linearly upon varying $U$.
+It is noteworthy, that in the AFM phase the peak in $\spectral{l.AFM}$ lies energetically
+lower than the one \red{Welchen meinst Du? CDW oder l.AFM? Uneindeutig ...} in $\spectral{CDW}$. \blue{Der AFM-peak ist in der AFM-phase bei kleinerer Energie als der CDW-peak in der AFM-phase.}
+This is reversed if the system is in the CDW phase.
+We conclude that it is energetically more favorable to create an AFM excitation (magnon) than a CDW
+exciton if the system is in the AFM phase. In the CDW phase, the creation of the CDW exciton is
+energetically cheaper than the creation of a magnon. \red{Habe ich das so richtig dargestellt?} \blue{Ja.}
+
+Additionally, we plot the peak positions in panel (b) relative to the lower edge of the two-particle continuum.
+We see that the lower-lying peak, i.e., the peak corresponding to the phase in which the system is, 
+shifts further away from the continuum as the system moves away from the phase boundary.
+The other peak, however, shifts closer to the continuum until it dives into it.
+At this point, the weight of the merging peak vanishes, see panels (c).
+\blue{This occurs around $U \approx 4.8t + 1.428t$ ($\spectral{CDW}$) and $U \approx 4.8t - 1.428t$ ($\spectral{l.AFM}$) for the square lattice 
+and around $U \approx 4.8t + 0.321t$  ($\spectral{CDW}$) and $U \approx 4.8t - 0.321t$  ($\spectral{l.AFM}$) for the simple cubic lattice.}
+\red{Was willst Du mit dem $\pm$ ausdruecken? Verstehe ich nicht ... Besser etwas ausfuehrlicher trotz
+einer gewissen Redundanz.}
+
+The weights of the peaks in $\spectral{l.AFM}$ in the AFM phase (the same applies to $\spectral{CDW}$ in the CDW phase) grow as the system moves away from the phase transition.
+The same applies to the peaks in $\spectral{CDW}$ in the CDW phase.
+
+In Fig.\ \ref{fig:afm_cdw_peaks_details}, we revisit the data of panels (b) and (c) of the previous figure
+on a double logarithmic scale.
+We restrict the analysis to $\spectral{l.AFM}$ in the CDW phase as the swapped case of $\spectral{CDW}$ in the 
+AFM phase shows the same behavior.
+We consider $U$ relative to the value $U_0$ at which the peak in $\spectral{l.AFM}$ ceases to exist.
+\red{Stimmt die Formulierung?} \blue{Ja.}
+This occurs at $U_0 = 3.372t$ on the square lattice and at $U_0 = 4.479t$ on the simple cubic lattice.
+The peak positions $\omega_0$ in panels (a) behave quadratically as they merge with the 
+two-particle continuum, i.e., 
+$\omega_0 \propto (U-U_0)^2$ while the weights $W_0$ in panel (b) decrease linearly, i.e., 
+$W_0 \propto (U-U_0)$ \red{Stimmt das Vorzeichen?}. This behavior is generic for the peaks of bound states merging with
+their continua at vanishing binding energy \cite{uhrig96b,uhrig96be,zhito13}.
 

### 2024-03-26 paper/afm_cdw_peaks_overview.py

@@ -64,6 +64,8 @@ for i in range(2):
             counter += 1
         
         label_subscript = name_suffix if name_suffix != "AFM" else "l.AFM"
+        
+        #us_same = np.array([np.concatenate((Us_square[::-1], Us_square)), np.concatenate((Us_cube[::-1], Us_cube))], dtype=object)
         plotters[0][i].plot(u_data, peak_positions, label=f"$\\mathcal{{A}}_\\mathrm{{{label_subscript}}} (\\omega)$")
         plotters[1][i].plot(u_data, peak_positions_to_cont)
         plotters[2][i].plot(u_data, np.exp(weights))

### 2024-03-26 paper/main.tex
conclusion

@@
 $\omega_0 \propto (U-U_0)^2$ while the weights $W_0$ in panel (b) decrease linearly, i.e., 
-$W_0 \propto (U-U_0)$ \red{Stimmt das Vorzeichen?}. This behavior is generic for the peaks of bound states merging with
-their continua at vanishing binding energy \cite{uhrig96b,uhrig96be,zhito13}.
+$W_0 \propto (U-U_0)$ \red{Stimmt das Vorzeichen?} \blue{Ja.}. This behavior is generic for the peaks of bound states merging with
+their continua at vanishing binding energy \cite{uhrig96b,uhrig96be,zhito13}. \blue{Das wusste ich tatsächlich nicht.}
 
@@
 
-We have conducted an analysis of the mean-field phase diagram of the extended Hubbard model in 2D and 3D. 
-Specifically, both systems provide a similar structure of $s$-wave SC, CDW, and AFM.
-Furthermore, we were able to identify an area in which our analysis is incomplete.
-In 2D, this region coincides with a phase-separated state that has already been observed in recent research \cite{Linner23}.
-
-We have also developed a novel method to obtain Fourier-transformed Green's functions and analyzed various such functions. 
-We have found collective excitations within the spectral functions $\spectral{Higgs}$, $\spectral{Phase}$, $\spectral{CDW}$, $\spectral{l.AFM}$, and $\spectral{t.AFM}$ 
-and examined their behavior as the system approaches phase transitions. 
-In particular, we identified the peak and singularity found in the first two as the well-known phase and amplitude modes in neutral superconductors 
+%%%
+% competing phases, collective modes, softening, weights, shift of energies
+% controlled, powerful formalism on top of mean-field Hamiltonian,
+%but dynamics well beyond!, can be extended to diagrammatics.
+
+The objective of this article was to study collective excitations in competing phases.
+We wanted to understand how collective excitations behave in the vicinity of phase transitions
+and how they signal these transitions, for example by softening or by losing spectral weight.
+To this end, we developed a general and versatile formalism based on iterated equations of motion.
+We could show that the formalism reproduces all rigorously known properties such as
+the existence of Goldstone bosons in case of broken continuous symmetries and the absence thereof
+if the broken symmetry is discrete.
+
+We conducted an analysis of the mean-field phase diagram of the extended Hubbard model in 
+two (2D) and three dimensions (3D). The results in both dimensions are qualitatively very similar.
+Specifically, we studied the competing phases 
+of $s$-wave superconducting order (SC), alternating charge density wave order
+(CDW), and N\'eel antiferromagnetism (AFM).
+Furthermore, we were able to identify regions in which our analysis is incomplete
+in the sense that the assumed phases turn out to be unstable, but it is not obvious which
+phases are the stable ones. Since we observed this phenomenon for strongly attractive interactions
+we conjecture that the instability indicates the occurrence of phase separation in 2D and 3D. 
+For the square lattice, recent findings at finite temperature also pointed in this direction \cite{Linner23}.
+
+We developed a method to obtain Fourier-transformed Green's functions
+based on iterated equations of motion and analyzed the most relevant
+of them. We identified the signatures of collective excitations in the spectral functions 
+$\spectral{Higgs}$, $\spectral{Phase}$, $\spectral{CDW}$, $\spectral{l.AFM}$, and $\spectral{t.AFM}$ 
+which are designed to excite the Higgs mode, the phase mode, a staggered density mode, a longitudinal, and a transversal magnon, respectively. 
+The focus was the analysis of their behavior as the system approaches and crosses phase transitions.
+In particular, we identified the peak and the singularity occurring in the first two 
+spectral functions related to superconductivity
+to be the well-known amplitude and phase modes in neutral superconductors 
 and thereby provided a technique to obtain them starting from a microscopic description.
-
-We observed the behavior of the peak in the SC-related spectral functions, \textcolor{\markEdited}{corresponding to a cooperon}.
-It moves towards 0 energy and attains more weight as the system moves from the CDW phase towards the SC phase. 
-The peak's relative position to the two-particle continuum and its weight plateau as the system moves away from the phase transition.
-
-In the SC phase close to the CDW phase, the peak in $\spectral{CDW}$, \textcolor{\markEdited}{corresponding to an exciton}, is located at a finite energy and and has a finite weight. 
-\textcolor{\markEdited}{It behaves in the same manner as the previously discussed peak}.
-
-Around the AFM-CDW phase transition, both $\spectral{l.AFM}$ and $\spectral{CDW}$ feature a peak. 
-\textcolor{\markEdited}{The former corresponds to a longitudinal magnon, while the latter represents an exciton.}
-The peak of the former in the AFM phase lies at lower energies than the latter one and vice-versa. 
-Moving away from the phase transition, the higher-lying peak moves into the two-particle continuum. 
-The peak position relative to the two-particle continuum approaches $0$ quadratically with $U$, and its weight approaches $0$ linearly.
-
-Furthermore, we have found a peak in $\spectral{CDW}$ that appears at large values of $V$, 
-which is most likely the same as the one found close to the CDW-AFM phase transition. 
-\textcolor{\markEdited}{It is also reasonable to assume, that this peak is always located outside of the two-particle continuum, even for small values of $V$.
-In this case, however, it would lie very close to the continuum, which we cannot resolve due to the limited accuracy of our numerics.
-Therefore, it appears as a singularity at $2\Delta$.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Some possible ideas for future research include incorporating phase-separated states into the mean-field theory.
-This would enable us to peer deeper into the negative $V$ regime of the phase diagrams and provide more analysis of the collective excitations that occur therein.
-
-\textcolor{\markEdited}{Specifically for the SC-related quantities, one can fathom including a coupling of the electronic system to the electromagnetic field.}
-This should move the position of the phase mode close to the plasma frequency as explained by the Anderson-Higgs mechanism.
-
-Additionally, one could describe multi-band systems with even richer phases and collective excitations.
+Outside an SC phase, both spectral functions are identical while in an SC phase,
+the phase mode is massless while the Higgs mode is at the lower edge of the continuum.
+So, the phase mode manifests as the derivative of the $\delta$ function at zero energy
+complying with the asymmetry of the spectral function.
+
+We observed the behavior of the peak in the SC-related spectral functions corresponding to a cooperon in various phases. 
+It shifts towards zero energy and acquires more and more weight as the system moves from the CDW phase toward the SC phase. 
+The peak's relative position to the two-particle continuum and its weight saturate 
+as the system moves away from the phase transition.
+In the SC phase close to the CDW phase, the peak in $\spectral{CDW}$ 
+is located at a finite energy and and has finite weight. 
+It must represent a bound state because it is located below the two-particle continuum. 
+This state is induced by the application of an electron creation and an electron annihilation without effect of its spin content so that we interpret it as an $S=0$ exciton.
+It behaves similarly to the SC-related peak in non-SC phases. \blue{Explizit in der CDW Phase, nicht?}
+
+In the vicinity of the AFM-CDW phase transition, the spectral densities
+$\spectral{CDW}$ and $\spectral{l.AFM}$ feature a peak. 
+The former is the aforementioned exciton while the latter is a longitudinal magnon. 
+Of course, this can also be seen as an exciton being a bound
+state of an electron and a hole, yet with spin content $S=1$ and $S^z=0$. 
+The longitudinal magnon lies at lower energy in the AFM phase than the CDW exciton. 
+In the CDW phases, the two peaks swap their relative energy positions. 
+Moving away from the phase transition, the higher-lying peak merges with the two-particle continuum. 
+The peak position relative to the two-particle continuum approaches $0$ 
+quadratically in $\Delta U$ while its weight approaches $0$ linearly with $\Delta U$ where
+$\Delta U$ measures the distance to the interaction \blue{strength?} where the merging takes place.
+
+Furthermore, we found the exciton peak in $\spectral{CDW}$ also at large values of $V$ in the CDW phase, 
+evolving smoothly from the CDW-AFM phase transition. \red{Das kannst Du vllt. noch stichprobenartig pruefen.}
+We assume that this peak is always located outside of the two-particle continuum, even for small values of $V$.
+In this case, however, it can lie very close to the continuum, so that we cannot resolve it due to the limited accuracy of our numerics.
+So it seems to appear as a singularity at $2\Delta$ for small values of $V$.
+\red{Stimmst Du dieser Darstellung zu?} \blue{Ja.}
+
+In the AFM phase, the spectral functions $\spectral{l.AMF}$ and $\spectral{t.AFM}$ are distinct.
+While the longitudinal magnon continues to manifest as a peak at relatively high energies
+the transversal magnon appears as a peak at zero energy within our numerical accuracy. Due to
+the asymmetry of the spectral, its peak is the derivative of a $\delta$ function.
+It is an advantageous feature of the adopted approach that the Goldstone theorem is 
+automatically fulfilled. Both, phase mode and transversal magnon are located at zero energy
+if the corresponding symmetry is broken, i.e., the U(1) symmetry and the $O(3)$ symmetry,
+respectively. \blue{Mathmode?}
+
+\red{Haben wir jetzt alle wesentlichen Beobachtungen erwaehnt?} \blue{Ja.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Future directions of research comprise incorporating the investigation of possible phase-separated states. 
+This would enable us to delve deeper into the negative $V$ regime 
+of the phase diagrams and to analyze its collective excitations. Anticipating the occurrence
+of regions of high and low density of electrons, a necessary prerequisite is to investigate doped systems.
+
+Another intriguing extension is to extend the study from the $\Gamma$ point to the full Brillouin zone.
+This implies studying the same phases with operators at finite wave vectors beyond the nesting vector. 
+Conceptually, this extension is straightforward. But it spoils the efficient approach
+to discretize the $\gamma$ space since the dependence on two wave vectors will no longer
+allow us to reduce all wave vector dependence to a single dependence on $\gamma$. \blue{Das verwirrt mich.}
+
+Additionally, one can fathom including a coupling of the electronic system to the electromagnetic fields
+so that we no longer study a neutral, but a charged superconducting system. One would expect
+to capture the important shift of the phase mode to finite energies close to the plasma frequency 
+as explained by the Anderson-Higgs mechanism.
+
+Lastly, one could deal with multi-band systems with even richer phase
+diagrams and corresponding collective excitations.
 
@@
 \begin{acknowledgments} 
-    \textcolor{\markEdited}{This research was partially funded by the MERCUR Kooperation.
-    We would like to thank the members of our group for various useful discussions.
-    [Oder hier lieber alle mal beim Namen nennen? Ich hab mich ja mit allen mal unterhalten]
-    [Götz Seibold zu danken klingt meines Erachtens auch sinnig, mit dem hast du ja viel gesprochen.
-    Lido habe ich nicht verwendet.]}
+	This research was partially funded by the MERCUR Kooperation
+		in project KO-2021-0027. We acknowledge very helpful discussions with
+		Anna B\"ohmer, J\"org B\"unemann, Ilya Eremin, G\"otz Seibold, Joachim Stolze, and Zhe Wang
+		as well as with all members of our research group.
 \end{acknowledgments}

### 2024-03-26 paper/main.tex
Paper korrektur

@@
 
-We show that $\mathcal{M}$ is positive semidefinite if the system is in thermal equilibrium.
-For any $\vec{x} \in \mathbb{C}^N$, consider
-\begin{align}
-    \vec{x}^\dagger \mM \vec{x} &= \sum_{ij} x_i^* x_j \mM_{ij} \nonumber \\
-        &= \langle \left[ \sum_i x_i^* A_i^\dagger, \left[ H, \sum_j x_j A_j \right] \right]  \rangle \nonumber \\
-        &= \langle [B^\dagger, [H, B]] \rangle\,,\quad B \coloneqq  \sum_j x_j A_j\,.
-\end{align}
-For $\mM$ to be positive semidefinite the expression above must not be negative,
-\textcolor{\markEdited}{which has already been proven in Refs. \cite{Dyson1978,mermin66}.}
+We argue that $\mathcal{M}$ is positive semidefinite if the system is in thermal equilibrium.
+For any $\vec{x} \in \mathbb{C}^N$, we consider
+\bs
+\begin{align}
+    \vec{x}^\dagger \mM \vec{x} &= \sum_{ij} x_i^* x_j \mM_{ij} 
+		\\
+        &= \Big\langle \Big[ \sum_i x_i^* A_i^\dagger, \Big[ H, \sum_j x_j A_j \Big] \Big]  \Big\rangle 
+				\\
+        &= \langle [B^\dagger, [H, B]] \rangle,\quad B \coloneqq  \sum_j x_j A_j.
+\end{align}
+\es
+For $\mM$ to be positive semidefinite the expression above must not be negative.
+Exactly this property has been already proven in Refs.\ \cite{mermin66,Dyson1978}
+as the non-negativity of the double commutator.
 
@@
 
-\begin{figure*}
+\begin{figure*}[htb]
     \centering
     \includegraphics[width=0.98\textwidth]{plots/zero_peaks.pdf}
-    \caption{The upper panel shows a log-log plot of the real part of $\spectral{Phase}$ in the SC phase at $U=-2.5t$ and $V=-0.1t$ as well as a linear fit to it.
-    The lower panel shows the same plot for $\spectral{Higgs}$ in the coexistence phase at $V=0$. The columns show the results for the square and the simple cubic lattice, respectively.
-    The functions behave as $1/\omega^2$ indicating that the peaks in the spectral functions are the derivative of a $\delta$ distribution.}
+    \caption{The upper panel shows a log-log plot of the real part of $\spectral{Phase}$ 
+		in the SC phase at $U=-2.5t$ and $V=-0.1t$ as well as a linear fit to it.
+    The lower panel shows the same plot for $\spectral{Higgs}$ in the coexistence phase at $V=0$. 
+		The columns show the results for the square and the simple cubic lattice, respectively.
+    The functions behave as $1/\omega^2$ indicating that the peaks in the spectral functions are derivatives 
+		of a $\delta$ distribution.}
     \label{fig:zero_peaks}
@@
 
-In this appendix section, we discuss fits to the real and imaginary parts of various Green's functions in the different phases.
-All fits are linear of the type $y = ax + b$ in double logarithmic plots, i.e., $a$ describes the power-law behavior of the functions.
-An example plot of the real part of $\greens{Phase}$ in the SC phase is shown in panel (a) of \autoref{fig:zero_peaks}.
-It behaves as $1/\omega^2$ indicating that the peak we find in the spectral function at $\omega=0$ corresponds to the derivative of a $\delta$ distribution.
-The same results are obtained for the peak in $\spectral{Higgs}$ and $\spectral{CDW}$ in the coexistence phase as well as in $\spectral{t.AFM}$ within the AFM phase.
-
-Continuing, we investigate the divergence at $\omega = 2\Delta$ found in $\spectral{Higgs}$ and $\spectral{CDW}$ at $V=0$. It behaves as $1/\sqrt{\omega}$.
-
-Lastly, all remaining peaks below the two-particle continuum behave identically.
-The real part of each one of them behaves as $1/\omega$ in close vicinity to the peak position.
+Here, we discuss fits to the real parts of various Green's functions in the different phases.
+All fits are linear of the type $y = ax + b$ in double logarithmic plots, i.e., $a$ describes the exponent of
+the power-law behavior of the functions.
+An examplary plot of the real part of $\greens{Phase}$ 
+in the SC phase is shown in panel (a) of Fig.\ \ref{fig:zero_peaks}.
+It behaves like $1/\omega^2$ indicating that the peak 
+at $\omega=0$ is the derivative of a $\delta$ distribution.
+The same kind of result is obtained for the transversal magnon in $\spectral{t.AFM}$ in the AFM phase, 
+as well as in $\spectral{Higgs}$ and $\spectral{CDW}$ in the coexistence phase.
+
+The analogous analysis of the divergence at $\omega = 2\Delta$ 
+found in $\spectral{Higgs}$ and $\spectral{CDW}$ at $V=0$
+reveals the power law  $1/\sqrt{\omega}$.
+
+Lastly, all other peaks below the two-particle continuum behave identically.
+The real part of them behaves like $1/\omega$ in close vicinity to the peak position.
 This indicates that the peaks are $\delta$ distributions.
-The peaks of $\spectral{l.AFM}$ and $\spectral{CDW}$ close the phase transition are identical when swapped, 
-i.e., $\spectral{l.AFM}$ in the CDW phase is the same as $\spectral{CDW}$ in the AFM phase.
-
-\section{Numerical treatment of the iEoM matrices in \hmath $\gamma$-space}
+The peaks of $\spectral{l.AFM}$ and $\spectral{CDW}$ close to the phase transition are identical 
+when swapped, i.e., $\spectral{l.AFM}$ in the CDW phase is the same as $\spectral{CDW}$ in the AFM phase.
+This reflects the SO(4) symmetry of the model. \red{Die Spektralfunktionen sind also komplett identisch, richtig?
+Oder nur so ungefähr?} \blue{Wirklich komplett identisch}
+
+\section{Numerical treatment of the matrix elements in $\gamma$-space}
 \label{sec:numerical_ieom}
 
-We would like to use operators like \eqref{eqn:ieom_basis_operator} to span our operator set.
-However, numerically, it is impossible to matrices with infinite dimensions, requiring us to discretize.
-Additionally, we cannot numerically write down $\delta$ distributions as matrix elements. Therefore, we need some special treatments, which we will describe in this section.
-We discretize the $\gamma$-space equally with each abscissa $\gamma_i$ being spaced by $\Delta \gamma$.
-Then, we define an approximate $\delta$ function
+We want to use operators such as \eqref{eqn:ieom_basis_operator} to span the considered operator set.
+Numerically, however, it is impossible to deal with matrices of infinite dimensions so a discretization is necessary.
+Additionally, we cannot use $\delta$ distributions as matrix elements. 
+Therefore, we also discretize the $\delta$ distribution as follows.
+A mesh of equidistant sampling points is chosen for $\gamma\in[-1,1]$.
+They are midpoints of intervals of length $\Delta \gamma$.
+Then, we define an approximate $\delta$ function by
 \begin{equation}
@@
         \frac{1}{\Delta \gamma} & |\gamma| < \frac{\Delta \gamma}{2} \\ 0 & \text{otherwise}
-    \end{cases}\,.
-\end{equation}
-Computing an integral numerically yields
-\begin{equation}
-    \int f(\tilde{\gamma}) h(\tilde{\gamma} - \gamma_j) \mathrm{d} \tilde{\gamma} \approx \sum_i f(\gamma_i) h(\gamma_i - \gamma_j) \Delta \gamma = f(\gamma_j)\,,
-\end{equation}
-showing that $h(\gamma)$ mimicks the continuous $\delta$ distribution for a discrete description.
-Note, that if one takes the limit $\Delta \gamma \to 0$ the $\delta$ distribution is exactly reproduced.
-
-Numerically, we can compute the matrix elements like this
+    \end{cases}.
+\end{equation}
+Numerical integration amounts up to the finite sum over the sampling points and for the approximate $\delta$ function in particular reads
+\begin{equation}
+    \int_{-1}^1 f(\tilde{\gamma}) h(\tilde{\gamma} - \gamma_j) \mathrm{d} \tilde{\gamma} \approx 
+		\sum_i f(\gamma_i) h(\gamma_i - \gamma_j) \Delta \gamma = f(\gamma_j),
+\end{equation}
+showing that $h(\gamma)$ mimics the continuous $\delta$ distribution on the discrete mesh.
+Note that the limit $\Delta \gamma \to 0$ reproduces the continuous case with the $\delta$ distribution.
+
+We compute the matrix elements as
 \begin{equation}
     \label{eqn:numerical_example}
-    (A_i | A_j) = \frac{1}{N} \sum_{\vk \vl} h(\gamma_i - \hat{\gamma}(\vk)) h(\gamma_j - \hat{\gamma}(\vl)) (A_{\vk} | A_{\vl})\,.
-\end{equation}
-Here, all expressions are finite numbers and do not require further treatment.
-Mutatis mutandis, one obtains a similar expression for $(A_i | [H, A_j])$.
-Additionally, note, that the expressions $(A_{\vk} | A_{\vl})$ and $(A_{\vk} | [H, A_{\vl}])$ can be reduced to sums of terms that are proportional to $\gamma_i$ or $\gamma_j$, respectively.
-Therefore, it is not necessary to implement any sort of momentum space computations.
-For example, consider $A_{\vk} = f_{\vk}^\dagger$, then
-\begin{equation}
-    ( f_{\vk}^\dagger | f_{\vl}^\dagger ) = \delta_{\vk, \vl}\, \langle 1 - n_{\vk \uparrow} - n_{\vk \downarrow} \rangle \eqqcolon \delta_{\vk, \vl}\, \alpha(\vk)
-\end{equation}
-holds. Inserting this into \eqref{eqn:numerical_example} yields
-\begin{equation}
-    (A_i | A_j) = \frac{1}{N} \sum_{\vk} h(\gamma_i - \hat{\gamma}(\vk)) h(\gamma_j - \hat{\gamma}(\vk)) \alpha(\vk)\,.
-\end{equation}
-As stated in the main text, see \eqref{eqn:equal_expecs}, $\alpha(\vk)$ depends only on $\hat{\gamma}(\vk)$, hence we can switch from the momentum sum to a $\gamma$ integration
-\begin{align}
-    (A_i | A_j) &= \int \rho(\gamma) h(\gamma_i - \gamma) h(\gamma_j - \gamma) \alpha(\gamma) \dgamma \nonumber \\
-        &\approx \rho(\gamma_i) h(\gamma_j - \gamma_i) \alpha(\gamma_i) \nonumber \\
-        &= \frac{\delta_{ij}}{\Delta \gamma} \rho(\gamma_i) \alpha(\gamma_i)\,.
-\end{align}
-Since $\Delta \gamma$ is a positive constant factor, it does not impact any of our matrix operations, i.e., we can pull it out to the front of the expressions $\mM \to \tilde{m} (\Delta \gamma)^2$ and $\mN \to \tilde{n} (\Delta \gamma)^2$.
-Then, we can rewrite \eqref{eqn:green_derivation} as
-\begin{equation}
-    G_{AB^\dagger}(z) = - (\Delta \gamma)^2 \vec{b}^\dagger (0) \left[ \tilde{n} \frac{1}{\tilde{m} + z \tilde{n}} \tilde{n} \right] \vec{a}(0)\,.
-\end{equation}
-
-\begin{figure}
+    (A_i | A_j) = \frac{1}{N} \sum_{\vk \vl} h(\gamma_i - \widehat{\gamma}(\vk)) h(\gamma_j - 
+		\widehat{\gamma}(\vl)) (A_{\vk} | A_{\vl}).
+\end{equation}
+Here, all expressions represent finite numbers so that they are suitable for
+numerical treatment. This procedure can also be applied to the matrix elements $(A_i | [H, A_j])$ of the dynamical matrix.
+
+Additionally, we stress that expressions such as $(A_{\vk} | A_{\vl})$ or
+$(A_{\vk} | [H, A_{\vl}])$ can be reduced to sums proportional to $\gamma_i$ or $\gamma_j$, respectively.
+Therefore, it is not necessary to implement any sort of computation in reciprocal space.
+As an example, let us consider $A_{\vk} = f_{\vk}^\dagger$ and 
+\begin{equation}
+    ( f_{\vk}^\dagger | f_{\vl}^\dagger ) = \delta_{\vk, \vl}\, \langle 1 - n_{\vk \uparrow} - n_{\vk \downarrow} \rangle = \alpha(\vk) \delta_{\vk, \vl}  
+\end{equation}
+with $\alpha(\vk)\coloneqq 1 - \langle n_{\vk \uparrow} + n_{\vk \downarrow} \rangle$. 
+Inserting this into Eq.\ \eqref{eqn:numerical_example} yields
+\begin{equation}
+    (A_i | A_j) = \frac{1}{N} \sum_{\vk} \alpha(\vk) h(\gamma_i 
+		- \widehat{\gamma}(\vk)) h(\gamma_j - \widehat{\gamma}(\vk)).
+\end{equation}
+As stated in the main text, see Eq.\ \eqref{eqn:equal_expecs}, $\alpha(\vk)$ depends only on $\widehat{\gamma}(\vk)$, 
+hence we can pass from the wave vector integration to a $\gamma$ integration and eventually to a $\gamma$ sum
+\bs
+\begin{align}
+    (A_i | A_j) &= \int \rho(\gamma) h(\gamma_i - \gamma) h(\gamma_j - \gamma) \alpha(\gamma) \dgamma 
+      \\
+    &\approx \rho(\gamma_i) h(\gamma_j - \gamma_i) \alpha(\gamma_i) 
+			\\
+    &= \frac{\delta_{ij}}{\Delta \gamma} \rho(\gamma_i) \alpha(\gamma_i).
+\end{align}
+\es
+Since $\Delta \gamma$ is a positive constant factor, it does not impact any of our matrix operations, i.e., we can shift it to the front of the expressions $\mM \to \tilde{m} (\Delta \gamma)^2$ 
+and $\mN \to \tilde{n} (\Delta \gamma)^2$.
+This allows us to rewrite \eqref{eqn:green_derivation} as
+\begin{equation}
+    G_{AB^\dagger}(z) = - (\Delta \gamma)^2 \vec{b}^\dagger (0) \left[ \tilde{n} \frac{1}{\tilde{m} + z \tilde{n}} \tilde{n} \right] \vec{a}(0)
+\end{equation}
+for the general operators $A$ and $B$ and the initial conditions
+$A=\sum a_i A_i$ and $B=\sum b_i A_i$. \red{Passt das?}  \blue{Tut es. Wir könnten überlegen hier auch $a_i$ und $a_j$ statt a und b zu verwenden, um dieselbe Notation wie im Haupttext zu nutzen?}
+
+In order to provide an explicit example, 
+let us compute $\greens{Higgs}$ from \eqref{eqn:resolvent_bases}.
+We order our operator set such that the operators $f_\gamma + f_\gamma^{\dagger}$ are the first ones
+in the set. Then, the initial conditions read 
+\begin{equation}
+    a_i = b_i = \begin{cases}
+        1 & 1\le i \le N_\gamma \\
+        0 & \text{otherwise}
+    \end{cases},
+\end{equation}
+where $N_\gamma$ is the number of sampling points.
+For the Green's function, this implies
+\bs
+\begin{align}
+    \green{Higgs} (z) &= -(\Delta \gamma)^2 \sum_{i=1}^{N_\gamma} \sum_{j=1}^{N_\gamma} \left[ \tilde{n} \frac{1}{\tilde{m} + z \tilde{n}} \tilde{n} \right]_{ij} 
+		\\
+        &\approx - \int \dgamma \int \dgamma' \left[ \tilde{n} 
+				\frac{1}{\tilde{m} + z \tilde{n}} \tilde{n} \right](\gamma, \gamma').
+\end{align}
+\es
+The first line is an approximation of the integral in the second line, as each matrix element corresponds to a specific value for $\gamma$.
+
+\section{Influence of the discretization}
+\label{sec:finite_size}
+
+\begin{figure}[htb]
     \centering
     \includegraphics[width=0.48\textwidth]{plots/finite_size.pdf}
-    \caption{Effect of changing the number of discretization points $N_\gamma$ on the absolute position of the peak in $\spectral{Phase}$ for $U=-2.5t$ and $V=-0.1t$.
-    On the simple cubic lattice, the peak already lies properly at $\omega=0$.
-    On the square lattice, its position approaches $0$ with $\sqrt{1/N_\gamma}$.}
+    \caption{\red{Die abbildung muss an beiden Achsen bei 0 beginnen. Der Fit sollte auch bei (0,0) 
+		beginnen. In der Legende sollte statt "`Data square"' einfach "`square lattice"' stehen und
+		entsprechend "`cubic lattice"'.} Effect of the number of  sampling points $N_\gamma$ 
+		on the absolute position of the peak in $\spectral{Phase}$ for $U=-2.5t$ and $V=-0.1t$.
+    On the simple cubic lattice, the peak already is located at $\omega=0$ within numerical accuracy.
+    On the square lattice, its position approaches $0$ following $\sqrt{1/N_\gamma}$.}
     \label{fig:finite_size}
@@
 
-To give a practical example, let us compute $\greens{Higgs}$ from \eqref{eqn:resolvent_bases}.
-We order our operator set such that all $f_\gamma + f_\gamma^{\dagger}$ are upfront. 
-This requires the vector elements $\vec{a}$ and $\vec{b}$ to be
-\begin{equation}
-    a_i = b_i = \begin{cases}
-        1 & i < N_\gamma \\
-        0 & \text{otherwise}
-    \end{cases}\,,
-\end{equation}
-where $N_\gamma$ is the number of discretization points.
-Using this, we can expand the relation for the Green's function
-\begin{align}
-    \greens{Higgs} (z) &= -(\Delta \gamma)^2 \sum_{i=0}^{N_\gamma} \sum_{j=0}^{N_\gamma} \left[ \tilde{n} \frac{1}{\tilde{m} + z \tilde{n}} \tilde{n} \right]_{ij} \nonumber \\
-        &\approx - \int \dgamma \int \dgamma' \left[ \tilde{n} \frac{1}{\tilde{m} + z \tilde{n}} \tilde{n} \right](\gamma, \gamma')\,.
-\end{align}
-The first line is an approximation of the integral in the second line, as each matrix element corresponds to a specific value for $\gamma$.
-
-\section{Dependence of the results on the discretization}
-\label{sec:finite_size}
-
-Most of our data barely depends on the number of discretization points $N_\gamma$ at all.
-However, specifically features that lie at very small energies, e.g., the peak in $\spectral{Phase}$ within the SC phase, can be difficult to properly resolve.
-We show this effect in \autoref{fig:finite_size}.
-Neglecting minor fluctuations, this peak is properly located at $\omega=0$ for the simple cubic lattice.
-On the square lattice, however, it follows a $\sqrt{1/N_\gamma}$ behavior, i.e., also approaching $0$.
+Most of the computed data barely depend on the number of sampling points $N_\gamma$.
+However, specific features at very small energies can be difficult to  resolve properly, e.g., 
+the peak in $\spectral{Phase}$ in the SC phase.
+We illustrate this effect in Fig.\ \ref{fig:finite_size}.
+Neglecting minor numerical scattering, the phase peak is properly located at $\omega=0$ for the simple cubic lattice.
+On the square lattice, however, it follows a $\sqrt{1/N_\gamma}$ behavior, i.e., also approaching $0$,
+but only in the limit $N_\gamma \to \infty$.
 This behavior can be observed for the other peaks at $\omega=0$ as well.
-How far away they are from $0$, or whether they are at all, depends on the spectral function as well as on the system parameters.
+How strong this effect is, i.e., how large the deviation from $0$ is depends on the spectral function
+as well as on the other parameters of the system, in particular its dimension.
 

### 2024-03-26 paper/main.tex
cdw peak evolution

@@
 Furthermore, we found the exciton peak in $\spectral{CDW}$ also at large values of $V$ in the CDW phase, 
-evolving smoothly from the CDW-AFM phase transition. \red{Das kannst Du vllt. noch stichprobenartig pruefen.}
+evolving smoothly from the CDW-AFM phase transition. \red{Das kannst Du vllt. noch stichprobenartig pruefen.} \blue{Tut es.}
 We assume that this peak is always located outside of the two-particle continuum, even for small values of $V$.

### 2024-03-27 paper/main.tex

@@
     we find a collective mode, an exciton, that does not change significantly 
-    and another mode, a longitudinal magnon, that emerges from the two-particle continuum as the system approaches the phase transition to the AFM phase. 
-    \red{Habe ich geaendert - stimmt es so?} \blue{Nicht ganz, das Magnon verschwindet, wenn man weg von der Phasengrenze geht, also zu kleineren U/größeren V. 
-    Umgekehrt in der AFM phase, verschwindet das Exziton, bei dem analogen Prozess, also zu großem U/kleinen V. Des Weiteren sind beide Magnonen außerhalb der AFM Phase identisch.
-    Ist es dann richtig, hier nur von dem longitudinalen zu sprechen?}
-		In the AFM phase, we identify both a longitudinal (amplitude) and a 
-		transversal Goldstone magnon; the latter is located at zero energy.
+    and another mode, a longitudinal magnon, 
+    that emerges from the two-particle continuum as the system approaches the phase transition to the AFM phase. 
+    It becomes identical with the former at the transition.
+		In the AFM phase, their roles are reversed.
+    Additionally, we find a transversal Goldstone magnon located at zero energy.
 \end{abstract}
@@
 exhibiting antiferromagnetism (AFM) \cite{Hirsch85}.
-The order parameters of the previously mentioned SC and CDW phases map to different spin expectation values \cite{zitko15,lieb89}.
-\blue{Den vorigen Satz verstehe ich leider gar nicht: phase = spin operator? Ja, das war ungenau. So ist es vermutlich besser?}
+The order parameters of the SC and CDW phases in the attractive model map to different spin expectation values in the repulsive one \cite{zitko15,lieb89}.
 
@@
 By extension, the corresponding spectral functions of the investigated systems can be computed and 
-we discuss the signatures of collective excitations in the spectral functions. \blue{within these?}
+we discuss the signatures of collective excitations in the spectral functions. 
 The most prominent examples in the SC phase are the well-known phase mode (Anderson-Bogoliubov) and 
@@
 
-If $\check{N}_X$ has a singular part, for instance, due to numerical inaccuracies \blue{Das kann auch völlig analytisch auftreten}, the inverse can be replaced by the Moore-Penrose pseudo-inverse. 
+If $\check{N}_X$ has a singular part, for instance, due to numerical inaccuracies or for particular operators, the inverse can be replaced by the Moore-Penrose pseudo-inverse. 
 A possible way to compute this inverse is to diagonalize 
@@
 so it is highly plausible that they gather in one region of the sample while leaving the remainder essentially empty.
-\red{Was ist in 3D - gibt es da nicht auch negative Eigenwerte usw.? Das solten wir dann hier
-ebenfalls besprechen. Wo wollten wir denn die Diskussion des Tricks von Biermann publizieren?}
+In 3D, we observe negative eigenvalues in $\mM$ for strongly negative interactions as well.
+Thus, we expect that phase separation also occurs on this lattice.
 
@@
 on the left-hand side, it is in the CDW phase (orange shading).
-Qualitatively, the peak in $\spectral{l.AFM}$ behaves like the peak in 
-$\spectral{CDW}$ if the phases are swapped. \red{Ist das exakt oder nur ungefaehr so?} \blue{tatsächlich exakt.}
+Qualitatively, the peak in $\spectral{l.AFM}$ behaves exactly like the peak in 
+$\spectral{CDW}$ if the phases are swapped.
+We attribute this behavior to the simplicity of our model and do not expect this behavior quantitatively generic.
 
@@
 when swapped, i.e., $\spectral{l.AFM}$ in the CDW phase is the same as $\spectral{CDW}$ in the AFM phase.
-This reflects the SO(4) symmetry of the model. \red{Die Spektralfunktionen sind also komplett identisch, richtig?
-Oder nur so ungefähr?} \blue{Wirklich komplett identisch}
+However, we do not believe that this identity is quantitatively generic.
 

### 2024-03-27 paper/main.tex
Paper fertig

@@
 
-\newcommand{\markEdited}{red}
-
 \newcommand{\bs}{\begin{subequations}}
@@
 \begin{equation}
-    \epsilon_0 (\vk) = -2t \sum_{\alpha=1}^D \cos(k_\alpha), \quad k_\alpha \in [-\pi, \pi)\,,
+    \epsilon_0 (\vk) = -2t \sum_{\alpha=1}^D \cos(k_\alpha), \quad k_\alpha \in [-\pi, \pi),
 \end{equation}
@@
     \label{eqn:mf_hamiltonian}
-    H_\text{MF} = \sum_{\vk} \Psi^\dagger (\vk) h(\vk) \Psi (\vk)\,,
+    H_\text{MF} = \sum_{\vk} \Psi^\dagger (\vk) h(\vk) \Psi (\vk),
 \end{equation}
@@
 \begin{equation}
-    \Psi^\dagger (\vk) \coloneqq  \left( c_{\vk\up}^\dagger\,, c_{\kplusQ\up}^\dagger\,, c_{-\vk\down}\,, c_{\kminusQ\down} \right)
+    \Psi^\dagger (\vk) \coloneqq  \left( c_{\vk\up}^\dagger, c_{\kplusQ\up}^\dagger, c_{-\vk\down}, c_{\kminusQ\down} \right)
 \end{equation}
@@
         \Delta_\eta^* & \Delta_\text{SC}^* & - \Delta_+^* & - \epsilon (-\vk - \vQ)
-        \end{pmatrix}\,,
+        \end{pmatrix},
 \end{equation}
@@
     \label{eqn:equal_expecs}
-    \langle \widehat{O}_{\vk} \rangle = \langle \widehat{O}_{\vk'} \rangle \eqqcolon \langle \widehat{O}( \gamma ) \rangle\,,
+    \langle \widehat{O}_{\vk} \rangle = \langle \widehat{O}_{\vk'} \rangle \eqqcolon \langle \widehat{O}( \gamma ) \rangle,
 \end{equation}
@@
 The dimension of these matrices depends on the number of operators in the set $\mathcal{B}$.
+
+In practice, however, generic Hamiltonians do not allow for
+a complete operator set $\mathcal{B}$ to exist because the commutations usually introduce terms which are not 
+yet in $\mathcal{B}$, e.g., because they are of higher order.
+For instance, commuting a bilinear term with a quartic Hamiltonian yields quartic terms. 
+Iterating the commutation yields hexatic ones and so on.
+One can include such additional terms and generically the results will improve the more
+terms are considered in $\mathcal{B}$. In practice, one has to restrict the operators
+to a suitable class of terms, thereby truncating certain terms. Here, we will restrict ourselves
+to bilinear operators to capture the leading effects of collective behavior.
+
+Furthermore, we use the symplectic product as operator product
+\begin{equation}
+\label{eqn:scalar_product}
+    (A | B) \coloneqq  \langle [A^\dagger, B] \rangle,
+\end{equation}
+where the expectation values are taken with respect to the assumed phase of the mean-field Hamiltonian 
+\eqref{eqn:mf_hamiltonian}.
+Note that this is not a proper scalar product since it is not positive semidefinite.
+For example, let us assume that for some operator $A$
+\bs
+\begin{equation}
+(A | A) = \langle [A^\dagger, A] \rangle > 0,
+\end{equation}
+then
+\begin{equation}
+(A^\dagger | A^\dagger) = \langle [A, A^\dagger] \rangle = - (A | A)  < 0.
+\end{equation}
+\es
+This does not pose a serious issue in our calculations but must be kept in mind.
+In particular, it implies that the norm matrix is \emph{not positive} as one might have expected.
+We emphasize, that the dynamical matrix  $\mM$ is computed
+by commuting with the \emph{full} Hubbard Hamiltonian \eqref{eqn:full_hamiltonian} 
+enabling us to capture collective behavior 
+rather than using only the mean-field Hamiltonian \eqref{eqn:mf_hamiltonian}
+which captures the one-particle dynamics, but misses the two-body dynamics.
 
@@
 The phase boundary that we propose here agrees qualitatively well with the one found in the aforementioned reference.
-We expect a similar set of phases to be present on the simple cubic lattice. \red{This is indicated by
-the negative eigenvalues of the corresponding dynamical matrix.
-Stimmt das so, Joshua?} \blue{ja.
-Ich überlege gerade, ob dieser Absatz evtl.
-mehr Sinn nach dem Einführen des symplektischen Produktes hat?}
+We expect a similar set of phases to be present on the simple cubic lattice.
 
@@
 For example, we do not find any negative eigenvalues of $\mM$ in the $U>0$, $V<0$ region despite previous studies indicating $d_{x^2 - y^2}$-wave superconductivity \cite{Micnas88b,Huang13}.
-
-In practice, however, generic Hamiltonians do not allow for
-a complete operator set $\mathcal{B}$ to exist because the commutations usually introduce terms which are not 
-yet in $\mathcal{B}$, e.g., because they are of higher order.
-For instance, commuting a bilinear term with a quartic Hamiltonian yields quartic terms. 
-Iterating the commutation yields hexatic ones and so on.
-One can include such additional terms and generically the results will improve the more
-terms are considered in $\mathcal{B}$. In practice, one has to restrict the operators
-to a suitable class of terms, thereby truncating certain terms. Here, we will restrict ourselves
-to bilinear operators to capture the leading effects of collective behavior.
-
-Furthermore, we use the symplectic product as operator product
-\begin{equation}
-\label{eqn:scalar_product}
-    (A | B) \coloneqq  \langle [A^\dagger, B] \rangle\,,
-\end{equation}
-where the expectation values are taken with respect to the assumed phase of the mean-field Hamiltonian 
-\eqref{eqn:mf_hamiltonian}.
-Note that this is not a proper scalar product since it is not positive semidefinite.
-For example, let us assume that for some operator $A$
-\bs
-\begin{equation}
-(A | A) = \langle [A^\dagger, A] \rangle > 0,
-\end{equation}
-then
-\begin{equation}
-(A^\dagger | A^\dagger) = \langle [A, A^\dagger] \rangle = - (A | A)  < 0.
-\end{equation}
-\es
-This does not pose a serious issue in our calculations but must be kept in mind.
-In particular, it implies that the norm matrix is \emph{not positive} as one might have expected.
-We emphasize, that the dynamical matrix  $\mM$ is computed
-by commuting with the \emph{full} Hubbard Hamiltonian \eqref{eqn:full_hamiltonian} 
-enabling us to capture collective behavior 
-rather than using only the mean-field Hamiltonian \eqref{eqn:mf_hamiltonian}
-which captures the one-particle dynamics, but misses
-the two-body dynamics.
 
@@
 \begin{equation}
-    X_i \coloneqq  A_i + A_i^\dagger\,,\quad P_i \coloneqq  A_i - A_i^\dagger.
+    X_i \coloneqq  A_i + A_i^\dagger,\quad P_i \coloneqq  A_i - A_i^\dagger.
 \end{equation}
@@
         \mathcal{K}_+ & \kappa \\ \kappa^\dagger & \mathcal{K}_-
-    \end{pmatrix}\,,\quad \mN = \begin{pmatrix}
+    \end{pmatrix},\quad \mN = \begin{pmatrix}
         \Lambda_+ & \mathcal{L} \\ \mathcal{L}^\dagger & \Lambda_-
@@
 This condition is fulfilled for all cases investigated in this article because the model displays
-inversion symmetry and time-reversal symmetry \red{or at least the combination of both in the AFM phase}.
+inversion symmetry and time-reversal symmetry or at least the combination of both in the AFM phase.
 
@@
 \begin{equation}
-    G_{AB}^\text{ret} (t) = - \im \langle [A(t), B] \rangle \Theta(t)\,,
+    G_{AB}^\text{ret} (t) = - \im \langle [A(t), B] \rangle \Theta(t),
 \end{equation}
@@
 relation between the Green's functions and the matrices for the operators $A_j$. Eventually, we 
-use the block representation resulting for the operators $X_i$ and $P_i$. \red{Wird das klar?}
+use the block representation resulting for the operators $X_i$ and $P_i$.
 The matrix element $(j,i)$ refers to
@@
 
-To this end, we exploit the matrix structure in \eqref{eqn:xp_set} and assume that all matrix entries are real so that $\kappa_{ij} = \Lambda_{\pm,ij} = 0$ holds. \red{Stimmt das so?}
+To this end, we exploit the matrix structure in \eqref{eqn:xp_set} 
+and assume that all matrix entries are real so that $\kappa_{ij} = \Lambda_{\pm,ij} = 0$ holds.
 Then, with $r_X(z)\coloneqq\mathcal{R}|_{XX}$ denoting the upper left block of a matrix $\mathcal{R}$ which 
@@
 
-If $\check{N}_X$ has a singular part, for instance, due to numerical inaccuracies or for particular operators, the inverse can be replaced by the Moore-Penrose pseudo-inverse. 
+If $\check{N}_X$ has a singular part, for instance, due to numerical inaccuracies or for particular operators, 
+the inverse can be replaced by the Moore-Penrose pseudo-inverse. 
 A possible way to compute this inverse is to diagonalize 
@@
 \begin{equation}
-    \check{N}^{-1} \coloneqq \mathcal{V} \mathcal{D}^{-1} \mathcal{V}^\dagger
-\end{equation}
-with \red{Ich habe das hoch + in ein hoch -1 geaendert, weil mir das "`+"' zu sehr an Transposition erinnerte.}
-\begin{equation}
-    (\mathcal{D}^{-1})_{ij} = \begin{cases}
+    \check{N}^{\mathrm{MP}} \coloneqq \mathcal{V} \mathcal{D}^{\mathrm{MP}} \mathcal{V}^\dagger
+\end{equation}
+with
+\begin{equation}
+    (\mathcal{D}^{\mathrm{MP}})_{ij} = \begin{cases}
         1/\mathcal{D}_{ij} & \mathcal{D}_{ij} \neq 0 \\ 0 & \text{otherwise}
@@
     \begin{align}
-        G_{X_j,X_i}  (z) &= - \left[ \vec{x}_j^\dagger (0) \right]_X \mathcal{L}^\dagger r_X (z) \mathcal{L} \left[ \vec{x}_i(0) \right]_X, 
-				\\
-        G_{P_j,P_i} (z) &= \red{+} \left[ \vec{p}_j^\dagger (0) \right]_P \mathcal{L} r_P (z) \mathcal{L}^\dagger \left[ \vec{p}_i(0) \right]_P\,,
+        G_{X_j,X_i}  (z) &= - \vec{x}_j^\dagger (0) \mathcal{L}^\dagger r_X (z) \mathcal{L} \vec{x}_i(0), 
+				\\
+        G_{P_j,P_i} (z) &= - \vec{p}_j^\dagger (0) \mathcal{L} r_P (z) \mathcal{L}^\dagger \vec{p}_i(0),
     \end{align}
 \end{subequations}
-\blue{Brauchen/wollen wir die $[]_{X/P}$ noch? Und ich bin mir ziemlich sicher, dass das in beiden Fällen ein Minus sein sollte.}
 where the vectors $x_j(0)$ and $x_i(0)$ describe the initial conditions for the operators
@@
 \end{equation}
-\red{@ Joshua: Bitte noch einmal sorgfaeltig alles pruefen, da ich doch einiges angepasst habe.}
 
@@
     \label{eqn:inf_lanczos}
-    a_\infty = \frac{\omega_+ + \omega_-}{2}\text{  and  } b_\infty = \frac{\omega_+ - \omega_-}{4}\,,
+    a_\infty = \frac{\omega_+ + \omega_-}{2}\text{  and  } b_\infty = \frac{\omega_+ - \omega_-}{4},
 \end{equation}
@@
     \includegraphics[width=.98\textwidth]{plots/resolvent_overview_AFM_CDW.pdf}
-    \caption{\red{Die ersten beiden Reihen muessen getauscht werden. Stimmt dann der Text?} 
-    \blue{Ich hab dir offenbar tatsächlich den falschen Plot geschickt... 
-    Das ist der Plot der auf dem Poster ist, hier hatte ich eigentlich einen 4 Zeilen-Plot angedacht.}
-		Same as Fig.\ \ref{fig:resolvent_overview_SC} except that we are focusing 
+    \caption{Same as Fig.\ \ref{fig:resolvent_overview_SC} except that we are focusing 
 		on the AFM-CDW phase transition.
@@
     \includegraphics[width=.98\textwidth]{plots/afm_cdw_peaks_details.pdf}
-    \caption{\red{Muss es im log-Argument nicht $U_0-U$ heissen, um klar zu sein?}  \blue{Wir plotten $U\in(U_0, 4.8t)$, also $U_0 < U$}
-		The upper panels (a) show double logarithmic plots of the positions $\omega_0$ 
+    \caption{The upper panels (a) show double logarithmic plots of the positions $\omega_0$ 
 		of the peak in $\spectral{l.AFM}$ relative to the lower edge of the two-particle continuum $\omega_-$.
@@
 		there is no peak below the two-particle continuum, i.e., for $U> U_0$ a peak occurs.
-		\red{Ja, was gilt? Wann gibt's einen Peak, wann nicht? Bitte konsistent im ganzen Artikel bezeichnen.}
     For the square lattice, we find $U_0 \approx 3.372t$ and for the simple cubic lattice $U_0 \approx 4.479t$.
@@
 App.\ \ref{sec:fit_greens_functions}, we confirm that these peaks are $\delta$ peaks.
-Moving further away from the phase transition, here $U=6.2t$ in panels (c) \blue{and $U=3.4t$ in panels (d)}
-\red{Im Text war (d) benannt, aber das existiert ja nicht.}, 
+Moving further away from the phase transition, here $U=6.2t$ in panels (c) and $U=3.4t$ in panels (d),
 the upper peak merges with the two-particle continuum while the lower one persists.
@@
 Having discussed the dominant peaks, we address their behavior when 
-the system approaches the phase transition \blue{between the SC and CDW phase} at $V=0$ for $U=-2.5t$.
+the system approaches the phase transition between the SC and CDW phase at $V=0$ for $U=-2.5t$.
 First, we investigate the identical peak in $\spectral{Phase}$ and $\spectral{Higgs}$, respectively, in the CDW phase.
@@
 It is noteworthy, that in the AFM phase the peak in $\spectral{l.AFM}$ lies energetically
-lower than the one \red{Welchen meinst Du? CDW oder l.AFM? Uneindeutig ...} in $\spectral{CDW}$. \blue{Der AFM-peak ist in der AFM-phase bei kleinerer Energie als der CDW-peak in der AFM-phase.}
+lower than the one in $\spectral{CDW}$.
 This is reversed if the system is in the CDW phase.
@@
 exciton if the system is in the AFM phase. In the CDW phase, the creation of the CDW exciton is
-energetically cheaper than the creation of a magnon. \red{Habe ich das so richtig dargestellt?} \blue{Ja.}
+energetically cheaper than the creation of a magnon.
 
@@
 At this point, the weight of the merging peak vanishes, see panels (c).
-\blue{This occurs around $U \approx 4.8t + 1.428t$ ($\spectral{CDW}$) and $U \approx 4.8t - 1.428t$ ($\spectral{l.AFM}$) for the square lattice 
-and around $U \approx 4.8t + 0.321t$  ($\spectral{CDW}$) and $U \approx 4.8t - 0.321t$  ($\spectral{l.AFM}$) for the simple cubic lattice.}
-\red{Was willst Du mit dem $\pm$ ausdruecken? Verstehe ich nicht ... Besser etwas ausfuehrlicher trotz
-einer gewissen Redundanz.}
+This occurs around $U \approx 4.8t + 1.428t$ ($\spectral{CDW}$) and $U \approx 4.8t - 1.428t$ ($\spectral{l.AFM}$) for the square lattice 
+and around $U \approx 4.8t + 0.321t$  ($\spectral{CDW}$) and $U \approx 4.8t - 0.321t$  ($\spectral{l.AFM}$) for the simple cubic lattice.
 
@@
 We consider $U$ relative to the value $U_0$ at which the peak in $\spectral{l.AFM}$ ceases to exist.
-\red{Stimmt die Formulierung?} \blue{Ja.}
 This occurs at $U_0 = 3.372t$ on the square lattice and at $U_0 = 4.479t$ on the simple cubic lattice.
@@
 $\omega_0 \propto (U-U_0)^2$ while the weights $W_0$ in panel (b) decrease linearly, i.e., 
-$W_0 \propto (U-U_0)$ \red{Stimmt das Vorzeichen?} \blue{Ja.}. This behavior is generic for the peaks of bound states merging with
-their continua at vanishing binding energy \cite{uhrig96b,uhrig96be,zhito13}. \blue{Das wusste ich tatsächlich nicht.}
+$W_0 \propto (U-U_0)$. This behavior is generic for the peaks of bound states merging with
+their continua at vanishing binding energy \cite{uhrig96b,uhrig96be,zhito13}.
 
@@
 This state is induced by the application of an electron creation and an electron annihilation without effect of its spin content so that we interpret it as an $S=0$ exciton.
-It behaves similarly to the SC-related peak in non-SC phases. \blue{Explizit in der CDW Phase, nicht?}
+It behaves similarly to the SC-related peak in non-SC phases.
 
@@
 quadratically in $\Delta U$ while its weight approaches $0$ linearly with $\Delta U$ where
-$\Delta U$ measures the distance to the interaction \blue{strength?} where the merging takes place.
+$\Delta U$ measures the distance to the interaction where the merging takes place.
 
 Furthermore, we found the exciton peak in $\spectral{CDW}$ also at large values of $V$ in the CDW phase, 
-evolving smoothly from the CDW-AFM phase transition. \red{Das kannst Du vllt. noch stichprobenartig pruefen.} \blue{Tut es.}
+evolving smoothly from the CDW-AFM phase transition. 
 We assume that this peak is always located outside of the two-particle continuum, even for small values of $V$.
@@
 So it seems to appear as a singularity at $2\Delta$ for small values of $V$.
-\red{Stimmst Du dieser Darstellung zu?} \blue{Ja.}
 
@@
 automatically fulfilled. Both, phase mode and transversal magnon are located at zero energy
-if the corresponding symmetry is broken, i.e., the U(1) symmetry and the $O(3)$ symmetry,
-respectively. \blue{Mathmode?}
-
-\red{Haben wir jetzt alle wesentlichen Beobachtungen erwaehnt?} \blue{Ja.}
+if the corresponding symmetry is broken, i.e., the U(1) symmetry and the O(3) symmetry,
+respectively.
 
@@
 to discretize the $\gamma$ space since the dependence on two wave vectors will no longer
-allow us to reduce all wave vector dependence to a single dependence on $\gamma$. \blue{Das verwirrt mich.}
+allow us to reduce all wave vector dependence to a single dependence on $\gamma$.
 
@@
 for the general operators $A$ and $B$ and the initial conditions
-$A=\sum a_i A_i$ and $B=\sum b_i A_i$. \red{Passt das?}  \blue{Tut es. Wir könnten überlegen hier auch $a_i$ und $a_j$ statt a und b zu verwenden, um dieselbe Notation wie im Haupttext zu nutzen?}
+$A=\sum a_i A_i$ and $B=\sum b_i A_i$.
 
@@
     \includegraphics[width=0.48\textwidth]{plots/finite_size.pdf}
-    \caption{\red{Die abbildung muss an beiden Achsen bei 0 beginnen. Der Fit sollte auch bei (0,0) 
-		beginnen. In der Legende sollte statt "`Data square"' einfach "`square lattice"' stehen und
-		entsprechend "`cubic lattice"'.} Effect of the number of  sampling points $N_\gamma$ 
+    \caption{Effect of the number of  sampling points $N_\gamma$ 
 		on the absolute position of the peak in $\spectral{Phase}$ for $U=-2.5t$ and $V=-0.1t$.

### 2024-05-21 paper/main.tex
x
uni

@@
 \end{equation}
-where the coefficients $c_j(t)$ capture the entire time dependence. 
+where the coefficients $a_n(t)$ capture the entire time dependence. 
 Inserting this into the Heisenberg equation of motion and applying a sort of operator scalar product $(A_i|\cdot)$ 
@@
 \begin{equation}
-    \tau_{k} \coloneqq c_{k \uparrow}^\dagger c_{k \downarrow}
+  \tau_k \coloneqq c_{\vec{k}\uparrow}^\dagger c_{\vec{k}+\vec{Q}\downarrow}
 \end{equation}
@@
 
-In the AFM phase, the spectral functions $\spectral{l.AMF}$ and $\spectral{t.AFM}$ are distinct.
+In the AFM phase, the spectral functions $\spectral{l.AFM}$ and $\spectral{t.AFM}$ are distinct.
 While the longitudinal magnon continues to manifest as a peak at relatively high energies
@@
 \begin{equation}
-    ( f_{\vk}^\dagger | f_{\vl}^\dagger ) = \delta_{\vk, \vl}\, \langle 1 - n_{\vk \uparrow} - n_{\vk \downarrow} \rangle = \alpha(\vk) \delta_{\vk, \vl}  
-\end{equation}
-with $\alpha(\vk)\coloneqq 1 - \langle n_{\vk \uparrow} + n_{\vk \downarrow} \rangle$. 
+    ( f_{\vk}^\dagger | f_{\vl}^\dagger ) = \delta_{\vk, \vl}\, \langle 1 - n_{-\vk \uparrow} - n_{\vk \downarrow} \rangle = \alpha(\vk) \delta_{\vk, \vl}  
+\end{equation}
+with $\alpha(\vk)\coloneqq 1 - \langle n_{\vk \uparrow} + n_{-\vk \downarrow} \rangle$. 
 Inserting this into Eq.\ \eqref{eqn:numerical_example} yields
@@
 
-\bibliography{sn-bibliography}
+\bibliography{main}
 %\bibliography{../../A_bibinput/liter10.bib}

### 2024-05-21 cpp/ContinuumSystem/sources/Continuum/ModeHelper.cpp

@@ -64,6 +64,19 @@ namespace Continuum {
 				}
 			}
 		}
+
+		//decltype(K_plus) diff = K_plus - K_plus.adjoint();
+		//for(int i = 0; i < diff.rows();  ++i){
+		//	for(int j = i + 1; j < diff.rows(); ++j){
+		//		if (!is_zero(diff(i, j))){
+		//			std::cout << "i: " << i % DISCRETIZATION << "\t" << i / DISCRETIZATION << "  ||  ";
+		//			std::cout << "j: " << j % DISCRETIZATION << "\t" << j / DISCRETIZATION << std::endl;
+		//		}
+		//	}
+		//}
+		//std::cout << "||K_+||" << (K_plus - K_plus.adjoint()).norm() << std::endl;
+		//std::cout << "||K_-||" << (K_minus - K_minus.adjoint()).norm() << std::endl;
+
 		for (int i = 0; i < K_plus.diagonal().real().size(); ++i) {
 			if (K_plus.diagonal().real()(i) < -PRECISION<c_float>) {
 				std::cout << i << "+: " << K_plus.diagonal().real()(i) << "\n";
@@ -202,7 +215,7 @@ namespace Continuum {
 			return q * q * value;
 			};
 #ifdef approximate_theta
-		if (k >= this->model->u_upper_bound(k)) return 0;
+		if (k > this->model->u_upper_bound(k)) return 0;
 #endif
 		return (term.multiplicity / (2 * M_PI * M_PI)) * this->model->computeCoefficient(term.coefficients.front(), c_float{})
 			* Utility::Numerics::Integration::trapezoidal_rule(integrand, model->u_lower_bound(k), model->u_upper_bound(k), DISCRETIZATION);

### 2024-05-21 cpp/FermionCommute/sources/WickTerm.hpp
uni

@@ -34,6 +34,8 @@ namespace SymbolicOperators {
 		WickTerm() = default;
 		WickTerm(const WickTerm& base, const TemplateResult::SingleResult& result);
 
+		explicit WickTerm(const std::string& expression);
+
 		inline bool includesType(const OperatorType operator_type) const {
 			return std::any_of(this->operators.begin(), this->operators.end(),
 				[operator_type](const WickOperator& op) { return op.type == operator_type; });
